### 2023-11-13 paper_IA.tex
Developped text

% mnras_template.tex 
%
% LaTeX template for creating an MNRAS paper
%
% v3.0 released 14 May 2015
% (version numbers match those of mnras.cls)
%
% Copyright (C) Royal Astronomical Society 2015
% Authors:
% Keith T. Smith (Royal Astronomical Society)

% Change log
%
% v3.0 May 2015
%    Renamed to match the new package name
%    Version number matches mnras.cls
%    A few minor tweaks to wording
% v1.0 September 2013
%    Beta testing only - never publicly released
%    First version: a simple (ish) template for creating an MNRAS paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Basic setup. Most papers should leave these options alone.
%\documentclass[fleqn,usenatbib]{mnras}
\documentclass[useAMS,usenatbib]{mn2e}

% MNRAS is set in Times font. If you don't have this installed (most LaTeX
% installations will be fine) or prefer the old Computer Modern fonts, comment
% out the following line
%\usepackage{newtxtext,newtxmath}
% Depending on your LaTeX fonts installation, you might get better results with one of these:
%\usepackage{mathptmx}
%\usepackage{txfonts}

% Use vector fonts, so it zooms properly in on-screen viewing software
% Don't change these lines unless you know what you are doing
%\usepackage[T1]{fontenc}

% Allow "Thomas van Noord" and "Simon de Laguarde" and alike to be sorted by "N" and "L" etc. in the bibliography.
% Write the name in the bibliography as "\VAN{Noord}{Van}{van} Noord, Thomas"
%\DeclareRobustCommand{\VAN}[3]{#2}
%\let\VANthebibliography\thebibliography
%\def\thebibliography{\DeclareRobustCommand{\VAN}[3]{##3}\VANthebibliography}

%%%%% AUTHORS - PLACE YOUR OWN PACKAGES HERE %%%%%
\input{abbrev}
\input{psfig.sty}

\usepackage{graphicx}
\usepackage{epsfig}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{txfonts}
\usepackage{multirow}
\usepackage{afterpage}
\usepackage{xcolor}
%\usepackage[draft]{hyperref}
%\usepackage{ulem} % allows for strikethrough with \sout{}

%\usepackage[paperheight=10in,paperwidth=8.5in]{geometry}

\setlength{\topmargin}{-0.8in}
\paperheight 11in
\paperwidth 8.5in
%\setlength{\textheight}{9.8in}
%\setlength{\textwidth}{7.3in}
\setlength{\textheight}{9.5in}
\setlength{\textwidth}{7.1in}

\definecolor{mypink1}{rgb}{0.858, 0.188, 0.478}
\definecolor{mygreen1}{rgb}{0.258, 0.788, 0.878}
\definecolor{myorange1}{rgb}{0.5, 0.2, 0.2}
\newcommand{\NM}[1]{\textcolor[RGB]{0,150,0}{#1}}
\newcommand{\RR}[1]{\textcolor{blue}{#1}}
\newcommand{\JHD}[1]{\textcolor{mypink1}{#1}}
\newcommand{\snr}{$\mathcal{S}/\mathcal{N}$ }
\newcommand{\mycomment}[1]{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%% AUTHORS - PLACE YOUR OWN COMMANDS HERE %%%%%

% Please keep new commands to a minimum, and use \newcommand not \def to avoid
% overwriting existing commands. Example:
%\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[Lensing beyond 2pt: accounting for IA]{Intrinsic alignments from projected tidal fields: non-linear  impact on cosmic shear probes}

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[J. Harnois-D\'{e}raps et al.]{Joachim Harnois-D\'{e}raps$^{1}$\thanks{E-mail: joachim.harnois-deraps@ncl.ac.uk} and others
\\
% List of institutions
$^{1}$School of Mathematics, Statistics and Physics, Newcastle University, Herschel Building, NE1 7RU, Newcastle-upon-Tyne, UK\\
}

% These dates will be filled out by the publisher
\date{Accepted XXX. Received YYY; in original form ZZZ}

% Enter the current year, for the copyright statements etc.
\pubyear{2021}

% Don't change these lines
\begin{document}
\label{firstpage}
\pagerange{\pageref{firstpage}--21}
%\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\maketitle

% Abstract of the paper
\begin{abstract}
TBD
\end{abstract}

% Select between one and six entries from the list of approved keywords.
% Don't make up new ones.
\begin{keywords}
Gravitational lensing: weak -- Methods: numerical -- Cosmology: dark matter, dark energy \& large-scale structure of Universe 
\end{keywords}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%% BODY OF PAPER %%%%%%%%%%%%%%%%%%

%----------
\section{Introduction}
\label{sec:intro}
%----------

Cosmology, gravitational lensing, cosmic shear, 2pt, beyond-2pt, simulations for signal and for secondary signal/systematics, IA-infusion, this paper...

 %----------
\section{Cosmic shear}
\label{sec:theory}
%----------

As mentioned in the introduction, cosmic shear can be measured and modelled from a variety of methods, many of which are used in this paper and presented in this section.  
%-------------------------
\subsection{$\gamma$-2PCF}
\label{subsec:wl-th}

%---------------
\begin{figure}
\includegraphics[width=\columnwidth]{graphs/Nz}
\caption{Redshift distribution in our simulations, taken from the Year-1 specifications of the LSST Science Requirement Document \citep{LSST-SRD} {[\it check Y1 vs Y10}].}
\label{fig:Nz}
\end{figure}
%--------------

 Shear two-point correlation functions ($\gamma$-2PCFs hereafter) can be predicted with percent-level precision and are therefore an ideal quantity to validate weak lensing simulations. In the Limber approximation\footnote{See \citet{Kilbinger17} for a comparison between the Limber approximation and the exact calculations.}, the lensing power spectrum $C^{ij}_{\ell}$ is obtained from an integral over the three-dimensional matter power spectrum $P_{\delta}(k,z)$:
  \begin{eqnarray}
C_{\ell}^{ij} = \int_0^{\chi_{\rm H}}  \frac{q^i(\chi) \,q^j(\chi)}{\chi^2} \, P_{\delta}\, \bigg(\frac{\ell+1/2}{\chi},z(\chi)\bigg) \ {\rm d}\chi,
\label{eq:C_ell}
\end{eqnarray}
where $\chi_{\rm H}$ is the co-moving distance to the horizon, $c$ is the speed of light, $H_0$ the Hubble parameter,  and the  lensing kernels $q^{i}$ are given by:
\begin{eqnarray}
q^i(\chi) = \frac{3}{2}\Omega_{\rm m} \, \bigg(\frac{H_0}{c} \bigg)^2 \frac{\chi}{a(\chi)} \int_{\chi}^{\chi_{\rm H}} n^i(\chi')\frac{{\rm d}z}{{\rm d} \chi'}\frac{\chi' - \chi}{\chi'}{\rm d}\chi' \, .
\label{eq:q_lensing}
\end{eqnarray}
In the previous expression, $n^i(z)$ refers to the redshift distribution  in tomographic bin `$i$', while $a(\chi)$ is the scale factor at comoving distance $\chi$ from the observer {[\it might need to define $\Omega_m$ here]}.  
 The matter power spectrum is computed from  {\sc Halofit} \citep{Takahashi2012}, however  other public tools provide $P_{\delta}(k,z)$ predictions, including e.g. {\sc HMcode} \citep{HMCode2020}, the {\sc EuclidEmulator} \citep{EuclidEmulator}, the {\sc BACCO} emulator \citep{BACCOEmulator} or the Mira Titan emulator \citep{miraTitan}. 
 Predictions for the $\gamma$-2PCFs are finally computed from Eq. (\ref{eq:C_ell}) as:
 \begin{eqnarray}
\xi_{\pm}^{ij}(\vartheta) = \frac{1}{2\pi}\int_0^{\infty} C_{\ell}^{ij} \, J_{0/4}(\ell \vartheta) \, \ell \, {\rm d}\ell,
\label{eq:xipm_th}
\end{eqnarray}
where $J_{0/4}(x)$ are Bessel functions of the first kind. In this paper, these calculations are carried out by {\sc pyccl}\footnote{{\sc pyccl}:pypi.org/project/pyccl}  \citep{CCL} {\it or do we use cosmosis in the end?]}.
The $n^i(z)$ are taken from the LSST Science Requirement Document \citep{LSST-SRD} and given by
 \begin{eqnarray}
n(z) = N_0 z^2 {\rm exp} \left[-\left(\frac{z}{z_0}\right)^\alpha \right]\, ,
\label{eq:nz}
\end{eqnarray}
with $(z_0, \alpha) = (0.13, 0.78)$ and $N_0$ normalised to provide a number density of $n_{\rm eff}$ = 3.0 gal arcmin$^{-2}$. This lower than the expected number density for the first data release ($n_{\rm eff}\sim10$ gal arcmin$^{-2}$), but is large enough to validate our methods, and makes the calculation more tractable. The $n(z)$ is further split into five equi-populated tomographic bins, and smoothed with a Gaussian filter of width $\sigma = 0.05(1+z)$ in order to mimic the photometric selection process [{\it confirm with Niko}].  The resulting distributions\footnote{The construction of these tomographic $n(z)$ can be reproduced in {github...CCL\_SRD\_Niko}.} are shown in Figure \ref{fig:Nz}.

The cosmic shear signal can be measured from the ellipticities $\epsilon_{1/2}$ of simulated or observed galaxies, which, in absence of systematics and secondary signals, are unbiased estimators  of the cosmic shear components $\gamma_{1/2}$. The $\gamma$-2PCF are then estimated as:
 \begin{eqnarray}
 \widehat{\xi_{\pm}^{ij}}(\vartheta) = \frac{\sum_{a,b} w_a w_b \left[\epsilon_{a, \rm t}^i\epsilon_{b, \rm t}^j     \pm \epsilon_{a, \times}^i\epsilon_{b, \times}^j    \right]\Delta_{ab}(\vartheta)}{\sum_{a,b} w_a w_b} \, ,
 \label{eq:2PCF_estimator}
  \end{eqnarray}
where the sum is over all pairs of galaxies $a,b$ separated by an angular separation $\vartheta$, taken from tomographic bins $i,j$. The tangential/cross components of their ellipticities are denoted as $\epsilon_{\rm t/\times}$, respectively. 
$\Delta_{ab}(\vartheta)$ is the binning operator, equal to unity if the angular separation between the two galaxies falls within the $\vartheta$-bin, and zero otherwise, and the shape weights $w_{a,b}$ are set to unity. In this paper, we construct lensing catalogues from numerical simulations (described in Sec. \ref{sec:sims}), from which we measure $ \widehat{\xi_{\pm}^{ij}}(\vartheta)$ with {\sc Treecorr} \citep{TreeCorr}. We set therein the {\sc bin\_slop} parameter to 0.05, then compute the correlations in nine logarithmically-spaced angular bins ranging from 0.5 to 475.5 arcmin.

 %-------------------------
\subsection{Beyond-2pt}
\label{subsec:beyond-2pt}

Non-Gaussian statistics, often referred to `beyond-2pt' statistics, have the potential to extract cosmological information stored in the complex phases of the density field, whereas two-point functions such as the $\gamma$-2PCF can only access that encoded in the complex amplitudes. No optimal estimator has been identified to-date as being able to capture `all' information, but the numerous studies presented in the introduction all show a clear gain in constraining power, especially when used in combination with 2pt functions. Some of these take as input the galaxy catalogues directly, while others require instead convergence maps. Therefore, we produce convergence maps from the catalogues by assigning the shear signal onto spherical {\sc Healpix}\footnote{{\sc Healpix}: http://healpix.sf.net}  maps \citep{healpix} with $N_{\rm side}=4096$, then using the standard Kaiser \& Squires inversion technique \citep{KaiserSquires} implemented in {\sc healpy} to reconstruct a convergence maps with the same angular resolution, including a baseline 2.0 arcmin smoothing beam in the inverse transform. Note that this smoothing scales is quite small; some probes are difficult to model in that case, and would instead prefer larger smoothing scales. We take this into account on a case-by-case basis, as described below.

  {\it [Discuss tomography...]}

\subsubsection{Catalogue-based estimators}

We consider the following shear-based estimators:
\begin{enumerate}
\item The squeezed bispectrum, has theoretical model (Anik, can you summarise the measurements and modelling, and provide references?)
\end{enumerate}

\subsubsection{Convergence-based estimators}

\begin{enumerate}
\item Convergence three-point correlation function: (Alejandro, can you summarise the measurements and modelling, and provide references?)
\item Peaks and Minima: local maxima and minima in the {\sc Healpix} convergence maps are counted in bins of signal-to-noise ratios, $\nu$. This is one of the most widely used non-Gaussian lensing statistics as it is simple to measure. Theoretical models have been developed to describe the largest peaks \citep[see][]{Shan18, HSCY1_Peaks_th}, however we report here the results on a much wider range of statistics, which can only be accurately modelled from numerical simulations, as in \citet{HD21, DESY3_Zuercher, HSCY1_Peaks_Sims, HD23}.
\item Lensing PDF, has theoretical model (Cora/Lina, can you summarise the measurements and modelling, and provide references?)
\item Map2 and Map3, has theoretical model  (Laila, can you summarise the measurements and modelling, and provide references?)
\item Minkowski functionals (Nisha, can you summarise the measurements and modelling, and provide references?)
\end{enumerate}

 %-------------------
 \section{Intrinsic alignment models}
 \label{sec:IA_th}
 %-------------------

Galaxies interact with the tidal forces caused by the large-scale structure  they live in, causing their intrinsic shapes to acquire correlated alignments that has nothing to do with the correlations caused by weak lensing. This therefore acts as a secondary signal that contaminates the shape correlation measurements carried out in a cosmic shear analysis. There is no consensus on the actual physical model that describes the IA signal, and even when adopting these, the free parameters they contain are only weakly constrained from the data \citep[see][for reviews]{IA_review1, IA_review2}.  %The most widely used model in the literature is the non-linear alignment model of \citet{NLA}, however it is now recognised that this is an effective model with limited precision, and the community is now progressively shifting towards more complex models. 
In this paper we consider four such IA models that we describe in the following sub-sections. In all cases, our models couple the galaxy intrinsic shapes with the local over-density and projected tidal field , then prescribe an intrinsic ellipticity tensor $\gamma_{ij}^{\rm IA}$, from which observed ellipticities are extracted as:
 \begin{eqnarray}
\epsilon_{1}^{\rm IA} = \gamma_{xx}^{\rm IA} - \gamma_{yy}^{\rm IA} \, , \hspace{1.5cm}\epsilon_{2}^{\rm IA} = 2 \gamma_{xy}^{\rm IA}\, .
\label{eq:tidal_th_deltaNLA}
\end{eqnarray}

\subsection{Non-linear alignment (NLA)}

%The observed ellipticity of a galaxy ${\boldsymbol \epsilon}_{\rm obs} $ is a combination of its intrinsic shape ${\boldsymbol \epsilon}_{\rm int}$ and a cosmic shear signal ${\boldsymbol \gamma}$, the former of which can be further divided in a random component ${\boldsymbol \epsilon}^{\rm ran}$ and an alignment term ${\boldsymbol \epsilon}^{\rm IA}$.
The NLA model of \citet{NLA} is the most widely used IA model in the cosmic shear literature thus far. According to the NLA, IA are caused by a linear coupling between galaxy shapes and the non-linear large-scale tidal field at the galaxy position. In the context of  two-point functions, these intrinsic shapes contribute to an intrinsic-intrinsic ($II$) term and an intrinsic-shear coupling ($GI$) term \citep{Hirata2004}, both secondary signals to the true cosmic shear ($GG$) term, with the latter typically dominating the IA sector in cross-tomographic measurements.  The $II$ and $GI$ terms  can be both computed from the matter power spectrum as: 
 \begin{eqnarray}
P_{II}(k,z) =  \left(\frac{A_{\rm IA}\bar{C_1}\bar{\rho}(z)}{D(z)}\right)^2a^4(z) P_{\delta}(k,z)
\label{eq:Pk_II_th}
\end{eqnarray}
and
 \begin{eqnarray}
P_{GI}(k,z) = - \frac{A_{\rm IA}\bar{C_1}\bar{\rho}(z)}{D(z)}a^2(z) P_{\delta}(k,z) \, ,
\label{eq:Pk_GI_th}
\end{eqnarray}
which can then be past to the Limber integration (Eqs. \ref{eq:C_ell} and \ref{eq:xipm_th}) to compute  the secondary signals $\xi_{\pm}^{II}(\vartheta)$ and $\xi_{\pm}^{GI}(\vartheta)$. 
In the above expression,  $D(z)$ is the linear growth factor, $\bar{\rho}(z)$ is the mean matter density at redshift $z$ and $\bar{C_1}=5\times 10^{-14} M_{\odot}^{-1} h^{-2} {\rm Mpc}^3$ is a constant calibrated in \citet{Brown2002}. 
The strength of the tidal coupling is modulated by the amplitude parameter $A_{\rm IA}$, which is the main NLA parameter constrained by current cosmic shear surveys. Note that this model can be augmented by redshift and luminosity dependences, however we do not use these here.

The NLA intrinsic ellipticities $\epsilon_{1,2}^{\rm NLA}$ are related to tidal field $s_{ij}$ by:
 \begin{eqnarray}
\epsilon_1^{\rm NLA} = - \frac{A_{\rm IA}\bar{C_1}\bar{\rho}(z)}{D(z)} (s_{xx} - s_{yy}) \,\,\,\,,   \epsilon_2^{\rm NLA} = - \frac{2 A_{\rm IA}\bar{C_1}\bar{\rho}(z)}{D(z)} s_{xy}\;,
\label{eq:tidal_th}
\end{eqnarray}
where $s_{ij} = \partial_{ij}\phi$ are the Cartesian components of the tidal tensor of the gravitational potential. Note that the term `non-linear' in the model name can be  misleading, as it refers to the non-linear matter power spectrum $P(k)$ that is used in its calculations; the coupling between the intrinsic galaxy shapes and the tidal field is still linear.   Eq.( \ref{eq:tidal_th}) is used to assign intrinsic ellipticities to galaxies, given maps of the tidal field components $s_{xx}$, $s_{yy}$ and $s_{xy}$ (see Sec. \ref {subsec:IA_infusion}).

\subsection{$\delta$-NLA}
\label{subsec:IA_th_ext}

%[{\it here}]

%As discussed later, the key quantity of interest to cosmic shear analysis is not the tidal tensor itself but its trace-free version, since shape correlations with the density field are subdominant, even though peaks in high density environments are less elliptical on average. Consequently, the model itself has a restricted range of validity: on small scales, higher order couplings to the ellipticity field ${\boldsymbol \epsilon}^{\rm IA}$  become important, however these are neglected in the NLA model. Only the non-linear evolution of the tidal tensor itself is taken into account, since it does fit observations quite well.

%We note that the NLA predicts additional higher-order terms and non-zero $B$-modes \citep{Hirata2004} that we neglect  in this analysis. Also, as shown in \citet{IA_EFT}, the NLA model can be interpreted as the lowest order description of the alignment process of galaxies in the light of an effective field theory description.

The NLA model presented in the last section has been widely used in cosmic data analyses, but it has important known limitations and is therefore bound to fail at describing the IA signal with high precision.
A perturbation theory extension to the NLA has been introduced in \citet{Blazek2015} and  \citet{Blazek2019},  where it is recognised that higher order couplings could be important and should be considered. The first additional term to be included is the over-density weighting term, which is caused by the fact that the intrinsic alignment of galaxies can only be observed at the galaxy positions, which are not distributed randomly on the sky but instead trace the underlying matter density,  `$\delta$', although the exact biasing scheme is not currently know. Accounting for this extra term in theoretical predictions is done with one-loop perturbation theory  \citep{Blazek2019}, and is implemented in {\sc pyccl}. Physically, it corresponds to adding a $\delta$-weight to the NLA predictions at the local galaxy positions, effectively representing the different tracer properties. At the level of numerical simulations, this could be done in principle simply by augmenting the NLA ellipticities with this weight, namely:
 \begin{eqnarray}
\epsilon_{1/2}^{\delta-\rm NLA} = \epsilon_{1/2}^{\rm NLA}\times(1 + b_{\rm TA}\delta) \, ,
\label{eq:tidal_th_deltaNLA}
\end{eqnarray}
where the term $b_{\rm TA}$ corresponds to the (largely unconstrained) biasing relation between these source galaxies and the underlying matter field. In practice, however, we find that this is noisy, and that it is instead preferable to generate mocks catalogues with the biasing scheme directly applied when assigning galaxy positions, after which no weighting is necessary. Nevertheless, Eq. (\ref{eq:tidal_th_deltaNLA}) can be used to modify the value of $b_{\rm TA}$. Indeed, from a mock with a given bias $b_{\rm TA, orig}$, we can rescale the IA contribution to a different $b_{\rm TA, new}$  as:
\begin{eqnarray}
{\boldsymbol \epsilon}^{\rm int}_{b_{\rm TA, new}}  = \frac{(1 + b_{\rm TA, new}\delta)}{(1 + b_{\rm TA, orig}\delta)}{\boldsymbol \epsilon}^{\rm int}_{b_{\rm TA, orig}} \, .
\label{eq:bta_rescale}
\end{eqnarray}

Compared to the NLA, the $\delta$-NLA is a stronger IA model, especially on small scales \citep{Blazek2019}, and seems to be preferred by some hydrodynamical simulations \citep{Hilbert_IA2017}. It is also better motivated from a physical point of view, since we know that the galaxies trace dark matter  and are not randomly distributed in our Universe as the NLA assumes.

%-----------------------------------
\subsection{Tidal Torque (TT)}
\label{subsec:IA_th_TT}

As shown in \citet{Blazek2019}, one-loop perturbative calculations include another term, by which galaxies acquire an intrinsic alignment via a coupling between their angular momentum and the tidal field, which can be re-expressed as a quadratic coupling between the tidal field and the shape. In this tidal torque model (TT), intrinsic ellipticities are given by:
\begin{eqnarray}
\gamma_{ij}^{\rm IA, TT} = C_2 \left[ \sum_{k=x,y,z} s_{ik} s_{kj} -\frac{1}{3} \delta_{ij} s^2 \right] \, ,
\label{eq:tidal_th_TT}
\end{eqnarray}
where 
\begin{eqnarray}
C_2 = \frac{5 A_2 \bar{C_1} \Omega_{\rm m} \rho_{\rm crit}}{D^2(z)} \,  = \left[ \frac{-5 A_2}{A_1 D(z)} \right] C_1.
\end{eqnarray}
Under the approximation that line-of-sight alignments are mostly suppressed from cosmic shear measurement due to the broad lensing kernels, 
we show in  Appendix \ref{app:2d_TT} that the terms inside the square bracket in Eq. (\ref{eq:tidal_th_TT}) leads to:
\begin{eqnarray}
\epsilon_1^{\rm TT} = C_2  \left[ s_{xx}^2 - s_{yy}^2\right] \, , \epsilon_2^{\rm TT} = 2 C_2 s_{xy}\left[s_{xx}+s_{yy}  \right]\, ,
\end{eqnarray}
both quadratic in the tidal field components.

%-----------------------------------
\subsection{$\delta$-TT}
\label{subsec:IA_th_TT}

Following the relation between the NLA and the $\delta$-NLA model, galaxies in the TT model are also assume to be randomly scattered on the sky, which we know to be a bad approximation. Computing the next-order contribution to the TT model involves two-loop perturbation theory calculations that have not been done yet due to the significantly higher complexity of such task. in simulations however, the $\delta$-weighting term is straight-forward to implement, as it involves to simply infuse the TT model onto galaxies that trace the matter field with a non-zero biasing factor. As for the $\delta$-NLA model, the $\delta$-TT ellipticities can  be related to the TT model as:
\begin{eqnarray}
\epsilon_{1/2}^{\delta-\rm TT} = \epsilon_{1/2}^{\rm TT}\times(1 + b_{\rm TA}\delta) \, .
\label{eq:tidal_th_deltaTT}
\end{eqnarray}
 There are currently no theoretical models for $\delta$-TT, which means that predictions from this model are, at the moment, completely simulation-based.

It is worth recalling here that other IA models exist in the literature, and that at this point observations are not precise enough to set strong constraints on them, further motivating our flexible multi-model approach.

%\subsection{Likelihood}
%\label{subsec:likelihood}

%Multi-Gaussian likelihood, analytical Covariance matrix (Gauss + non-Gauss + SSC) from {\sc TJPCov}, Firecrown, sampler, priors.

%---------------------
\section{Simulations}
\label{sec:sims}

%-------------
\subsection{Cosmic shear galaxy catalogues} 
\label{subsec:WL_cats}

The weak lensing simulations developed for this work are based on ray-tracing mass sheets produced from the Outer Rim $N$-body simulation \citep{OuterRim}, which evolved 10,240$^3$ particles in a (5.225 Gpc)$^3$ cosmological volume, assuming a flat $\Lambda$CDM cosmology with $\Omega_{\rm m}$=0.2648, $\Omega_{\rm b}$=0.0448, $h$=0.71, $\sigma_8$ = 0.801, $n_{\rm s}$= 0.963, $w_0$=-1.00. A total of 101 particle snapshots were originally saved, of which we use only those with $z<4.0$. Particles from each dump are assigned to curved mass shells approximately 114 Mpc thick, producing a sequence of 57 {\sc Healpix} maps $\delta(\theta,\phi,\chi_i)$ with {\sc nside} = 8192 and $i=1..57$, filling up a light-cone over an octant up to $z=3$. %More details on this procedure can be found  in \citet{cosmoDC}, where lensing quantities are computed specifically for the generation of the {\sc cosmoDC2}  synthetic sky catalogue.

Ray-tracing is performed in the Born approximation, summing over the mass shells using the $\chi$-integral of Eq. (\ref{eq:C_ell}). A source plane is placed at the high-redshift edge of every mass planes, resulting in a series of convergence  maps  $\kappa(\theta,\phi,\chi_i)$ that are subsequently transformed into shear maps $\gamma_{1/2}(\theta,\phi,\chi_i)$ using the Kaiser-Squires methods \citep{KaiserSquires}, which is implemented via efficient {\sc HealPy alm2map} routines.

We position galaxies in the light cone following exactly our chosen $N(z)$, and interpolate the shear quantities at their location. We follow two distinct algorithm to achieve this:
\begin{enumerate}
\item {\it Random:} galaxies RA and Dec are distributed randomly on the octant, thereby matching this fundamental assumptions in the NLA and TT models. 
\item {\it Linear bias:} galaxies RA and Dec are sampled from the mass sheets smoothed\footnote{We also tried sampling the field with 0.1 and 0.5 $h^{-1}$Mpc but this resulted in noisier results.} over 1.0 $h^{-1}$Mpc (comoving), assuming a linear bias of $b_{\rm TA}$, now matching instead the assumptions of the $\delta$-NLA and $\delta$-TT models. With this method we produce galaxy positions assuming first $b_{\rm TA}=1.0$ (our fiducial case) and also $b_{\rm TA}=2.0$, enhancing the  model flexibility. 
\end{enumerate}

Since source clustering is a higher order effect in cosmic shear, the measured $\xi_{\pm}$ from these three mocks (random, $b_{\rm TA}=1.0$ and $b_{\rm TA}=2.0$) show negligible differences ({\it to quantify and cite}).
In contrast, the impact on the IA contamination is significant and can double the secondary signal in certain circumstances. The main explanation for this is that while clustered sources are uncorrelated with the foreground matter responsible for the lensing signal, the high-density regions they live are also subject to the largest tidal fields.

%----------
\subsection{Projected tidal fields}
\label{subsec:IA_sims}

\begin{figure*}
\caption{Density field and the associated projected tidal field tensors.}
\label{fig:maps}
\end{figure*}

Our infusion method completely relies on couplings between intrinsic galaxy shapes and the local tidal field, hence the first step in our method consist in extracting the tidal field maps $s_{ij}(\theta,\phi,\chi_i)$ from the mass maps $\delta(\theta,\phi,\chi_i)$ that source them. In three dimensions, trace-free tidal tensor $s_{ij}(\boldsymbol x)$ can be obtained from the matter over-density field $\delta(\boldsymbol x)$ as   \citep{Catelan_IA_Tidal}:
\begin{eqnarray}
 \widetilde{s}_{ij} (\boldsymbol k)  = \left[\frac{k_i k_j}{k^2} - \frac{\delta_{ij}}{3}\right]  \widetilde {\delta}(\boldsymbol k) \mathcal{G}(\sigma_{\rm G}) \, ,
 \label{eq:sij}
\end{eqnarray}
where $\mathcal{G}(\sigma_{\rm G})$ is a three-dimensional Gaussian function described by a single (free) parameter $\sigma_{\rm G}$ that  controls the physical scales which are allowed to affect the IA term in our model. 
Tilde symbols  denote Fourier transformed quantities,  the indices $(i,j)$ label the components of the Cartesian wave-vector $\boldsymbol{k}^T = (k_x,k_y,k_z)$, and $k^2 = k_x^2 + k_y^2 + k_z^2$. 
As shown in \citet{Tidalator} for Cartesian coordinates, projected tidal fields  computed from projected mass sheets provide and excellent agreement with the NLA model, which in contrast computes the full tidal fields from the three-dimensional matter density and project along the radial dimension at the end. We promote this transformation to curved-sky in this work, exploiting the  polarisation {\sc alm2map} operations built in {\sc Healpy}. In particular, noting that $Q=s_{xx}-s_{yy}$, $U=s_{xy}$ and $\delta=s_{xx}+s_{yy}$, we compute the curved-sky tidal field tensors ${s}_{ij}({\boldsymbol \theta})$ as:
 \begin{eqnarray}
s_{xx}({\boldsymbol \theta})  =  \left[\frac{ \delta + Q}{2}  - \frac{\delta}{3}\right] \, ,s_{yy}({\boldsymbol \theta})  =  \left[\frac{\delta - Q}{2}  - \frac{\delta}{3}\right] \, , s_{xy}({\boldsymbol \theta}) = U
 \label{eq:sij_2D_sph}
 \end{eqnarray}
where the $U({\boldsymbol \theta})$ and $Q({\boldsymbol \theta})$ maps are smoothed by the Gaussian beam with width $\sigma_{\rm G}$. We suppress large artificial tidal fields at the maps boundary by replicating 8$\times$ the density maps defined on the octant and working on a full sky density $\delta$; we re-apply the octant mask on the tidal field maps after the operation. Note that the value of $\sigma_{\rm G}$ is a free parameter both in the infusion technique described in this paper and in the NLA and TATT models. We therefore explore two cases, $\sigma_{\rm G}=0.1$Mpc and 0.5Mpc, however this may be further optimised in the future.

%are specified within the NLA model. Smoothing amounts to selecting physical scales that do not contribute to the alignment of galaxies, which is still a debatable quantity, but is also introduced for numerical stability. \citet{Blazek2015} argues that 1.0 $h^{-1}$Mpc could be a reasonable fiducial value, being larger then the typical halo size, but recognizes that one-halo terms are also required to better match the observations. In their later work, \citet{Blazek2019} do not include smoothing at all, and neither do the KiDS-1000 nor DES-Y1 analyses based on the NLA model \citep{KiDS1000_Asgari,DESY1_Troxel}. In this work we used a two-dimensional Gaussian filter and calibrated $\sigma_{\rm G}$ empirically to $\sigma_{\rm G}=0.1h^{-1}$Mpc (see Sec. \ref{subsubsec:sigma_G}), however these two choices are arbitrary and could possibly be better optimised in the future; we also explore $\sigma_{\rm G}=0.5h^{-1}$Mpc later on.  We note that the smoothing scale is degenerate with the resolution of the simulation itself, and that one should use caution when smoothing on scales that approach the resolution limits.

%We employ a numerical technique worth mentioning here: the Fourier transforms involved in computing Eq. (\ref{eq:sij_2D}) are computed from the full (projected) periodic boxes of the simulations, then interpolated on the light-cones. We find that tidal field computed directly from the $10\times10$ deg$^2$ light-cones introduces significant large scales features in the tidal field maps, largely caused by  the non-periodic boundary conditions, which our method avoids.
Projected tidal field maps $s_{11}$, $s_{22}$ and $s_{12}$ are constructed that way for each mass sheets; Fig. \ref{fig:maps} shows the  three tidal fields and the mass maps for one of them. We can clearly see the connection between all maps around over-dense regions. {\it (Include a figure of $s_ij$ and $\delta$)}.

{\it [Mention normalisation of the tidal fields by $0.6252 = H_0/114$ = 1/shell-thickness}

%of every light-cones and interpolated at the position of every galaxy. Fig. \ref{fig:tidalator} illustrates this process for a small zoomed-in patch at $z\sim0$, starting from a $\delta_{2D}(\boldsymbol \theta)$ map (upper large panel), computing the tidal field components (middle four panels) and comparing the results with the cosmic shear signal generated by the same mass distribution (bottom two panels). The tidal field maps clearly reproduce the cosmic shear maps, and the minus sign in front of both terms in Eq. (\ref{eq:tidal_th}) causes the IA to undo some of the lensing signal.

\subsection{Infusion of intrinsic alignments}
\label{subsec:IA_infusion}

Having now produced shear catalogues and tidal field maps, we can now use Eq. \ref{eq:tidal_th} to couple linearly the alignment of galaxies with the local tidal field, or Eq. \ref{eq:tidal_th_TT} to use instead a quadratic coupling. These allow us to compute the intrinsic ellipticities ${\boldsymbol \epsilon}^{\rm int}$ for the four IA models described in Sec. \ref{sec:IA_th}, which we combine with the cosmic shear signal ${\boldsymbol g}$ to compute observed ellipticities: 
\begin{eqnarray}
{\boldsymbol \epsilon}^{\rm obs} = \frac{{\boldsymbol \epsilon}^{\rm int} + {\boldsymbol g}}{1 + {\boldsymbol \epsilon}^{\rm int}{\boldsymbol g^*}} \,, {\rm with \, \, } 
{\boldsymbol \epsilon}^{\rm int}  = \frac{{\boldsymbol \epsilon}^{\rm IA} + {\boldsymbol \epsilon}^{\rm ran}}{1 + {\boldsymbol \epsilon}^{\rm IA}{\boldsymbol \epsilon^{\rm ran, *}}}.
\label{eq:eps_obs}
\end{eqnarray}
In the above expressions, the denominators ensures that the combined  ellipticities never exceed unity.
The complex spin-2 reduced shear ${\boldsymbol g} \equiv (\gamma_1 + {\rm i} \gamma_2)/(1+\kappa)$ is computed from the shear  $(\gamma_{1/2}$) and convergence ($\kappa$) maps, interpolated at the galaxy positions and redshifts. The  random orientation term ${\boldsymbol \epsilon}^{\rm ran}$ is drawn from two Gaussians (one per component) with their standard deviations matching the LSST-Y1 forecast, $\sigma_{\epsilon} = 027$. We further constraint  the random ellipticity to satisfy $|{\boldsymbol \epsilon}^{\rm ran}| \le 1.0$. 
%We recall that since our simulated galaxy catalogues trace the dark matter density, our default IA-infusion method  is consistent with the $\delta$-NLA model (see Sec. \ref{subsec:IA_th_ext}). Analytical predictions for the two-point functions are more involved in this case \citep[see][]{Blazek2019} and not yet available on the public {\sc cosmoSIS} release. We therefore validate our methods with the standard NLA first, which we infuse by `correcting' the $\delta$-NLA measurement with Eq. (\ref{eq:tidal_th_deltaNLA}), i.e. by replacing ${\boldsymbol \epsilon}^{\rm IA}$ by ${\boldsymbol \epsilon}^{\rm IA}/(1 + b_{\rm TA} \delta)$ in our simulations. Once again, these are less realistic but better suited for validation of the measured $\gamma$-2PCFs against a theoretical model; after this is established, we use the $\delta-$NLA catalogues as our fiducial infusion model. 
We re-iterate here that the same tidal fields, shear maps and IA coupling equations are used for the NLA and $\delta$-NLA models, and separately for the TT and $\delta$-TT models; these  only differ by the fact that in one case the galaxies are placed at random on the octant, while in the other case they are linearly tracing the dark matter.

Also note that our current IA models make no differentiation between galaxy colours or type, and instead treats the full sample as a single population that has a single, effective, alignment signall \citep[see][for an example with a red/blue split]{DESY1_IA_Samuroff}.

%---------------------
\section{Validation with $\xi_{\pm}$}
\label{sec:validation}

% Requires the booktabs if the memoir class is not being used
\begin{table}
   \centering
   %\topcaption{Table captions are better up top} % requires the topcapt package
   \begin{tabular}{@{} lcr @{}} % Column formatting, @{} suppresses leading/trailing space
      \hline
      \hline
       %\multicolumn{2}{c}{Item} \\
      model   		& ($A_{\rm IA}, b_{\rm TA}, A_2)$ \\
      \hline
      NLA     		& {($\pm$1,0,0) }&  \\
      \multirow{2}{*}{$\delta-$NLA }  	&   {($\pm$1,1,0)}   \\
      							&  {(1,2,0)}   \\
      TT 			&  {(0,0,$\pm$1)} &  \\
      \multirow{2}{*}{$\delta$-TT} 	&  {(0,1,$\pm$1)}   \\
      				&  {(0,2,1)}   \\
      TATT- fiducial	&  { (1,1,1)}  \\
      %TATT-DESY3	&   (-0.7,1,1.9) & \\
      \hline
      \hline

   \end{tabular}
   \caption{IA models infused in this work.}
   \label{table:IAmodels}
\end{table}

%------------------------------
\subsection{NLA model}
\label{subsubsec:sigma_G}

See Fig. \ref{fig:xi_NLA}
%---------------
\begin{figure*}
%\includegraphics[width=\columnwidth]{graphs/frac_xip_IA1_skysim}
\includegraphics[width=\columnwidth]{graphs/frac_xip_IA1_skysim_NLA_srd.jpg}
\includegraphics[width=\columnwidth]{graphs/frac_xim_IA1_skysim_NLA_srd.jpg}
\caption{Ratio between the shear correlation functions with and without IA, assuming the NLA model with $A_{\rm IA}=1.0$ both in the simulations and theory. Measurements shown in green and brown correspond to smoothing scales of 0.1 and 0.5 $h^{-1}$Mpc in the tidal field. There is no shape noise in the simulations, but it is included in the error bars.}
\label{fig:xi_NLA}
\end{figure*}
%---------------

%------------------------------
\subsection{$\delta$-NLA model}
\label{subsec:deltaNLA}

See Fig. \ref{fig:xi_deltaNLA}.

\begin{figure*}
\includegraphics[width=\columnwidth]{graphs/frac_xip_IA1_skysim_deltaNLA_srd}
\includegraphics[width=\columnwidth]{graphs/frac_xim_IA1_skysim_deltaNLA_srd}
\caption{Same as Fig. \ref{fig:xi_NLA}, but for the $\delta$-NLA model with $A_{\rm IA}=1.0$ and $b_{\rm TA}=1.0$, and only for smoothing of 0.5$h^{-1}$Mpc. The dashed black lines show the NLA predictions to better highlight the differences.  }
\label{fig:xi_deltaNLA}
\end{figure*}

\begin{figure}
\includegraphics[width=\columnwidth]{graphs/frac_xip_bta1_rescaled}
\caption{Ratio between the shear correlation functions with and without IA in tomographic bin combination 2-5. The brown and green symbols show measurements from simulations constructed with $b_{\rm TA}$ = 0.0 and 2.0 respectively,  the black solid and dotted lines shown their predictions, while the blue symbols are obtained by rescaling $b_{\rm TA}$ = 1.0 simulations using Eq. \ref{eq:bta_rescale}.  }
\label{fig:xi_deltaNLA_rescaled}
\end{figure}

We verified that it works equally well for $b_{\rm TA}$ = 1.0 and 2.0.

%------------------------------

Using this, we $b_{\rm TA}$-rescale our $b_{\rm TA}=1.0$ mock to $b_{\rm TA}=2.0$ and to $0.0$ mocks. Results are shown in Fig. \ref{fig:xi_deltaNLA_rescaled} for one of the tomographic bin. It works reasonably well, but lower redshift are less accurate due to the increased  shot noise (not shown), hence we do not recommend using this.

%------------------------------
\subsection{TT model}
\label{subsec:TT}

See Fig. \ref{fig:xi_TT}

\begin{figure*}
\includegraphics[width=\columnwidth]{graphs/frac_xip_IA1_skysim_TT_srd.jpg}
\includegraphics[width=\columnwidth]{graphs/frac_xim_IA1_skysim_TT_srd.jpg}
\caption{Same as Fig. \ref{fig:xi_NLA}, but for the TT model with $A_2=1.0$. Here, the dashed black lines show the NLA predictions to better highlight the differences. }
\label{fig:xi_TT}
\end{figure*}

\begin{figure*}
%\includegraphics[width=\columnwidth]{graphs/frac_xip_C2_m1_skysim_deltaTT}
\includegraphics[width=\columnwidth]{graphs/frac_xip_IA1_skysim_deltaTT_srd.jpg}
\includegraphics[width=\columnwidth]{graphs/frac_xim_IA1_skysim_deltaTT_srd.jpg}
\caption{Same as Fig. \ref{fig:xi_deltaNLA}, but comparing the TT and the $\delta$-TT models, with $A_2=1.0$, $b_{\rm TA}$ = 1.0, and only for smoothing of 0.5$h^{-1}$Mpc. }
\label{fig:xi_deltaTT}
\end{figure*}

To match the theory, we need to apply the following calibration: $\epsilon^{\rm IA, TT}(z<0.5) \rightarrow \epsilon^{\rm IA, TT} /2.5$.

%------------------------------
\subsection{$\delta$-TT model}
\label{subsec:TT}

See Fig. \ref{fig:xi_deltaTT}

To match the TT theory, we need to apply the following calibration: $\epsilon^{\rm IA, TT}(z<0.5) \rightarrow \epsilon^{\rm IA, TT} /5.0$, followed by $\epsilon^{\rm IA, TT} \rightarrow \epsilon^{\rm IA, TT}/7.0$.

%\subsection{Validation with full inference}
 %\label{sec:inference}

%priors, firecrown, Takahashi $P(k)$

\section{Higher-order weak lensing statistics}
\label{sec:HOWLS}

... use the mocks from Table \ref{table:IAmodels} to compute derivatives. Show.

%----------
\section{Conclusions}
\label{sec:conclusion}
%----------

\section*{Acknowledgements}

JHD acknowledges support from an STFC Ernest Rutherford Fellowship (project reference ST/S004858/1). Ray-tracing computations were carried on the NERSC [acknowledgments] ... HACC [acknowledgements] ... OuterRim [Acknowledgments]
\\

Some of the results in this paper have been derived using the {\sc healpy} and {\sc HEALPix} packages.
\\
\\
\\
{\footnotesize All authors contributed to the development and writing of this paper. JHD led the analysis.... }

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Data Availability}

%The SLICS numerical simulations can be found at http://slics.roe.ac.uk/, while the cosmo-SLICS can be made available upon request.

%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%

% The best way to enter references is to use BibTeX:

\bibliographystyle{hapj}
\bibliography{IA} % if your bibtex file is called example.bib

% Alternatively you could enter them by hand, like this:
% This method is tedious and prone to error if you have lots of references
%\begin{thebibliography}{99}
%\bibitem[\protect\citeauthoryear{Author}{2012}]{Author2012}
%Author A.~N., 2013, Journal of Improbable Astronomy, 1, 1
%\bibitem[\protect\citeauthoryear{Others}{2013}]{Others2013}
%Others S., 2012, Journal of Interesting Stuff, 17, 198
%\end{thebibliography}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%% APPENDICES %%%%%%%%%%%%%%%%%%%%%

\appendix

\section{Projected Tidal Field}
\label{app:2d_TT}

\JHD{[To reword]} We derive in this Appendix...  
The prescription to assign an intrinsic alignment based on the projected tidal field, described in Eq. (\ref{eq:tidal_th}), involves the combinations $(s_{xx} - s_{yy})$ and $s_{xy}$, which therefore correspond to:
\begin{eqnarray}
 \widetilde{\epsilon}_1^{\rm IA} (\boldsymbol k_{\perp})  &\propto& \left(\frac{k_x^2 - k_y^2}{k^2} \right) \widetilde{\delta}_{\rm 2D}(\boldsymbol k_{\perp})\mathcal{G_{\rm 2D}}(\sigma_{\rm G})  \, ,\nonumber \\
 \widetilde{\epsilon}_2^{\rm IA} (\boldsymbol k_\perp)  &\propto& \left(\frac{k_x k_y}{k^2} \right) \widetilde {\delta}_{\rm 2D}(\boldsymbol k_\perp)\mathcal{G_{\rm 2D}}(\sigma_{\rm G}) 
 %\label{eq:sij}
\end{eqnarray}

Aside from the smoothing kernel, these are the same filters that are used for converting convergence maps to shear maps under the \citet[][KS hereafter]{KaiserSquires} inversion:
 \begin{eqnarray}
 \widetilde{\gamma_1} (\boldsymbol \ell)  = \left(\frac{k_x^2 - k_y^2}{k^2} \right) \widetilde {\kappa}(\boldsymbol \ell) \, , \hspace{1cm} \widetilde{\gamma_2} (\boldsymbol \ell)  = \left(\frac{k_x k_y}{k^2} \right) \widetilde {\kappa}(\boldsymbol \ell)
 %\label{eq:sij}
\end{eqnarray}
meaning that on can linearly combine the mass sheets with the correct coefficients and obtain intrinsic ellipticities from a normal KS inversion.

Projecting out the $z$ components (e.i. $s_{0i}$=$s_{i0}$=0 for all $i$),  the tidal torque terms from Eq. (\ref{eq:tidal_th_TT}) can be expanded as:
 \begin{eqnarray}
\gamma^{\rm TT}_{ij}&=& C_2 \left[\sum_{k=x,y} s_{ik} s_{kj} -\frac{1}{3} \delta_{ij} s^2\right] \\
                                  &=&C_2 \left[ s_{ix}s_{xj}  + s_{iy}s_{yj}  -  \frac{1}{3} \delta_{ij} \left( s_{xx}^2 + s_{yy}^2 +2s_{xy}^2 \right)  \right] \, .
\end{eqnarray}
Specifically, this yields:
 \begin{eqnarray}
\gamma^{\rm TT}_{xx}&=& C_2 \left[\frac{2}{3}s_{xx}^2  -  \frac{1}{3}s_{yy}^2 + \frac{1}{3}s_{xy}^2 \right]\, ,  \nonumber \\
\gamma^{\rm TT}_{yy}&=& C_2 \left[-\frac{1}{3}s_{xx}^2  +  \frac{2}{3}s_{yy}^2 + \frac{1}{3}s_{xy}^2  \right]\, , \\
\gamma^{\rm TT}_{xy}&=& C_2 s_{xy}\left[s_{xx}+s_{yy}  \right]\, . \nonumber                                  
\end{eqnarray}
With the standard ellipticity definitions $\epsilon_1^{\rm TT}\equiv \gamma_{xx}^{\rm TT} - \gamma_{yy}^{\rm TT}$ and $\epsilon_2^{\rm TT}\equiv -2 \gamma_{xy}$, we obtain:
\begin{eqnarray}
\epsilon_1^{\rm TT} = C_2  \left[ s_{xx}^2 - s_{yy}^2\right] \, , \epsilon_2^{\rm TT} = -2 C_2 s_{xy}\left[s_{xx}+s_{yy}  \right]\, .
\end{eqnarray}
In the TATT model, the total intrinsic ellipticity component is therefore given by $\epsilon_{1/2}^{\rm IA} = \epsilon_{1/2}^{\rm TATT} = \epsilon_{1/2}^{\delta{\rm-NLA}} + \epsilon_{1/2}^{\rm TT}$.

% Don't change these lines
\bsp	% typesetting comment
\label{lastpage}
\end{document}

% End of mnras_template.tex

### 2024-02-19 paper_IA.tex
Added first MCMC chains

@@
 We therefore explore two cases, $\sigma_{\rm G}=0.1$Mpc and 0.5Mpc, however this may be further optimised in the future.
+Finally, the full-sky density field is downgraded from $N_{\rm side}=8192$ to $N_{\rm side}=4096$ since the smoothing washed the smallest angular scales.
 
@@
 
-%\subsection{Validation with full inference}
- %\label{sec:inference}
-
-%priors, firecrown, Takahashi $P(k)$
+\subsection{Validation with full inference}
+ \label{sec:inference}
+\begin{figure}
+%\includegraphics[width=\columnwidth]{graphs/triangle_nla_5D.pdf}
+\includegraphics[width=\columnwidth]{graphs/triangle_bta_sweep.pdf}
+\caption{Cosmological inference from the NLA-infused simulations, analysed the extended-NLA model. The cross-hairs represent the truth as fixed in the OuterRim $N$-body simulations \citep{OuterRim}.}
+\label{fig:triangle_nla}
+\end{figure}
+priors, {\sc CosmoSIS}, Takahashi $P(k)$, etc.
 
@@
 
+\begin{figure*}
+\includegraphics[width=\columnwidth]{graphs/xip_sims_vs_th.eps}
+\includegraphics[width=\columnwidth]{graphs/xim_sims_vs_th.eps}
+\caption{Fractional difference on $\xi_\pm$ between the measurements from SkySim5000 and the model predictions.  }
+\label{fig:frac_err_sims_th}
+\end{figure*}
+
 \section{Projected Tidal Field}

### 2024-03-18 paper_IA.tex
Added preliminary HOD results

@@
 
-Cosmology, gravitational lensing, cosmic shear, 2pt, beyond-2pt, simulations for signal and for secondary signal/systematics, IA-infusion, this paper...
+Recent cosmic shear measurements from the Kilo Degree Survey\footnote{KiDS:kids.strw.leidenuniv.nl}, the Dark Energy Survey\footnote{DES:www.darkenergysurvey.org} and the Hyper Suprime Camera Survey\footnote{HSC:www.naoj.org/Projects/HSC} have established weak gravitational lensing as a competitive probe of cosmology \citep[see.
+e.g.,][]{KiDS1000_Asgari, KiDS1000_vdB, KiDS1000_Li, DESY3_Secco, DESY3_Amon, HSCY3_Cl, HSCY3_2PCF}, achieving  percent-level measurements of the structure growth parameter $S_8\equiv\sigma_8\sqrt{\Omega_{\rm m}/0.3}$.
+The parameters $\Omega_{\rm m}$ and $\sigma_8$, which respectively describe the abundance and the fluctuations of the matter density fluctuations  on scales of $8h^{-1}$ Mpc, are highly degenerate in the lensing signal, and additional date (e.g.
+galaxy clustering data) are required to measure the two individually \citep{Heymans, DES3x2pt, HSC3x2}.
+Despite these highly successful achievements, the current precision of cosmic shear cosmology is mainly limited by the large uncertainty in the intrinsic alignment  (IA) of galaxies, a secondary signal that tends to cancel some of the shape correlations produced by lensing \citep[see.
+e.g.
+][for reviews on IA]{Joachim_IA, Kiessling_IA}.
+If unaccounted for, IA can bias by XYZ$\sigma$ the inferred cosmological parameters \citep{BlazekKrause}.
+Furthermore, a wrong IA model can also cause significant damage to the inference, as shown in \citet{DESY3_Secco} in the context of DES-Y3 analysis, or in \citep{Paopiamsap2024} in the context of an LSST-like cosmic shear analysis.
+
+Different physical model have been developed to describe the origin and impact of the IA, including the linear non-linear alignment model \citep[][NLA hereafter]{BridleKing07}, the density-weighted NLA (aka $\delta$-NLA or extended-NLA) and the tidal torque model \citep[][TT hereafter]{Blazek2017}, which respectively assume a linear and quadratic coupling between galaxy ellipticities and the local tidal field.
+The halo model can also describe the IA signal as a function of halo properties such as their mass, concentration and shapes \citep{FortunaIA}.
+A number of observations have sought to place constraints on the parameters from these models \citep[e.g.][]{Singh, Sammuroff, Sammuroff, Christos, Fortuna, Johnston}, which seem to converge towards a strong colour-dependence (red bright galaxies are generally strongly aligned, with hints of a radial dependence), while blue galaxies are consistent with no-alignment.
+The selection effects play a crucial role, making it difficult to generalise these measurements to a different galaxy sample, therefore leaving behind a large uncertainty on the IA parameters.
+
+While most of these methods have been developed to provide prescriptions for modelling IA in lensing  two-point statistics, some have been used to infuse galaxy alignments directly into cosmological simulations, as in \citet{Fluri2019, Tidalator2D, MICE_IA, Borg, Lanzieri}.
+Having access to such IA-infused numerical simulations is crucial for a number of applications, including the possibility to validate theoretical models deep in the non-linear regime (or using non-linear galaxy bias model) \citep{IA_gal_bias}, to predict the impact of IA on non-Gaussian lensing probes  for which no model exists \citep{ZuercherXYZ, Tidalator2D}, to test IA mitigation techniques \citep{IA_selfCalibration}, or to learn about  the connection between large dark matter haloes and IA  \citep{vanAlfen}.
+{\it (Any other important references?)}
+
+This paper addresses several of the above-mentioned applications.
+After reviewing the modelling and measurement of cosmic shear data in Sec.
+\ref{sec:theory},  we describes our new flexible method to infuse different IA models in cosmological simulations (Sec.
+\ref{sec:IA_th}).
+Specifically, we  infuse the NLA model, the $\delta$-NLA  and the TT model on the same underlying lensing simulation.
+In addition, we introduce the $\delta$-TT model (which takes into account the fact that galaxies trace dark matter even in the TT model), then proceed to couple the cosmic tidal fields with galaxies taken from halo occupation distributions (HOD) to investigate the impact of realistic non-linear galaxy bias on the IA signal.
+These new models are both physically motivated and challenging to describe theoretically as they require perturbation expansions beyond the second order.
+The full numerical implementation is described in Sec.
+\ref{sec:sims} and validated against theoretical predictions at the level of  two-point shear correlation functions in Sec.
+\ref{sec:validation}.
+Since our infusion method acts on shear galaxy catalogues and on convergence maps, we are in an ideal position to quantify the impact of multiple IA models on different non-Gaussian statistics, which we report in Sec.
+\ref{sec:HOWLS}, before concluding in Sec.
+\ref{sec:conclusion}.
 
  %----------
-\section{Cosmic shear}
+\section{Cosmic shear statistics}
 \label{sec:theory}
@@
 
-As mentioned in the introduction, cosmic shear can be measured and modelled from a variety of methods, many of which are used in this paper and presented in this section.  
+Cosmic shear data can be analysed by a number of summary statistics, which all have their pros and cons.
+We first review the modelling and measurement methods of shear  two-point functions, then present other complementary cosmic shear statistics in the second part of this section.
 %-------------------------
@@
 \includegraphics[width=\columnwidth]{graphs/Nz}
-\caption{Redshift distribution in our simulations, taken from the Year-1 specifications of the LSST Science Requirement Document \citep{LSST-SRD} {[\it check Y1 vs Y10}].}
+\caption{Redshift distributions in our simulations, either taken from the Year-1 specifications for LSST (solid) or from a matched selection applied to an HOD galaxy catalogue (dashed, see Sec.
+\ref{subsec:HOD}).}
 \label{fig:Nz}
@@
 \end{eqnarray}
-In the previous expression, $n^i(z)$ refers to the redshift distribution  in tomographic bin `$i$', while $a(\chi)$ is the scale factor at comoving distance $\chi$ from the observer {[\it might need to define $\Omega_m$ here]}.
- The matter power spectrum is computed from  {\sc Halofit} \citep{Takahashi2012}, however  other public tools provide $P_{\delta}(k,z)$ predictions, including e.g.
-{\sc HMcode} \citep{HMCode2020}, the {\sc EuclidEmulator} \citep{EuclidEmulator}, the {\sc BACCO} emulator \citep{BACCOEmulator} or the Mira Titan emulator \citep{miraTitan}.
+In the previous expression, $n^i(z)$ refers to the redshift distribution  in tomographic bin `$i$', while $a(\chi)$ is the scale factor at comoving distance $\chi$ from the observer.  
+ The matter power spectrum is computed from  {\sc Halofit} \citep{Takahashi2012} in this work, however  other public tools provide accurate predictions, including e.g.
+{\sc HMcode} \citep{HMCode2020}, the {\sc EuclidEmulator} \citep{EuclidEmulator}, the {\sc Bacco} emulator \citep{BACCOEmulator} or the {\sc MiraTitan} emulator \citep{miraTitan}.
  Predictions for the $\gamma$-2PCFs are finally computed from Eq. (\ref{eq:C_ell}) as:
@@
 where $J_{0/4}(x)$ are Bessel functions of the first kind.
-In this paper, these calculations are carried out by {\sc pyccl}\footnote{{\sc pyccl}:pypi.org/project/pyccl}  \citep{CCL} {\it or do we use cosmosis in the end?]}.
-The $n^i(z)$ are taken from the LSST Science Requirement Document \citep{LSST-SRD} and given by
+In this paper, these calculations are carried out by the {\sc CosmoSIS} cosmological inference package \citep{cosmoSIS}.
+The $n^i(z)$ are taken from the LSST Science Requirement Document \citep{LSST-SRD} and given by:
  \begin{eqnarray}
@@
 This lower than the expected number density for the first data release ($n_{\rm eff}\sim10$ gal arcmin$^{-2}$), but is large enough to validate our methods, and makes the calculation more tractable.
-The $n(z)$ is further split into five equi-populated tomographic bins, and smoothed with a Gaussian filter of width $\sigma = 0.05(1+z)$ in order to mimic the photometric selection process [{\it confirm with Niko}].
-The resulting distributions\footnote{The construction of these tomographic $n(z)$ can be reproduced in {github...CCL\_SRD\_Niko}.} are shown in Figure \ref{fig:Nz}.
+This global $n(z)$ is further split into five equi-populated tomographic bins, and smoothed with a Gaussian filter of width $\sigma = 0.05(1+z)$ to mimic the photometric selection process [{\it confirm with Niko}], shown by the solid lines in Fig.
+\ref{fig:Nz}.
 
-The cosmic shear signal can be measured from the ellipticities $\epsilon_{1/2}$ of simulated or observed galaxies, which, in absence of systematics and secondary signals, are unbiased estimators  of the cosmic shear components $\gamma_{1/2}$.
-The $\gamma$-2PCF are then estimated as:
+The  weak lensing signal is  measured from the ellipticities $\epsilon_{1/2}$ of simulated or observed galaxies, which, in absence of systematics and secondary signals, are unbiased estimators  of the cosmic shear components $\gamma_{1/2}$.
+In particular, the $\gamma$-2PCF are estimated as:
  \begin{eqnarray}
@@
   \end{eqnarray}
-where the sum is over all pairs of galaxies $a,b$ separated by an angular separation $\vartheta$, taken from tomographic bins $i,j$.
+where the sum is over all pairs of galaxies $a,b$ separated by an angular distance $\vartheta$ on the sky, respectively belonging to the tomographic bins $i$ and $j$.
 The tangential/cross components of their ellipticities are denoted as $\epsilon_{\rm t/\times}$, respectively.
-$\Delta_{ab}(\vartheta)$ is the binning operator, equal to unity if the angular separation between the two galaxies falls within the $\vartheta$-bin, and zero otherwise, and the shape weights $w_{a,b}$ are set to unity.
+$\Delta_{ab}(\vartheta)$ is the binning operator, equal to unity if the angular separation between the two galaxies falls within the $\vartheta$-bin, and zero otherwise, while the shape weights $w_{a,b}$ are set to unity.
 In this paper, we construct lensing catalogues from numerical simulations (described in Sec.
 \ref{sec:sims}), from which we measure $ \widehat{\xi_{\pm}^{ij}}(\vartheta)$ with {\sc Treecorr} \citep{TreeCorr}.
-We set therein the {\sc bin\_slop} parameter to 0.05, then compute the correlations in nine logarithmically-spaced angular bins ranging from 0.5 to 475.5 arcmin.
+We set therein the {\sc bin\_slop} parameter to 0.05, then compute the correlations in 20 logarithmically-spaced angular bins with outer edges ranging from 0.5 to 475.5 arcmin.
 
  %-------------------------
-\subsection{Beyond-2pt}
+\subsection{Non-Gaussian lensing statistics}
 \label{subsec:beyond-2pt}
 
-Non-Gaussian statistics, often referred to `beyond-2pt' statistics, have the potential to extract cosmological information stored in the complex phases of the density field, whereas two-point functions such as the $\gamma$-2PCF can only access that encoded in the complex amplitudes.
-No optimal estimator has been identified to-date as being able to capture `all' information, but the numerous studies presented in the introduction all show a clear gain in constraining power, especially when used in combination with 2pt functions.
-Some of these take as input the galaxy catalogues directly, while others require instead convergence maps.
-Therefore, we produce convergence maps from the catalogues by assigning the shear signal onto spherical {\sc Healpix}\footnote{{\sc Healpix}: http://healpix.sf.net}  maps \citep{healpix} with $N_{\rm side}=4096$, then using the standard Kaiser \& Squires inversion technique \citep{KaiserSquires} implemented in {\sc healpy} to reconstruct a convergence maps with the same angular resolution, including a baseline 2.0 arcmin smoothing beam in the inverse transform.
-Note that this smoothing scales is quite small; some probes are difficult to model in that case, and would instead prefer larger smoothing scales.
-We take this into account on a case-by-case basis, as described below.
+Non-Gaussian statistics have the potential to extract cosmological information stored in the complex phases of the density field, outperforming in that sense the $\gamma$-2PCF that can only access information encoded in the complex amplitudes.
+No optimal estimator has been identified to-date as being able to capture `all' information, but numerous studies all show a clear gain in constraining power, especially when used in combination with two-point functions \citep{HD21, DESY3_Zurcher, HSC_PeaksSims}.
+While some of these act on galaxy catalogues directly, many non-Gaussian statistics are measured on convergence or aperture mass maps, requiring the post-process the galaxy catalogues with a mass-reconstruction algorithm.
+To accommodate a variety of case we therefore provide both galaxy catalogues and convergence maps, the latter being  produced from the galaxies' observed ellipticities with  the standard Kaiser \& Squires inversion technique \citep{KaiserSquires}.
+These are spherical {\sc Healpix}\footnote{{\sc Healpix}: http://healpix.sf.net}  maps \citep{healpix} with $N_{\rm side}=4096$ generated over an octant,  and includes a baseline 2.0 arcmin smoothing beam to suppress numerical noise.
+Note that this smoothing scales is quite small; some probes are difficult to model theoretically in that regime, in which case the modelling needs to be inferred from simulations directly \citep[as in][]{HD21, DESY3_Zuercher, HSCY1_Peaks_sims}.
+We do not discuss statistics based on aperture mass maps in this paper for the sake of conciseness, but all our methods can be applied to those estimators as well.
 
-  {\it [Discuss tomography...]}
+Whereas tomographic $\gamma$-2PCFs data consists of auto-correlation and cross-redshift correlations, some non-Gaussian statistics can learn additional information from analysing catalogues or maps constructed from triplets, quadruplets or quintuplet of redshift bins \citep{Martinet21a}.
+We do not fully exploit this possibility here and consider auto-tomographic bin only, nevertheless all of our methods and findings can be easily generalised to include this.
 
-\subsubsection{Catalogue-based estimators}
+\subsection{Catalogue-based statistics}
 
-We consider the following shear-based estimators:
+A number of higher-order statistics work at the level of shear catalogue,  and here we consider the following:
 \begin{enumerate}
-\item The squeezed bispectrum, has theoretical model (Anik, can you summarise the measurements and modelling, and provide references?)
+\item {\it Three-point correlation functions (or $M_{\rm ap}^3(\vartheta)$)}:  [{\it Lucas/Laila, can you summarise the measurements and modelling, and provide references?}]
+\item {\it Squeezed bispectrum}: [{\it Anik, can you summarise the measurements and modelling, and provide references?}]
 \end{enumerate}
 
-\subsubsection{Convergence-based estimators}
+\subsection{Convergence-based statistics}
 
+We further consider the following convergence map-based statistics:
 \begin{enumerate}
-\item Convergence three-point correlation function: (Alejandro, can you summarise the measurements and modelling, and provide references?)
-\item Peaks and Minima: local maxima and minima in the {\sc Healpix} convergence maps are counted in bins of signal-to-noise ratios, $\nu$.
-This is one of the most widely used non-Gaussian lensing statistics as it is simple to measure.
-Theoretical models have been developed to describe the largest peaks \citep[see][]{Shan18, HSCY1_Peaks_th}, however we report here the results on a much wider range of statistics, which can only be accurately modelled from numerical simulations, as in \citet{HD21, DESY3_Zuercher, HSCY1_Peaks_Sims, HD23}.
-\item Lensing PDF, has theoretical model (Cora/Lina, can you summarise the measurements and modelling, and provide references?)
-\item Map2 and Map3, has theoretical model  (Laila, can you summarise the measurements and modelling, and provide references?)
-\item Minkowski functionals (Nisha, can you summarise the measurements and modelling, and provide references?)
+\item {\it Convergence three-point correlation function}: [{\it Alejandro, can you summarise the measurements and modelling, and provide references?}]
+\item {\it Peaks and Minima}: local maxima and minima in the {\sc Healpix} convergence maps are counted in bins of signal-to-noise ratios, $\nu$, computed from the global level of shape noise in the survey.
+These are amongst the most widely used non-Gaussian lensing statistics, as it is simple to measure yet highly sensitive to non-Gaussian structures.
+Although some theoretical models have been developed to describe the largest peaks \citep[see][]{Shan18, HSCY1_Peaks_th}, we report here the results on a much wider range of statistics, which can only be accurately modelled from numerical simulations.
+\item {\it Lensing PDF}:  [{\it Cora/Lina, can you summarise the measurements and modelling, and provide references?}]
+\item {\it Minkowski functionals}: [{\it Nisha, can you summarise the measurements and modelling, and provide references?}]
 \end{enumerate}
+
+ Each of these statistics probe different physical scales and non-linearities, causing their sensitivities to cosmological and systematics to vary.
+For example, a probe that is performing well at recovering cosmological information might be heavily affected by secondary signals such as IA and therefore deemed not robust.
+Having infused IA mocks at the field-level is therefore critical to answer such questions.
 
@@
 %The most widely used model in the literature is the non-linear alignment model of \citet{NLA}, however it is now recognised that this is an effective model with limited precision, and the community is now progressively shifting towards more complex models.
-In this paper we consider four such IA models that we describe in the following sub-sections.
-In all cases, our models couple the galaxy intrinsic shapes with the local over-density and projected tidal field , then prescribe an intrinsic ellipticity tensor $\gamma_{ij}^{\rm IA}$, from which observed ellipticities are extracted as:
+In this paper we consider two coupling models each applied on three galaxy bias cases, resulting in six different IA models, described in the following sub-sections.
+In all cases, our models couple the galaxy intrinsic shapes with the local over-density and projected tidal field, then prescribes an intrinsic ellipticity tensor $\gamma_{ij}^{\rm IA}$, from which intrinsic  ellipticities are extracted:
  \begin{eqnarray}
@@
 According to the NLA, IA are caused by a linear coupling between galaxy shapes and the non-linear large-scale tidal field at the galaxy position.
-In the context of  two-point functions, these intrinsic shapes contribute to an intrinsic-intrinsic ($II$) term and an intrinsic-shear coupling ($GI$) term \citep{Hirata2004}, both secondary signals to the true cosmic shear ($GG$) term, with the latter typically dominating the IA sector in cross-tomographic measurements.
+The intrinsic ellipticities $\epsilon_{1,2}^{\rm NLA}$ are related to tidal field $s_{ij}$ by:
+ \begin{eqnarray}
+\epsilon_1^{\rm NLA} = - \frac{A_{\rm IA}\bar{C_1}\bar{\rho}(z)}{D(z)} (s_{xx} - s_{yy}) \,\,\,\,,   \epsilon_2^{\rm NLA} = - \frac{2 A_{\rm IA}\bar{C_1}\bar{\rho}(z)}{D(z)} s_{xy}\;,
+\label{eq:tidal_th}
+\end{eqnarray}
+where $s_{ij} = \partial_{ij}\phi$ are the Cartesian components of the tidal tensor of the gravitational potential,  $D(z)$ is the linear growth factor, $\bar{\rho}(z)$ is the mean matter density at redshift $z$ and $\bar{C_1}=5\times 10^{-14} M_{\odot}^{-1} h^{-2} {\rm Mpc}^3$ is a constant calibrated in \citet{Brown2002}.
+The strength of the tidal coupling is modulated by the amplitude parameter $A_{\rm IA}$, which is the main NLA parameter constrained by current cosmic shear surveys.
+Note that this model can be augmented by redshift and luminosity dependences, however we do not use these here.
+Also note that the term `non-linear' in the model name can be  misleading, as it refers to the non-linear matter power spectrum $P(k)$ that is used in its calculations; the coupling between the intrinsic galaxy shapes and the tidal field is still linear and   Eq.( \ref{eq:tidal_th}) is used to assign intrinsic ellipticities to galaxies, given maps of the tidal field components $s_{xx}$, $s_{yy}$ and $s_{xy}$ (presented in  Sec.
+\ref {subsec:IA_infusion}).
+
+In the context of  two-point functions, these intrinsic shapes contribute to an intrinsic-intrinsic ($II$) term and an intrinsic-shear coupling ($GI$) term \citep{Hirata2004}, both secondary signals to the true cosmic shear ($GG$) term, with the $GI$ typically dominating the IA sector in cross-tomographic measurements.
 The $II$ and $GI$ terms  can be both computed from the matter power spectrum as:
@@
 which can then be past to the Limber integration (Eqs. \ref{eq:C_ell} and \ref{eq:xipm_th}) to compute  the secondary signals $\xi_{\pm}^{II}(\vartheta)$ and $\xi_{\pm}^{GI}(\vartheta)$.
-In the above expression,  $D(z)$ is the linear growth factor, $\bar{\rho}(z)$ is the mean matter density at redshift $z$ and $\bar{C_1}=5\times 10^{-14} M_{\odot}^{-1} h^{-2} {\rm Mpc}^3$ is a constant calibrated in \citet{Brown2002}.
-The strength of the tidal coupling is modulated by the amplitude parameter $A_{\rm IA}$, which is the main NLA parameter constrained by current cosmic shear surveys.
-Note that this model can be augmented by redshift and luminosity dependences, however we do not use these here.
-
-The NLA intrinsic ellipticities $\epsilon_{1,2}^{\rm NLA}$ are related to tidal field $s_{ij}$ by:
- \begin{eqnarray}
-\epsilon_1^{\rm NLA} = - \frac{A_{\rm IA}\bar{C_1}\bar{\rho}(z)}{D(z)} (s_{xx} - s_{yy}) \,\,\,\,,   \epsilon_2^{\rm NLA} = - \frac{2 A_{\rm IA}\bar{C_1}\bar{\rho}(z)}{D(z)} s_{xy}\;,
-\label{eq:tidal_th}
-\end{eqnarray}
-where $s_{ij} = \partial_{ij}\phi$ are the Cartesian components of the tidal tensor of the gravitational potential.
-Note that the term `non-linear' in the model name can be  misleading, as it refers to the non-linear matter power spectrum $P(k)$ that is used in its calculations; the coupling between the intrinsic galaxy shapes and the tidal field is still linear.
-Eq.( \ref{eq:tidal_th}) is used to assign intrinsic ellipticities to galaxies, given maps of the tidal field components $s_{xx}$, $s_{yy}$ and $s_{xy}$ (see Sec.
-\ref {subsec:IA_infusion}).
 
@@
 A perturbation theory extension to the NLA has been introduced in \citet{Blazek2015} and  \citet{Blazek2019},  where it is recognised that higher order couplings could be important and should be considered.
-The first additional term to be included is the over-density weighting term, which is caused by the fact that the intrinsic alignment of galaxies can only be observed at the galaxy positions, which are not distributed randomly on the sky but instead trace the underlying matter density,  `$\delta$', although the exact biasing scheme is not currently know.
-Accounting for this extra term in theoretical predictions is done with one-loop perturbation theory  \citep{Blazek2019}, and is implemented in {\sc pyccl}.
-Physically, it corresponds to adding a $\delta$-weight to the NLA predictions at the local galaxy positions, effectively representing the different tracer properties.
+The first additional term to be included is an over-density weighting term, which arises from the fact that  the intrinsic alignment of galaxies can only be observed at the galaxy positions, which are not distributed randomly on the sky but instead trace the underlying matter density.
+Accounting for this extra term in theoretical predictions is done with one-loop perturbation theory  \citep{Blazek2019} by assuming that the over-density  `$\delta$' is linearly traced by the galaxies.
+Physically, it corresponds to adding a $\delta$-weight to the NLA predictions at the local galaxy positions.
 At the level of numerical simulations, this could be done in principle simply by augmenting the NLA ellipticities with this weight, namely:
@@
 \end{eqnarray}
-where the term $b_{\rm TA}$ corresponds to the (largely unconstrained) biasing relation between these source galaxies and the underlying matter field.
-In practice, however, we find that this is noisy, and that it is instead preferable to generate mocks catalogues with the biasing scheme directly applied when assigning galaxy positions, after which no weighting is necessary.
-Nevertheless, Eq.
-(\ref{eq:tidal_th_deltaNLA}) can be used to modify the value of $b_{\rm TA}$.
+where the term $b_{\rm TA}$ corresponds to the (largely unconstrained) biasing relation between the galaxies and the underlying matter field.
+In practice however, we find this method to be noisy, as many galaxies placed at random actually live in regions of negative or small $\delta$.
+It is instead preferable to generate mock catalogues with the linear biasing directly applied when assigning galaxy positions, after which no weighting is necessary.
+Subsequently, Eq.
+(\ref{eq:tidal_th_deltaNLA}) can be used to modify the value of the effective $b_{\rm TA}$ if not wanting to re-populate the light-cone.
 Indeed, from a mock with a given bias $b_{\rm TA, orig}$, we can rescale the IA contribution to a different $b_{\rm TA, new}$  as:
@@
 Compared to the NLA, the $\delta$-NLA is a stronger IA model, especially on small scales \citep{Blazek2019}, and seems to be preferred by some hydrodynamical simulations \citep{Hilbert_IA2017}.
-It is also better motivated from a physical point of view, since we know that the galaxies trace dark matter  and are not randomly distributed in our Universe as the NLA assumes.
+It is also better motivated from a physical point of view, since galaxies are not randomly distributed in our Universe as the NLA assumes.
 
@@
 
-As shown in \citet{Blazek2019}, one-loop perturbative calculations include another term, by which galaxies acquire an intrinsic alignment via a coupling between their angular momentum and the tidal field, which can be re-expressed as a quadratic coupling between the tidal field and the shape.
+As shown in \citet{Blazek2019}, one-loop perturbative calculations include another term, by which galaxies acquire an intrinsic alignment via a coupling between their angular momentum and the tidal field, which can be re-expressed as a quadratic coupling between the tidal field and their shape.
 In this tidal torque model (TT), intrinsic ellipticities are given by:
@@
 \end{eqnarray}
-both quadratic in the tidal field components.
+both quadratic in the tidal field components. In this model, galaxies are also assumed to be randomly distributed on the sky; the $\delta$-weighted term requires third order perturbations.
 
@@
 
-Following the relation between the NLA and the $\delta$-NLA model, galaxies in the TT model are also assume to be randomly scattered on the sky, which we know to be a bad approximation.
-Computing the next-order contribution to the TT model involves two-loop perturbation theory calculations that have not been done yet due to the significantly higher complexity of such task.
-in simulations however, the $\delta$-weighting term is straight-forward to implement, as it involves to simply infuse the TT model onto galaxies that trace the matter field with a non-zero biasing factor.
+%Following the relation between the NLA and the $\delta$-NLA model, galaxies in the TT model are also assume to be randomly scattered on the sky, which we know to be a bad approximation. 
+Computing the next-order contribution to the TT model involves two-loop perturbation theory calculations that have not been carried out  yet due to the significantly complexity of such task.
+In simulations however, the $\delta$-weighting term is straight-forward to implement, as it involves to simply infuse the TT model onto galaxies that trace the matter field with a non-zero biasing factor.
 As for the $\delta$-NLA model, the $\delta$-TT ellipticities can  be related to the TT model as:
 \begin{eqnarray}
-\epsilon_{1/2}^{\delta-\rm TT} = \epsilon_{1/2}^{\rm TT}\times(1 + b_{\rm TA}\delta) \, .
+\epsilon_{1/2}^{\delta-\rm TT} = \epsilon_{1/2}^{\rm TT}\times(1 + b_{\rm TA}\delta) \, ,
 \label{eq:tidal_th_deltaTT}
 \end{eqnarray}
- There are currently no theoretical models for $\delta$-TT, which means that predictions from this model are, at the moment, completely simulation-based.
+however we choose instead here again to use galaxy positions that themselves are linearly biased.
+As there are currently no theoretical models for $\delta$-TT, predictions from this model are, at the moment, completely simulation-based.
 
-It is worth recalling here that other IA models exist in the literature, and that at this point observations are not precise enough to set strong constraints on them, further motivating our flexible multi-model approach.
+ %-----------------------------------
+\subsection{$b_{\rm nl}$-TATT}
+\label{subsec:HOD-TATT}
+
+The previous four models combine the linear and quadratic couplings to the cosmic tidal forces  (Eqs.
+\ref{eq:tidal_th} and \ref{eq:tidal_th_TT} respectively) with galaxies positioned  either at random or linearly tracing the total matter distribution.
+While these are interesting and useful approximations, the connection between galaxies and dark matter is far more complex, and a more accurate picture consists of galaxies populating dark matter haloes, typically with a relaxed, older galaxy close to the centre, and a number of other satellite galaxies orbiting the former.
+This halo occupation distribution (HOD) formalism has been used to describe many galaxy samples \citep[e.g.][]{SDSS-HOD, BOSS-HOD, GAMA-HOD, DESI-HOD} and is therefore routinely used to in-paint galaxies in dark matter-only simulations.
+The last two models from this paper exploit such HOD galaxy samples, extracted from the same underlying distributions, but in this case the galaxy bias is non-linear (labelled $b_{\rm nl}$), with levels on non-linearity that vary with HOD parameters (see Sec.
+\ref{subsec:HOD}).
+We couple these galaxies with both Eqs.
+\ref{eq:tidal_th} and \ref{eq:tidal_th_TT}, resulting in two final models which we name  $b_{\rm nl}$-NLA and  $b_{\rm nl}$-TT, both being combined into the more general  $b_{\rm nl}$-TATT model.
+
+%Finally, it is worth recalling here that other IA models exist in the literature, and that at this point observations are not precise enough to set strong constraints on them, further motivating our flexible multi-model approach.
 
@@
 
-The weak lensing simulations developed for this work are based on ray-tracing mass sheets produced from the Outer Rim $N$-body simulation \citep{OuterRim}, which evolved 10,240$^3$ particles in a (5.225 Gpc)$^3$ cosmological volume, assuming a flat $\Lambda$CDM cosmology with $\Omega_{\rm m}$=0.2648, $\Omega_{\rm b}$=0.0448, $h$=0.71, $\sigma_8$ = 0.801, $n_{\rm s}$= 0.963, $w_0$=-1.00.
+The weak lensing simulations developed for this work are based on ray-tracing mass sheets produced from the {\it Outer Rim} $N$-body simulation \citep{OuterRim}, which evolved 10,240$^3$ particles in a (5.225 Gpc)$^3$ cosmological volume, assuming a flat $\Lambda$CDM cosmology with $\Omega_{\rm m}$=0.2648, $\Omega_{\rm b}$=0.0448, $h$=0.71, $\sigma_8$ = 0.801, $n_{\rm s}$= 0.963, $w_0$=-1.00.
 A total of 101 particle snapshots were originally saved, of which we use only those with $z<4.0$.
@@
 A source plane is placed at the high-redshift edge of every mass planes, resulting in a series of convergence  maps  $\kappa(\theta,\phi,\chi_i)$ that are subsequently transformed into shear maps $\gamma_{1/2}(\theta,\phi,\chi_i)$ using the Kaiser-Squires methods \citep{KaiserSquires}, which is implemented via efficient {\sc HealPy alm2map} routines.
-
-We position galaxies in the light cone following exactly our chosen $N(z)$, and interpolate the shear quantities at their location. We follow two distinct algorithm to achieve this:
+We finally position galaxies in the light cone following three distinct algorithm, each impacting the strength of the IA signal:
 \begin{enumerate}
-\item {\it Random:} galaxies RA and Dec are distributed randomly on the octant, thereby matching this fundamental assumptions in the NLA and TT models. 
-\item {\it Linear bias:} galaxies RA and Dec are sampled from the mass sheets smoothed\footnote{We also tried sampling the field with 0.1 and 0.5 $h^{-1}$Mpc but this resulted in noisier results.} over 1.0 $h^{-1}$Mpc (comoving), assuming a linear bias of $b_{\rm TA}$, now matching instead the assumptions of the $\delta$-NLA and $\delta$-TT models.
-With this method we produce galaxy positions assuming first $b_{\rm TA}=1.0$ (our fiducial case) and also $b_{\rm TA}=2.0$, enhancing the  model flexibility.
+\item {\it Random:} galaxies are distributed randomly on the octant, thereby reproducing one of the  fundamental assumptions in the NLA and TT models. 
+\item {\it Linear bias:} galaxy positons are sampled from the mass sheets smoothed\footnote{We also tried sampling the field with 0.1 and 0.5 $h^{-1}$Mpc but this resulted in noisier results.} with a  1.0 $h^{-1}$Mpc (comoving) beam, assuming a linear bias of $b_{\rm TA}$, thereby building the one of the key assumptions of the $\delta$-NLA and $\delta$-TT models.
+We assume $b_{\rm TA}=1.0$ as our fiducial case but also consider $b_{\rm TA}=2.0$ to test  the  model flexibility.
+\item{\it Non-linear bias:} galaxy positions are obtained by populating dark matter haloes with the Halo Occupation Distribution prescription described in \citet{cosmoDC2}. 
 \end{enumerate}
-
-Since source clustering is a higher order effect in cosmic shear, the measured $\xi_{\pm}$ from these three mocks (random, $b_{\rm TA}=1.0$ and $b_{\rm TA}=2.0$) show negligible differences ({\it to quantify and cite}).
-In contrast, the impact on the IA contamination is significant and can double the secondary signal in certain circumstances.
-The main explanation for this is that while clustered sources are uncorrelated with the foreground matter responsible for the lensing signal, the high-density regions they live are also subject to the largest tidal fields.
+Note that while cases (i) and (ii) exactly the SRD-Y1 $N(z)$ presented in Fig.
+\ref{fig:Nz} (solid lines), the $N(z)$ in the latter case is not a perfect match (dashed lines); we return to this in Sec.
+\ref{subsec:HOD}, where we describe the HOD model and related quantities.
 
@@
 Also note that our current IA models make no differentiation between galaxy colours or type, and instead treats the full sample as a single population that has a single, effective, alignment signall \citep[see][for an example with a red/blue split]{DESY1_IA_Samuroff}.
+
+Finally, once all galaxies have been placed in the light-cone, we interpolate the shear and IA quantities at their exact location.
 
@@
 
+%------------------------------
+\subsection{HOD-NLA model}
+\label{subsec:HOD}
+
+%--------------
+\begin{figure*}
+%\includegraphics[width=\columnwidth]{graphs/frac_xip_C2_m1_skysim_deltaTT}
+\includegraphics[width=\columnwidth]{graphs/frac_xip_sims_HOD.jpg}
+\includegraphics[width=\columnwidth]{graphs/frac_xim_sims_HOD.jpg}
+\caption{Same as Fig. \ref{fig:xi_deltaNLA}, but showing the HOD galaxies with shapes linearly coupled with the tidal field. }
+\label{fig:xi_HOD}
+\end{figure*}
+
+%--------------
+\begin{figure*}
+%\includegraphics[width=\columnwidth]{graphs/frac_xip_C2_m1_skysim_deltaTT}
+\includegraphics[width=\columnwidth]{graphs/frac_xip_sims_HOD_TT.jpg}
+\includegraphics[width=\columnwidth]{graphs/frac_xim_sims_HOD_TT.jpg}
+\caption{Same as Fig. \ref{fig:xi_deltaTT}, but showing the HOD galaxies with shapes quadratically coupled with the tidal field. }
+\label{fig:xi_HOD}
+\end{figure*}
+
+The NLA and extended-NLA models respectively assume a null and a linear bias between the source galaxies and the underlying matter field, both of which are approximations to the galaxy dark matter connection.
+In fact, galaxies populate dark matter over-densities in a more complex manner \citep{GalaxyPopulationPapers}, which is better described by the Halo Occupation Distribution approach (HOD hereafter).
+The largest difference here is that these HOD galaxies are non-linear biased tracers of the matter distribution, which means that a larger number can populate regions of large over-densities, where the tidal fields are generally stronger.
+We therefore expect the impact of IA to be stronger in this case.
+
+We investigate this effect with HOD galaxies extracted from the  SkySim5000 simulation \citep{SkySim5000_HOD} \footnote{We used version: {\tt skysim5000\_v1.2}, as detailed in XYZ..}, which are obtained by [...] (mention the TXPipe paper).
+Specifically, we select objects over a patch of 732.20 des$^2$ given by  0$<$RA$<$ 20 and -36.61$<$Dec$<$0, we apply a magnitude cut of mag$_r<$24.8, and further downsample randomly to retain 20\% of the galaxies,
+therefore matching the global galaxy redshift distribution and number density found in the rest of this paper (Eq.
+\ref{eq:nz}).
+The sample is further split into five tomographic bins by using Charlie's magical code (Charlie), resulting in the $n(z)$ presented in Fig.
+\ref{fig:NzHOD}.
+Compared to the analytical SRD-Y1 presented in Fig.
+\ref{fig:Nz}, the mean redshifts of the five tomographic bins are shifted by [-0.027, -0.018,  0.003, -0.010,  0.038], respectively.
+
+[{\it To put somewhere?: Since source clustering is a higher order effect in cosmic shear, the measured $\xi_{\pm}$ from these three mocks (random, $b_{\rm TA}=1.0$ and $b_{\rm TA}=2.0$) show negligible differences ({\it to quantify and cite}).
+In contrast, the impact on the IA contamination is significant and can double the secondary signal in certain circumstances.
+The main explanation for this is that while clustered sources are uncorrelated with the foreground matter responsible for the lensing signal, the high-density regions they live are also subject to the largest tidal fields.
+}]
+
 \subsection{Validation with full inference}
@@
 \includegraphics[width=\columnwidth]{graphs/triangle_bta_sweep.pdf}
-\caption{Cosmological inference from the NLA-infused simulations, analysed the extended-NLA model. The cross-hairs represent the truth as fixed in the OuterRim $N$-body simulations \citep{OuterRim}.}
+\caption{Cosmological inference from the NLA-infused simulations, analysed the extended-NLA model.
+The cross-hairs represent the truth as fixed in the {\it Outer Rim} $N$-body simulations \citep{OuterRim}.}
 \label{fig:triangle_nla}
@@
 HACC [acknowledgements] ...
-OuterRim [Acknowledgments]
+{\it Outer Rim}[Acknowledgments]
 \\
@@
 %The SLICS numerical simulations can be found at http://slics.roe.ac.uk/, while the cosmo-SLICS can be made available upon request.
+The construction of our tomographic $n^i(z)$ can be reproduced in {\tt github...CCL\_SRD\_Niko}.
 

### 2024-03-27 figures/shear_corr_funcs/xi_nla.tex
Changes made by Niko

--- 2023-11-13 paper_IA.tex
@@
-% mnras_template.tex 
-%
-% LaTeX template for creating an MNRAS paper
-%
-% v3.0 released 14 May 2015
-% (version numbers match those of mnras.cls)
-%
-% Copyright (C) Royal Astronomical Society 2015
-% Authors:
-% Keith T. Smith (Royal Astronomical Society)
-
-% Change log
-%
-% v3.0 May 2015
-%    Renamed to match the new package name
-%    Version number matches mnras.cls
-%    A few minor tweaks to wording
-% v1.0 September 2013
-%    Beta testing only - never publicly released
-%    First version: a simple (ish) template for creating an MNRAS paper
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Basic setup. Most papers should leave these options alone.
-%\documentclass[fleqn,usenatbib]{mnras}
-\documentclass[useAMS,usenatbib]{mn2e}
-
-% MNRAS is set in Times font. If you don't have this installed (most LaTeX
-% installations will be fine) or prefer the old Computer Modern fonts, comment
-% out the following line
-%\usepackage{newtxtext,newtxmath}
-% Depending on your LaTeX fonts installation, you might get better results with one of these:
-%\usepackage{mathptmx}
-%\usepackage{txfonts}
-
-% Use vector fonts, so it zooms properly in on-screen viewing software
-% Don't change these lines unless you know what you are doing
-%\usepackage[T1]{fontenc}
-
-% Allow "Thomas van Noord" and "Simon de Laguarde" and alike to be sorted by "N" and "L" etc. in the bibliography.
-% Write the name in the bibliography as "\VAN{Noord}{Van}{van} Noord, Thomas"
-%\DeclareRobustCommand{\VAN}[3]{#2}
-%\let\VANthebibliography\thebibliography
-%\def\thebibliography{\DeclareRobustCommand{\VAN}[3]{##3}\VANthebibliography}
-
-%%%%% AUTHORS - PLACE YOUR OWN PACKAGES HERE %%%%%
-\input{abbrev}
-\input{psfig.sty}
-
-\usepackage{graphicx}
-\usepackage{epsfig}
-\usepackage{amssymb}
-\usepackage{amsmath}
-\usepackage{amsfonts}
-\usepackage{txfonts}
-\usepackage{multirow}
-\usepackage{afterpage}
-\usepackage{xcolor}
-%\usepackage[draft]{hyperref}
-%\usepackage{ulem} % allows for strikethrough with \sout{}
-
-%\usepackage[paperheight=10in,paperwidth=8.5in]{geometry}
-
-\setlength{\topmargin}{-0.8in}
-\paperheight 11in
-\paperwidth 8.5in
-%\setlength{\textheight}{9.8in}
-%\setlength{\textwidth}{7.3in}
-\setlength{\textheight}{9.5in}
-\setlength{\textwidth}{7.1in}
-
-\definecolor{mypink1}{rgb}{0.858, 0.188, 0.478}
-\definecolor{mygreen1}{rgb}{0.258, 0.788, 0.878}
-\definecolor{myorange1}{rgb}{0.5, 0.2, 0.2}
-\newcommand{\NM}[1]{\textcolor[RGB]{0,150,0}{#1}}
-\newcommand{\RR}[1]{\textcolor{blue}{#1}}
-\newcommand{\JHD}[1]{\textcolor{mypink1}{#1}}
-\newcommand{\snr}{$\mathcal{S}/\mathcal{N}$ }
-\newcommand{\mycomment}[1]{}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%% AUTHORS - PLACE YOUR OWN COMMANDS HERE %%%%%
-
-% Please keep new commands to a minimum, and use \newcommand not \def to avoid
-% overwriting existing commands. Example:
-%\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%
-
-% Title of the paper, and the short title which is used in the headers.
-% Keep the title short and informative.
-\title[Lensing beyond 2pt: accounting for IA]{Intrinsic alignments from projected tidal fields: non-linear  impact on cosmic shear probes}
-
-% The list of authors, and the short list which is used in the headers.
-% If you need two or more lines of authors, add an extra line using \newauthor
-\author[J. Harnois-D\'{e}raps et al.]{Joachim Harnois-D\'{e}raps$^{1}$\thanks{E-mail: joachim.harnois-deraps@ncl.ac.uk} and others
-\\
-% List of institutions
-$^{1}$School of Mathematics, Statistics and Physics, Newcastle University, Herschel Building, NE1 7RU, Newcastle-upon-Tyne, UK\\
-}
-
-% These dates will be filled out by the publisher
-\date{Accepted XXX. Received YYY; in original form ZZZ}
-
-% Enter the current year, for the copyright statements etc.
-\pubyear{2021}
-
-% Don't change these lines
-\begin{document}
-\label{firstpage}
-\pagerange{\pageref{firstpage}--21}
-%\pagerange{\pageref{firstpage}--\pageref{lastpage}}
-\maketitle
-
-% Abstract of the paper
-\begin{abstract}
-TBD
-\end{abstract}
-
-% Select between one and six entries from the list of approved keywords.
-% Don't make up new ones.
-\begin{keywords}
-Gravitational lensing: weak -- Methods: numerical -- Cosmology: dark matter, dark energy \& large-scale structure of Universe 
-\end{keywords}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%% BODY OF PAPER %%%%%%%%%%%%%%%%%%
-
-%----------
-\section{Introduction}
-\label{sec:intro}
-%----------
-
-Cosmology, gravitational lensing, cosmic shear, 2pt, beyond-2pt, simulations for signal and for secondary signal/systematics, IA-infusion, this paper...
-
- %----------
-\section{Cosmic shear}
-\label{sec:theory}
-%----------
-
-As mentioned in the introduction, cosmic shear can be measured and modelled from a variety of methods, many of which are used in this paper and presented in this section.  
-%-------------------------
-\subsection{$\gamma$-2PCF}
-\label{subsec:wl-th}
-
-%---------------
-\begin{figure}
-\includegraphics[width=\columnwidth]{graphs/Nz}
-\caption{Redshift distribution in our simulations, taken from the Year-1 specifications of the LSST Science Requirement Document \citep{LSST-SRD} {[\it check Y1 vs Y10}].}
-\label{fig:Nz}
-\end{figure}
-%--------------
-
- Shear two-point correlation functions ($\gamma$-2PCFs hereafter) can be predicted with percent-level precision and are therefore an ideal quantity to validate weak lensing simulations.
-In the Limber approximation\footnote{See \citet{Kilbinger17} for a comparison between the Limber approximation and the exact calculations.}, the lensing power spectrum $C^{ij}_{\ell}$ is obtained from an integral over the three-dimensional matter power spectrum $P_{\delta}(k,z)$:
-  \begin{eqnarray}
-C_{\ell}^{ij} = \int_0^{\chi_{\rm H}}  \frac{q^i(\chi) \,q^j(\chi)}{\chi^2} \, P_{\delta}\, \bigg(\frac{\ell+1/2}{\chi},z(\chi)\bigg) \ {\rm d}\chi,
-\label{eq:C_ell}
-\end{eqnarray}
-where $\chi_{\rm H}$ is the co-moving distance to the horizon, $c$ is the speed of light, $H_0$ the Hubble parameter,  and the  lensing kernels $q^{i}$ are given by:
-\begin{eqnarray}
-q^i(\chi) = \frac{3}{2}\Omega_{\rm m} \, \bigg(\frac{H_0}{c} \bigg)^2 \frac{\chi}{a(\chi)} \int_{\chi}^{\chi_{\rm H}} n^i(\chi')\frac{{\rm d}z}{{\rm d} \chi'}\frac{\chi' - \chi}{\chi'}{\rm d}\chi' \, .
-\label{eq:q_lensing}
-\end{eqnarray}
-In the previous expression, $n^i(z)$ refers to the redshift distribution  in tomographic bin `$i$', while $a(\chi)$ is the scale factor at comoving distance $\chi$ from the observer {[\it might need to define $\Omega_m$ here]}.
- The matter power spectrum is computed from  {\sc Halofit} \citep{Takahashi2012}, however  other public tools provide $P_{\delta}(k,z)$ predictions, including e.g.
-{\sc HMcode} \citep{HMCode2020}, the {\sc EuclidEmulator} \citep{EuclidEmulator}, the {\sc BACCO} emulator \citep{BACCOEmulator} or the Mira Titan emulator \citep{miraTitan}.
- Predictions for the $\gamma$-2PCFs are finally computed from Eq. (\ref{eq:C_ell}) as:
- \begin{eqnarray}
-\xi_{\pm}^{ij}(\vartheta) = \frac{1}{2\pi}\int_0^{\infty} C_{\ell}^{ij} \, J_{0/4}(\ell \vartheta) \, \ell \, {\rm d}\ell,
-\label{eq:xipm_th}
-\end{eqnarray}
-where $J_{0/4}(x)$ are Bessel functions of the first kind.
-In this paper, these calculations are carried out by {\sc pyccl}\footnote{{\sc pyccl}:pypi.org/project/pyccl}  \citep{CCL} {\it or do we use cosmosis in the end?]}.
-The $n^i(z)$ are taken from the LSST Science Requirement Document \citep{LSST-SRD} and given by
- \begin{eqnarray}
-n(z) = N_0 z^2 {\rm exp} \left[-\left(\frac{z}{z_0}\right)^\alpha \right]\, ,
-\label{eq:nz}
-\end{eqnarray}
-with $(z_0, \alpha) = (0.13, 0.78)$ and $N_0$ normalised to provide a number density of $n_{\rm eff}$ = 3.0 gal arcmin$^{-2}$.
-This lower than the expected number density for the first data release ($n_{\rm eff}\sim10$ gal arcmin$^{-2}$), but is large enough to validate our methods, and makes the calculation more tractable.
-The $n(z)$ is further split into five equi-populated tomographic bins, and smoothed with a Gaussian filter of width $\sigma = 0.05(1+z)$ in order to mimic the photometric selection process [{\it confirm with Niko}].
-The resulting distributions\footnote{The construction of these tomographic $n(z)$ can be reproduced in {github...CCL\_SRD\_Niko}.} are shown in Figure \ref{fig:Nz}.
-
-The cosmic shear signal can be measured from the ellipticities $\epsilon_{1/2}$ of simulated or observed galaxies, which, in absence of systematics and secondary signals, are unbiased estimators  of the cosmic shear components $\gamma_{1/2}$.
-The $\gamma$-2PCF are then estimated as:
- \begin{eqnarray}
- \widehat{\xi_{\pm}^{ij}}(\vartheta) = \frac{\sum_{a,b} w_a w_b \left[\epsilon_{a, \rm t}^i\epsilon_{b, \rm t}^j     \pm \epsilon_{a, \times}^i\epsilon_{b, \times}^j    \right]\Delta_{ab}(\vartheta)}{\sum_{a,b} w_a w_b} \, ,
- \label{eq:2PCF_estimator}
-  \end{eqnarray}
-where the sum is over all pairs of galaxies $a,b$ separated by an angular separation $\vartheta$, taken from tomographic bins $i,j$.
-The tangential/cross components of their ellipticities are denoted as $\epsilon_{\rm t/\times}$, respectively.
-$\Delta_{ab}(\vartheta)$ is the binning operator, equal to unity if the angular separation between the two galaxies falls within the $\vartheta$-bin, and zero otherwise, and the shape weights $w_{a,b}$ are set to unity.
-In this paper, we construct lensing catalogues from numerical simulations (described in Sec.
-\ref{sec:sims}), from which we measure $ \widehat{\xi_{\pm}^{ij}}(\vartheta)$ with {\sc Treecorr} \citep{TreeCorr}.
-We set therein the {\sc bin\_slop} parameter to 0.05, then compute the correlations in nine logarithmically-spaced angular bins ranging from 0.5 to 475.5 arcmin.
-
- %-------------------------
-\subsection{Beyond-2pt}
-\label{subsec:beyond-2pt}
-
-Non-Gaussian statistics, often referred to `beyond-2pt' statistics, have the potential to extract cosmological information stored in the complex phases of the density field, whereas two-point functions such as the $\gamma$-2PCF can only access that encoded in the complex amplitudes.
-No optimal estimator has been identified to-date as being able to capture `all' information, but the numerous studies presented in the introduction all show a clear gain in constraining power, especially when used in combination with 2pt functions.
-Some of these take as input the galaxy catalogues directly, while others require instead convergence maps.
-Therefore, we produce convergence maps from the catalogues by assigning the shear signal onto spherical {\sc Healpix}\footnote{{\sc Healpix}: http://healpix.sf.net}  maps \citep{healpix} with $N_{\rm side}=4096$, then using the standard Kaiser \& Squires inversion technique \citep{KaiserSquires} implemented in {\sc healpy} to reconstruct a convergence maps with the same angular resolution, including a baseline 2.0 arcmin smoothing beam in the inverse transform.
-Note that this smoothing scales is quite small; some probes are difficult to model in that case, and would instead prefer larger smoothing scales.
-We take this into account on a case-by-case basis, as described below.
-
-  {\it [Discuss tomography...]}
-
-\subsubsection{Catalogue-based estimators}
-
-We consider the following shear-based estimators:
-\begin{enumerate}
-\item The squeezed bispectrum, has theoretical model (Anik, can you summarise the measurements and modelling, and provide references?)
-\end{enumerate}
-
-\subsubsection{Convergence-based estimators}
-
-\begin{enumerate}
-\item Convergence three-point correlation function: (Alejandro, can you summarise the measurements and modelling, and provide references?)
-\item Peaks and Minima: local maxima and minima in the {\sc Healpix} convergence maps are counted in bins of signal-to-noise ratios, $\nu$.
-This is one of the most widely used non-Gaussian lensing statistics as it is simple to measure.
-Theoretical models have been developed to describe the largest peaks \citep[see][]{Shan18, HSCY1_Peaks_th}, however we report here the results on a much wider range of statistics, which can only be accurately modelled from numerical simulations, as in \citet{HD21, DESY3_Zuercher, HSCY1_Peaks_Sims, HD23}.
-\item Lensing PDF, has theoretical model (Cora/Lina, can you summarise the measurements and modelling, and provide references?)
-\item Map2 and Map3, has theoretical model  (Laila, can you summarise the measurements and modelling, and provide references?)
-\item Minkowski functionals (Nisha, can you summarise the measurements and modelling, and provide references?)
-\end{enumerate}
-
- %-------------------
- \section{Intrinsic alignment models}
- \label{sec:IA_th}
- %-------------------
-
-Galaxies interact with the tidal forces caused by the large-scale structure  they live in, causing their intrinsic shapes to acquire correlated alignments that has nothing to do with the correlations caused by weak lensing.
-This therefore acts as a secondary signal that contaminates the shape correlation measurements carried out in a cosmic shear analysis.
-There is no consensus on the actual physical model that describes the IA signal, and even when adopting these, the free parameters they contain are only weakly constrained from the data \citep[see][for reviews]{IA_review1, IA_review2}.
-%The most widely used model in the literature is the non-linear alignment model of \citet{NLA}, however it is now recognised that this is an effective model with limited precision, and the community is now progressively shifting towards more complex models.
-In this paper we consider four such IA models that we describe in the following sub-sections.
-In all cases, our models couple the galaxy intrinsic shapes with the local over-density and projected tidal field , then prescribe an intrinsic ellipticity tensor $\gamma_{ij}^{\rm IA}$, from which observed ellipticities are extracted as:
- \begin{eqnarray}
-\epsilon_{1}^{\rm IA} = \gamma_{xx}^{\rm IA} - \gamma_{yy}^{\rm IA} \, , \hspace{1.5cm}\epsilon_{2}^{\rm IA} = 2 \gamma_{xy}^{\rm IA}\, .
-\label{eq:tidal_th_deltaNLA}
-\end{eqnarray}
-
-\subsection{Non-linear alignment (NLA)}
-
-%The observed ellipticity of a galaxy ${\boldsymbol \epsilon}_{\rm obs} $ is a combination of its intrinsic shape ${\boldsymbol \epsilon}_{\rm int}$ and a cosmic shear signal ${\boldsymbol \gamma}$, the former of which can be further divided in a random component ${\boldsymbol \epsilon}^{\rm ran}$ and an alignment term ${\boldsymbol \epsilon}^{\rm IA}$.
-The NLA model of \citet{NLA} is the most widely used IA model in the cosmic shear literature thus far.
-According to the NLA, IA are caused by a linear coupling between galaxy shapes and the non-linear large-scale tidal field at the galaxy position.
-In the context of  two-point functions, these intrinsic shapes contribute to an intrinsic-intrinsic ($II$) term and an intrinsic-shear coupling ($GI$) term \citep{Hirata2004}, both secondary signals to the true cosmic shear ($GG$) term, with the latter typically dominating the IA sector in cross-tomographic measurements.
-The $II$ and $GI$ terms  can be both computed from the matter power spectrum as:
- \begin{eqnarray}
-P_{II}(k,z) =  \left(\frac{A_{\rm IA}\bar{C_1}\bar{\rho}(z)}{D(z)}\right)^2a^4(z) P_{\delta}(k,z)
-\label{eq:Pk_II_th}
-\end{eqnarray}
-and
- \begin{eqnarray}
-P_{GI}(k,z) = - \frac{A_{\rm IA}\bar{C_1}\bar{\rho}(z)}{D(z)}a^2(z) P_{\delta}(k,z) \, ,
-\label{eq:Pk_GI_th}
-\end{eqnarray}
-which can then be past to the Limber integration (Eqs. \ref{eq:C_ell} and \ref{eq:xipm_th}) to compute  the secondary signals $\xi_{\pm}^{II}(\vartheta)$ and $\xi_{\pm}^{GI}(\vartheta)$. 
-In the above expression,  $D(z)$ is the linear growth factor, $\bar{\rho}(z)$ is the mean matter density at redshift $z$ and $\bar{C_1}=5\times 10^{-14} M_{\odot}^{-1} h^{-2} {\rm Mpc}^3$ is a constant calibrated in \citet{Brown2002}.
-The strength of the tidal coupling is modulated by the amplitude parameter $A_{\rm IA}$, which is the main NLA parameter constrained by current cosmic shear surveys.
-Note that this model can be augmented by redshift and luminosity dependences, however we do not use these here.
-
-The NLA intrinsic ellipticities $\epsilon_{1,2}^{\rm NLA}$ are related to tidal field $s_{ij}$ by:
- \begin{eqnarray}
-\epsilon_1^{\rm NLA} = - \frac{A_{\rm IA}\bar{C_1}\bar{\rho}(z)}{D(z)} (s_{xx} - s_{yy}) \,\,\,\,,   \epsilon_2^{\rm NLA} = - \frac{2 A_{\rm IA}\bar{C_1}\bar{\rho}(z)}{D(z)} s_{xy}\;,
-\label{eq:tidal_th}
-\end{eqnarray}
-where $s_{ij} = \partial_{ij}\phi$ are the Cartesian components of the tidal tensor of the gravitational potential.
-Note that the term `non-linear' in the model name can be  misleading, as it refers to the non-linear matter power spectrum $P(k)$ that is used in its calculations; the coupling between the intrinsic galaxy shapes and the tidal field is still linear.
-Eq.( \ref{eq:tidal_th}) is used to assign intrinsic ellipticities to galaxies, given maps of the tidal field components $s_{xx}$, $s_{yy}$ and $s_{xy}$ (see Sec.
-\ref {subsec:IA_infusion}).
-
-\subsection{$\delta$-NLA}
-\label{subsec:IA_th_ext}
-
-%[{\it here}]
-
-%As discussed later, the key quantity of interest to cosmic shear analysis is not the tidal tensor itself but its trace-free version, since shape correlations with the density field are subdominant, even though peaks in high density environments are less elliptical on average.
-Consequently, the model itself has a restricted range of validity: on small scales, higher order couplings to the ellipticity field ${\boldsymbol \epsilon}^{\rm IA}$  become important, however these are neglected in the NLA model.
-Only the non-linear evolution of the tidal tensor itself is taken into account, since it does fit observations quite well.
-
-%We note that the NLA predicts additional higher-order terms and non-zero $B$-modes \citep{Hirata2004} that we neglect  in this analysis.
-Also, as shown in \citet{IA_EFT}, the NLA model can be interpreted as the lowest order description of the alignment process of galaxies in the light of an effective field theory description.
-
-The NLA model presented in the last section has been widely used in cosmic data analyses, but it has important known limitations and is therefore bound to fail at describing the IA signal with high precision.
-A perturbation theory extension to the NLA has been introduced in \citet{Blazek2015} and  \citet{Blazek2019},  where it is recognised that higher order couplings could be important and should be considered.
-The first additional term to be included is the over-density weighting term, which is caused by the fact that the intrinsic alignment of galaxies can only be observed at the galaxy positions, which are not distributed randomly on the sky but instead trace the underlying matter density,  `$\delta$', although the exact biasing scheme is not currently know.
-Accounting for this extra term in theoretical predictions is done with one-loop perturbation theory  \citep{Blazek2019}, and is implemented in {\sc pyccl}.
-Physically, it corresponds to adding a $\delta$-weight to the NLA predictions at the local galaxy positions, effectively representing the different tracer properties.
-At the level of numerical simulations, this could be done in principle simply by augmenting the NLA ellipticities with this weight, namely:
- \begin{eqnarray}
-\epsilon_{1/2}^{\delta-\rm NLA} = \epsilon_{1/2}^{\rm NLA}\times(1 + b_{\rm TA}\delta) \, ,
-\label{eq:tidal_th_deltaNLA}
-\end{eqnarray}
-where the term $b_{\rm TA}$ corresponds to the (largely unconstrained) biasing relation between these source galaxies and the underlying matter field.
-In practice, however, we find that this is noisy, and that it is instead preferable to generate mocks catalogues with the biasing scheme directly applied when assigning galaxy positions, after which no weighting is necessary.
-Nevertheless, Eq.
-(\ref{eq:tidal_th_deltaNLA}) can be used to modify the value of $b_{\rm TA}$.
-Indeed, from a mock with a given bias $b_{\rm TA, orig}$, we can rescale the IA contribution to a different $b_{\rm TA, new}$  as:
-\begin{eqnarray}
-{\boldsymbol \epsilon}^{\rm int}_{b_{\rm TA, new}}  = \frac{(1 + b_{\rm TA, new}\delta)}{(1 + b_{\rm TA, orig}\delta)}{\boldsymbol \epsilon}^{\rm int}_{b_{\rm TA, orig}} \, .
-\label{eq:bta_rescale}
-\end{eqnarray}
-
-Compared to the NLA, the $\delta$-NLA is a stronger IA model, especially on small scales \citep{Blazek2019}, and seems to be preferred by some hydrodynamical simulations \citep{Hilbert_IA2017}.
-It is also better motivated from a physical point of view, since we know that the galaxies trace dark matter  and are not randomly distributed in our Universe as the NLA assumes.
-
-%-----------------------------------
-\subsection{Tidal Torque (TT)}
-\label{subsec:IA_th_TT}
-
-As shown in \citet{Blazek2019}, one-loop perturbative calculations include another term, by which galaxies acquire an intrinsic alignment via a coupling between their angular momentum and the tidal field, which can be re-expressed as a quadratic coupling between the tidal field and the shape.
-In this tidal torque model (TT), intrinsic ellipticities are given by:
-\begin{eqnarray}
-\gamma_{ij}^{\rm IA, TT} = C_2 \left[ \sum_{k=x,y,z} s_{ik} s_{kj} -\frac{1}{3} \delta_{ij} s^2 \right] \, ,
-\label{eq:tidal_th_TT}
-\end{eqnarray}
-where 
-\begin{eqnarray}
-C_2 = \frac{5 A_2 \bar{C_1} \Omega_{\rm m} \rho_{\rm crit}}{D^2(z)} \,  = \left[ \frac{-5 A_2}{A_1 D(z)} \right] C_1.
-\end{eqnarray}
-Under the approximation that line-of-sight alignments are mostly suppressed from cosmic shear measurement due to the broad lensing kernels, 
-we show in  Appendix \ref{app:2d_TT} that the terms inside the square bracket in Eq. (\ref{eq:tidal_th_TT}) leads to:
-\begin{eqnarray}
-\epsilon_1^{\rm TT} = C_2  \left[ s_{xx}^2 - s_{yy}^2\right] \, , \epsilon_2^{\rm TT} = 2 C_2 s_{xy}\left[s_{xx}+s_{yy}  \right]\, ,
-\end{eqnarray}
-both quadratic in the tidal field components.
-
-%-----------------------------------
-\subsection{$\delta$-TT}
-\label{subsec:IA_th_TT}
-
-Following the relation between the NLA and the $\delta$-NLA model, galaxies in the TT model are also assume to be randomly scattered on the sky, which we know to be a bad approximation.
-Computing the next-order contribution to the TT model involves two-loop perturbation theory calculations that have not been done yet due to the significantly higher complexity of such task.
-in simulations however, the $\delta$-weighting term is straight-forward to implement, as it involves to simply infuse the TT model onto galaxies that trace the matter field with a non-zero biasing factor.
-As for the $\delta$-NLA model, the $\delta$-TT ellipticities can  be related to the TT model as:
-\begin{eqnarray}
-\epsilon_{1/2}^{\delta-\rm TT} = \epsilon_{1/2}^{\rm TT}\times(1 + b_{\rm TA}\delta) \, .
-\label{eq:tidal_th_deltaTT}
-\end{eqnarray}
- There are currently no theoretical models for $\delta$-TT, which means that predictions from this model are, at the moment, completely simulation-based.
-
-It is worth recalling here that other IA models exist in the literature, and that at this point observations are not precise enough to set strong constraints on them, further motivating our flexible multi-model approach.
-
-%\subsection{Likelihood}
-%\label{subsec:likelihood}
-
-%Multi-Gaussian likelihood, analytical Covariance matrix (Gauss + non-Gauss + SSC) from {\sc TJPCov}, Firecrown, sampler, priors.
-
-%---------------------
-\section{Simulations}
-\label{sec:sims}
-
-%-------------
-\subsection{Cosmic shear galaxy catalogues} 
-\label{subsec:WL_cats}
-
-The weak lensing simulations developed for this work are based on ray-tracing mass sheets produced from the Outer Rim $N$-body simulation \citep{OuterRim}, which evolved 10,240$^3$ particles in a (5.225 Gpc)$^3$ cosmological volume, assuming a flat $\Lambda$CDM cosmology with $\Omega_{\rm m}$=0.2648, $\Omega_{\rm b}$=0.0448, $h$=0.71, $\sigma_8$ = 0.801, $n_{\rm s}$= 0.963, $w_0$=-1.00.
-A total of 101 particle snapshots were originally saved, of which we use only those with $z<4.0$.
-Particles from each dump are assigned to curved mass shells approximately 114 Mpc thick, producing a sequence of 57 {\sc Healpix} maps $\delta(\theta,\phi,\chi_i)$ with {\sc nside} = 8192 and $i=1..57$, filling up a light-cone over an octant up to $z=3$.
-%More details on this procedure can be found  in \citet{cosmoDC}, where lensing quantities are computed specifically for the generation of the {\sc cosmoDC2}  synthetic sky catalogue.
-
-Ray-tracing is performed in the Born approximation, summing over the mass shells using the $\chi$-integral of Eq.
-(\ref{eq:C_ell}).
-A source plane is placed at the high-redshift edge of every mass planes, resulting in a series of convergence  maps  $\kappa(\theta,\phi,\chi_i)$ that are subsequently transformed into shear maps $\gamma_{1/2}(\theta,\phi,\chi_i)$ using the Kaiser-Squires methods \citep{KaiserSquires}, which is implemented via efficient {\sc HealPy alm2map} routines.
-
-We position galaxies in the light cone following exactly our chosen $N(z)$, and interpolate the shear quantities at their location. We follow two distinct algorithm to achieve this:
-\begin{enumerate}
-\item {\it Random:} galaxies RA and Dec are distributed randomly on the octant, thereby matching this fundamental assumptions in the NLA and TT models. 
-\item {\it Linear bias:} galaxies RA and Dec are sampled from the mass sheets smoothed\footnote{We also tried sampling the field with 0.1 and 0.5 $h^{-1}$Mpc but this resulted in noisier results.} over 1.0 $h^{-1}$Mpc (comoving), assuming a linear bias of $b_{\rm TA}$, now matching instead the assumptions of the $\delta$-NLA and $\delta$-TT models.
-With this method we produce galaxy positions assuming first $b_{\rm TA}=1.0$ (our fiducial case) and also $b_{\rm TA}=2.0$, enhancing the  model flexibility.
-\end{enumerate}
-
-Since source clustering is a higher order effect in cosmic shear, the measured $\xi_{\pm}$ from these three mocks (random, $b_{\rm TA}=1.0$ and $b_{\rm TA}=2.0$) show negligible differences ({\it to quantify and cite}).
-In contrast, the impact on the IA contamination is significant and can double the secondary signal in certain circumstances.
-The main explanation for this is that while clustered sources are uncorrelated with the foreground matter responsible for the lensing signal, the high-density regions they live are also subject to the largest tidal fields.
-
-%----------
-\subsection{Projected tidal fields}
-\label{subsec:IA_sims}
-
-\begin{figure*}
-\caption{Density field and the associated projected tidal field tensors.}
-\label{fig:maps}
-\end{figure*}
-
-Our infusion method completely relies on couplings between intrinsic galaxy shapes and the local tidal field, hence the first step in our method consist in extracting the tidal field maps $s_{ij}(\theta,\phi,\chi_i)$ from the mass maps $\delta(\theta,\phi,\chi_i)$ that source them.
-In three dimensions, trace-free tidal tensor $s_{ij}(\boldsymbol x)$ can be obtained from the matter over-density field $\delta(\boldsymbol x)$ as   \citep{Catelan_IA_Tidal}:
-\begin{eqnarray}
- \widetilde{s}_{ij} (\boldsymbol k)  = \left[\frac{k_i k_j}{k^2} - \frac{\delta_{ij}}{3}\right]  \widetilde {\delta}(\boldsymbol k) \mathcal{G}(\sigma_{\rm G}) \, ,
- \label{eq:sij}
-\end{eqnarray}
-where $\mathcal{G}(\sigma_{\rm G})$ is a three-dimensional Gaussian function described by a single (free) parameter $\sigma_{\rm G}$ that  controls the physical scales which are allowed to affect the IA term in our model.
-Tilde symbols  denote Fourier transformed quantities,  the indices $(i,j)$ label the components of the Cartesian wave-vector $\boldsymbol{k}^T = (k_x,k_y,k_z)$, and $k^2 = k_x^2 + k_y^2 + k_z^2$. 
-As shown in \citet{Tidalator} for Cartesian coordinates, projected tidal fields  computed from projected mass sheets provide and excellent agreement with the NLA model, which in contrast computes the full tidal fields from the three-dimensional matter density and project along the radial dimension at the end.
-We promote this transformation to curved-sky in this work, exploiting the  polarisation {\sc alm2map} operations built in {\sc Healpy}.
-In particular, noting that $Q=s_{xx}-s_{yy}$, $U=s_{xy}$ and $\delta=s_{xx}+s_{yy}$, we compute the curved-sky tidal field tensors ${s}_{ij}({\boldsymbol \theta})$ as:
- \begin{eqnarray}
-s_{xx}({\boldsymbol \theta})  =  \left[\frac{ \delta + Q}{2}  - \frac{\delta}{3}\right] \, ,s_{yy}({\boldsymbol \theta})  =  \left[\frac{\delta - Q}{2}  - \frac{\delta}{3}\right] \, , s_{xy}({\boldsymbol \theta}) = U
- \label{eq:sij_2D_sph}
- \end{eqnarray}
-where the $U({\boldsymbol \theta})$ and $Q({\boldsymbol \theta})$ maps are smoothed by the Gaussian beam with width $\sigma_{\rm G}$.
-We suppress large artificial tidal fields at the maps boundary by replicating 8$\times$ the density maps defined on the octant and working on a full sky density $\delta$; we re-apply the octant mask on the tidal field maps after the operation.
-Note that the value of $\sigma_{\rm G}$ is a free parameter both in the infusion technique described in this paper and in the NLA and TATT models.
-We therefore explore two cases, $\sigma_{\rm G}=0.1$Mpc and 0.5Mpc, however this may be further optimised in the future.
-
-%are specified within the NLA model.
-Smoothing amounts to selecting physical scales that do not contribute to the alignment of galaxies, which is still a debatable quantity, but is also introduced for numerical stability.
-\citet{Blazek2015} argues that 1.0 $h^{-1}$Mpc could be a reasonable fiducial value, being larger then the typical halo size, but recognizes that one-halo terms are also required to better match the observations.
-In their later work, \citet{Blazek2019} do not include smoothing at all, and neither do the KiDS-1000 nor DES-Y1 analyses based on the NLA model \citep{KiDS1000_Asgari,DESY1_Troxel}.
-In this work we used a two-dimensional Gaussian filter and calibrated $\sigma_{\rm G}$ empirically to $\sigma_{\rm G}=0.1h^{-1}$Mpc (see Sec.
-\ref{subsubsec:sigma_G}), however these two choices are arbitrary and could possibly be better optimised in the future; we also explore $\sigma_{\rm G}=0.5h^{-1}$Mpc later on.
-We note that the smoothing scale is degenerate with the resolution of the simulation itself, and that one should use caution when smoothing on scales that approach the resolution limits.
-
-%We employ a numerical technique worth mentioning here: the Fourier transforms involved in computing Eq.
-(\ref{eq:sij_2D}) are computed from the full (projected) periodic boxes of the simulations, then interpolated on the light-cones.
-We find that tidal field computed directly from the $10\times10$ deg$^2$ light-cones introduces significant large scales features in the tidal field maps, largely caused by  the non-periodic boundary conditions, which our method avoids.
-Projected tidal field maps $s_{11}$, $s_{22}$ and $s_{12}$ are constructed that way for each mass sheets; Fig.
-\ref{fig:maps} shows the  three tidal fields and the mass maps for one of them.
-We can clearly see the connection between all maps around over-dense regions.
-{\it (Include a figure of $s_ij$ and $\delta$)}.
-
-{\it [Mention normalisation of the tidal fields by $0.6252 = H_0/114$ = 1/shell-thickness}
-
-%of every light-cones and interpolated at the position of every galaxy.
-Fig.
-\ref{fig:tidalator} illustrates this process for a small zoomed-in patch at $z\sim0$, starting from a $\delta_{2D}(\boldsymbol \theta)$ map (upper large panel), computing the tidal field components (middle four panels) and comparing the results with the cosmic shear signal generated by the same mass distribution (bottom two panels).
-The tidal field maps clearly reproduce the cosmic shear maps, and the minus sign in front of both terms in Eq.
-(\ref{eq:tidal_th}) causes the IA to undo some of the lensing signal.
-
-\subsection{Infusion of intrinsic alignments}
-\label{subsec:IA_infusion}
-
-Having now produced shear catalogues and tidal field maps, we can now use Eq.
-\ref{eq:tidal_th} to couple linearly the alignment of galaxies with the local tidal field, or Eq.
-\ref{eq:tidal_th_TT} to use instead a quadratic coupling.
-These allow us to compute the intrinsic ellipticities ${\boldsymbol \epsilon}^{\rm int}$ for the four IA models described in Sec.
-\ref{sec:IA_th}, which we combine with the cosmic shear signal ${\boldsymbol g}$ to compute observed ellipticities:
-\begin{eqnarray}
-{\boldsymbol \epsilon}^{\rm obs} = \frac{{\boldsymbol \epsilon}^{\rm int} + {\boldsymbol g}}{1 + {\boldsymbol \epsilon}^{\rm int}{\boldsymbol g^*}} \,, {\rm with \, \, } 
-{\boldsymbol \epsilon}^{\rm int}  = \frac{{\boldsymbol \epsilon}^{\rm IA} + {\boldsymbol \epsilon}^{\rm ran}}{1 + {\boldsymbol \epsilon}^{\rm IA}{\boldsymbol \epsilon^{\rm ran, *}}}.
-\label{eq:eps_obs}
-\end{eqnarray}
-In the above expressions, the denominators ensures that the combined  ellipticities never exceed unity.
-The complex spin-2 reduced shear ${\boldsymbol g} \equiv (\gamma_1 + {\rm i} \gamma_2)/(1+\kappa)$ is computed from the shear  $(\gamma_{1/2}$) and convergence ($\kappa$) maps, interpolated at the galaxy positions and redshifts.
-The  random orientation term ${\boldsymbol \epsilon}^{\rm ran}$ is drawn from two Gaussians (one per component) with their standard deviations matching the LSST-Y1 forecast, $\sigma_{\epsilon} = 027$.
-We further constraint  the random ellipticity to satisfy $|{\boldsymbol \epsilon}^{\rm ran}| \le 1.0$.
-%We recall that since our simulated galaxy catalogues trace the dark matter density, our default IA-infusion method  is consistent with the $\delta$-NLA model (see Sec.
-\ref{subsec:IA_th_ext}).
-Analytical predictions for the two-point functions are more involved in this case \citep[see][]{Blazek2019} and not yet available on the public {\sc cosmoSIS} release.
-We therefore validate our methods with the standard NLA first, which we infuse by `correcting' the $\delta$-NLA measurement with Eq.
-(\ref{eq:tidal_th_deltaNLA}), i.e.
-by replacing ${\boldsymbol \epsilon}^{\rm IA}$ by ${\boldsymbol \epsilon}^{\rm IA}/(1 + b_{\rm TA} \delta)$ in our simulations.
-Once again, these are less realistic but better suited for validation of the measured $\gamma$-2PCFs against a theoretical model; after this is established, we use the $\delta-$NLA catalogues as our fiducial infusion model.
-We re-iterate here that the same tidal fields, shear maps and IA coupling equations are used for the NLA and $\delta$-NLA models, and separately for the TT and $\delta$-TT models; these  only differ by the fact that in one case the galaxies are placed at random on the octant, while in the other case they are linearly tracing the dark matter.
-
-Also note that our current IA models make no differentiation between galaxy colours or type, and instead treats the full sample as a single population that has a single, effective, alignment signall \citep[see][for an example with a red/blue split]{DESY1_IA_Samuroff}.
-
-%---------------------
-\section{Validation with $\xi_{\pm}$}
-\label{sec:validation}
-
-% Requires the booktabs if the memoir class is not being used
-\begin{table}
-   \centering
-   %\topcaption{Table captions are better up top} % requires the topcapt package
-   \begin{tabular}{@{} lcr @{}} % Column formatting, @{} suppresses leading/trailing space
-      \hline
-      \hline
-       %\multicolumn{2}{c}{Item} \\
-      model   		& ($A_{\rm IA}, b_{\rm TA}, A_2)$ \\
-      \hline
-      NLA     		& {($\pm$1,0,0) }&  \\
-      \multirow{2}{*}{$\delta-$NLA }  	&   {($\pm$1,1,0)}   \\
-      							&  {(1,2,0)}   \\
-      TT 			&  {(0,0,$\pm$1)} &  \\
-      \multirow{2}{*}{$\delta$-TT} 	&  {(0,1,$\pm$1)}   \\
-      				&  {(0,2,1)}   \\
-      TATT- fiducial	&  { (1,1,1)}  \\
-      %TATT-DESY3	&   (-0.7,1,1.9) & \\
-      \hline
-      \hline
-
-   \end{tabular}
-   \caption{IA models infused in this work.}
-   \label{table:IAmodels}
-\end{table}
-
-%------------------------------
-\subsection{NLA model}
-\label{subsubsec:sigma_G}
-
-See Fig. \ref{fig:xi_NLA}
 %---------------
@@
 %---------------
-
-%------------------------------
-\subsection{$\delta$-NLA model}
-\label{subsec:deltaNLA}
-
-See Fig. \ref{fig:xi_deltaNLA}.
-
-\begin{figure*}
-\includegraphics[width=\columnwidth]{graphs/frac_xip_IA1_skysim_deltaNLA_srd}
-\includegraphics[width=\columnwidth]{graphs/frac_xim_IA1_skysim_deltaNLA_srd}
-\caption{Same as Fig.
-\ref{fig:xi_NLA}, but for the $\delta$-NLA model with $A_{\rm IA}=1.0$ and $b_{\rm TA}=1.0$, and only for smoothing of 0.5$h^{-1}$Mpc.
-The dashed black lines show the NLA predictions to better highlight the differences.
-}
-\label{fig:xi_deltaNLA}
-\end{figure*}
-
-\begin{figure}
-\includegraphics[width=\columnwidth]{graphs/frac_xip_bta1_rescaled}
-\caption{Ratio between the shear correlation functions with and without IA in tomographic bin combination 2-5.
-The brown and green symbols show measurements from simulations constructed with $b_{\rm TA}$ = 0.0 and 2.0 respectively,  the black solid and dotted lines shown their predictions, while the blue symbols are obtained by rescaling $b_{\rm TA}$ = 1.0 simulations using Eq.
-\ref{eq:bta_rescale}.
-}
-\label{fig:xi_deltaNLA_rescaled}
-\end{figure}
-
-We verified that it works equally well for $b_{\rm TA}$ = 1.0 and 2.0.
-
-%------------------------------
-
-Using this, we $b_{\rm TA}$-rescale our $b_{\rm TA}=1.0$ mock to $b_{\rm TA}=2.0$ and to $0.0$ mocks.
-Results are shown in Fig.
-\ref{fig:xi_deltaNLA_rescaled} for one of the tomographic bin.
-It works reasonably well, but lower redshift are less accurate due to the increased  shot noise (not shown), hence we do not recommend using this.
-
-%------------------------------
-\subsection{TT model}
-\label{subsec:TT}
-
-See Fig. \ref{fig:xi_TT}
-
-\begin{figure*}
-\includegraphics[width=\columnwidth]{graphs/frac_xip_IA1_skysim_TT_srd.jpg}
-\includegraphics[width=\columnwidth]{graphs/frac_xim_IA1_skysim_TT_srd.jpg}
-\caption{Same as Fig. \ref{fig:xi_NLA}, but for the TT model with $A_2=1.0$. Here, the dashed black lines show the NLA predictions to better highlight the differences. }
-\label{fig:xi_TT}
-\end{figure*}
-
-\begin{figure*}
-%\includegraphics[width=\columnwidth]{graphs/frac_xip_C2_m1_skysim_deltaTT}
-\includegraphics[width=\columnwidth]{graphs/frac_xip_IA1_skysim_deltaTT_srd.jpg}
-\includegraphics[width=\columnwidth]{graphs/frac_xim_IA1_skysim_deltaTT_srd.jpg}
-\caption{Same as Fig. \ref{fig:xi_deltaNLA}, but comparing the TT and the $\delta$-TT models, with $A_2=1.0$, $b_{\rm TA}$ = 1.0, and only for smoothing of 0.5$h^{-1}$Mpc. }
-\label{fig:xi_deltaTT}
-\end{figure*}
-
-To match the theory, we need to apply the following calibration: $\epsilon^{\rm IA, TT}(z<0.5) \rightarrow \epsilon^{\rm IA, TT} /2.5$.
-
-%------------------------------
-\subsection{$\delta$-TT model}
-\label{subsec:TT}
-
-See Fig. \ref{fig:xi_deltaTT}
-
-To match the TT theory, we need to apply the following calibration: $\epsilon^{\rm IA, TT}(z<0.5) \rightarrow \epsilon^{\rm IA, TT} /5.0$, followed by $\epsilon^{\rm IA, TT} \rightarrow \epsilon^{\rm IA, TT}/7.0$.
-
-%\subsection{Validation with full inference}
- %\label{sec:inference}
-
-%priors, firecrown, Takahashi $P(k)$
-
-\section{Higher-order weak lensing statistics}
-\label{sec:HOWLS}
-
-... use the mocks from Table \ref{table:IAmodels} to compute derivatives. Show.
-
-%----------
-\section{Conclusions}
-\label{sec:conclusion}
-%----------
-
-\section*{Acknowledgements}
-
-JHD acknowledges support from an STFC Ernest Rutherford Fellowship (project reference ST/S004858/1).
-Ray-tracing computations were carried on the NERSC [acknowledgments] ...
-HACC [acknowledgements] ...
-OuterRim [Acknowledgments]
-\\
-
-Some of the results in this paper have been derived using the {\sc healpy} and {\sc HEALPix} packages.
-\\
-\\
-\\
-{\footnotesize All authors contributed to the development and writing of this paper. JHD led the analysis.... }
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Data Availability}
-
-%The SLICS numerical simulations can be found at http://slics.roe.ac.uk/, while the cosmo-SLICS can be made available upon request.
-
-%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%
-
-% The best way to enter references is to use BibTeX:
-
-\bibliographystyle{hapj}
-\bibliography{IA} % if your bibtex file is called example.bib
-
-% Alternatively you could enter them by hand, like this:
-% This method is tedious and prone to error if you have lots of references
-%\begin{thebibliography}{99}
-%\bibitem[\protect\citeauthoryear{Author}{2012}]{Author2012}
-%Author A.~N., 2013, Journal of Improbable Astronomy, 1, 1
-%\bibitem[\protect\citeauthoryear{Others}{2013}]{Others2013}
-%Others S., 2012, Journal of Interesting Stuff, 17, 198
-%\end{thebibliography}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%% APPENDICES %%%%%%%%%%%%%%%%%%%%%
-
-\appendix
-
-\section{Projected Tidal Field}
-\label{app:2d_TT}
-
-\JHD{[To reword]} We derive in this Appendix...  
-The prescription to assign an intrinsic alignment based on the projected tidal field, described in Eq.
-(\ref{eq:tidal_th}), involves the combinations $(s_{xx} - s_{yy})$ and $s_{xy}$, which therefore correspond to:
-\begin{eqnarray}
- \widetilde{\epsilon}_1^{\rm IA} (\boldsymbol k_{\perp})  &\propto& \left(\frac{k_x^2 - k_y^2}{k^2} \right) \widetilde{\delta}_{\rm 2D}(\boldsymbol k_{\perp})\mathcal{G_{\rm 2D}}(\sigma_{\rm G})  \, ,\nonumber \\
- \widetilde{\epsilon}_2^{\rm IA} (\boldsymbol k_\perp)  &\propto& \left(\frac{k_x k_y}{k^2} \right) \widetilde {\delta}_{\rm 2D}(\boldsymbol k_\perp)\mathcal{G_{\rm 2D}}(\sigma_{\rm G}) 
- %\label{eq:sij}
-\end{eqnarray}
-
-Aside from the smoothing kernel, these are the same filters that are used for converting convergence maps to shear maps under the \citet[][KS hereafter]{KaiserSquires} inversion:
- \begin{eqnarray}
- \widetilde{\gamma_1} (\boldsymbol \ell)  = \left(\frac{k_x^2 - k_y^2}{k^2} \right) \widetilde {\kappa}(\boldsymbol \ell) \, , \hspace{1cm} \widetilde{\gamma_2} (\boldsymbol \ell)  = \left(\frac{k_x k_y}{k^2} \right) \widetilde {\kappa}(\boldsymbol \ell)
- %\label{eq:sij}
-\end{eqnarray}
-meaning that on can linearly combine the mass sheets with the correct coefficients and obtain intrinsic ellipticities from a normal KS inversion.
-
-Projecting out the $z$ components (e.i. $s_{0i}$=$s_{i0}$=0 for all $i$),  the tidal torque terms from Eq. (\ref{eq:tidal_th_TT}) can be expanded as:
- \begin{eqnarray}
-\gamma^{\rm TT}_{ij}&=& C_2 \left[\sum_{k=x,y} s_{ik} s_{kj} -\frac{1}{3} \delta_{ij} s^2\right] \\
-                                  &=&C_2 \left[ s_{ix}s_{xj}  + s_{iy}s_{yj}  -  \frac{1}{3} \delta_{ij} \left( s_{xx}^2 + s_{yy}^2 +2s_{xy}^2 \right)  \right] \, .
-\end{eqnarray}
-Specifically, this yields:
- \begin{eqnarray}
-\gamma^{\rm TT}_{xx}&=& C_2 \left[\frac{2}{3}s_{xx}^2  -  \frac{1}{3}s_{yy}^2 + \frac{1}{3}s_{xy}^2 \right]\, ,  \nonumber \\
-\gamma^{\rm TT}_{yy}&=& C_2 \left[-\frac{1}{3}s_{xx}^2  +  \frac{2}{3}s_{yy}^2 + \frac{1}{3}s_{xy}^2  \right]\, , \\
-\gamma^{\rm TT}_{xy}&=& C_2 s_{xy}\left[s_{xx}+s_{yy}  \right]\, . \nonumber                                  
-\end{eqnarray}
-With the standard ellipticity definitions $\epsilon_1^{\rm TT}\equiv \gamma_{xx}^{\rm TT} - \gamma_{yy}^{\rm TT}$ and $\epsilon_2^{\rm TT}\equiv -2 \gamma_{xy}$, we obtain:
-\begin{eqnarray}
-\epsilon_1^{\rm TT} = C_2  \left[ s_{xx}^2 - s_{yy}^2\right] \, , \epsilon_2^{\rm TT} = -2 C_2 s_{xy}\left[s_{xx}+s_{yy}  \right]\, .
-\end{eqnarray}
-In the TATT model, the total intrinsic ellipticity component is therefore given by $\epsilon_{1/2}^{\rm IA} = \epsilon_{1/2}^{\rm TATT} = \epsilon_{1/2}^{\delta{\rm-NLA}} + \epsilon_{1/2}^{\rm TT}$.
-
-% Don't change these lines
-\bsp	% typesetting comment
-\label{lastpage}
-\end{document}
-
-% End of mnras_template.tex

### 2024-03-27 sections/10_appendix.tex
Changes made by Niko

--- 2023-11-13 paper_IA.tex
@@
-% mnras_template.tex 
-%
-% LaTeX template for creating an MNRAS paper
-%
-% v3.0 released 14 May 2015
-% (version numbers match those of mnras.cls)
-%
-% Copyright (C) Royal Astronomical Society 2015
-% Authors:
-% Keith T. Smith (Royal Astronomical Society)
-
-% Change log
-%
-% v3.0 May 2015
-%    Renamed to match the new package name
-%    Version number matches mnras.cls
-%    A few minor tweaks to wording
-% v1.0 September 2013
-%    Beta testing only - never publicly released
-%    First version: a simple (ish) template for creating an MNRAS paper
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Basic setup. Most papers should leave these options alone.
-%\documentclass[fleqn,usenatbib]{mnras}
-\documentclass[useAMS,usenatbib]{mn2e}
-
-% MNRAS is set in Times font. If you don't have this installed (most LaTeX
-% installations will be fine) or prefer the old Computer Modern fonts, comment
-% out the following line
-%\usepackage{newtxtext,newtxmath}
-% Depending on your LaTeX fonts installation, you might get better results with one of these:
-%\usepackage{mathptmx}
-%\usepackage{txfonts}
-
-% Use vector fonts, so it zooms properly in on-screen viewing software
-% Don't change these lines unless you know what you are doing
-%\usepackage[T1]{fontenc}
-
-% Allow "Thomas van Noord" and "Simon de Laguarde" and alike to be sorted by "N" and "L" etc. in the bibliography.
-% Write the name in the bibliography as "\VAN{Noord}{Van}{van} Noord, Thomas"
-%\DeclareRobustCommand{\VAN}[3]{#2}
-%\let\VANthebibliography\thebibliography
-%\def\thebibliography{\DeclareRobustCommand{\VAN}[3]{##3}\VANthebibliography}
-
-%%%%% AUTHORS - PLACE YOUR OWN PACKAGES HERE %%%%%
-\input{abbrev}
-\input{psfig.sty}
-
-\usepackage{graphicx}
-\usepackage{epsfig}
-\usepackage{amssymb}
-\usepackage{amsmath}
-\usepackage{amsfonts}
-\usepackage{txfonts}
-\usepackage{multirow}
-\usepackage{afterpage}
-\usepackage{xcolor}
-%\usepackage[draft]{hyperref}
-%\usepackage{ulem} % allows for strikethrough with \sout{}
-
-%\usepackage[paperheight=10in,paperwidth=8.5in]{geometry}
-
-\setlength{\topmargin}{-0.8in}
-\paperheight 11in
-\paperwidth 8.5in
-%\setlength{\textheight}{9.8in}
-%\setlength{\textwidth}{7.3in}
-\setlength{\textheight}{9.5in}
-\setlength{\textwidth}{7.1in}
-
-\definecolor{mypink1}{rgb}{0.858, 0.188, 0.478}
-\definecolor{mygreen1}{rgb}{0.258, 0.788, 0.878}
-\definecolor{myorange1}{rgb}{0.5, 0.2, 0.2}
-\newcommand{\NM}[1]{\textcolor[RGB]{0,150,0}{#1}}
-\newcommand{\RR}[1]{\textcolor{blue}{#1}}
-\newcommand{\JHD}[1]{\textcolor{mypink1}{#1}}
-\newcommand{\snr}{$\mathcal{S}/\mathcal{N}$ }
-\newcommand{\mycomment}[1]{}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%% AUTHORS - PLACE YOUR OWN COMMANDS HERE %%%%%
-
-% Please keep new commands to a minimum, and use \newcommand not \def to avoid
-% overwriting existing commands. Example:
-%\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%
-
-% Title of the paper, and the short title which is used in the headers.
-% Keep the title short and informative.
-\title[Lensing beyond 2pt: accounting for IA]{Intrinsic alignments from projected tidal fields: non-linear  impact on cosmic shear probes}
-
-% The list of authors, and the short list which is used in the headers.
-% If you need two or more lines of authors, add an extra line using \newauthor
-\author[J. Harnois-D\'{e}raps et al.]{Joachim Harnois-D\'{e}raps$^{1}$\thanks{E-mail: joachim.harnois-deraps@ncl.ac.uk} and others
-\\
-% List of institutions
-$^{1}$School of Mathematics, Statistics and Physics, Newcastle University, Herschel Building, NE1 7RU, Newcastle-upon-Tyne, UK\\
-}
-
-% These dates will be filled out by the publisher
-\date{Accepted XXX. Received YYY; in original form ZZZ}
-
-% Enter the current year, for the copyright statements etc.
-\pubyear{2021}
-
-% Don't change these lines
-\begin{document}
-\label{firstpage}
-\pagerange{\pageref{firstpage}--21}
-%\pagerange{\pageref{firstpage}--\pageref{lastpage}}
-\maketitle
-
-% Abstract of the paper
-\begin{abstract}
-TBD
-\end{abstract}
-
-% Select between one and six entries from the list of approved keywords.
-% Don't make up new ones.
-\begin{keywords}
-Gravitational lensing: weak -- Methods: numerical -- Cosmology: dark matter, dark energy \& large-scale structure of Universe 
-\end{keywords}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%% BODY OF PAPER %%%%%%%%%%%%%%%%%%
-
-%----------
-\section{Introduction}
-\label{sec:intro}
-%----------
-
-Cosmology, gravitational lensing, cosmic shear, 2pt, beyond-2pt, simulations for signal and for secondary signal/systematics, IA-infusion, this paper...
-
- %----------
-\section{Cosmic shear}
-\label{sec:theory}
-%----------
-
-As mentioned in the introduction, cosmic shear can be measured and modelled from a variety of methods, many of which are used in this paper and presented in this section.  
-%-------------------------
-\subsection{$\gamma$-2PCF}
-\label{subsec:wl-th}
-
-%---------------
-\begin{figure}
-\includegraphics[width=\columnwidth]{graphs/Nz}
-\caption{Redshift distribution in our simulations, taken from the Year-1 specifications of the LSST Science Requirement Document \citep{LSST-SRD} {[\it check Y1 vs Y10}].}
-\label{fig:Nz}
-\end{figure}
-%--------------
-
- Shear two-point correlation functions ($\gamma$-2PCFs hereafter) can be predicted with percent-level precision and are therefore an ideal quantity to validate weak lensing simulations.
-In the Limber approximation\footnote{See \citet{Kilbinger17} for a comparison between the Limber approximation and the exact calculations.}, the lensing power spectrum $C^{ij}_{\ell}$ is obtained from an integral over the three-dimensional matter power spectrum $P_{\delta}(k,z)$:
-  \begin{eqnarray}
-C_{\ell}^{ij} = \int_0^{\chi_{\rm H}}  \frac{q^i(\chi) \,q^j(\chi)}{\chi^2} \, P_{\delta}\, \bigg(\frac{\ell+1/2}{\chi},z(\chi)\bigg) \ {\rm d}\chi,
-\label{eq:C_ell}
-\end{eqnarray}
-where $\chi_{\rm H}$ is the co-moving distance to the horizon, $c$ is the speed of light, $H_0$ the Hubble parameter,  and the  lensing kernels $q^{i}$ are given by:
-\begin{eqnarray}
-q^i(\chi) = \frac{3}{2}\Omega_{\rm m} \, \bigg(\frac{H_0}{c} \bigg)^2 \frac{\chi}{a(\chi)} \int_{\chi}^{\chi_{\rm H}} n^i(\chi')\frac{{\rm d}z}{{\rm d} \chi'}\frac{\chi' - \chi}{\chi'}{\rm d}\chi' \, .
-\label{eq:q_lensing}
-\end{eqnarray}
-In the previous expression, $n^i(z)$ refers to the redshift distribution  in tomographic bin `$i$', while $a(\chi)$ is the scale factor at comoving distance $\chi$ from the observer {[\it might need to define $\Omega_m$ here]}.
- The matter power spectrum is computed from  {\sc Halofit} \citep{Takahashi2012}, however  other public tools provide $P_{\delta}(k,z)$ predictions, including e.g.
-{\sc HMcode} \citep{HMCode2020}, the {\sc EuclidEmulator} \citep{EuclidEmulator}, the {\sc BACCO} emulator \citep{BACCOEmulator} or the Mira Titan emulator \citep{miraTitan}.
- Predictions for the $\gamma$-2PCFs are finally computed from Eq. (\ref{eq:C_ell}) as:
- \begin{eqnarray}
-\xi_{\pm}^{ij}(\vartheta) = \frac{1}{2\pi}\int_0^{\infty} C_{\ell}^{ij} \, J_{0/4}(\ell \vartheta) \, \ell \, {\rm d}\ell,
-\label{eq:xipm_th}
-\end{eqnarray}
-where $J_{0/4}(x)$ are Bessel functions of the first kind.
-In this paper, these calculations are carried out by {\sc pyccl}\footnote{{\sc pyccl}:pypi.org/project/pyccl}  \citep{CCL} {\it or do we use cosmosis in the end?]}.
-The $n^i(z)$ are taken from the LSST Science Requirement Document \citep{LSST-SRD} and given by
- \begin{eqnarray}
-n(z) = N_0 z^2 {\rm exp} \left[-\left(\frac{z}{z_0}\right)^\alpha \right]\, ,
-\label{eq:nz}
-\end{eqnarray}
-with $(z_0, \alpha) = (0.13, 0.78)$ and $N_0$ normalised to provide a number density of $n_{\rm eff}$ = 3.0 gal arcmin$^{-2}$.
-This lower than the expected number density for the first data release ($n_{\rm eff}\sim10$ gal arcmin$^{-2}$), but is large enough to validate our methods, and makes the calculation more tractable.
-The $n(z)$ is further split into five equi-populated tomographic bins, and smoothed with a Gaussian filter of width $\sigma = 0.05(1+z)$ in order to mimic the photometric selection process [{\it confirm with Niko}].
-The resulting distributions\footnote{The construction of these tomographic $n(z)$ can be reproduced in {github...CCL\_SRD\_Niko}.} are shown in Figure \ref{fig:Nz}.
-
-The cosmic shear signal can be measured from the ellipticities $\epsilon_{1/2}$ of simulated or observed galaxies, which, in absence of systematics and secondary signals, are unbiased estimators  of the cosmic shear components $\gamma_{1/2}$.
-The $\gamma$-2PCF are then estimated as:
- \begin{eqnarray}
- \widehat{\xi_{\pm}^{ij}}(\vartheta) = \frac{\sum_{a,b} w_a w_b \left[\epsilon_{a, \rm t}^i\epsilon_{b, \rm t}^j     \pm \epsilon_{a, \times}^i\epsilon_{b, \times}^j    \right]\Delta_{ab}(\vartheta)}{\sum_{a,b} w_a w_b} \, ,
- \label{eq:2PCF_estimator}
-  \end{eqnarray}
-where the sum is over all pairs of galaxies $a,b$ separated by an angular separation $\vartheta$, taken from tomographic bins $i,j$.
-The tangential/cross components of their ellipticities are denoted as $\epsilon_{\rm t/\times}$, respectively.
-$\Delta_{ab}(\vartheta)$ is the binning operator, equal to unity if the angular separation between the two galaxies falls within the $\vartheta$-bin, and zero otherwise, and the shape weights $w_{a,b}$ are set to unity.
-In this paper, we construct lensing catalogues from numerical simulations (described in Sec.
-\ref{sec:sims}), from which we measure $ \widehat{\xi_{\pm}^{ij}}(\vartheta)$ with {\sc Treecorr} \citep{TreeCorr}.
-We set therein the {\sc bin\_slop} parameter to 0.05, then compute the correlations in nine logarithmically-spaced angular bins ranging from 0.5 to 475.5 arcmin.
-
- %-------------------------
-\subsection{Beyond-2pt}
-\label{subsec:beyond-2pt}
-
-Non-Gaussian statistics, often referred to `beyond-2pt' statistics, have the potential to extract cosmological information stored in the complex phases of the density field, whereas two-point functions such as the $\gamma$-2PCF can only access that encoded in the complex amplitudes.
-No optimal estimator has been identified to-date as being able to capture `all' information, but the numerous studies presented in the introduction all show a clear gain in constraining power, especially when used in combination with 2pt functions.
-Some of these take as input the galaxy catalogues directly, while others require instead convergence maps.
-Therefore, we produce convergence maps from the catalogues by assigning the shear signal onto spherical {\sc Healpix}\footnote{{\sc Healpix}: http://healpix.sf.net}  maps \citep{healpix} with $N_{\rm side}=4096$, then using the standard Kaiser \& Squires inversion technique \citep{KaiserSquires} implemented in {\sc healpy} to reconstruct a convergence maps with the same angular resolution, including a baseline 2.0 arcmin smoothing beam in the inverse transform.
-Note that this smoothing scales is quite small; some probes are difficult to model in that case, and would instead prefer larger smoothing scales.
-We take this into account on a case-by-case basis, as described below.
-
-  {\it [Discuss tomography...]}
-
-\subsubsection{Catalogue-based estimators}
-
-We consider the following shear-based estimators:
-\begin{enumerate}
-\item The squeezed bispectrum, has theoretical model (Anik, can you summarise the measurements and modelling, and provide references?)
-\end{enumerate}
-
-\subsubsection{Convergence-based estimators}
-
-\begin{enumerate}
-\item Convergence three-point correlation function: (Alejandro, can you summarise the measurements and modelling, and provide references?)
-\item Peaks and Minima: local maxima and minima in the {\sc Healpix} convergence maps are counted in bins of signal-to-noise ratios, $\nu$.
-This is one of the most widely used non-Gaussian lensing statistics as it is simple to measure.
-Theoretical models have been developed to describe the largest peaks \citep[see][]{Shan18, HSCY1_Peaks_th}, however we report here the results on a much wider range of statistics, which can only be accurately modelled from numerical simulations, as in \citet{HD21, DESY3_Zuercher, HSCY1_Peaks_Sims, HD23}.
-\item Lensing PDF, has theoretical model (Cora/Lina, can you summarise the measurements and modelling, and provide references?)
-\item Map2 and Map3, has theoretical model  (Laila, can you summarise the measurements and modelling, and provide references?)
-\item Minkowski functionals (Nisha, can you summarise the measurements and modelling, and provide references?)
-\end{enumerate}
-
- %-------------------
- \section{Intrinsic alignment models}
- \label{sec:IA_th}
- %-------------------
-
-Galaxies interact with the tidal forces caused by the large-scale structure  they live in, causing their intrinsic shapes to acquire correlated alignments that has nothing to do with the correlations caused by weak lensing.
-This therefore acts as a secondary signal that contaminates the shape correlation measurements carried out in a cosmic shear analysis.
-There is no consensus on the actual physical model that describes the IA signal, and even when adopting these, the free parameters they contain are only weakly constrained from the data \citep[see][for reviews]{IA_review1, IA_review2}.
-%The most widely used model in the literature is the non-linear alignment model of \citet{NLA}, however it is now recognised that this is an effective model with limited precision, and the community is now progressively shifting towards more complex models.
-In this paper we consider four such IA models that we describe in the following sub-sections.
-In all cases, our models couple the galaxy intrinsic shapes with the local over-density and projected tidal field , then prescribe an intrinsic ellipticity tensor $\gamma_{ij}^{\rm IA}$, from which observed ellipticities are extracted as:
- \begin{eqnarray}
-\epsilon_{1}^{\rm IA} = \gamma_{xx}^{\rm IA} - \gamma_{yy}^{\rm IA} \, , \hspace{1.5cm}\epsilon_{2}^{\rm IA} = 2 \gamma_{xy}^{\rm IA}\, .
-\label{eq:tidal_th_deltaNLA}
-\end{eqnarray}
-
-\subsection{Non-linear alignment (NLA)}
-
-%The observed ellipticity of a galaxy ${\boldsymbol \epsilon}_{\rm obs} $ is a combination of its intrinsic shape ${\boldsymbol \epsilon}_{\rm int}$ and a cosmic shear signal ${\boldsymbol \gamma}$, the former of which can be further divided in a random component ${\boldsymbol \epsilon}^{\rm ran}$ and an alignment term ${\boldsymbol \epsilon}^{\rm IA}$.
-The NLA model of \citet{NLA} is the most widely used IA model in the cosmic shear literature thus far.
-According to the NLA, IA are caused by a linear coupling between galaxy shapes and the non-linear large-scale tidal field at the galaxy position.
-In the context of  two-point functions, these intrinsic shapes contribute to an intrinsic-intrinsic ($II$) term and an intrinsic-shear coupling ($GI$) term \citep{Hirata2004}, both secondary signals to the true cosmic shear ($GG$) term, with the latter typically dominating the IA sector in cross-tomographic measurements.
-The $II$ and $GI$ terms  can be both computed from the matter power spectrum as:
- \begin{eqnarray}
-P_{II}(k,z) =  \left(\frac{A_{\rm IA}\bar{C_1}\bar{\rho}(z)}{D(z)}\right)^2a^4(z) P_{\delta}(k,z)
-\label{eq:Pk_II_th}
-\end{eqnarray}
-and
- \begin{eqnarray}
-P_{GI}(k,z) = - \frac{A_{\rm IA}\bar{C_1}\bar{\rho}(z)}{D(z)}a^2(z) P_{\delta}(k,z) \, ,
-\label{eq:Pk_GI_th}
-\end{eqnarray}
-which can then be past to the Limber integration (Eqs. \ref{eq:C_ell} and \ref{eq:xipm_th}) to compute  the secondary signals $\xi_{\pm}^{II}(\vartheta)$ and $\xi_{\pm}^{GI}(\vartheta)$. 
-In the above expression,  $D(z)$ is the linear growth factor, $\bar{\rho}(z)$ is the mean matter density at redshift $z$ and $\bar{C_1}=5\times 10^{-14} M_{\odot}^{-1} h^{-2} {\rm Mpc}^3$ is a constant calibrated in \citet{Brown2002}.
-The strength of the tidal coupling is modulated by the amplitude parameter $A_{\rm IA}$, which is the main NLA parameter constrained by current cosmic shear surveys.
-Note that this model can be augmented by redshift and luminosity dependences, however we do not use these here.
-
-The NLA intrinsic ellipticities $\epsilon_{1,2}^{\rm NLA}$ are related to tidal field $s_{ij}$ by:
- \begin{eqnarray}
-\epsilon_1^{\rm NLA} = - \frac{A_{\rm IA}\bar{C_1}\bar{\rho}(z)}{D(z)} (s_{xx} - s_{yy}) \,\,\,\,,   \epsilon_2^{\rm NLA} = - \frac{2 A_{\rm IA}\bar{C_1}\bar{\rho}(z)}{D(z)} s_{xy}\;,
-\label{eq:tidal_th}
-\end{eqnarray}
-where $s_{ij} = \partial_{ij}\phi$ are the Cartesian components of the tidal tensor of the gravitational potential.
-Note that the term `non-linear' in the model name can be  misleading, as it refers to the non-linear matter power spectrum $P(k)$ that is used in its calculations; the coupling between the intrinsic galaxy shapes and the tidal field is still linear.
-Eq.( \ref{eq:tidal_th}) is used to assign intrinsic ellipticities to galaxies, given maps of the tidal field components $s_{xx}$, $s_{yy}$ and $s_{xy}$ (see Sec.
-\ref {subsec:IA_infusion}).
-
-\subsection{$\delta$-NLA}
-\label{subsec:IA_th_ext}
-
-%[{\it here}]
-
-%As discussed later, the key quantity of interest to cosmic shear analysis is not the tidal tensor itself but its trace-free version, since shape correlations with the density field are subdominant, even though peaks in high density environments are less elliptical on average.
-Consequently, the model itself has a restricted range of validity: on small scales, higher order couplings to the ellipticity field ${\boldsymbol \epsilon}^{\rm IA}$  become important, however these are neglected in the NLA model.
-Only the non-linear evolution of the tidal tensor itself is taken into account, since it does fit observations quite well.
-
-%We note that the NLA predicts additional higher-order terms and non-zero $B$-modes \citep{Hirata2004} that we neglect  in this analysis.
-Also, as shown in \citet{IA_EFT}, the NLA model can be interpreted as the lowest order description of the alignment process of galaxies in the light of an effective field theory description.
-
-The NLA model presented in the last section has been widely used in cosmic data analyses, but it has important known limitations and is therefore bound to fail at describing the IA signal with high precision.
-A perturbation theory extension to the NLA has been introduced in \citet{Blazek2015} and  \citet{Blazek2019},  where it is recognised that higher order couplings could be important and should be considered.
-The first additional term to be included is the over-density weighting term, which is caused by the fact that the intrinsic alignment of galaxies can only be observed at the galaxy positions, which are not distributed randomly on the sky but instead trace the underlying matter density,  `$\delta$', although the exact biasing scheme is not currently know.
-Accounting for this extra term in theoretical predictions is done with one-loop perturbation theory  \citep{Blazek2019}, and is implemented in {\sc pyccl}.
-Physically, it corresponds to adding a $\delta$-weight to the NLA predictions at the local galaxy positions, effectively representing the different tracer properties.
-At the level of numerical simulations, this could be done in principle simply by augmenting the NLA ellipticities with this weight, namely:
- \begin{eqnarray}
-\epsilon_{1/2}^{\delta-\rm NLA} = \epsilon_{1/2}^{\rm NLA}\times(1 + b_{\rm TA}\delta) \, ,
-\label{eq:tidal_th_deltaNLA}
-\end{eqnarray}
-where the term $b_{\rm TA}$ corresponds to the (largely unconstrained) biasing relation between these source galaxies and the underlying matter field.
-In practice, however, we find that this is noisy, and that it is instead preferable to generate mocks catalogues with the biasing scheme directly applied when assigning galaxy positions, after which no weighting is necessary.
-Nevertheless, Eq.
-(\ref{eq:tidal_th_deltaNLA}) can be used to modify the value of $b_{\rm TA}$.
-Indeed, from a mock with a given bias $b_{\rm TA, orig}$, we can rescale the IA contribution to a different $b_{\rm TA, new}$  as:
-\begin{eqnarray}
-{\boldsymbol \epsilon}^{\rm int}_{b_{\rm TA, new}}  = \frac{(1 + b_{\rm TA, new}\delta)}{(1 + b_{\rm TA, orig}\delta)}{\boldsymbol \epsilon}^{\rm int}_{b_{\rm TA, orig}} \, .
-\label{eq:bta_rescale}
-\end{eqnarray}
-
-Compared to the NLA, the $\delta$-NLA is a stronger IA model, especially on small scales \citep{Blazek2019}, and seems to be preferred by some hydrodynamical simulations \citep{Hilbert_IA2017}.
-It is also better motivated from a physical point of view, since we know that the galaxies trace dark matter  and are not randomly distributed in our Universe as the NLA assumes.
-
-%-----------------------------------
-\subsection{Tidal Torque (TT)}
-\label{subsec:IA_th_TT}
-
-As shown in \citet{Blazek2019}, one-loop perturbative calculations include another term, by which galaxies acquire an intrinsic alignment via a coupling between their angular momentum and the tidal field, which can be re-expressed as a quadratic coupling between the tidal field and the shape.
-In this tidal torque model (TT), intrinsic ellipticities are given by:
-\begin{eqnarray}
-\gamma_{ij}^{\rm IA, TT} = C_2 \left[ \sum_{k=x,y,z} s_{ik} s_{kj} -\frac{1}{3} \delta_{ij} s^2 \right] \, ,
-\label{eq:tidal_th_TT}
-\end{eqnarray}
-where 
-\begin{eqnarray}
-C_2 = \frac{5 A_2 \bar{C_1} \Omega_{\rm m} \rho_{\rm crit}}{D^2(z)} \,  = \left[ \frac{-5 A_2}{A_1 D(z)} \right] C_1.
-\end{eqnarray}
-Under the approximation that line-of-sight alignments are mostly suppressed from cosmic shear measurement due to the broad lensing kernels, 
-we show in  Appendix \ref{app:2d_TT} that the terms inside the square bracket in Eq. (\ref{eq:tidal_th_TT}) leads to:
-\begin{eqnarray}
-\epsilon_1^{\rm TT} = C_2  \left[ s_{xx}^2 - s_{yy}^2\right] \, , \epsilon_2^{\rm TT} = 2 C_2 s_{xy}\left[s_{xx}+s_{yy}  \right]\, ,
-\end{eqnarray}
-both quadratic in the tidal field components.
-
-%-----------------------------------
-\subsection{$\delta$-TT}
-\label{subsec:IA_th_TT}
-
-Following the relation between the NLA and the $\delta$-NLA model, galaxies in the TT model are also assume to be randomly scattered on the sky, which we know to be a bad approximation.
-Computing the next-order contribution to the TT model involves two-loop perturbation theory calculations that have not been done yet due to the significantly higher complexity of such task.
-in simulations however, the $\delta$-weighting term is straight-forward to implement, as it involves to simply infuse the TT model onto galaxies that trace the matter field with a non-zero biasing factor.
-As for the $\delta$-NLA model, the $\delta$-TT ellipticities can  be related to the TT model as:
-\begin{eqnarray}
-\epsilon_{1/2}^{\delta-\rm TT} = \epsilon_{1/2}^{\rm TT}\times(1 + b_{\rm TA}\delta) \, .
-\label{eq:tidal_th_deltaTT}
-\end{eqnarray}
- There are currently no theoretical models for $\delta$-TT, which means that predictions from this model are, at the moment, completely simulation-based.
-
-It is worth recalling here that other IA models exist in the literature, and that at this point observations are not precise enough to set strong constraints on them, further motivating our flexible multi-model approach.
-
-%\subsection{Likelihood}
-%\label{subsec:likelihood}
-
-%Multi-Gaussian likelihood, analytical Covariance matrix (Gauss + non-Gauss + SSC) from {\sc TJPCov}, Firecrown, sampler, priors.
-
-%---------------------
-\section{Simulations}
-\label{sec:sims}
-
-%-------------
-\subsection{Cosmic shear galaxy catalogues} 
-\label{subsec:WL_cats}
-
-The weak lensing simulations developed for this work are based on ray-tracing mass sheets produced from the Outer Rim $N$-body simulation \citep{OuterRim}, which evolved 10,240$^3$ particles in a (5.225 Gpc)$^3$ cosmological volume, assuming a flat $\Lambda$CDM cosmology with $\Omega_{\rm m}$=0.2648, $\Omega_{\rm b}$=0.0448, $h$=0.71, $\sigma_8$ = 0.801, $n_{\rm s}$= 0.963, $w_0$=-1.00.
-A total of 101 particle snapshots were originally saved, of which we use only those with $z<4.0$.
-Particles from each dump are assigned to curved mass shells approximately 114 Mpc thick, producing a sequence of 57 {\sc Healpix} maps $\delta(\theta,\phi,\chi_i)$ with {\sc nside} = 8192 and $i=1..57$, filling up a light-cone over an octant up to $z=3$.
-%More details on this procedure can be found  in \citet{cosmoDC}, where lensing quantities are computed specifically for the generation of the {\sc cosmoDC2}  synthetic sky catalogue.
-
-Ray-tracing is performed in the Born approximation, summing over the mass shells using the $\chi$-integral of Eq.
-(\ref{eq:C_ell}).
-A source plane is placed at the high-redshift edge of every mass planes, resulting in a series of convergence  maps  $\kappa(\theta,\phi,\chi_i)$ that are subsequently transformed into shear maps $\gamma_{1/2}(\theta,\phi,\chi_i)$ using the Kaiser-Squires methods \citep{KaiserSquires}, which is implemented via efficient {\sc HealPy alm2map} routines.
-
-We position galaxies in the light cone following exactly our chosen $N(z)$, and interpolate the shear quantities at their location. We follow two distinct algorithm to achieve this:
-\begin{enumerate}
-\item {\it Random:} galaxies RA and Dec are distributed randomly on the octant, thereby matching this fundamental assumptions in the NLA and TT models. 
-\item {\it Linear bias:} galaxies RA and Dec are sampled from the mass sheets smoothed\footnote{We also tried sampling the field with 0.1 and 0.5 $h^{-1}$Mpc but this resulted in noisier results.} over 1.0 $h^{-1}$Mpc (comoving), assuming a linear bias of $b_{\rm TA}$, now matching instead the assumptions of the $\delta$-NLA and $\delta$-TT models.
-With this method we produce galaxy positions assuming first $b_{\rm TA}=1.0$ (our fiducial case) and also $b_{\rm TA}=2.0$, enhancing the  model flexibility.
-\end{enumerate}
-
-Since source clustering is a higher order effect in cosmic shear, the measured $\xi_{\pm}$ from these three mocks (random, $b_{\rm TA}=1.0$ and $b_{\rm TA}=2.0$) show negligible differences ({\it to quantify and cite}).
-In contrast, the impact on the IA contamination is significant and can double the secondary signal in certain circumstances.
-The main explanation for this is that while clustered sources are uncorrelated with the foreground matter responsible for the lensing signal, the high-density regions they live are also subject to the largest tidal fields.
-
-%----------
-\subsection{Projected tidal fields}
-\label{subsec:IA_sims}
+\appendix
 
 \begin{figure*}
-\caption{Density field and the associated projected tidal field tensors.}
-\label{fig:maps}
+\includegraphics[width=\columnwidth]{graphs/xip_sims_vs_th.eps}
+\includegraphics[width=\columnwidth]{graphs/xim_sims_vs_th.eps}
+\caption{Fractional difference on $\xi_\pm$ between the measurements from SkySim5000 and the model predictions.  }
+\label{fig:frac_err_sims_th}
 \end{figure*}
-
-Our infusion method completely relies on couplings between intrinsic galaxy shapes and the local tidal field, hence the first step in our method consist in extracting the tidal field maps $s_{ij}(\theta,\phi,\chi_i)$ from the mass maps $\delta(\theta,\phi,\chi_i)$ that source them.
-In three dimensions, trace-free tidal tensor $s_{ij}(\boldsymbol x)$ can be obtained from the matter over-density field $\delta(\boldsymbol x)$ as   \citep{Catelan_IA_Tidal}:
-\begin{eqnarray}
- \widetilde{s}_{ij} (\boldsymbol k)  = \left[\frac{k_i k_j}{k^2} - \frac{\delta_{ij}}{3}\right]  \widetilde {\delta}(\boldsymbol k) \mathcal{G}(\sigma_{\rm G}) \, ,
- \label{eq:sij}
-\end{eqnarray}
-where $\mathcal{G}(\sigma_{\rm G})$ is a three-dimensional Gaussian function described by a single (free) parameter $\sigma_{\rm G}$ that  controls the physical scales which are allowed to affect the IA term in our model.
-Tilde symbols  denote Fourier transformed quantities,  the indices $(i,j)$ label the components of the Cartesian wave-vector $\boldsymbol{k}^T = (k_x,k_y,k_z)$, and $k^2 = k_x^2 + k_y^2 + k_z^2$. 
-As shown in \citet{Tidalator} for Cartesian coordinates, projected tidal fields  computed from projected mass sheets provide and excellent agreement with the NLA model, which in contrast computes the full tidal fields from the three-dimensional matter density and project along the radial dimension at the end.
-We promote this transformation to curved-sky in this work, exploiting the  polarisation {\sc alm2map} operations built in {\sc Healpy}.
-In particular, noting that $Q=s_{xx}-s_{yy}$, $U=s_{xy}$ and $\delta=s_{xx}+s_{yy}$, we compute the curved-sky tidal field tensors ${s}_{ij}({\boldsymbol \theta})$ as:
- \begin{eqnarray}
-s_{xx}({\boldsymbol \theta})  =  \left[\frac{ \delta + Q}{2}  - \frac{\delta}{3}\right] \, ,s_{yy}({\boldsymbol \theta})  =  \left[\frac{\delta - Q}{2}  - \frac{\delta}{3}\right] \, , s_{xy}({\boldsymbol \theta}) = U
- \label{eq:sij_2D_sph}
- \end{eqnarray}
-where the $U({\boldsymbol \theta})$ and $Q({\boldsymbol \theta})$ maps are smoothed by the Gaussian beam with width $\sigma_{\rm G}$.
-We suppress large artificial tidal fields at the maps boundary by replicating 8$\times$ the density maps defined on the octant and working on a full sky density $\delta$; we re-apply the octant mask on the tidal field maps after the operation.
-Note that the value of $\sigma_{\rm G}$ is a free parameter both in the infusion technique described in this paper and in the NLA and TATT models.
-We therefore explore two cases, $\sigma_{\rm G}=0.1$Mpc and 0.5Mpc, however this may be further optimised in the future.
-
-%are specified within the NLA model.
-Smoothing amounts to selecting physical scales that do not contribute to the alignment of galaxies, which is still a debatable quantity, but is also introduced for numerical stability.
-\citet{Blazek2015} argues that 1.0 $h^{-1}$Mpc could be a reasonable fiducial value, being larger then the typical halo size, but recognizes that one-halo terms are also required to better match the observations.
-In their later work, \citet{Blazek2019} do not include smoothing at all, and neither do the KiDS-1000 nor DES-Y1 analyses based on the NLA model \citep{KiDS1000_Asgari,DESY1_Troxel}.
-In this work we used a two-dimensional Gaussian filter and calibrated $\sigma_{\rm G}$ empirically to $\sigma_{\rm G}=0.1h^{-1}$Mpc (see Sec.
-\ref{subsubsec:sigma_G}), however these two choices are arbitrary and could possibly be better optimised in the future; we also explore $\sigma_{\rm G}=0.5h^{-1}$Mpc later on.
-We note that the smoothing scale is degenerate with the resolution of the simulation itself, and that one should use caution when smoothing on scales that approach the resolution limits.
-
-%We employ a numerical technique worth mentioning here: the Fourier transforms involved in computing Eq.
-(\ref{eq:sij_2D}) are computed from the full (projected) periodic boxes of the simulations, then interpolated on the light-cones.
-We find that tidal field computed directly from the $10\times10$ deg$^2$ light-cones introduces significant large scales features in the tidal field maps, largely caused by  the non-periodic boundary conditions, which our method avoids.
-Projected tidal field maps $s_{11}$, $s_{22}$ and $s_{12}$ are constructed that way for each mass sheets; Fig.
-\ref{fig:maps} shows the  three tidal fields and the mass maps for one of them.
-We can clearly see the connection between all maps around over-dense regions.
-{\it (Include a figure of $s_ij$ and $\delta$)}.
-
-{\it [Mention normalisation of the tidal fields by $0.6252 = H_0/114$ = 1/shell-thickness}
-
-%of every light-cones and interpolated at the position of every galaxy.
-Fig.
-\ref{fig:tidalator} illustrates this process for a small zoomed-in patch at $z\sim0$, starting from a $\delta_{2D}(\boldsymbol \theta)$ map (upper large panel), computing the tidal field components (middle four panels) and comparing the results with the cosmic shear signal generated by the same mass distribution (bottom two panels).
-The tidal field maps clearly reproduce the cosmic shear maps, and the minus sign in front of both terms in Eq.
-(\ref{eq:tidal_th}) causes the IA to undo some of the lensing signal.
-
-\subsection{Infusion of intrinsic alignments}
-\label{subsec:IA_infusion}
-
-Having now produced shear catalogues and tidal field maps, we can now use Eq.
-\ref{eq:tidal_th} to couple linearly the alignment of galaxies with the local tidal field, or Eq.
-\ref{eq:tidal_th_TT} to use instead a quadratic coupling.
-These allow us to compute the intrinsic ellipticities ${\boldsymbol \epsilon}^{\rm int}$ for the four IA models described in Sec.
-\ref{sec:IA_th}, which we combine with the cosmic shear signal ${\boldsymbol g}$ to compute observed ellipticities:
-\begin{eqnarray}
-{\boldsymbol \epsilon}^{\rm obs} = \frac{{\boldsymbol \epsilon}^{\rm int} + {\boldsymbol g}}{1 + {\boldsymbol \epsilon}^{\rm int}{\boldsymbol g^*}} \,, {\rm with \, \, } 
-{\boldsymbol \epsilon}^{\rm int}  = \frac{{\boldsymbol \epsilon}^{\rm IA} + {\boldsymbol \epsilon}^{\rm ran}}{1 + {\boldsymbol \epsilon}^{\rm IA}{\boldsymbol \epsilon^{\rm ran, *}}}.
-\label{eq:eps_obs}
-\end{eqnarray}
-In the above expressions, the denominators ensures that the combined  ellipticities never exceed unity.
-The complex spin-2 reduced shear ${\boldsymbol g} \equiv (\gamma_1 + {\rm i} \gamma_2)/(1+\kappa)$ is computed from the shear  $(\gamma_{1/2}$) and convergence ($\kappa$) maps, interpolated at the galaxy positions and redshifts.
-The  random orientation term ${\boldsymbol \epsilon}^{\rm ran}$ is drawn from two Gaussians (one per component) with their standard deviations matching the LSST-Y1 forecast, $\sigma_{\epsilon} = 027$.
-We further constraint  the random ellipticity to satisfy $|{\boldsymbol \epsilon}^{\rm ran}| \le 1.0$.
-%We recall that since our simulated galaxy catalogues trace the dark matter density, our default IA-infusion method  is consistent with the $\delta$-NLA model (see Sec.
-\ref{subsec:IA_th_ext}).
-Analytical predictions for the two-point functions are more involved in this case \citep[see][]{Blazek2019} and not yet available on the public {\sc cosmoSIS} release.
-We therefore validate our methods with the standard NLA first, which we infuse by `correcting' the $\delta$-NLA measurement with Eq.
-(\ref{eq:tidal_th_deltaNLA}), i.e.
-by replacing ${\boldsymbol \epsilon}^{\rm IA}$ by ${\boldsymbol \epsilon}^{\rm IA}/(1 + b_{\rm TA} \delta)$ in our simulations.
-Once again, these are less realistic but better suited for validation of the measured $\gamma$-2PCFs against a theoretical model; after this is established, we use the $\delta-$NLA catalogues as our fiducial infusion model.
-We re-iterate here that the same tidal fields, shear maps and IA coupling equations are used for the NLA and $\delta$-NLA models, and separately for the TT and $\delta$-TT models; these  only differ by the fact that in one case the galaxies are placed at random on the octant, while in the other case they are linearly tracing the dark matter.
-
-Also note that our current IA models make no differentiation between galaxy colours or type, and instead treats the full sample as a single population that has a single, effective, alignment signall \citep[see][for an example with a red/blue split]{DESY1_IA_Samuroff}.
-
-%---------------------
-\section{Validation with $\xi_{\pm}$}
-\label{sec:validation}
-
-% Requires the booktabs if the memoir class is not being used
-\begin{table}
-   \centering
-   %\topcaption{Table captions are better up top} % requires the topcapt package
-   \begin{tabular}{@{} lcr @{}} % Column formatting, @{} suppresses leading/trailing space
-      \hline
-      \hline
-       %\multicolumn{2}{c}{Item} \\
-      model   		& ($A_{\rm IA}, b_{\rm TA}, A_2)$ \\
-      \hline
-      NLA     		& {($\pm$1,0,0) }&  \\
-      \multirow{2}{*}{$\delta-$NLA }  	&   {($\pm$1,1,0)}   \\
-      							&  {(1,2,0)}   \\
-      TT 			&  {(0,0,$\pm$1)} &  \\
-      \multirow{2}{*}{$\delta$-TT} 	&  {(0,1,$\pm$1)}   \\
-      				&  {(0,2,1)}   \\
-      TATT- fiducial	&  { (1,1,1)}  \\
-      %TATT-DESY3	&   (-0.7,1,1.9) & \\
-      \hline
-      \hline
-
-   \end{tabular}
-   \caption{IA models infused in this work.}
-   \label{table:IAmodels}
-\end{table}
-
-%------------------------------
-\subsection{NLA model}
-\label{subsubsec:sigma_G}
-
-See Fig. \ref{fig:xi_NLA}
-%---------------
-\begin{figure*}
-%\includegraphics[width=\columnwidth]{graphs/frac_xip_IA1_skysim}
-\includegraphics[width=\columnwidth]{graphs/frac_xip_IA1_skysim_NLA_srd.jpg}
-\includegraphics[width=\columnwidth]{graphs/frac_xim_IA1_skysim_NLA_srd.jpg}
-\caption{Ratio between the shear correlation functions with and without IA, assuming the NLA model with $A_{\rm IA}=1.0$ both in the simulations and theory.
-Measurements shown in green and brown correspond to smoothing scales of 0.1 and 0.5 $h^{-1}$Mpc in the tidal field.
-There is no shape noise in the simulations, but it is included in the error bars.}
-\label{fig:xi_NLA}
-\end{figure*}
-%---------------
-
-%------------------------------
-\subsection{$\delta$-NLA model}
-\label{subsec:deltaNLA}
-
-See Fig. \ref{fig:xi_deltaNLA}.
-
-\begin{figure*}
-\includegraphics[width=\columnwidth]{graphs/frac_xip_IA1_skysim_deltaNLA_srd}
-\includegraphics[width=\columnwidth]{graphs/frac_xim_IA1_skysim_deltaNLA_srd}
-\caption{Same as Fig.
-\ref{fig:xi_NLA}, but for the $\delta$-NLA model with $A_{\rm IA}=1.0$ and $b_{\rm TA}=1.0$, and only for smoothing of 0.5$h^{-1}$Mpc.
-The dashed black lines show the NLA predictions to better highlight the differences.
-}
-\label{fig:xi_deltaNLA}
-\end{figure*}
-
-\begin{figure}
-\includegraphics[width=\columnwidth]{graphs/frac_xip_bta1_rescaled}
-\caption{Ratio between the shear correlation functions with and without IA in tomographic bin combination 2-5.
-The brown and green symbols show measurements from simulations constructed with $b_{\rm TA}$ = 0.0 and 2.0 respectively,  the black solid and dotted lines shown their predictions, while the blue symbols are obtained by rescaling $b_{\rm TA}$ = 1.0 simulations using Eq.
-\ref{eq:bta_rescale}.
-}
-\label{fig:xi_deltaNLA_rescaled}
-\end{figure}
-
-We verified that it works equally well for $b_{\rm TA}$ = 1.0 and 2.0.
-
-%------------------------------
-
-Using this, we $b_{\rm TA}$-rescale our $b_{\rm TA}=1.0$ mock to $b_{\rm TA}=2.0$ and to $0.0$ mocks.
-Results are shown in Fig.
-\ref{fig:xi_deltaNLA_rescaled} for one of the tomographic bin.
-It works reasonably well, but lower redshift are less accurate due to the increased  shot noise (not shown), hence we do not recommend using this.
-
-%------------------------------
-\subsection{TT model}
-\label{subsec:TT}
-
-See Fig. \ref{fig:xi_TT}
-
-\begin{figure*}
-\includegraphics[width=\columnwidth]{graphs/frac_xip_IA1_skysim_TT_srd.jpg}
-\includegraphics[width=\columnwidth]{graphs/frac_xim_IA1_skysim_TT_srd.jpg}
-\caption{Same as Fig. \ref{fig:xi_NLA}, but for the TT model with $A_2=1.0$. Here, the dashed black lines show the NLA predictions to better highlight the differences. }
-\label{fig:xi_TT}
-\end{figure*}
-
-\begin{figure*}
-%\includegraphics[width=\columnwidth]{graphs/frac_xip_C2_m1_skysim_deltaTT}
-\includegraphics[width=\columnwidth]{graphs/frac_xip_IA1_skysim_deltaTT_srd.jpg}
-\includegraphics[width=\columnwidth]{graphs/frac_xim_IA1_skysim_deltaTT_srd.jpg}
-\caption{Same as Fig. \ref{fig:xi_deltaNLA}, but comparing the TT and the $\delta$-TT models, with $A_2=1.0$, $b_{\rm TA}$ = 1.0, and only for smoothing of 0.5$h^{-1}$Mpc. }
-\label{fig:xi_deltaTT}
-\end{figure*}
-
-To match the theory, we need to apply the following calibration: $\epsilon^{\rm IA, TT}(z<0.5) \rightarrow \epsilon^{\rm IA, TT} /2.5$.
-
-%------------------------------
-\subsection{$\delta$-TT model}
-\label{subsec:TT}
-
-See Fig. \ref{fig:xi_deltaTT}
-
-To match the TT theory, we need to apply the following calibration: $\epsilon^{\rm IA, TT}(z<0.5) \rightarrow \epsilon^{\rm IA, TT} /5.0$, followed by $\epsilon^{\rm IA, TT} \rightarrow \epsilon^{\rm IA, TT}/7.0$.
-
-%\subsection{Validation with full inference}
- %\label{sec:inference}
-
-%priors, firecrown, Takahashi $P(k)$
-
-\section{Higher-order weak lensing statistics}
-\label{sec:HOWLS}
-
-... use the mocks from Table \ref{table:IAmodels} to compute derivatives. Show.
-
-%----------
-\section{Conclusions}
-\label{sec:conclusion}
-%----------
-
-\section*{Acknowledgements}
-
-JHD acknowledges support from an STFC Ernest Rutherford Fellowship (project reference ST/S004858/1).
-Ray-tracing computations were carried on the NERSC [acknowledgments] ...
-HACC [acknowledgements] ...
-OuterRim [Acknowledgments]
-\\
-
-Some of the results in this paper have been derived using the {\sc healpy} and {\sc HEALPix} packages.
-\\
-\\
-\\
-{\footnotesize All authors contributed to the development and writing of this paper. JHD led the analysis.... }
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Data Availability}
-
-%The SLICS numerical simulations can be found at http://slics.roe.ac.uk/, while the cosmo-SLICS can be made available upon request.
-
-%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%
-
-% The best way to enter references is to use BibTeX:
-
-\bibliographystyle{hapj}
-\bibliography{IA} % if your bibtex file is called example.bib
-
-% Alternatively you could enter them by hand, like this:
-% This method is tedious and prone to error if you have lots of references
-%\begin{thebibliography}{99}
-%\bibitem[\protect\citeauthoryear{Author}{2012}]{Author2012}
-%Author A.~N., 2013, Journal of Improbable Astronomy, 1, 1
-%\bibitem[\protect\citeauthoryear{Others}{2013}]{Others2013}
-%Others S., 2012, Journal of Interesting Stuff, 17, 198
-%\end{thebibliography}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%% APPENDICES %%%%%%%%%%%%%%%%%%%%%
-
-\appendix
 
@@
 In the TATT model, the total intrinsic ellipticity component is therefore given by $\epsilon_{1/2}^{\rm IA} = \epsilon_{1/2}^{\rm TATT} = \epsilon_{1/2}^{\delta{\rm-NLA}} + \epsilon_{1/2}^{\rm TT}$.
-
-% Don't change these lines
-\bsp	% typesetting comment
-\label{lastpage}
-\end{document}
-
-% End of mnras_template.tex

### 2024-03-27 sections/5_validation.tex
Changes made by Niko

--- 2023-11-13 paper_IA.tex
@@
-% mnras_template.tex 
-%
-% LaTeX template for creating an MNRAS paper
-%
-% v3.0 released 14 May 2015
-% (version numbers match those of mnras.cls)
-%
-% Copyright (C) Royal Astronomical Society 2015
-% Authors:
-% Keith T. Smith (Royal Astronomical Society)
-
-% Change log
-%
-% v3.0 May 2015
-%    Renamed to match the new package name
-%    Version number matches mnras.cls
-%    A few minor tweaks to wording
-% v1.0 September 2013
-%    Beta testing only - never publicly released
-%    First version: a simple (ish) template for creating an MNRAS paper
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Basic setup. Most papers should leave these options alone.
-%\documentclass[fleqn,usenatbib]{mnras}
-\documentclass[useAMS,usenatbib]{mn2e}
-
-% MNRAS is set in Times font. If you don't have this installed (most LaTeX
-% installations will be fine) or prefer the old Computer Modern fonts, comment
-% out the following line
-%\usepackage{newtxtext,newtxmath}
-% Depending on your LaTeX fonts installation, you might get better results with one of these:
-%\usepackage{mathptmx}
-%\usepackage{txfonts}
-
-% Use vector fonts, so it zooms properly in on-screen viewing software
-% Don't change these lines unless you know what you are doing
-%\usepackage[T1]{fontenc}
-
-% Allow "Thomas van Noord" and "Simon de Laguarde" and alike to be sorted by "N" and "L" etc. in the bibliography.
-% Write the name in the bibliography as "\VAN{Noord}{Van}{van} Noord, Thomas"
-%\DeclareRobustCommand{\VAN}[3]{#2}
-%\let\VANthebibliography\thebibliography
-%\def\thebibliography{\DeclareRobustCommand{\VAN}[3]{##3}\VANthebibliography}
-
-%%%%% AUTHORS - PLACE YOUR OWN PACKAGES HERE %%%%%
-\input{abbrev}
-\input{psfig.sty}
-
-\usepackage{graphicx}
-\usepackage{epsfig}
-\usepackage{amssymb}
-\usepackage{amsmath}
-\usepackage{amsfonts}
-\usepackage{txfonts}
-\usepackage{multirow}
-\usepackage{afterpage}
-\usepackage{xcolor}
-%\usepackage[draft]{hyperref}
-%\usepackage{ulem} % allows for strikethrough with \sout{}
-
-%\usepackage[paperheight=10in,paperwidth=8.5in]{geometry}
-
-\setlength{\topmargin}{-0.8in}
-\paperheight 11in
-\paperwidth 8.5in
-%\setlength{\textheight}{9.8in}
-%\setlength{\textwidth}{7.3in}
-\setlength{\textheight}{9.5in}
-\setlength{\textwidth}{7.1in}
-
-\definecolor{mypink1}{rgb}{0.858, 0.188, 0.478}
-\definecolor{mygreen1}{rgb}{0.258, 0.788, 0.878}
-\definecolor{myorange1}{rgb}{0.5, 0.2, 0.2}
-\newcommand{\NM}[1]{\textcolor[RGB]{0,150,0}{#1}}
-\newcommand{\RR}[1]{\textcolor{blue}{#1}}
-\newcommand{\JHD}[1]{\textcolor{mypink1}{#1}}
-\newcommand{\snr}{$\mathcal{S}/\mathcal{N}$ }
-\newcommand{\mycomment}[1]{}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%% AUTHORS - PLACE YOUR OWN COMMANDS HERE %%%%%
-
-% Please keep new commands to a minimum, and use \newcommand not \def to avoid
-% overwriting existing commands. Example:
-%\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%
-
-% Title of the paper, and the short title which is used in the headers.
-% Keep the title short and informative.
-\title[Lensing beyond 2pt: accounting for IA]{Intrinsic alignments from projected tidal fields: non-linear  impact on cosmic shear probes}
-
-% The list of authors, and the short list which is used in the headers.
-% If you need two or more lines of authors, add an extra line using \newauthor
-\author[J. Harnois-D\'{e}raps et al.]{Joachim Harnois-D\'{e}raps$^{1}$\thanks{E-mail: joachim.harnois-deraps@ncl.ac.uk} and others
-\\
-% List of institutions
-$^{1}$School of Mathematics, Statistics and Physics, Newcastle University, Herschel Building, NE1 7RU, Newcastle-upon-Tyne, UK\\
-}
-
-% These dates will be filled out by the publisher
-\date{Accepted XXX. Received YYY; in original form ZZZ}
-
-% Enter the current year, for the copyright statements etc.
-\pubyear{2021}
-
-% Don't change these lines
-\begin{document}
-\label{firstpage}
-\pagerange{\pageref{firstpage}--21}
-%\pagerange{\pageref{firstpage}--\pageref{lastpage}}
-\maketitle
-
-% Abstract of the paper
-\begin{abstract}
-TBD
-\end{abstract}
-
-% Select between one and six entries from the list of approved keywords.
-% Don't make up new ones.
-\begin{keywords}
-Gravitational lensing: weak -- Methods: numerical -- Cosmology: dark matter, dark energy \& large-scale structure of Universe 
-\end{keywords}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%% BODY OF PAPER %%%%%%%%%%%%%%%%%%
-
-%----------
-\section{Introduction}
-\label{sec:intro}
-%----------
-
-Cosmology, gravitational lensing, cosmic shear, 2pt, beyond-2pt, simulations for signal and for secondary signal/systematics, IA-infusion, this paper...
-
- %----------
-\section{Cosmic shear}
-\label{sec:theory}
-%----------
-
-As mentioned in the introduction, cosmic shear can be measured and modelled from a variety of methods, many of which are used in this paper and presented in this section.  
-%-------------------------
-\subsection{$\gamma$-2PCF}
-\label{subsec:wl-th}
-
-%---------------
-\begin{figure}
-\includegraphics[width=\columnwidth]{graphs/Nz}
-\caption{Redshift distribution in our simulations, taken from the Year-1 specifications of the LSST Science Requirement Document \citep{LSST-SRD} {[\it check Y1 vs Y10}].}
-\label{fig:Nz}
-\end{figure}
-%--------------
-
- Shear two-point correlation functions ($\gamma$-2PCFs hereafter) can be predicted with percent-level precision and are therefore an ideal quantity to validate weak lensing simulations.
-In the Limber approximation\footnote{See \citet{Kilbinger17} for a comparison between the Limber approximation and the exact calculations.}, the lensing power spectrum $C^{ij}_{\ell}$ is obtained from an integral over the three-dimensional matter power spectrum $P_{\delta}(k,z)$:
-  \begin{eqnarray}
-C_{\ell}^{ij} = \int_0^{\chi_{\rm H}}  \frac{q^i(\chi) \,q^j(\chi)}{\chi^2} \, P_{\delta}\, \bigg(\frac{\ell+1/2}{\chi},z(\chi)\bigg) \ {\rm d}\chi,
-\label{eq:C_ell}
-\end{eqnarray}
-where $\chi_{\rm H}$ is the co-moving distance to the horizon, $c$ is the speed of light, $H_0$ the Hubble parameter,  and the  lensing kernels $q^{i}$ are given by:
-\begin{eqnarray}
-q^i(\chi) = \frac{3}{2}\Omega_{\rm m} \, \bigg(\frac{H_0}{c} \bigg)^2 \frac{\chi}{a(\chi)} \int_{\chi}^{\chi_{\rm H}} n^i(\chi')\frac{{\rm d}z}{{\rm d} \chi'}\frac{\chi' - \chi}{\chi'}{\rm d}\chi' \, .
-\label{eq:q_lensing}
-\end{eqnarray}
-In the previous expression, $n^i(z)$ refers to the redshift distribution  in tomographic bin `$i$', while $a(\chi)$ is the scale factor at comoving distance $\chi$ from the observer {[\it might need to define $\Omega_m$ here]}.
- The matter power spectrum is computed from  {\sc Halofit} \citep{Takahashi2012}, however  other public tools provide $P_{\delta}(k,z)$ predictions, including e.g.
-{\sc HMcode} \citep{HMCode2020}, the {\sc EuclidEmulator} \citep{EuclidEmulator}, the {\sc BACCO} emulator \citep{BACCOEmulator} or the Mira Titan emulator \citep{miraTitan}.
- Predictions for the $\gamma$-2PCFs are finally computed from Eq. (\ref{eq:C_ell}) as:
- \begin{eqnarray}
-\xi_{\pm}^{ij}(\vartheta) = \frac{1}{2\pi}\int_0^{\infty} C_{\ell}^{ij} \, J_{0/4}(\ell \vartheta) \, \ell \, {\rm d}\ell,
-\label{eq:xipm_th}
-\end{eqnarray}
-where $J_{0/4}(x)$ are Bessel functions of the first kind.
-In this paper, these calculations are carried out by {\sc pyccl}\footnote{{\sc pyccl}:pypi.org/project/pyccl}  \citep{CCL} {\it or do we use cosmosis in the end?]}.
-The $n^i(z)$ are taken from the LSST Science Requirement Document \citep{LSST-SRD} and given by
- \begin{eqnarray}
-n(z) = N_0 z^2 {\rm exp} \left[-\left(\frac{z}{z_0}\right)^\alpha \right]\, ,
-\label{eq:nz}
-\end{eqnarray}
-with $(z_0, \alpha) = (0.13, 0.78)$ and $N_0$ normalised to provide a number density of $n_{\rm eff}$ = 3.0 gal arcmin$^{-2}$.
-This lower than the expected number density for the first data release ($n_{\rm eff}\sim10$ gal arcmin$^{-2}$), but is large enough to validate our methods, and makes the calculation more tractable.
-The $n(z)$ is further split into five equi-populated tomographic bins, and smoothed with a Gaussian filter of width $\sigma = 0.05(1+z)$ in order to mimic the photometric selection process [{\it confirm with Niko}].
-The resulting distributions\footnote{The construction of these tomographic $n(z)$ can be reproduced in {github...CCL\_SRD\_Niko}.} are shown in Figure \ref{fig:Nz}.
-
-The cosmic shear signal can be measured from the ellipticities $\epsilon_{1/2}$ of simulated or observed galaxies, which, in absence of systematics and secondary signals, are unbiased estimators  of the cosmic shear components $\gamma_{1/2}$.
-The $\gamma$-2PCF are then estimated as:
- \begin{eqnarray}
- \widehat{\xi_{\pm}^{ij}}(\vartheta) = \frac{\sum_{a,b} w_a w_b \left[\epsilon_{a, \rm t}^i\epsilon_{b, \rm t}^j     \pm \epsilon_{a, \times}^i\epsilon_{b, \times}^j    \right]\Delta_{ab}(\vartheta)}{\sum_{a,b} w_a w_b} \, ,
- \label{eq:2PCF_estimator}
-  \end{eqnarray}
-where the sum is over all pairs of galaxies $a,b$ separated by an angular separation $\vartheta$, taken from tomographic bins $i,j$.
-The tangential/cross components of their ellipticities are denoted as $\epsilon_{\rm t/\times}$, respectively.
-$\Delta_{ab}(\vartheta)$ is the binning operator, equal to unity if the angular separation between the two galaxies falls within the $\vartheta$-bin, and zero otherwise, and the shape weights $w_{a,b}$ are set to unity.
-In this paper, we construct lensing catalogues from numerical simulations (described in Sec.
-\ref{sec:sims}), from which we measure $ \widehat{\xi_{\pm}^{ij}}(\vartheta)$ with {\sc Treecorr} \citep{TreeCorr}.
-We set therein the {\sc bin\_slop} parameter to 0.05, then compute the correlations in nine logarithmically-spaced angular bins ranging from 0.5 to 475.5 arcmin.
-
- %-------------------------
-\subsection{Beyond-2pt}
-\label{subsec:beyond-2pt}
-
-Non-Gaussian statistics, often referred to `beyond-2pt' statistics, have the potential to extract cosmological information stored in the complex phases of the density field, whereas two-point functions such as the $\gamma$-2PCF can only access that encoded in the complex amplitudes.
-No optimal estimator has been identified to-date as being able to capture `all' information, but the numerous studies presented in the introduction all show a clear gain in constraining power, especially when used in combination with 2pt functions.
-Some of these take as input the galaxy catalogues directly, while others require instead convergence maps.
-Therefore, we produce convergence maps from the catalogues by assigning the shear signal onto spherical {\sc Healpix}\footnote{{\sc Healpix}: http://healpix.sf.net}  maps \citep{healpix} with $N_{\rm side}=4096$, then using the standard Kaiser \& Squires inversion technique \citep{KaiserSquires} implemented in {\sc healpy} to reconstruct a convergence maps with the same angular resolution, including a baseline 2.0 arcmin smoothing beam in the inverse transform.
-Note that this smoothing scales is quite small; some probes are difficult to model in that case, and would instead prefer larger smoothing scales.
-We take this into account on a case-by-case basis, as described below.
-
-  {\it [Discuss tomography...]}
-
-\subsubsection{Catalogue-based estimators}
-
-We consider the following shear-based estimators:
-\begin{enumerate}
-\item The squeezed bispectrum, has theoretical model (Anik, can you summarise the measurements and modelling, and provide references?)
-\end{enumerate}
-
-\subsubsection{Convergence-based estimators}
-
-\begin{enumerate}
-\item Convergence three-point correlation function: (Alejandro, can you summarise the measurements and modelling, and provide references?)
-\item Peaks and Minima: local maxima and minima in the {\sc Healpix} convergence maps are counted in bins of signal-to-noise ratios, $\nu$.
-This is one of the most widely used non-Gaussian lensing statistics as it is simple to measure.
-Theoretical models have been developed to describe the largest peaks \citep[see][]{Shan18, HSCY1_Peaks_th}, however we report here the results on a much wider range of statistics, which can only be accurately modelled from numerical simulations, as in \citet{HD21, DESY3_Zuercher, HSCY1_Peaks_Sims, HD23}.
-\item Lensing PDF, has theoretical model (Cora/Lina, can you summarise the measurements and modelling, and provide references?)
-\item Map2 and Map3, has theoretical model  (Laila, can you summarise the measurements and modelling, and provide references?)
-\item Minkowski functionals (Nisha, can you summarise the measurements and modelling, and provide references?)
-\end{enumerate}
-
- %-------------------
- \section{Intrinsic alignment models}
- \label{sec:IA_th}
- %-------------------
-
-Galaxies interact with the tidal forces caused by the large-scale structure  they live in, causing their intrinsic shapes to acquire correlated alignments that has nothing to do with the correlations caused by weak lensing.
-This therefore acts as a secondary signal that contaminates the shape correlation measurements carried out in a cosmic shear analysis.
-There is no consensus on the actual physical model that describes the IA signal, and even when adopting these, the free parameters they contain are only weakly constrained from the data \citep[see][for reviews]{IA_review1, IA_review2}.
-%The most widely used model in the literature is the non-linear alignment model of \citet{NLA}, however it is now recognised that this is an effective model with limited precision, and the community is now progressively shifting towards more complex models.
-In this paper we consider four such IA models that we describe in the following sub-sections.
-In all cases, our models couple the galaxy intrinsic shapes with the local over-density and projected tidal field , then prescribe an intrinsic ellipticity tensor $\gamma_{ij}^{\rm IA}$, from which observed ellipticities are extracted as:
- \begin{eqnarray}
-\epsilon_{1}^{\rm IA} = \gamma_{xx}^{\rm IA} - \gamma_{yy}^{\rm IA} \, , \hspace{1.5cm}\epsilon_{2}^{\rm IA} = 2 \gamma_{xy}^{\rm IA}\, .
-\label{eq:tidal_th_deltaNLA}
-\end{eqnarray}
-
-\subsection{Non-linear alignment (NLA)}
-
-%The observed ellipticity of a galaxy ${\boldsymbol \epsilon}_{\rm obs} $ is a combination of its intrinsic shape ${\boldsymbol \epsilon}_{\rm int}$ and a cosmic shear signal ${\boldsymbol \gamma}$, the former of which can be further divided in a random component ${\boldsymbol \epsilon}^{\rm ran}$ and an alignment term ${\boldsymbol \epsilon}^{\rm IA}$.
-The NLA model of \citet{NLA} is the most widely used IA model in the cosmic shear literature thus far.
-According to the NLA, IA are caused by a linear coupling between galaxy shapes and the non-linear large-scale tidal field at the galaxy position.
-In the context of  two-point functions, these intrinsic shapes contribute to an intrinsic-intrinsic ($II$) term and an intrinsic-shear coupling ($GI$) term \citep{Hirata2004}, both secondary signals to the true cosmic shear ($GG$) term, with the latter typically dominating the IA sector in cross-tomographic measurements.
-The $II$ and $GI$ terms  can be both computed from the matter power spectrum as:
- \begin{eqnarray}
-P_{II}(k,z) =  \left(\frac{A_{\rm IA}\bar{C_1}\bar{\rho}(z)}{D(z)}\right)^2a^4(z) P_{\delta}(k,z)
-\label{eq:Pk_II_th}
-\end{eqnarray}
-and
- \begin{eqnarray}
-P_{GI}(k,z) = - \frac{A_{\rm IA}\bar{C_1}\bar{\rho}(z)}{D(z)}a^2(z) P_{\delta}(k,z) \, ,
-\label{eq:Pk_GI_th}
-\end{eqnarray}
-which can then be past to the Limber integration (Eqs. \ref{eq:C_ell} and \ref{eq:xipm_th}) to compute  the secondary signals $\xi_{\pm}^{II}(\vartheta)$ and $\xi_{\pm}^{GI}(\vartheta)$. 
-In the above expression,  $D(z)$ is the linear growth factor, $\bar{\rho}(z)$ is the mean matter density at redshift $z$ and $\bar{C_1}=5\times 10^{-14} M_{\odot}^{-1} h^{-2} {\rm Mpc}^3$ is a constant calibrated in \citet{Brown2002}.
-The strength of the tidal coupling is modulated by the amplitude parameter $A_{\rm IA}$, which is the main NLA parameter constrained by current cosmic shear surveys.
-Note that this model can be augmented by redshift and luminosity dependences, however we do not use these here.
-
-The NLA intrinsic ellipticities $\epsilon_{1,2}^{\rm NLA}$ are related to tidal field $s_{ij}$ by:
- \begin{eqnarray}
-\epsilon_1^{\rm NLA} = - \frac{A_{\rm IA}\bar{C_1}\bar{\rho}(z)}{D(z)} (s_{xx} - s_{yy}) \,\,\,\,,   \epsilon_2^{\rm NLA} = - \frac{2 A_{\rm IA}\bar{C_1}\bar{\rho}(z)}{D(z)} s_{xy}\;,
-\label{eq:tidal_th}
-\end{eqnarray}
-where $s_{ij} = \partial_{ij}\phi$ are the Cartesian components of the tidal tensor of the gravitational potential.
-Note that the term `non-linear' in the model name can be  misleading, as it refers to the non-linear matter power spectrum $P(k)$ that is used in its calculations; the coupling between the intrinsic galaxy shapes and the tidal field is still linear.
-Eq.( \ref{eq:tidal_th}) is used to assign intrinsic ellipticities to galaxies, given maps of the tidal field components $s_{xx}$, $s_{yy}$ and $s_{xy}$ (see Sec.
-\ref {subsec:IA_infusion}).
-
-\subsection{$\delta$-NLA}
-\label{subsec:IA_th_ext}
-
-%[{\it here}]
-
-%As discussed later, the key quantity of interest to cosmic shear analysis is not the tidal tensor itself but its trace-free version, since shape correlations with the density field are subdominant, even though peaks in high density environments are less elliptical on average.
-Consequently, the model itself has a restricted range of validity: on small scales, higher order couplings to the ellipticity field ${\boldsymbol \epsilon}^{\rm IA}$  become important, however these are neglected in the NLA model.
-Only the non-linear evolution of the tidal tensor itself is taken into account, since it does fit observations quite well.
-
-%We note that the NLA predicts additional higher-order terms and non-zero $B$-modes \citep{Hirata2004} that we neglect  in this analysis.
-Also, as shown in \citet{IA_EFT}, the NLA model can be interpreted as the lowest order description of the alignment process of galaxies in the light of an effective field theory description.
-
-The NLA model presented in the last section has been widely used in cosmic data analyses, but it has important known limitations and is therefore bound to fail at describing the IA signal with high precision.
-A perturbation theory extension to the NLA has been introduced in \citet{Blazek2015} and  \citet{Blazek2019},  where it is recognised that higher order couplings could be important and should be considered.
-The first additional term to be included is the over-density weighting term, which is caused by the fact that the intrinsic alignment of galaxies can only be observed at the galaxy positions, which are not distributed randomly on the sky but instead trace the underlying matter density,  `$\delta$', although the exact biasing scheme is not currently know.
-Accounting for this extra term in theoretical predictions is done with one-loop perturbation theory  \citep{Blazek2019}, and is implemented in {\sc pyccl}.
-Physically, it corresponds to adding a $\delta$-weight to the NLA predictions at the local galaxy positions, effectively representing the different tracer properties.
-At the level of numerical simulations, this could be done in principle simply by augmenting the NLA ellipticities with this weight, namely:
- \begin{eqnarray}
-\epsilon_{1/2}^{\delta-\rm NLA} = \epsilon_{1/2}^{\rm NLA}\times(1 + b_{\rm TA}\delta) \, ,
-\label{eq:tidal_th_deltaNLA}
-\end{eqnarray}
-where the term $b_{\rm TA}$ corresponds to the (largely unconstrained) biasing relation between these source galaxies and the underlying matter field.
-In practice, however, we find that this is noisy, and that it is instead preferable to generate mocks catalogues with the biasing scheme directly applied when assigning galaxy positions, after which no weighting is necessary.
-Nevertheless, Eq.
-(\ref{eq:tidal_th_deltaNLA}) can be used to modify the value of $b_{\rm TA}$.
-Indeed, from a mock with a given bias $b_{\rm TA, orig}$, we can rescale the IA contribution to a different $b_{\rm TA, new}$  as:
-\begin{eqnarray}
-{\boldsymbol \epsilon}^{\rm int}_{b_{\rm TA, new}}  = \frac{(1 + b_{\rm TA, new}\delta)}{(1 + b_{\rm TA, orig}\delta)}{\boldsymbol \epsilon}^{\rm int}_{b_{\rm TA, orig}} \, .
-\label{eq:bta_rescale}
-\end{eqnarray}
-
-Compared to the NLA, the $\delta$-NLA is a stronger IA model, especially on small scales \citep{Blazek2019}, and seems to be preferred by some hydrodynamical simulations \citep{Hilbert_IA2017}.
-It is also better motivated from a physical point of view, since we know that the galaxies trace dark matter  and are not randomly distributed in our Universe as the NLA assumes.
-
-%-----------------------------------
-\subsection{Tidal Torque (TT)}
-\label{subsec:IA_th_TT}
-
-As shown in \citet{Blazek2019}, one-loop perturbative calculations include another term, by which galaxies acquire an intrinsic alignment via a coupling between their angular momentum and the tidal field, which can be re-expressed as a quadratic coupling between the tidal field and the shape.
-In this tidal torque model (TT), intrinsic ellipticities are given by:
-\begin{eqnarray}
-\gamma_{ij}^{\rm IA, TT} = C_2 \left[ \sum_{k=x,y,z} s_{ik} s_{kj} -\frac{1}{3} \delta_{ij} s^2 \right] \, ,
-\label{eq:tidal_th_TT}
-\end{eqnarray}
-where 
-\begin{eqnarray}
-C_2 = \frac{5 A_2 \bar{C_1} \Omega_{\rm m} \rho_{\rm crit}}{D^2(z)} \,  = \left[ \frac{-5 A_2}{A_1 D(z)} \right] C_1.
-\end{eqnarray}
-Under the approximation that line-of-sight alignments are mostly suppressed from cosmic shear measurement due to the broad lensing kernels, 
-we show in  Appendix \ref{app:2d_TT} that the terms inside the square bracket in Eq. (\ref{eq:tidal_th_TT}) leads to:
-\begin{eqnarray}
-\epsilon_1^{\rm TT} = C_2  \left[ s_{xx}^2 - s_{yy}^2\right] \, , \epsilon_2^{\rm TT} = 2 C_2 s_{xy}\left[s_{xx}+s_{yy}  \right]\, ,
-\end{eqnarray}
-both quadratic in the tidal field components.
-
-%-----------------------------------
-\subsection{$\delta$-TT}
-\label{subsec:IA_th_TT}
-
-Following the relation between the NLA and the $\delta$-NLA model, galaxies in the TT model are also assume to be randomly scattered on the sky, which we know to be a bad approximation.
-Computing the next-order contribution to the TT model involves two-loop perturbation theory calculations that have not been done yet due to the significantly higher complexity of such task.
-in simulations however, the $\delta$-weighting term is straight-forward to implement, as it involves to simply infuse the TT model onto galaxies that trace the matter field with a non-zero biasing factor.
-As for the $\delta$-NLA model, the $\delta$-TT ellipticities can  be related to the TT model as:
-\begin{eqnarray}
-\epsilon_{1/2}^{\delta-\rm TT} = \epsilon_{1/2}^{\rm TT}\times(1 + b_{\rm TA}\delta) \, .
-\label{eq:tidal_th_deltaTT}
-\end{eqnarray}
- There are currently no theoretical models for $\delta$-TT, which means that predictions from this model are, at the moment, completely simulation-based.
-
-It is worth recalling here that other IA models exist in the literature, and that at this point observations are not precise enough to set strong constraints on them, further motivating our flexible multi-model approach.
-
-%\subsection{Likelihood}
-%\label{subsec:likelihood}
-
-%Multi-Gaussian likelihood, analytical Covariance matrix (Gauss + non-Gauss + SSC) from {\sc TJPCov}, Firecrown, sampler, priors.
-
-%---------------------
-\section{Simulations}
-\label{sec:sims}
-
-%-------------
-\subsection{Cosmic shear galaxy catalogues} 
-\label{subsec:WL_cats}
-
-The weak lensing simulations developed for this work are based on ray-tracing mass sheets produced from the Outer Rim $N$-body simulation \citep{OuterRim}, which evolved 10,240$^3$ particles in a (5.225 Gpc)$^3$ cosmological volume, assuming a flat $\Lambda$CDM cosmology with $\Omega_{\rm m}$=0.2648, $\Omega_{\rm b}$=0.0448, $h$=0.71, $\sigma_8$ = 0.801, $n_{\rm s}$= 0.963, $w_0$=-1.00.
-A total of 101 particle snapshots were originally saved, of which we use only those with $z<4.0$.
-Particles from each dump are assigned to curved mass shells approximately 114 Mpc thick, producing a sequence of 57 {\sc Healpix} maps $\delta(\theta,\phi,\chi_i)$ with {\sc nside} = 8192 and $i=1..57$, filling up a light-cone over an octant up to $z=3$.
-%More details on this procedure can be found  in \citet{cosmoDC}, where lensing quantities are computed specifically for the generation of the {\sc cosmoDC2}  synthetic sky catalogue.
-
-Ray-tracing is performed in the Born approximation, summing over the mass shells using the $\chi$-integral of Eq.
-(\ref{eq:C_ell}).
-A source plane is placed at the high-redshift edge of every mass planes, resulting in a series of convergence  maps  $\kappa(\theta,\phi,\chi_i)$ that are subsequently transformed into shear maps $\gamma_{1/2}(\theta,\phi,\chi_i)$ using the Kaiser-Squires methods \citep{KaiserSquires}, which is implemented via efficient {\sc HealPy alm2map} routines.
-
-We position galaxies in the light cone following exactly our chosen $N(z)$, and interpolate the shear quantities at their location. We follow two distinct algorithm to achieve this:
-\begin{enumerate}
-\item {\it Random:} galaxies RA and Dec are distributed randomly on the octant, thereby matching this fundamental assumptions in the NLA and TT models. 
-\item {\it Linear bias:} galaxies RA and Dec are sampled from the mass sheets smoothed\footnote{We also tried sampling the field with 0.1 and 0.5 $h^{-1}$Mpc but this resulted in noisier results.} over 1.0 $h^{-1}$Mpc (comoving), assuming a linear bias of $b_{\rm TA}$, now matching instead the assumptions of the $\delta$-NLA and $\delta$-TT models.
-With this method we produce galaxy positions assuming first $b_{\rm TA}=1.0$ (our fiducial case) and also $b_{\rm TA}=2.0$, enhancing the  model flexibility.
-\end{enumerate}
-
-Since source clustering is a higher order effect in cosmic shear, the measured $\xi_{\pm}$ from these three mocks (random, $b_{\rm TA}=1.0$ and $b_{\rm TA}=2.0$) show negligible differences ({\it to quantify and cite}).
-In contrast, the impact on the IA contamination is significant and can double the secondary signal in certain circumstances.
-The main explanation for this is that while clustered sources are uncorrelated with the foreground matter responsible for the lensing signal, the high-density regions they live are also subject to the largest tidal fields.
-
-%----------
-\subsection{Projected tidal fields}
-\label{subsec:IA_sims}
-
-\begin{figure*}
-\caption{Density field and the associated projected tidal field tensors.}
-\label{fig:maps}
-\end{figure*}
-
-Our infusion method completely relies on couplings between intrinsic galaxy shapes and the local tidal field, hence the first step in our method consist in extracting the tidal field maps $s_{ij}(\theta,\phi,\chi_i)$ from the mass maps $\delta(\theta,\phi,\chi_i)$ that source them.
-In three dimensions, trace-free tidal tensor $s_{ij}(\boldsymbol x)$ can be obtained from the matter over-density field $\delta(\boldsymbol x)$ as   \citep{Catelan_IA_Tidal}:
-\begin{eqnarray}
- \widetilde{s}_{ij} (\boldsymbol k)  = \left[\frac{k_i k_j}{k^2} - \frac{\delta_{ij}}{3}\right]  \widetilde {\delta}(\boldsymbol k) \mathcal{G}(\sigma_{\rm G}) \, ,
- \label{eq:sij}
-\end{eqnarray}
-where $\mathcal{G}(\sigma_{\rm G})$ is a three-dimensional Gaussian function described by a single (free) parameter $\sigma_{\rm G}$ that  controls the physical scales which are allowed to affect the IA term in our model.
-Tilde symbols  denote Fourier transformed quantities,  the indices $(i,j)$ label the components of the Cartesian wave-vector $\boldsymbol{k}^T = (k_x,k_y,k_z)$, and $k^2 = k_x^2 + k_y^2 + k_z^2$. 
-As shown in \citet{Tidalator} for Cartesian coordinates, projected tidal fields  computed from projected mass sheets provide and excellent agreement with the NLA model, which in contrast computes the full tidal fields from the three-dimensional matter density and project along the radial dimension at the end.
-We promote this transformation to curved-sky in this work, exploiting the  polarisation {\sc alm2map} operations built in {\sc Healpy}.
-In particular, noting that $Q=s_{xx}-s_{yy}$, $U=s_{xy}$ and $\delta=s_{xx}+s_{yy}$, we compute the curved-sky tidal field tensors ${s}_{ij}({\boldsymbol \theta})$ as:
- \begin{eqnarray}
-s_{xx}({\boldsymbol \theta})  =  \left[\frac{ \delta + Q}{2}  - \frac{\delta}{3}\right] \, ,s_{yy}({\boldsymbol \theta})  =  \left[\frac{\delta - Q}{2}  - \frac{\delta}{3}\right] \, , s_{xy}({\boldsymbol \theta}) = U
- \label{eq:sij_2D_sph}
- \end{eqnarray}
-where the $U({\boldsymbol \theta})$ and $Q({\boldsymbol \theta})$ maps are smoothed by the Gaussian beam with width $\sigma_{\rm G}$.
-We suppress large artificial tidal fields at the maps boundary by replicating 8$\times$ the density maps defined on the octant and working on a full sky density $\delta$; we re-apply the octant mask on the tidal field maps after the operation.
-Note that the value of $\sigma_{\rm G}$ is a free parameter both in the infusion technique described in this paper and in the NLA and TATT models.
-We therefore explore two cases, $\sigma_{\rm G}=0.1$Mpc and 0.5Mpc, however this may be further optimised in the future.
-
-%are specified within the NLA model.
-Smoothing amounts to selecting physical scales that do not contribute to the alignment of galaxies, which is still a debatable quantity, but is also introduced for numerical stability.
-\citet{Blazek2015} argues that 1.0 $h^{-1}$Mpc could be a reasonable fiducial value, being larger then the typical halo size, but recognizes that one-halo terms are also required to better match the observations.
-In their later work, \citet{Blazek2019} do not include smoothing at all, and neither do the KiDS-1000 nor DES-Y1 analyses based on the NLA model \citep{KiDS1000_Asgari,DESY1_Troxel}.
-In this work we used a two-dimensional Gaussian filter and calibrated $\sigma_{\rm G}$ empirically to $\sigma_{\rm G}=0.1h^{-1}$Mpc (see Sec.
-\ref{subsubsec:sigma_G}), however these two choices are arbitrary and could possibly be better optimised in the future; we also explore $\sigma_{\rm G}=0.5h^{-1}$Mpc later on.
-We note that the smoothing scale is degenerate with the resolution of the simulation itself, and that one should use caution when smoothing on scales that approach the resolution limits.
-
-%We employ a numerical technique worth mentioning here: the Fourier transforms involved in computing Eq.
-(\ref{eq:sij_2D}) are computed from the full (projected) periodic boxes of the simulations, then interpolated on the light-cones.
-We find that tidal field computed directly from the $10\times10$ deg$^2$ light-cones introduces significant large scales features in the tidal field maps, largely caused by  the non-periodic boundary conditions, which our method avoids.
-Projected tidal field maps $s_{11}$, $s_{22}$ and $s_{12}$ are constructed that way for each mass sheets; Fig.
-\ref{fig:maps} shows the  three tidal fields and the mass maps for one of them.
-We can clearly see the connection between all maps around over-dense regions.
-{\it (Include a figure of $s_ij$ and $\delta$)}.
-
-{\it [Mention normalisation of the tidal fields by $0.6252 = H_0/114$ = 1/shell-thickness}
-
-%of every light-cones and interpolated at the position of every galaxy.
-Fig.
-\ref{fig:tidalator} illustrates this process for a small zoomed-in patch at $z\sim0$, starting from a $\delta_{2D}(\boldsymbol \theta)$ map (upper large panel), computing the tidal field components (middle four panels) and comparing the results with the cosmic shear signal generated by the same mass distribution (bottom two panels).
-The tidal field maps clearly reproduce the cosmic shear maps, and the minus sign in front of both terms in Eq.
-(\ref{eq:tidal_th}) causes the IA to undo some of the lensing signal.
-
-\subsection{Infusion of intrinsic alignments}
-\label{subsec:IA_infusion}
-
-Having now produced shear catalogues and tidal field maps, we can now use Eq.
-\ref{eq:tidal_th} to couple linearly the alignment of galaxies with the local tidal field, or Eq.
-\ref{eq:tidal_th_TT} to use instead a quadratic coupling.
-These allow us to compute the intrinsic ellipticities ${\boldsymbol \epsilon}^{\rm int}$ for the four IA models described in Sec.
-\ref{sec:IA_th}, which we combine with the cosmic shear signal ${\boldsymbol g}$ to compute observed ellipticities:
-\begin{eqnarray}
-{\boldsymbol \epsilon}^{\rm obs} = \frac{{\boldsymbol \epsilon}^{\rm int} + {\boldsymbol g}}{1 + {\boldsymbol \epsilon}^{\rm int}{\boldsymbol g^*}} \,, {\rm with \, \, } 
-{\boldsymbol \epsilon}^{\rm int}  = \frac{{\boldsymbol \epsilon}^{\rm IA} + {\boldsymbol \epsilon}^{\rm ran}}{1 + {\boldsymbol \epsilon}^{\rm IA}{\boldsymbol \epsilon^{\rm ran, *}}}.
-\label{eq:eps_obs}
-\end{eqnarray}
-In the above expressions, the denominators ensures that the combined  ellipticities never exceed unity.
-The complex spin-2 reduced shear ${\boldsymbol g} \equiv (\gamma_1 + {\rm i} \gamma_2)/(1+\kappa)$ is computed from the shear  $(\gamma_{1/2}$) and convergence ($\kappa$) maps, interpolated at the galaxy positions and redshifts.
-The  random orientation term ${\boldsymbol \epsilon}^{\rm ran}$ is drawn from two Gaussians (one per component) with their standard deviations matching the LSST-Y1 forecast, $\sigma_{\epsilon} = 027$.
-We further constraint  the random ellipticity to satisfy $|{\boldsymbol \epsilon}^{\rm ran}| \le 1.0$.
-%We recall that since our simulated galaxy catalogues trace the dark matter density, our default IA-infusion method  is consistent with the $\delta$-NLA model (see Sec.
-\ref{subsec:IA_th_ext}).
-Analytical predictions for the two-point functions are more involved in this case \citep[see][]{Blazek2019} and not yet available on the public {\sc cosmoSIS} release.
-We therefore validate our methods with the standard NLA first, which we infuse by `correcting' the $\delta$-NLA measurement with Eq.
-(\ref{eq:tidal_th_deltaNLA}), i.e.
-by replacing ${\boldsymbol \epsilon}^{\rm IA}$ by ${\boldsymbol \epsilon}^{\rm IA}/(1 + b_{\rm TA} \delta)$ in our simulations.
-Once again, these are less realistic but better suited for validation of the measured $\gamma$-2PCFs against a theoretical model; after this is established, we use the $\delta-$NLA catalogues as our fiducial infusion model.
-We re-iterate here that the same tidal fields, shear maps and IA coupling equations are used for the NLA and $\delta$-NLA models, and separately for the TT and $\delta$-TT models; these  only differ by the fact that in one case the galaxies are placed at random on the octant, while in the other case they are linearly tracing the dark matter.
-
-Also note that our current IA models make no differentiation between galaxy colours or type, and instead treats the full sample as a single population that has a single, effective, alignment signall \citep[see][for an example with a red/blue split]{DESY1_IA_Samuroff}.
-
-%---------------------
 \section{Validation with $\xi_{\pm}$}
@@
 
-% Requires the booktabs if the memoir class is not being used
-\begin{table}
-   \centering
-   %\topcaption{Table captions are better up top} % requires the topcapt package
-   \begin{tabular}{@{} lcr @{}} % Column formatting, @{} suppresses leading/trailing space
-      \hline
-      \hline
-       %\multicolumn{2}{c}{Item} \\
-      model   		& ($A_{\rm IA}, b_{\rm TA}, A_2)$ \\
-      \hline
-      NLA     		& {($\pm$1,0,0) }&  \\
-      \multirow{2}{*}{$\delta-$NLA }  	&   {($\pm$1,1,0)}   \\
-      							&  {(1,2,0)}   \\
-      TT 			&  {(0,0,$\pm$1)} &  \\
-      \multirow{2}{*}{$\delta$-TT} 	&  {(0,1,$\pm$1)}   \\
-      				&  {(0,2,1)}   \\
-      TATT- fiducial	&  { (1,1,1)}  \\
-      %TATT-DESY3	&   (-0.7,1,1.9) & \\
-      \hline
-      \hline
-
-   \end{tabular}
-   \caption{IA models infused in this work.}
-   \label{table:IAmodels}
-\end{table}
+\input{tables/ia_models}
 
@@
 See Fig. \ref{fig:xi_NLA}
-%---------------
-\begin{figure*}
-%\includegraphics[width=\columnwidth]{graphs/frac_xip_IA1_skysim}
-\includegraphics[width=\columnwidth]{graphs/frac_xip_IA1_skysim_NLA_srd.jpg}
-\includegraphics[width=\columnwidth]{graphs/frac_xim_IA1_skysim_NLA_srd.jpg}
-\caption{Ratio between the shear correlation functions with and without IA, assuming the NLA model with $A_{\rm IA}=1.0$ both in the simulations and theory.
-Measurements shown in green and brown correspond to smoothing scales of 0.1 and 0.5 $h^{-1}$Mpc in the tidal field.
-There is no shape noise in the simulations, but it is included in the error bars.}
-\label{fig:xi_NLA}
-\end{figure*}
-%---------------
+
+\input{figures/shear_corr_funcs/xi_nla}
 
 %------------------------------
-\subsection{$\delta$-NLA model}
+\subsection{Extended-NLA model}
 \label{subsec:deltaNLA}
@@
 
-\begin{figure*}
-\includegraphics[width=\columnwidth]{graphs/frac_xip_IA1_skysim_deltaNLA_srd}
-\includegraphics[width=\columnwidth]{graphs/frac_xim_IA1_skysim_deltaNLA_srd}
-\caption{Same as Fig.
-\ref{fig:xi_NLA}, but for the $\delta$-NLA model with $A_{\rm IA}=1.0$ and $b_{\rm TA}=1.0$, and only for smoothing of 0.5$h^{-1}$Mpc.
-The dashed black lines show the NLA predictions to better highlight the differences.
-}
-\label{fig:xi_deltaNLA}
-\end{figure*}
+\input{figures/shear_corr_funcs/xi_delta_nla}
 
-\begin{figure}
-\includegraphics[width=\columnwidth]{graphs/frac_xip_bta1_rescaled}
-\caption{Ratio between the shear correlation functions with and without IA in tomographic bin combination 2-5.
-The brown and green symbols show measurements from simulations constructed with $b_{\rm TA}$ = 0.0 and 2.0 respectively,  the black solid and dotted lines shown their predictions, while the blue symbols are obtained by rescaling $b_{\rm TA}$ = 1.0 simulations using Eq.
-\ref{eq:bta_rescale}.
-}
-\label{fig:xi_deltaNLA_rescaled}
-\end{figure}
+\input{figures/shear_corr_funcs/xi_delta_nla_rescaled}
 
@@
 
-Using this, we $b_{\rm TA}$-rescale our $b_{\rm TA}=1.0$ mock to $b_{\rm TA}=2.0$ and to $0.0$ mocks.
-Results are shown in Fig.
-\ref{fig:xi_deltaNLA_rescaled} for one of the tomographic bin.
+Using this, we $b_{\rm TA}$-rescale our $b_{\rm TA}=1.0$ mock to $b_{\rm TA}=2.0$ and to $0.0$ mocks. Results are shown in Fig. \ref{fig:xi_deltaNLA_rescaled} for one of the tomographic bin. 
 It works reasonably well, but lower redshift are less accurate due to the increased  shot noise (not shown), hence we do not recommend using this.
@@
 
-\begin{figure*}
-\includegraphics[width=\columnwidth]{graphs/frac_xip_IA1_skysim_TT_srd.jpg}
-\includegraphics[width=\columnwidth]{graphs/frac_xim_IA1_skysim_TT_srd.jpg}
-\caption{Same as Fig. \ref{fig:xi_NLA}, but for the TT model with $A_2=1.0$. Here, the dashed black lines show the NLA predictions to better highlight the differences. }
-\label{fig:xi_TT}
-\end{figure*}
+\input{figures/shear_corr_funcs/xi_tt}
 
-\begin{figure*}
-%\includegraphics[width=\columnwidth]{graphs/frac_xip_C2_m1_skysim_deltaTT}
-\includegraphics[width=\columnwidth]{graphs/frac_xip_IA1_skysim_deltaTT_srd.jpg}
-\includegraphics[width=\columnwidth]{graphs/frac_xim_IA1_skysim_deltaTT_srd.jpg}
-\caption{Same as Fig. \ref{fig:xi_deltaNLA}, but comparing the TT and the $\delta$-TT models, with $A_2=1.0$, $b_{\rm TA}$ = 1.0, and only for smoothing of 0.5$h^{-1}$Mpc. }
-\label{fig:xi_deltaTT}
-\end{figure*}
+\input{figures/shear_corr_funcs/xi_delta_tt}
 
@@
 %------------------------------
-\subsection{$\delta$-TT model}
+\subsection{Extended-TT model}
 \label{subsec:TT}
@@
 
-%\subsection{Validation with full inference}
- %\label{sec:inference}
+%------------------------------
+\subsection{HOD-NLA model}
+\label{subsec:HOD}
 
-%priors, firecrown, Takahashi $P(k)$
+\input{figures/shear_corr_funcs/xi_hod_nla}
 
-\section{Higher-order weak lensing statistics}
-\label{sec:HOWLS}
+\input{figures/shear_corr_funcs/xi_hod_tt}
 
-... use the mocks from Table \ref{table:IAmodels} to compute derivatives. Show.
+The NLA and extended-NLA models respectively assume a null and a linear bias between the source galaxies and the underlying matter field, both of which are approximations to the galaxy dark matter connection.
+In fact, galaxies populate dark matter over-densities in a more complex manner \citep{GalaxyPopulationPapers}, which is better described by the Halo Occupation Distribution approach (HOD hereafter).
+The largest difference here is that these HOD galaxies are non-linear biased tracers of the matter distribution, which means that a larger number can populate regions of large over-densities, where the tidal fields are generally stronger.
+We therefore expect the impact of IA to be stronger in this case.
 
-%----------
-\section{Conclusions}
-\label{sec:conclusion}
-%----------
+We investigate this effect with HOD galaxies extracted from the SkySim5000 simulation \citep{SkySim5000_HOD} \footnote{We used version: {\tt skysim5000\_v1.2}, as detailed in XYZ..}, which are obtained by [...] (mention the TXPipe paper).
+Specifically, we select objects over a patch of 732.20 deg$^2$ given by  0$<$RA$<$ 20 and -36.61$<$DEC$<$0, we apply a magnitude cut of mag$_r<$24.8, and further downsample randomly to retain 20\% of the galaxies,
+therefore matching the global galaxy redshift distribution and number density found in the rest of this paper (Eq. \ref{eq:nz}).
+The sample is further split into five tomographic bins by using Charlie's magical code (Charlie), resulting in the $n(z)$ presented in Fig. \ref{fig:NzHOD}. 
+Compared to the analytical SRD-Y1 presented in Fig. \ref{fig:Nz}, the mean redshifts of the five tomographic bins are shifted by [-0.027, -0.018,  0.003, -0.010,  0.038], respectively.
 
-\section*{Acknowledgements}
+[{\it To put somewhere?: Since source clustering is a higher order effect in cosmic shear, the measured $\xi_{\pm}$ from these three mocks (random, $b_{\rm TA}=1.0$ and $b_{\rm TA}=2.0$) show negligible differences ({\it to quantify and cite}).
+In contrast, the impact on the IA contamination is significant and can double the secondary signal in certain circumstances. 
+The main explanation for this is that while clustered sources are uncorrelated with the foreground matter responsible for the lensing signal, the high-density regions they live are also subject to the largest tidal fields.
+}]
 
-JHD acknowledges support from an STFC Ernest Rutherford Fellowship (project reference ST/S004858/1).
-Ray-tracing computations were carried on the NERSC [acknowledgments] ...
-HACC [acknowledgements] ...
-OuterRim [Acknowledgments]
-\\
+\subsection{Validation with full inference}
+ \label{sec:inference}
+\begin{figure}
+%\includegraphics[width=\columnwidth]{graphs/triangle_nla_5D.pdf}
+\includegraphics[width=\columnwidth]{graphs/triangle_bta_sweep.pdf}
+\caption{Cosmological inference from the NLA-infused simulations, analysed the extended-NLA model. 
+The cross-hairs represent the truth as fixed in the {\it Outer Rim} $N$-body simulations \citep{OuterRim}.}
+\label{fig:triangle_nla}
+\end{figure}
+priors, {\sc CosmoSIS}, Takahashi $P(k)$, etc.
 
-Some of the results in this paper have been derived using the {\sc healpy} and {\sc HEALPix} packages.
-\\
-\\
-\\
-{\footnotesize All authors contributed to the development and writing of this paper. JHD led the analysis.... }
+\input{figures/corner_plots/corner_NLA_all}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Data Availability}
+\begin{figure}
+%\includegraphics[width=\columnwidth]{graphs/triangle_nla_5D.pdf}
+\includegraphics[width=\columnwidth]{graphs/TT_allsweep.pdf}
+\caption{Cosmological inference from the TT-infused simulations, with all 3 IA params varied.
+The cross-hairs represent the truth as fixed in the {\it Outer Rim} $N$-body simulations \citep{OuterRim}.}
+\label{fig:triangle_tt_all_ia_params}
+\end{figure}
 
-%The SLICS numerical simulations can be found at http://slics.roe.ac.uk/, while the cosmo-SLICS can be made available upon request.
-
-%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%
-
-% The best way to enter references is to use BibTeX:
-
-\bibliographystyle{hapj}
-\bibliography{IA} % if your bibtex file is called example.bib
-
-% Alternatively you could enter them by hand, like this:
-% This method is tedious and prone to error if you have lots of references
-%\begin{thebibliography}{99}
-%\bibitem[\protect\citeauthoryear{Author}{2012}]{Author2012}
-%Author A.~N., 2013, Journal of Improbable Astronomy, 1, 1
-%\bibitem[\protect\citeauthoryear{Others}{2013}]{Others2013}
-%Others S., 2012, Journal of Interesting Stuff, 17, 198
-%\end{thebibliography}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%% APPENDICES %%%%%%%%%%%%%%%%%%%%%
-
-\appendix
-
-\section{Projected Tidal Field}
-\label{app:2d_TT}
-
-\JHD{[To reword]} We derive in this Appendix...  
-The prescription to assign an intrinsic alignment based on the projected tidal field, described in Eq.
-(\ref{eq:tidal_th}), involves the combinations $(s_{xx} - s_{yy})$ and $s_{xy}$, which therefore correspond to:
-\begin{eqnarray}
- \widetilde{\epsilon}_1^{\rm IA} (\boldsymbol k_{\perp})  &\propto& \left(\frac{k_x^2 - k_y^2}{k^2} \right) \widetilde{\delta}_{\rm 2D}(\boldsymbol k_{\perp})\mathcal{G_{\rm 2D}}(\sigma_{\rm G})  \, ,\nonumber \\
- \widetilde{\epsilon}_2^{\rm IA} (\boldsymbol k_\perp)  &\propto& \left(\frac{k_x k_y}{k^2} \right) \widetilde {\delta}_{\rm 2D}(\boldsymbol k_\perp)\mathcal{G_{\rm 2D}}(\sigma_{\rm G}) 
- %\label{eq:sij}
-\end{eqnarray}
-
-Aside from the smoothing kernel, these are the same filters that are used for converting convergence maps to shear maps under the \citet[][KS hereafter]{KaiserSquires} inversion:
- \begin{eqnarray}
- \widetilde{\gamma_1} (\boldsymbol \ell)  = \left(\frac{k_x^2 - k_y^2}{k^2} \right) \widetilde {\kappa}(\boldsymbol \ell) \, , \hspace{1cm} \widetilde{\gamma_2} (\boldsymbol \ell)  = \left(\frac{k_x k_y}{k^2} \right) \widetilde {\kappa}(\boldsymbol \ell)
- %\label{eq:sij}
-\end{eqnarray}
-meaning that on can linearly combine the mass sheets with the correct coefficients and obtain intrinsic ellipticities from a normal KS inversion.
-
-Projecting out the $z$ components (e.i. $s_{0i}$=$s_{i0}$=0 for all $i$),  the tidal torque terms from Eq. (\ref{eq:tidal_th_TT}) can be expanded as:
- \begin{eqnarray}
-\gamma^{\rm TT}_{ij}&=& C_2 \left[\sum_{k=x,y} s_{ik} s_{kj} -\frac{1}{3} \delta_{ij} s^2\right] \\
-                                  &=&C_2 \left[ s_{ix}s_{xj}  + s_{iy}s_{yj}  -  \frac{1}{3} \delta_{ij} \left( s_{xx}^2 + s_{yy}^2 +2s_{xy}^2 \right)  \right] \, .
-\end{eqnarray}
-Specifically, this yields:
- \begin{eqnarray}
-\gamma^{\rm TT}_{xx}&=& C_2 \left[\frac{2}{3}s_{xx}^2  -  \frac{1}{3}s_{yy}^2 + \frac{1}{3}s_{xy}^2 \right]\, ,  \nonumber \\
-\gamma^{\rm TT}_{yy}&=& C_2 \left[-\frac{1}{3}s_{xx}^2  +  \frac{2}{3}s_{yy}^2 + \frac{1}{3}s_{xy}^2  \right]\, , \\
-\gamma^{\rm TT}_{xy}&=& C_2 s_{xy}\left[s_{xx}+s_{yy}  \right]\, . \nonumber                                  
-\end{eqnarray}
-With the standard ellipticity definitions $\epsilon_1^{\rm TT}\equiv \gamma_{xx}^{\rm TT} - \gamma_{yy}^{\rm TT}$ and $\epsilon_2^{\rm TT}\equiv -2 \gamma_{xy}$, we obtain:
-\begin{eqnarray}
-\epsilon_1^{\rm TT} = C_2  \left[ s_{xx}^2 - s_{yy}^2\right] \, , \epsilon_2^{\rm TT} = -2 C_2 s_{xy}\left[s_{xx}+s_{yy}  \right]\, .
-\end{eqnarray}
-In the TATT model, the total intrinsic ellipticity component is therefore given by $\epsilon_{1/2}^{\rm IA} = \epsilon_{1/2}^{\rm TATT} = \epsilon_{1/2}^{\delta{\rm-NLA}} + \epsilon_{1/2}^{\rm TT}$.
-
-% Don't change these lines
-\bsp	% typesetting comment
-\label{lastpage}
-\end{document}
-
-% End of mnras_template.tex
+\input{figures/corner_plots/corner_TT}

### 2024-03-27 sections/6_higher_order_wl_stats.tex
Changes made by Niko

--- 2023-11-13 paper_IA.tex
@@
-% mnras_template.tex 
-%
-% LaTeX template for creating an MNRAS paper
-%
-% v3.0 released 14 May 2015
-% (version numbers match those of mnras.cls)
-%
-% Copyright (C) Royal Astronomical Society 2015
-% Authors:
-% Keith T. Smith (Royal Astronomical Society)
-
-% Change log
-%
-% v3.0 May 2015
-%    Renamed to match the new package name
-%    Version number matches mnras.cls
-%    A few minor tweaks to wording
-% v1.0 September 2013
-%    Beta testing only - never publicly released
-%    First version: a simple (ish) template for creating an MNRAS paper
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Basic setup. Most papers should leave these options alone.
-%\documentclass[fleqn,usenatbib]{mnras}
-\documentclass[useAMS,usenatbib]{mn2e}
-
-% MNRAS is set in Times font. If you don't have this installed (most LaTeX
-% installations will be fine) or prefer the old Computer Modern fonts, comment
-% out the following line
-%\usepackage{newtxtext,newtxmath}
-% Depending on your LaTeX fonts installation, you might get better results with one of these:
-%\usepackage{mathptmx}
-%\usepackage{txfonts}
-
-% Use vector fonts, so it zooms properly in on-screen viewing software
-% Don't change these lines unless you know what you are doing
-%\usepackage[T1]{fontenc}
-
-% Allow "Thomas van Noord" and "Simon de Laguarde" and alike to be sorted by "N" and "L" etc. in the bibliography.
-% Write the name in the bibliography as "\VAN{Noord}{Van}{van} Noord, Thomas"
-%\DeclareRobustCommand{\VAN}[3]{#2}
-%\let\VANthebibliography\thebibliography
-%\def\thebibliography{\DeclareRobustCommand{\VAN}[3]{##3}\VANthebibliography}
-
-%%%%% AUTHORS - PLACE YOUR OWN PACKAGES HERE %%%%%
-\input{abbrev}
-\input{psfig.sty}
-
-\usepackage{graphicx}
-\usepackage{epsfig}
-\usepackage{amssymb}
-\usepackage{amsmath}
-\usepackage{amsfonts}
-\usepackage{txfonts}
-\usepackage{multirow}
-\usepackage{afterpage}
-\usepackage{xcolor}
-%\usepackage[draft]{hyperref}
-%\usepackage{ulem} % allows for strikethrough with \sout{}
-
-%\usepackage[paperheight=10in,paperwidth=8.5in]{geometry}
-
-\setlength{\topmargin}{-0.8in}
-\paperheight 11in
-\paperwidth 8.5in
-%\setlength{\textheight}{9.8in}
-%\setlength{\textwidth}{7.3in}
-\setlength{\textheight}{9.5in}
-\setlength{\textwidth}{7.1in}
-
-\definecolor{mypink1}{rgb}{0.858, 0.188, 0.478}
-\definecolor{mygreen1}{rgb}{0.258, 0.788, 0.878}
-\definecolor{myorange1}{rgb}{0.5, 0.2, 0.2}
-\newcommand{\NM}[1]{\textcolor[RGB]{0,150,0}{#1}}
-\newcommand{\RR}[1]{\textcolor{blue}{#1}}
-\newcommand{\JHD}[1]{\textcolor{mypink1}{#1}}
-\newcommand{\snr}{$\mathcal{S}/\mathcal{N}$ }
-\newcommand{\mycomment}[1]{}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%% AUTHORS - PLACE YOUR OWN COMMANDS HERE %%%%%
-
-% Please keep new commands to a minimum, and use \newcommand not \def to avoid
-% overwriting existing commands. Example:
-%\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%
-
-% Title of the paper, and the short title which is used in the headers.
-% Keep the title short and informative.
-\title[Lensing beyond 2pt: accounting for IA]{Intrinsic alignments from projected tidal fields: non-linear  impact on cosmic shear probes}
-
-% The list of authors, and the short list which is used in the headers.
-% If you need two or more lines of authors, add an extra line using \newauthor
-\author[J. Harnois-D\'{e}raps et al.]{Joachim Harnois-D\'{e}raps$^{1}$\thanks{E-mail: joachim.harnois-deraps@ncl.ac.uk} and others
-\\
-% List of institutions
-$^{1}$School of Mathematics, Statistics and Physics, Newcastle University, Herschel Building, NE1 7RU, Newcastle-upon-Tyne, UK\\
-}
-
-% These dates will be filled out by the publisher
-\date{Accepted XXX. Received YYY; in original form ZZZ}
-
-% Enter the current year, for the copyright statements etc.
-\pubyear{2021}
-
-% Don't change these lines
-\begin{document}
-\label{firstpage}
-\pagerange{\pageref{firstpage}--21}
-%\pagerange{\pageref{firstpage}--\pageref{lastpage}}
-\maketitle
-
-% Abstract of the paper
-\begin{abstract}
-TBD
-\end{abstract}
-
-% Select between one and six entries from the list of approved keywords.
-% Don't make up new ones.
-\begin{keywords}
-Gravitational lensing: weak -- Methods: numerical -- Cosmology: dark matter, dark energy \& large-scale structure of Universe 
-\end{keywords}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%% BODY OF PAPER %%%%%%%%%%%%%%%%%%
-
-%----------
-\section{Introduction}
-\label{sec:intro}
-%----------
-
-Cosmology, gravitational lensing, cosmic shear, 2pt, beyond-2pt, simulations for signal and for secondary signal/systematics, IA-infusion, this paper...
-
- %----------
-\section{Cosmic shear}
-\label{sec:theory}
-%----------
-
-As mentioned in the introduction, cosmic shear can be measured and modelled from a variety of methods, many of which are used in this paper and presented in this section.  
-%-------------------------
-\subsection{$\gamma$-2PCF}
-\label{subsec:wl-th}
-
-%---------------
-\begin{figure}
-\includegraphics[width=\columnwidth]{graphs/Nz}
-\caption{Redshift distribution in our simulations, taken from the Year-1 specifications of the LSST Science Requirement Document \citep{LSST-SRD} {[\it check Y1 vs Y10}].}
-\label{fig:Nz}
-\end{figure}
-%--------------
-
- Shear two-point correlation functions ($\gamma$-2PCFs hereafter) can be predicted with percent-level precision and are therefore an ideal quantity to validate weak lensing simulations.
-In the Limber approximation\footnote{See \citet{Kilbinger17} for a comparison between the Limber approximation and the exact calculations.}, the lensing power spectrum $C^{ij}_{\ell}$ is obtained from an integral over the three-dimensional matter power spectrum $P_{\delta}(k,z)$:
-  \begin{eqnarray}
-C_{\ell}^{ij} = \int_0^{\chi_{\rm H}}  \frac{q^i(\chi) \,q^j(\chi)}{\chi^2} \, P_{\delta}\, \bigg(\frac{\ell+1/2}{\chi},z(\chi)\bigg) \ {\rm d}\chi,
-\label{eq:C_ell}
-\end{eqnarray}
-where $\chi_{\rm H}$ is the co-moving distance to the horizon, $c$ is the speed of light, $H_0$ the Hubble parameter,  and the  lensing kernels $q^{i}$ are given by:
-\begin{eqnarray}
-q^i(\chi) = \frac{3}{2}\Omega_{\rm m} \, \bigg(\frac{H_0}{c} \bigg)^2 \frac{\chi}{a(\chi)} \int_{\chi}^{\chi_{\rm H}} n^i(\chi')\frac{{\rm d}z}{{\rm d} \chi'}\frac{\chi' - \chi}{\chi'}{\rm d}\chi' \, .
-\label{eq:q_lensing}
-\end{eqnarray}
-In the previous expression, $n^i(z)$ refers to the redshift distribution  in tomographic bin `$i$', while $a(\chi)$ is the scale factor at comoving distance $\chi$ from the observer {[\it might need to define $\Omega_m$ here]}.
- The matter power spectrum is computed from  {\sc Halofit} \citep{Takahashi2012}, however  other public tools provide $P_{\delta}(k,z)$ predictions, including e.g.
-{\sc HMcode} \citep{HMCode2020}, the {\sc EuclidEmulator} \citep{EuclidEmulator}, the {\sc BACCO} emulator \citep{BACCOEmulator} or the Mira Titan emulator \citep{miraTitan}.
- Predictions for the $\gamma$-2PCFs are finally computed from Eq. (\ref{eq:C_ell}) as:
- \begin{eqnarray}
-\xi_{\pm}^{ij}(\vartheta) = \frac{1}{2\pi}\int_0^{\infty} C_{\ell}^{ij} \, J_{0/4}(\ell \vartheta) \, \ell \, {\rm d}\ell,
-\label{eq:xipm_th}
-\end{eqnarray}
-where $J_{0/4}(x)$ are Bessel functions of the first kind.
-In this paper, these calculations are carried out by {\sc pyccl}\footnote{{\sc pyccl}:pypi.org/project/pyccl}  \citep{CCL} {\it or do we use cosmosis in the end?]}.
-The $n^i(z)$ are taken from the LSST Science Requirement Document \citep{LSST-SRD} and given by
- \begin{eqnarray}
-n(z) = N_0 z^2 {\rm exp} \left[-\left(\frac{z}{z_0}\right)^\alpha \right]\, ,
-\label{eq:nz}
-\end{eqnarray}
-with $(z_0, \alpha) = (0.13, 0.78)$ and $N_0$ normalised to provide a number density of $n_{\rm eff}$ = 3.0 gal arcmin$^{-2}$.
-This lower than the expected number density for the first data release ($n_{\rm eff}\sim10$ gal arcmin$^{-2}$), but is large enough to validate our methods, and makes the calculation more tractable.
-The $n(z)$ is further split into five equi-populated tomographic bins, and smoothed with a Gaussian filter of width $\sigma = 0.05(1+z)$ in order to mimic the photometric selection process [{\it confirm with Niko}].
-The resulting distributions\footnote{The construction of these tomographic $n(z)$ can be reproduced in {github...CCL\_SRD\_Niko}.} are shown in Figure \ref{fig:Nz}.
-
-The cosmic shear signal can be measured from the ellipticities $\epsilon_{1/2}$ of simulated or observed galaxies, which, in absence of systematics and secondary signals, are unbiased estimators  of the cosmic shear components $\gamma_{1/2}$.
-The $\gamma$-2PCF are then estimated as:
- \begin{eqnarray}
- \widehat{\xi_{\pm}^{ij}}(\vartheta) = \frac{\sum_{a,b} w_a w_b \left[\epsilon_{a, \rm t}^i\epsilon_{b, \rm t}^j     \pm \epsilon_{a, \times}^i\epsilon_{b, \times}^j    \right]\Delta_{ab}(\vartheta)}{\sum_{a,b} w_a w_b} \, ,
- \label{eq:2PCF_estimator}
-  \end{eqnarray}
-where the sum is over all pairs of galaxies $a,b$ separated by an angular separation $\vartheta$, taken from tomographic bins $i,j$.
-The tangential/cross components of their ellipticities are denoted as $\epsilon_{\rm t/\times}$, respectively.
-$\Delta_{ab}(\vartheta)$ is the binning operator, equal to unity if the angular separation between the two galaxies falls within the $\vartheta$-bin, and zero otherwise, and the shape weights $w_{a,b}$ are set to unity.
-In this paper, we construct lensing catalogues from numerical simulations (described in Sec.
-\ref{sec:sims}), from which we measure $ \widehat{\xi_{\pm}^{ij}}(\vartheta)$ with {\sc Treecorr} \citep{TreeCorr}.
-We set therein the {\sc bin\_slop} parameter to 0.05, then compute the correlations in nine logarithmically-spaced angular bins ranging from 0.5 to 475.5 arcmin.
-
- %-------------------------
-\subsection{Beyond-2pt}
-\label{subsec:beyond-2pt}
-
-Non-Gaussian statistics, often referred to `beyond-2pt' statistics, have the potential to extract cosmological information stored in the complex phases of the density field, whereas two-point functions such as the $\gamma$-2PCF can only access that encoded in the complex amplitudes.
-No optimal estimator has been identified to-date as being able to capture `all' information, but the numerous studies presented in the introduction all show a clear gain in constraining power, especially when used in combination with 2pt functions.
-Some of these take as input the galaxy catalogues directly, while others require instead convergence maps.
-Therefore, we produce convergence maps from the catalogues by assigning the shear signal onto spherical {\sc Healpix}\footnote{{\sc Healpix}: http://healpix.sf.net}  maps \citep{healpix} with $N_{\rm side}=4096$, then using the standard Kaiser \& Squires inversion technique \citep{KaiserSquires} implemented in {\sc healpy} to reconstruct a convergence maps with the same angular resolution, including a baseline 2.0 arcmin smoothing beam in the inverse transform.
-Note that this smoothing scales is quite small; some probes are difficult to model in that case, and would instead prefer larger smoothing scales.
-We take this into account on a case-by-case basis, as described below.
-
-  {\it [Discuss tomography...]}
-
-\subsubsection{Catalogue-based estimators}
-
-We consider the following shear-based estimators:
-\begin{enumerate}
-\item The squeezed bispectrum, has theoretical model (Anik, can you summarise the measurements and modelling, and provide references?)
-\end{enumerate}
-
-\subsubsection{Convergence-based estimators}
-
-\begin{enumerate}
-\item Convergence three-point correlation function: (Alejandro, can you summarise the measurements and modelling, and provide references?)
-\item Peaks and Minima: local maxima and minima in the {\sc Healpix} convergence maps are counted in bins of signal-to-noise ratios, $\nu$.
-This is one of the most widely used non-Gaussian lensing statistics as it is simple to measure.
-Theoretical models have been developed to describe the largest peaks \citep[see][]{Shan18, HSCY1_Peaks_th}, however we report here the results on a much wider range of statistics, which can only be accurately modelled from numerical simulations, as in \citet{HD21, DESY3_Zuercher, HSCY1_Peaks_Sims, HD23}.
-\item Lensing PDF, has theoretical model (Cora/Lina, can you summarise the measurements and modelling, and provide references?)
-\item Map2 and Map3, has theoretical model  (Laila, can you summarise the measurements and modelling, and provide references?)
-\item Minkowski functionals (Nisha, can you summarise the measurements and modelling, and provide references?)
-\end{enumerate}
-
- %-------------------
- \section{Intrinsic alignment models}
- \label{sec:IA_th}
- %-------------------
-
-Galaxies interact with the tidal forces caused by the large-scale structure  they live in, causing their intrinsic shapes to acquire correlated alignments that has nothing to do with the correlations caused by weak lensing.
-This therefore acts as a secondary signal that contaminates the shape correlation measurements carried out in a cosmic shear analysis.
-There is no consensus on the actual physical model that describes the IA signal, and even when adopting these, the free parameters they contain are only weakly constrained from the data \citep[see][for reviews]{IA_review1, IA_review2}.
-%The most widely used model in the literature is the non-linear alignment model of \citet{NLA}, however it is now recognised that this is an effective model with limited precision, and the community is now progressively shifting towards more complex models.
-In this paper we consider four such IA models that we describe in the following sub-sections.
-In all cases, our models couple the galaxy intrinsic shapes with the local over-density and projected tidal field , then prescribe an intrinsic ellipticity tensor $\gamma_{ij}^{\rm IA}$, from which observed ellipticities are extracted as:
- \begin{eqnarray}
-\epsilon_{1}^{\rm IA} = \gamma_{xx}^{\rm IA} - \gamma_{yy}^{\rm IA} \, , \hspace{1.5cm}\epsilon_{2}^{\rm IA} = 2 \gamma_{xy}^{\rm IA}\, .
-\label{eq:tidal_th_deltaNLA}
-\end{eqnarray}
-
-\subsection{Non-linear alignment (NLA)}
-
-%The observed ellipticity of a galaxy ${\boldsymbol \epsilon}_{\rm obs} $ is a combination of its intrinsic shape ${\boldsymbol \epsilon}_{\rm int}$ and a cosmic shear signal ${\boldsymbol \gamma}$, the former of which can be further divided in a random component ${\boldsymbol \epsilon}^{\rm ran}$ and an alignment term ${\boldsymbol \epsilon}^{\rm IA}$.
-The NLA model of \citet{NLA} is the most widely used IA model in the cosmic shear literature thus far.
-According to the NLA, IA are caused by a linear coupling between galaxy shapes and the non-linear large-scale tidal field at the galaxy position.
-In the context of  two-point functions, these intrinsic shapes contribute to an intrinsic-intrinsic ($II$) term and an intrinsic-shear coupling ($GI$) term \citep{Hirata2004}, both secondary signals to the true cosmic shear ($GG$) term, with the latter typically dominating the IA sector in cross-tomographic measurements.
-The $II$ and $GI$ terms  can be both computed from the matter power spectrum as:
- \begin{eqnarray}
-P_{II}(k,z) =  \left(\frac{A_{\rm IA}\bar{C_1}\bar{\rho}(z)}{D(z)}\right)^2a^4(z) P_{\delta}(k,z)
-\label{eq:Pk_II_th}
-\end{eqnarray}
-and
- \begin{eqnarray}
-P_{GI}(k,z) = - \frac{A_{\rm IA}\bar{C_1}\bar{\rho}(z)}{D(z)}a^2(z) P_{\delta}(k,z) \, ,
-\label{eq:Pk_GI_th}
-\end{eqnarray}
-which can then be past to the Limber integration (Eqs. \ref{eq:C_ell} and \ref{eq:xipm_th}) to compute  the secondary signals $\xi_{\pm}^{II}(\vartheta)$ and $\xi_{\pm}^{GI}(\vartheta)$. 
-In the above expression,  $D(z)$ is the linear growth factor, $\bar{\rho}(z)$ is the mean matter density at redshift $z$ and $\bar{C_1}=5\times 10^{-14} M_{\odot}^{-1} h^{-2} {\rm Mpc}^3$ is a constant calibrated in \citet{Brown2002}.
-The strength of the tidal coupling is modulated by the amplitude parameter $A_{\rm IA}$, which is the main NLA parameter constrained by current cosmic shear surveys.
-Note that this model can be augmented by redshift and luminosity dependences, however we do not use these here.
-
-The NLA intrinsic ellipticities $\epsilon_{1,2}^{\rm NLA}$ are related to tidal field $s_{ij}$ by:
- \begin{eqnarray}
-\epsilon_1^{\rm NLA} = - \frac{A_{\rm IA}\bar{C_1}\bar{\rho}(z)}{D(z)} (s_{xx} - s_{yy}) \,\,\,\,,   \epsilon_2^{\rm NLA} = - \frac{2 A_{\rm IA}\bar{C_1}\bar{\rho}(z)}{D(z)} s_{xy}\;,
-\label{eq:tidal_th}
-\end{eqnarray}
-where $s_{ij} = \partial_{ij}\phi$ are the Cartesian components of the tidal tensor of the gravitational potential.
-Note that the term `non-linear' in the model name can be  misleading, as it refers to the non-linear matter power spectrum $P(k)$ that is used in its calculations; the coupling between the intrinsic galaxy shapes and the tidal field is still linear.
-Eq.( \ref{eq:tidal_th}) is used to assign intrinsic ellipticities to galaxies, given maps of the tidal field components $s_{xx}$, $s_{yy}$ and $s_{xy}$ (see Sec.
-\ref {subsec:IA_infusion}).
-
-\subsection{$\delta$-NLA}
-\label{subsec:IA_th_ext}
-
-%[{\it here}]
-
-%As discussed later, the key quantity of interest to cosmic shear analysis is not the tidal tensor itself but its trace-free version, since shape correlations with the density field are subdominant, even though peaks in high density environments are less elliptical on average.
-Consequently, the model itself has a restricted range of validity: on small scales, higher order couplings to the ellipticity field ${\boldsymbol \epsilon}^{\rm IA}$  become important, however these are neglected in the NLA model.
-Only the non-linear evolution of the tidal tensor itself is taken into account, since it does fit observations quite well.
-
-%We note that the NLA predicts additional higher-order terms and non-zero $B$-modes \citep{Hirata2004} that we neglect  in this analysis.
-Also, as shown in \citet{IA_EFT}, the NLA model can be interpreted as the lowest order description of the alignment process of galaxies in the light of an effective field theory description.
-
-The NLA model presented in the last section has been widely used in cosmic data analyses, but it has important known limitations and is therefore bound to fail at describing the IA signal with high precision.
-A perturbation theory extension to the NLA has been introduced in \citet{Blazek2015} and  \citet{Blazek2019},  where it is recognised that higher order couplings could be important and should be considered.
-The first additional term to be included is the over-density weighting term, which is caused by the fact that the intrinsic alignment of galaxies can only be observed at the galaxy positions, which are not distributed randomly on the sky but instead trace the underlying matter density,  `$\delta$', although the exact biasing scheme is not currently know.
-Accounting for this extra term in theoretical predictions is done with one-loop perturbation theory  \citep{Blazek2019}, and is implemented in {\sc pyccl}.
-Physically, it corresponds to adding a $\delta$-weight to the NLA predictions at the local galaxy positions, effectively representing the different tracer properties.
-At the level of numerical simulations, this could be done in principle simply by augmenting the NLA ellipticities with this weight, namely:
- \begin{eqnarray}
-\epsilon_{1/2}^{\delta-\rm NLA} = \epsilon_{1/2}^{\rm NLA}\times(1 + b_{\rm TA}\delta) \, ,
-\label{eq:tidal_th_deltaNLA}
-\end{eqnarray}
-where the term $b_{\rm TA}$ corresponds to the (largely unconstrained) biasing relation between these source galaxies and the underlying matter field.
-In practice, however, we find that this is noisy, and that it is instead preferable to generate mocks catalogues with the biasing scheme directly applied when assigning galaxy positions, after which no weighting is necessary.
-Nevertheless, Eq.
-(\ref{eq:tidal_th_deltaNLA}) can be used to modify the value of $b_{\rm TA}$.
-Indeed, from a mock with a given bias $b_{\rm TA, orig}$, we can rescale the IA contribution to a different $b_{\rm TA, new}$  as:
-\begin{eqnarray}
-{\boldsymbol \epsilon}^{\rm int}_{b_{\rm TA, new}}  = \frac{(1 + b_{\rm TA, new}\delta)}{(1 + b_{\rm TA, orig}\delta)}{\boldsymbol \epsilon}^{\rm int}_{b_{\rm TA, orig}} \, .
-\label{eq:bta_rescale}
-\end{eqnarray}
-
-Compared to the NLA, the $\delta$-NLA is a stronger IA model, especially on small scales \citep{Blazek2019}, and seems to be preferred by some hydrodynamical simulations \citep{Hilbert_IA2017}.
-It is also better motivated from a physical point of view, since we know that the galaxies trace dark matter  and are not randomly distributed in our Universe as the NLA assumes.
-
-%-----------------------------------
-\subsection{Tidal Torque (TT)}
-\label{subsec:IA_th_TT}
-
-As shown in \citet{Blazek2019}, one-loop perturbative calculations include another term, by which galaxies acquire an intrinsic alignment via a coupling between their angular momentum and the tidal field, which can be re-expressed as a quadratic coupling between the tidal field and the shape.
-In this tidal torque model (TT), intrinsic ellipticities are given by:
-\begin{eqnarray}
-\gamma_{ij}^{\rm IA, TT} = C_2 \left[ \sum_{k=x,y,z} s_{ik} s_{kj} -\frac{1}{3} \delta_{ij} s^2 \right] \, ,
-\label{eq:tidal_th_TT}
-\end{eqnarray}
-where 
-\begin{eqnarray}
-C_2 = \frac{5 A_2 \bar{C_1} \Omega_{\rm m} \rho_{\rm crit}}{D^2(z)} \,  = \left[ \frac{-5 A_2}{A_1 D(z)} \right] C_1.
-\end{eqnarray}
-Under the approximation that line-of-sight alignments are mostly suppressed from cosmic shear measurement due to the broad lensing kernels, 
-we show in  Appendix \ref{app:2d_TT} that the terms inside the square bracket in Eq. (\ref{eq:tidal_th_TT}) leads to:
-\begin{eqnarray}
-\epsilon_1^{\rm TT} = C_2  \left[ s_{xx}^2 - s_{yy}^2\right] \, , \epsilon_2^{\rm TT} = 2 C_2 s_{xy}\left[s_{xx}+s_{yy}  \right]\, ,
-\end{eqnarray}
-both quadratic in the tidal field components.
-
-%-----------------------------------
-\subsection{$\delta$-TT}
-\label{subsec:IA_th_TT}
-
-Following the relation between the NLA and the $\delta$-NLA model, galaxies in the TT model are also assume to be randomly scattered on the sky, which we know to be a bad approximation.
-Computing the next-order contribution to the TT model involves two-loop perturbation theory calculations that have not been done yet due to the significantly higher complexity of such task.
-in simulations however, the $\delta$-weighting term is straight-forward to implement, as it involves to simply infuse the TT model onto galaxies that trace the matter field with a non-zero biasing factor.
-As for the $\delta$-NLA model, the $\delta$-TT ellipticities can  be related to the TT model as:
-\begin{eqnarray}
-\epsilon_{1/2}^{\delta-\rm TT} = \epsilon_{1/2}^{\rm TT}\times(1 + b_{\rm TA}\delta) \, .
-\label{eq:tidal_th_deltaTT}
-\end{eqnarray}
- There are currently no theoretical models for $\delta$-TT, which means that predictions from this model are, at the moment, completely simulation-based.
-
-It is worth recalling here that other IA models exist in the literature, and that at this point observations are not precise enough to set strong constraints on them, further motivating our flexible multi-model approach.
-
-%\subsection{Likelihood}
-%\label{subsec:likelihood}
-
-%Multi-Gaussian likelihood, analytical Covariance matrix (Gauss + non-Gauss + SSC) from {\sc TJPCov}, Firecrown, sampler, priors.
-
-%---------------------
-\section{Simulations}
-\label{sec:sims}
-
-%-------------
-\subsection{Cosmic shear galaxy catalogues} 
-\label{subsec:WL_cats}
-
-The weak lensing simulations developed for this work are based on ray-tracing mass sheets produced from the Outer Rim $N$-body simulation \citep{OuterRim}, which evolved 10,240$^3$ particles in a (5.225 Gpc)$^3$ cosmological volume, assuming a flat $\Lambda$CDM cosmology with $\Omega_{\rm m}$=0.2648, $\Omega_{\rm b}$=0.0448, $h$=0.71, $\sigma_8$ = 0.801, $n_{\rm s}$= 0.963, $w_0$=-1.00.
-A total of 101 particle snapshots were originally saved, of which we use only those with $z<4.0$.
-Particles from each dump are assigned to curved mass shells approximately 114 Mpc thick, producing a sequence of 57 {\sc Healpix} maps $\delta(\theta,\phi,\chi_i)$ with {\sc nside} = 8192 and $i=1..57$, filling up a light-cone over an octant up to $z=3$.
-%More details on this procedure can be found  in \citet{cosmoDC}, where lensing quantities are computed specifically for the generation of the {\sc cosmoDC2}  synthetic sky catalogue.
-
-Ray-tracing is performed in the Born approximation, summing over the mass shells using the $\chi$-integral of Eq.
-(\ref{eq:C_ell}).
-A source plane is placed at the high-redshift edge of every mass planes, resulting in a series of convergence  maps  $\kappa(\theta,\phi,\chi_i)$ that are subsequently transformed into shear maps $\gamma_{1/2}(\theta,\phi,\chi_i)$ using the Kaiser-Squires methods \citep{KaiserSquires}, which is implemented via efficient {\sc HealPy alm2map} routines.
-
-We position galaxies in the light cone following exactly our chosen $N(z)$, and interpolate the shear quantities at their location. We follow two distinct algorithm to achieve this:
-\begin{enumerate}
-\item {\it Random:} galaxies RA and Dec are distributed randomly on the octant, thereby matching this fundamental assumptions in the NLA and TT models. 
-\item {\it Linear bias:} galaxies RA and Dec are sampled from the mass sheets smoothed\footnote{We also tried sampling the field with 0.1 and 0.5 $h^{-1}$Mpc but this resulted in noisier results.} over 1.0 $h^{-1}$Mpc (comoving), assuming a linear bias of $b_{\rm TA}$, now matching instead the assumptions of the $\delta$-NLA and $\delta$-TT models.
-With this method we produce galaxy positions assuming first $b_{\rm TA}=1.0$ (our fiducial case) and also $b_{\rm TA}=2.0$, enhancing the  model flexibility.
-\end{enumerate}
-
-Since source clustering is a higher order effect in cosmic shear, the measured $\xi_{\pm}$ from these three mocks (random, $b_{\rm TA}=1.0$ and $b_{\rm TA}=2.0$) show negligible differences ({\it to quantify and cite}).
-In contrast, the impact on the IA contamination is significant and can double the secondary signal in certain circumstances.
-The main explanation for this is that while clustered sources are uncorrelated with the foreground matter responsible for the lensing signal, the high-density regions they live are also subject to the largest tidal fields.
-
-%----------
-\subsection{Projected tidal fields}
-\label{subsec:IA_sims}
-
-\begin{figure*}
-\caption{Density field and the associated projected tidal field tensors.}
-\label{fig:maps}
-\end{figure*}
-
-Our infusion method completely relies on couplings between intrinsic galaxy shapes and the local tidal field, hence the first step in our method consist in extracting the tidal field maps $s_{ij}(\theta,\phi,\chi_i)$ from the mass maps $\delta(\theta,\phi,\chi_i)$ that source them.
-In three dimensions, trace-free tidal tensor $s_{ij}(\boldsymbol x)$ can be obtained from the matter over-density field $\delta(\boldsymbol x)$ as   \citep{Catelan_IA_Tidal}:
-\begin{eqnarray}
- \widetilde{s}_{ij} (\boldsymbol k)  = \left[\frac{k_i k_j}{k^2} - \frac{\delta_{ij}}{3}\right]  \widetilde {\delta}(\boldsymbol k) \mathcal{G}(\sigma_{\rm G}) \, ,
- \label{eq:sij}
-\end{eqnarray}
-where $\mathcal{G}(\sigma_{\rm G})$ is a three-dimensional Gaussian function described by a single (free) parameter $\sigma_{\rm G}$ that  controls the physical scales which are allowed to affect the IA term in our model.
-Tilde symbols  denote Fourier transformed quantities,  the indices $(i,j)$ label the components of the Cartesian wave-vector $\boldsymbol{k}^T = (k_x,k_y,k_z)$, and $k^2 = k_x^2 + k_y^2 + k_z^2$. 
-As shown in \citet{Tidalator} for Cartesian coordinates, projected tidal fields  computed from projected mass sheets provide and excellent agreement with the NLA model, which in contrast computes the full tidal fields from the three-dimensional matter density and project along the radial dimension at the end.
-We promote this transformation to curved-sky in this work, exploiting the  polarisation {\sc alm2map} operations built in {\sc Healpy}.
-In particular, noting that $Q=s_{xx}-s_{yy}$, $U=s_{xy}$ and $\delta=s_{xx}+s_{yy}$, we compute the curved-sky tidal field tensors ${s}_{ij}({\boldsymbol \theta})$ as:
- \begin{eqnarray}
-s_{xx}({\boldsymbol \theta})  =  \left[\frac{ \delta + Q}{2}  - \frac{\delta}{3}\right] \, ,s_{yy}({\boldsymbol \theta})  =  \left[\frac{\delta - Q}{2}  - \frac{\delta}{3}\right] \, , s_{xy}({\boldsymbol \theta}) = U
- \label{eq:sij_2D_sph}
- \end{eqnarray}
-where the $U({\boldsymbol \theta})$ and $Q({\boldsymbol \theta})$ maps are smoothed by the Gaussian beam with width $\sigma_{\rm G}$.
-We suppress large artificial tidal fields at the maps boundary by replicating 8$\times$ the density maps defined on the octant and working on a full sky density $\delta$; we re-apply the octant mask on the tidal field maps after the operation.
-Note that the value of $\sigma_{\rm G}$ is a free parameter both in the infusion technique described in this paper and in the NLA and TATT models.
-We therefore explore two cases, $\sigma_{\rm G}=0.1$Mpc and 0.5Mpc, however this may be further optimised in the future.
-
-%are specified within the NLA model.
-Smoothing amounts to selecting physical scales that do not contribute to the alignment of galaxies, which is still a debatable quantity, but is also introduced for numerical stability.
-\citet{Blazek2015} argues that 1.0 $h^{-1}$Mpc could be a reasonable fiducial value, being larger then the typical halo size, but recognizes that one-halo terms are also required to better match the observations.
-In their later work, \citet{Blazek2019} do not include smoothing at all, and neither do the KiDS-1000 nor DES-Y1 analyses based on the NLA model \citep{KiDS1000_Asgari,DESY1_Troxel}.
-In this work we used a two-dimensional Gaussian filter and calibrated $\sigma_{\rm G}$ empirically to $\sigma_{\rm G}=0.1h^{-1}$Mpc (see Sec.
-\ref{subsubsec:sigma_G}), however these two choices are arbitrary and could possibly be better optimised in the future; we also explore $\sigma_{\rm G}=0.5h^{-1}$Mpc later on.
-We note that the smoothing scale is degenerate with the resolution of the simulation itself, and that one should use caution when smoothing on scales that approach the resolution limits.
-
-%We employ a numerical technique worth mentioning here: the Fourier transforms involved in computing Eq.
-(\ref{eq:sij_2D}) are computed from the full (projected) periodic boxes of the simulations, then interpolated on the light-cones.
-We find that tidal field computed directly from the $10\times10$ deg$^2$ light-cones introduces significant large scales features in the tidal field maps, largely caused by  the non-periodic boundary conditions, which our method avoids.
-Projected tidal field maps $s_{11}$, $s_{22}$ and $s_{12}$ are constructed that way for each mass sheets; Fig.
-\ref{fig:maps} shows the  three tidal fields and the mass maps for one of them.
-We can clearly see the connection between all maps around over-dense regions.
-{\it (Include a figure of $s_ij$ and $\delta$)}.
-
-{\it [Mention normalisation of the tidal fields by $0.6252 = H_0/114$ = 1/shell-thickness}
-
-%of every light-cones and interpolated at the position of every galaxy.
-Fig.
-\ref{fig:tidalator} illustrates this process for a small zoomed-in patch at $z\sim0$, starting from a $\delta_{2D}(\boldsymbol \theta)$ map (upper large panel), computing the tidal field components (middle four panels) and comparing the results with the cosmic shear signal generated by the same mass distribution (bottom two panels).
-The tidal field maps clearly reproduce the cosmic shear maps, and the minus sign in front of both terms in Eq.
-(\ref{eq:tidal_th}) causes the IA to undo some of the lensing signal.
-
-\subsection{Infusion of intrinsic alignments}
-\label{subsec:IA_infusion}
-
-Having now produced shear catalogues and tidal field maps, we can now use Eq.
-\ref{eq:tidal_th} to couple linearly the alignment of galaxies with the local tidal field, or Eq.
-\ref{eq:tidal_th_TT} to use instead a quadratic coupling.
-These allow us to compute the intrinsic ellipticities ${\boldsymbol \epsilon}^{\rm int}$ for the four IA models described in Sec.
-\ref{sec:IA_th}, which we combine with the cosmic shear signal ${\boldsymbol g}$ to compute observed ellipticities:
-\begin{eqnarray}
-{\boldsymbol \epsilon}^{\rm obs} = \frac{{\boldsymbol \epsilon}^{\rm int} + {\boldsymbol g}}{1 + {\boldsymbol \epsilon}^{\rm int}{\boldsymbol g^*}} \,, {\rm with \, \, } 
-{\boldsymbol \epsilon}^{\rm int}  = \frac{{\boldsymbol \epsilon}^{\rm IA} + {\boldsymbol \epsilon}^{\rm ran}}{1 + {\boldsymbol \epsilon}^{\rm IA}{\boldsymbol \epsilon^{\rm ran, *}}}.
-\label{eq:eps_obs}
-\end{eqnarray}
-In the above expressions, the denominators ensures that the combined  ellipticities never exceed unity.
-The complex spin-2 reduced shear ${\boldsymbol g} \equiv (\gamma_1 + {\rm i} \gamma_2)/(1+\kappa)$ is computed from the shear  $(\gamma_{1/2}$) and convergence ($\kappa$) maps, interpolated at the galaxy positions and redshifts.
-The  random orientation term ${\boldsymbol \epsilon}^{\rm ran}$ is drawn from two Gaussians (one per component) with their standard deviations matching the LSST-Y1 forecast, $\sigma_{\epsilon} = 027$.
-We further constraint  the random ellipticity to satisfy $|{\boldsymbol \epsilon}^{\rm ran}| \le 1.0$.
-%We recall that since our simulated galaxy catalogues trace the dark matter density, our default IA-infusion method  is consistent with the $\delta$-NLA model (see Sec.
-\ref{subsec:IA_th_ext}).
-Analytical predictions for the two-point functions are more involved in this case \citep[see][]{Blazek2019} and not yet available on the public {\sc cosmoSIS} release.
-We therefore validate our methods with the standard NLA first, which we infuse by `correcting' the $\delta$-NLA measurement with Eq.
-(\ref{eq:tidal_th_deltaNLA}), i.e.
-by replacing ${\boldsymbol \epsilon}^{\rm IA}$ by ${\boldsymbol \epsilon}^{\rm IA}/(1 + b_{\rm TA} \delta)$ in our simulations.
-Once again, these are less realistic but better suited for validation of the measured $\gamma$-2PCFs against a theoretical model; after this is established, we use the $\delta-$NLA catalogues as our fiducial infusion model.
-We re-iterate here that the same tidal fields, shear maps and IA coupling equations are used for the NLA and $\delta$-NLA models, and separately for the TT and $\delta$-TT models; these  only differ by the fact that in one case the galaxies are placed at random on the octant, while in the other case they are linearly tracing the dark matter.
-
-Also note that our current IA models make no differentiation between galaxy colours or type, and instead treats the full sample as a single population that has a single, effective, alignment signall \citep[see][for an example with a red/blue split]{DESY1_IA_Samuroff}.
-
-%---------------------
-\section{Validation with $\xi_{\pm}$}
-\label{sec:validation}
-
-% Requires the booktabs if the memoir class is not being used
-\begin{table}
-   \centering
-   %\topcaption{Table captions are better up top} % requires the topcapt package
-   \begin{tabular}{@{} lcr @{}} % Column formatting, @{} suppresses leading/trailing space
-      \hline
-      \hline
-       %\multicolumn{2}{c}{Item} \\
-      model   		& ($A_{\rm IA}, b_{\rm TA}, A_2)$ \\
-      \hline
-      NLA     		& {($\pm$1,0,0) }&  \\
-      \multirow{2}{*}{$\delta-$NLA }  	&   {($\pm$1,1,0)}   \\
-      							&  {(1,2,0)}   \\
-      TT 			&  {(0,0,$\pm$1)} &  \\
-      \multirow{2}{*}{$\delta$-TT} 	&  {(0,1,$\pm$1)}   \\
-      				&  {(0,2,1)}   \\
-      TATT- fiducial	&  { (1,1,1)}  \\
-      %TATT-DESY3	&   (-0.7,1,1.9) & \\
-      \hline
-      \hline
-
-   \end{tabular}
-   \caption{IA models infused in this work.}
-   \label{table:IAmodels}
-\end{table}
-
-%------------------------------
-\subsection{NLA model}
-\label{subsubsec:sigma_G}
-
-See Fig. \ref{fig:xi_NLA}
-%---------------
-\begin{figure*}
-%\includegraphics[width=\columnwidth]{graphs/frac_xip_IA1_skysim}
-\includegraphics[width=\columnwidth]{graphs/frac_xip_IA1_skysim_NLA_srd.jpg}
-\includegraphics[width=\columnwidth]{graphs/frac_xim_IA1_skysim_NLA_srd.jpg}
-\caption{Ratio between the shear correlation functions with and without IA, assuming the NLA model with $A_{\rm IA}=1.0$ both in the simulations and theory.
-Measurements shown in green and brown correspond to smoothing scales of 0.1 and 0.5 $h^{-1}$Mpc in the tidal field.
-There is no shape noise in the simulations, but it is included in the error bars.}
-\label{fig:xi_NLA}
-\end{figure*}
-%---------------
-
-%------------------------------
-\subsection{$\delta$-NLA model}
-\label{subsec:deltaNLA}
-
-See Fig. \ref{fig:xi_deltaNLA}.
-
-\begin{figure*}
-\includegraphics[width=\columnwidth]{graphs/frac_xip_IA1_skysim_deltaNLA_srd}
-\includegraphics[width=\columnwidth]{graphs/frac_xim_IA1_skysim_deltaNLA_srd}
-\caption{Same as Fig.
-\ref{fig:xi_NLA}, but for the $\delta$-NLA model with $A_{\rm IA}=1.0$ and $b_{\rm TA}=1.0$, and only for smoothing of 0.5$h^{-1}$Mpc.
-The dashed black lines show the NLA predictions to better highlight the differences.
-}
-\label{fig:xi_deltaNLA}
-\end{figure*}
-
-\begin{figure}
-\includegraphics[width=\columnwidth]{graphs/frac_xip_bta1_rescaled}
-\caption{Ratio between the shear correlation functions with and without IA in tomographic bin combination 2-5.
-The brown and green symbols show measurements from simulations constructed with $b_{\rm TA}$ = 0.0 and 2.0 respectively,  the black solid and dotted lines shown their predictions, while the blue symbols are obtained by rescaling $b_{\rm TA}$ = 1.0 simulations using Eq.
-\ref{eq:bta_rescale}.
-}
-\label{fig:xi_deltaNLA_rescaled}
-\end{figure}
-
-We verified that it works equally well for $b_{\rm TA}$ = 1.0 and 2.0.
-
-%------------------------------
-
-Using this, we $b_{\rm TA}$-rescale our $b_{\rm TA}=1.0$ mock to $b_{\rm TA}=2.0$ and to $0.0$ mocks.
-Results are shown in Fig.
-\ref{fig:xi_deltaNLA_rescaled} for one of the tomographic bin.
-It works reasonably well, but lower redshift are less accurate due to the increased  shot noise (not shown), hence we do not recommend using this.
-
-%------------------------------
-\subsection{TT model}
-\label{subsec:TT}
-
-See Fig. \ref{fig:xi_TT}
-
-\begin{figure*}
-\includegraphics[width=\columnwidth]{graphs/frac_xip_IA1_skysim_TT_srd.jpg}
-\includegraphics[width=\columnwidth]{graphs/frac_xim_IA1_skysim_TT_srd.jpg}
-\caption{Same as Fig. \ref{fig:xi_NLA}, but for the TT model with $A_2=1.0$. Here, the dashed black lines show the NLA predictions to better highlight the differences. }
-\label{fig:xi_TT}
-\end{figure*}
-
-\begin{figure*}
-%\includegraphics[width=\columnwidth]{graphs/frac_xip_C2_m1_skysim_deltaTT}
-\includegraphics[width=\columnwidth]{graphs/frac_xip_IA1_skysim_deltaTT_srd.jpg}
-\includegraphics[width=\columnwidth]{graphs/frac_xim_IA1_skysim_deltaTT_srd.jpg}
-\caption{Same as Fig. \ref{fig:xi_deltaNLA}, but comparing the TT and the $\delta$-TT models, with $A_2=1.0$, $b_{\rm TA}$ = 1.0, and only for smoothing of 0.5$h^{-1}$Mpc. }
-\label{fig:xi_deltaTT}
-\end{figure*}
-
-To match the theory, we need to apply the following calibration: $\epsilon^{\rm IA, TT}(z<0.5) \rightarrow \epsilon^{\rm IA, TT} /2.5$.
-
-%------------------------------
-\subsection{$\delta$-TT model}
-\label{subsec:TT}
-
-See Fig. \ref{fig:xi_deltaTT}
-
-To match the TT theory, we need to apply the following calibration: $\epsilon^{\rm IA, TT}(z<0.5) \rightarrow \epsilon^{\rm IA, TT} /5.0$, followed by $\epsilon^{\rm IA, TT} \rightarrow \epsilon^{\rm IA, TT}/7.0$.
-
-%\subsection{Validation with full inference}
- %\label{sec:inference}
-
-%priors, firecrown, Takahashi $P(k)$
-
 \section{Higher-order weak lensing statistics}
@@
 ... use the mocks from Table \ref{table:IAmodels} to compute derivatives. Show.
-
-%----------
-\section{Conclusions}
-\label{sec:conclusion}
-%----------
-
-\section*{Acknowledgements}
-
-JHD acknowledges support from an STFC Ernest Rutherford Fellowship (project reference ST/S004858/1).
-Ray-tracing computations were carried on the NERSC [acknowledgments] ...
-HACC [acknowledgements] ...
-OuterRim [Acknowledgments]
-\\
-
-Some of the results in this paper have been derived using the {\sc healpy} and {\sc HEALPix} packages.
-\\
-\\
-\\
-{\footnotesize All authors contributed to the development and writing of this paper. JHD led the analysis.... }
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Data Availability}
-
-%The SLICS numerical simulations can be found at http://slics.roe.ac.uk/, while the cosmo-SLICS can be made available upon request.
-
-%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%
-
-% The best way to enter references is to use BibTeX:
-
-\bibliographystyle{hapj}
-\bibliography{IA} % if your bibtex file is called example.bib
-
-% Alternatively you could enter them by hand, like this:
-% This method is tedious and prone to error if you have lots of references
-%\begin{thebibliography}{99}
-%\bibitem[\protect\citeauthoryear{Author}{2012}]{Author2012}
-%Author A.~N., 2013, Journal of Improbable Astronomy, 1, 1
-%\bibitem[\protect\citeauthoryear{Others}{2013}]{Others2013}
-%Others S., 2012, Journal of Interesting Stuff, 17, 198
-%\end{thebibliography}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%% APPENDICES %%%%%%%%%%%%%%%%%%%%%
-
-\appendix
-
-\section{Projected Tidal Field}
-\label{app:2d_TT}
-
-\JHD{[To reword]} We derive in this Appendix...  
-The prescription to assign an intrinsic alignment based on the projected tidal field, described in Eq.
-(\ref{eq:tidal_th}), involves the combinations $(s_{xx} - s_{yy})$ and $s_{xy}$, which therefore correspond to:
-\begin{eqnarray}
- \widetilde{\epsilon}_1^{\rm IA} (\boldsymbol k_{\perp})  &\propto& \left(\frac{k_x^2 - k_y^2}{k^2} \right) \widetilde{\delta}_{\rm 2D}(\boldsymbol k_{\perp})\mathcal{G_{\rm 2D}}(\sigma_{\rm G})  \, ,\nonumber \\
- \widetilde{\epsilon}_2^{\rm IA} (\boldsymbol k_\perp)  &\propto& \left(\frac{k_x k_y}{k^2} \right) \widetilde {\delta}_{\rm 2D}(\boldsymbol k_\perp)\mathcal{G_{\rm 2D}}(\sigma_{\rm G}) 
- %\label{eq:sij}
-\end{eqnarray}
-
-Aside from the smoothing kernel, these are the same filters that are used for converting convergence maps to shear maps under the \citet[][KS hereafter]{KaiserSquires} inversion:
- \begin{eqnarray}
- \widetilde{\gamma_1} (\boldsymbol \ell)  = \left(\frac{k_x^2 - k_y^2}{k^2} \right) \widetilde {\kappa}(\boldsymbol \ell) \, , \hspace{1cm} \widetilde{\gamma_2} (\boldsymbol \ell)  = \left(\frac{k_x k_y}{k^2} \right) \widetilde {\kappa}(\boldsymbol \ell)
- %\label{eq:sij}
-\end{eqnarray}
-meaning that on can linearly combine the mass sheets with the correct coefficients and obtain intrinsic ellipticities from a normal KS inversion.
-
-Projecting out the $z$ components (e.i. $s_{0i}$=$s_{i0}$=0 for all $i$),  the tidal torque terms from Eq. (\ref{eq:tidal_th_TT}) can be expanded as:
- \begin{eqnarray}
-\gamma^{\rm TT}_{ij}&=& C_2 \left[\sum_{k=x,y} s_{ik} s_{kj} -\frac{1}{3} \delta_{ij} s^2\right] \\
-                                  &=&C_2 \left[ s_{ix}s_{xj}  + s_{iy}s_{yj}  -  \frac{1}{3} \delta_{ij} \left( s_{xx}^2 + s_{yy}^2 +2s_{xy}^2 \right)  \right] \, .
-\end{eqnarray}
-Specifically, this yields:
- \begin{eqnarray}
-\gamma^{\rm TT}_{xx}&=& C_2 \left[\frac{2}{3}s_{xx}^2  -  \frac{1}{3}s_{yy}^2 + \frac{1}{3}s_{xy}^2 \right]\, ,  \nonumber \\
-\gamma^{\rm TT}_{yy}&=& C_2 \left[-\frac{1}{3}s_{xx}^2  +  \frac{2}{3}s_{yy}^2 + \frac{1}{3}s_{xy}^2  \right]\, , \\
-\gamma^{\rm TT}_{xy}&=& C_2 s_{xy}\left[s_{xx}+s_{yy}  \right]\, . \nonumber                                  
-\end{eqnarray}
-With the standard ellipticity definitions $\epsilon_1^{\rm TT}\equiv \gamma_{xx}^{\rm TT} - \gamma_{yy}^{\rm TT}$ and $\epsilon_2^{\rm TT}\equiv -2 \gamma_{xy}$, we obtain:
-\begin{eqnarray}
-\epsilon_1^{\rm TT} = C_2  \left[ s_{xx}^2 - s_{yy}^2\right] \, , \epsilon_2^{\rm TT} = -2 C_2 s_{xy}\left[s_{xx}+s_{yy}  \right]\, .
-\end{eqnarray}
-In the TATT model, the total intrinsic ellipticity component is therefore given by $\epsilon_{1/2}^{\rm IA} = \epsilon_{1/2}^{\rm TATT} = \epsilon_{1/2}^{\delta{\rm-NLA}} + \epsilon_{1/2}^{\rm TT}$.
-
-% Don't change these lines
-\bsp	% typesetting comment
-\label{lastpage}
-\end{document}
-
-% End of mnras_template.tex

### 2024-03-27 paper_IA.tex
Add more equations about delta-NLA model

@@
 
+Finally, we note that fully modelling our infusion method includes contributions beyond one-loop calculations in the $II$ term.
+Indeed, the two-point function correlating ellipticities (Eq.
+\ref{eq:tidal_th_deltaNLA}) between redshift bins $i,j$ is given by:
+ \begin{eqnarray}
+\langle \epsilon_{i}^{\delta-\rm NLA} \epsilon_{j}^{\delta-\rm NLA}\rangle &=& \langle \epsilon_{i}^{\rm NLA}\times(1 + b_{\rm TA}\delta_i) \epsilon_{j}^{\rm NLA}\times(1 + b_{\rm TA}\delta_j)\rangle\\
+&=& \langle \epsilon_{i}^{\rm NLA}  \epsilon_{j}^{\rm NLA}\rangle \nonumber \\
+&+& b_{\rm TA} \times \left(\langle \epsilon_{i}^{\rm NLA}  \epsilon_{j}^{\rm NLA}\delta_j  \rangle + \langle \epsilon_{i}^{\rm NLA}  \epsilon_{j}^{\rm NLA}\delta_i  \rangle \right)\nonumber\\
+&+& b_{\rm TA}^2 \langle \epsilon_{i}^{\rm NLA}  \epsilon_{j}^{\rm NLA}\delta_i  \delta_j \rangle \, ,
+\label{eq:2pcf_deltaNLA}
+\end{eqnarray}
+where the last term is fourth order and involves two-loop calculations.
+For this reason, our $\delta$-NLA model is not expected to be well described by the one-loop calculations.
+Note that replacing one of the ellipticity terms by the cosmic term includes only terms up to third order in the field (e.g $\langle \epsilon_{i}^{NLA}\delta_i \gamma_j \rangle$, ...), hence  we expect the GI term to be well described.
+The above equation also predict that the deviations from one-loop theory scales as $b_{\rm TA}^2$, hence should be larger for population that are more biased.
+
 %-----------------------------------
@@
 \begin{figure}
+\includegraphics[width=\columnwidth]{graphs/xip_deltaNLA_bta1.jpg}
 \includegraphics[width=\columnwidth]{graphs/frac_xip_bta1_rescaled}

### 2024-03-27 sections/3_ia_models.tex
Included some delta-NLA equations

\section{Intrinsic alignment models}
 \label{sec:IA_th}

Galaxies are influenced by the gravitational tidal forces from the vast structures in which they reside, leading to their intrinsic shapes being aligned in a way unrelated to the effects observed through weak lensing.
This alignment serves as an additional factor (a contamination) that skews the accuracy of shape correlation measurements carried in cosmic shear analyses.
The underlying physical principles that govern intrinsic alignments (IA) remain unclear, and even the models that attempt to describe these alignments have parameters that are not definitively determined by existing data, as discussed in various review articles \citep[see][for reviews]{Joachimi_IA_review_2015, Kirk_IA_review_2015, Troxel_IA_review_2015, Kiessling_IA_review_2015}.

%Galaxies interact with the tidal forces caused by the large-scale structure they are located in, causing their intrinsic shapes to acquire correlated alignments that has nothing to do with the correlations caused by weak lensing (the cosmic shear).
%This therefore acts as a secondary signal that contaminates the shape correlation measurements carried out in a cosmic shear analysis. 
%There is no consensus on the actual physical model that describes the IA signal, and even when adopting these, the free parameters they contain are only weakly constrained from the data \citep[see][for reviews]{Joachimi_IA_review_2015, Kirk_IA_review_2015, Troxel_IA_review_2015, Kiessling_IA_review_2015}.
%The most widely used model in the literature is the non-linear alignment model of \citet{NLA}, however it is now recognised that this is an effective model with limited precision, and the community is now progressively shifting towards more complex models. 
In this study, we explore two models of coupling, each implemented across three scenarios of galaxy bias.
This approach yields six distinct models for intrinsic alignments, which are detailed in the subsequent subsections. 
Our models establish a connection between the intrinsic shapes of galaxies and the local density fluctuations as well as the projected tidal fields. 
This linkage then defines an intrinsic ellipticity tensor, $\gamma_{ij}^{\rm IA}$, from which the intrinsic ellipticities are extracted.
%In this work we consider two coupling models, each applied on three galaxy bias cases, resulting in six different IA models, described in the following sub-sections.
%In all cases, our models couple the galaxy intrinsic shapes with the local over-density and projected tidal field, then prescribes an intrinsic ellipticity tensor $\gamma_{ij}^{\rm IA}$, from which intrinsic  ellipticities are extracted:
\begin{equation}
\begin{split}
\epsilon_{1}^{\rm IA} &= \gamma_{xx}^{\rm IA} - \gamma_{yy}^{\rm IA} \, , 
\\
\epsilon_{2}^{\rm IA} &= 2 \gamma_{xy}^{\rm IA} \, .
\label{eq:tidal_th_deltaNLA}
\end{split}
\end{equation}
\niko{shouldn't the indices be $i$ and $j$ here in the equation?}

\subsection{Nonlinear alignment (NLA) Model}

%The observed ellipticity of a galaxy ${\boldsymbol \epsilon}_{\rm obs} $ is a combination of its intrinsic shape ${\boldsymbol \epsilon}_{\rm int}$ and a cosmic shear signal ${\boldsymbol \gamma}$, the former of which can be further divided in a random component ${\boldsymbol \epsilon}^{\rm ran}$ and an alignment term ${\boldsymbol \epsilon}^{\rm IA}$.
The NLA model of \citet{NLA} is the most widely used intrinsic alignment model in the cosmic shear literature thus far.
According to the NLA, IA are caused by a linear coupling between galaxy shapes and the nonlinear large-scale tidal field at the galaxy position.
The intrinsic ellipticities $\epsilon_{1,2}^{\rm NLA}$ are related to tidal field $s_{ij}$ by:
\begin{equation}
\begin{split}
\epsilon_1^{\rm NLA} &= - \frac{A_{\rm IA}\bar{C_1}\bar{\rho}(z)}{D(z)} (s_{xx} - s_{yy}) , \\    \epsilon_2^{\rm NLA} &= - \frac{2 A_{\rm IA}\bar{C_1}\bar{\rho}(z)}{D(z)} s_{xy}\;,
\label{eq:tidal_th}
\end{split}
\end{equation}
where $s_{ij} = \partial_{ij}\phi$ are the Cartesian components of the tidal tensor of the gravitational potential,  $D(z)$ is the linear growth factor, $\bar{\rho}(z)$ is the mean matter density at redshift $z$, and $\bar{C_1}=5\times 10^{-14} M_{\odot}^{-1} h^{-2} {\rm Mpc}^3$ is a constant calibrated in \citet{Brown2002}. 
The strength of tidal coupling is controlled by the parameter $A_{\rm IA}$, a key variable in the NLA model primarily constrained by current cosmic shear studies.
While this model can incorporate the dependency  on redshift and luminosity, such adjustments are not applied in our analysis.
It's important to clarify that the "nonlinear" aspect of the model's name might be somewhat misleading; it actually pertains to the use of the nonlinear matter power spectrum $P(k)$ in its computations. 
The relationship between the intrinsic shapes of galaxies and the tidal field remains linear.
Equation (\ref{eq:tidal_th}) is employed to determine the intrinsic ellipticities of galaxies using the tidal field components $s_{xx}$, $s_{yy}$, and $s_{xy}$, which are detailed in Section \ref{subsec:IA_infusion}.
%The strength of the tidal coupling is modulated by the amplitude parameter $A_{\rm IA}$, which is the main NLA parameter constrained by current cosmic shear surveys.
%Note that this model can be augmented by redshift and luminosity dependencies, however we do not use these here. 
%Also note that the term `nonlinear' in the model name can be  misleading, as it refers to the nonlinear matter power spectrum $P(k)$ that is used in its calculations; the coupling between the intrinsic galaxy shapes and the tidal field is still linear and Eq.( \ref{eq:tidal_th}) is used to assign intrinsic ellipticities to galaxies, given maps of the tidal field components $s_{xx}$, $s_{yy}$ and $s_{xy}$ (presented in  Sec. \ref {subsec:IA_infusion}).

\niko{I think we should introduce II, GG, GI, and IG terms in the cosmic shear stats at the beginning when we define C ells. That way we do not mention them out of the blue here}
In the context of two-point functions, these intrinsic shapes contribute to an intrinsic-intrinsic ($II$) term and an intrinsic-shear coupling ($GI$) term \citep{Hirata2004}, both secondary signals to the true cosmic shear ($GG$) term, with the $GI$ typically dominating the IA sector in cross-tomographic measurements. 
The $II$ and $GI$ terms  can be both computed from the matter power spectrum as: 
 \begin{eqnarray}
P_{II}(k,z) =  \left(\frac{A_{\rm IA}\bar{C_1}\bar{\rho}(z)}{D(z)}\right)^2a^4(z) P_{\delta}(k,z)
\label{eq:Pk_II_th}
\end{eqnarray}
and
\begin{eqnarray}
P_{GI}(k,z) = - \frac{A_{\rm IA}\bar{C_1}\bar{\rho}(z)}{D(z)}a^2(z) P_{\delta}(k,z) \, ,
\label{eq:Pk_GI_th}
\end{eqnarray}
which can then be past to the Limber integration (Eqs. \ref{eq:C_ell} and \ref{eq:xipm_th}) to compute  the secondary signals $\xi_{\pm}^{II}(\theta)$ and $\xi_{\pm}^{GI}(\theta)$.

\subsection{Extended-NLA Model}
\label{subsec:IA_th_extNLA}

%[{\it here}]

%As discussed later, the key quantity of interest to cosmic shear analysis is not the tidal tensor itself but its trace-free version, since shape correlations with the density field are subdominant, even though peaks in high density environments are less elliptical on average. Consequently, the model itself has a restricted range of validity: on small scales, higher order couplings to the ellipticity field ${\boldsymbol \epsilon}^{\rm IA}$  become important, however these are neglected in the NLA model. Only the non-linear evolution of the tidal tensor itself is taken into account, since it does fit observations quite well.

%We note that the NLA predicts additional higher-order terms and non-zero $B$-modes \citep{Hirata2004} that we neglect  in this analysis. Also, as shown in \citet{IA_EFT}, the NLA model can be interpreted as the lowest order description of the alignment process of galaxies in the light of an effective field theory description.

The NLA model, as discussed in the previous section, is a common tool for analyzing cosmic data but has significant limitations, indicating it might not accurately capture the intricacies of the intrinsic alignment signal. 
Recognizing the potential importance of more complex interactions, extensions to the NLA model that incorporate perturbation theory have been proposed by \citet{Blazek2015} and  \citet{Blazek2019}. 
These extensions highlight the necessity of considering higher-order couplings.
A key enhancement involves incorporating a term that accounts for over-density weighting.
This adjustment stems from the observation that galaxies, which serve as the observational basis for IA, are not randomly distributed but rather follow the underlying matter density distribution. 
The theoretical framework for including this term employs one-loop perturbation theory, as outlined by \citep{Blazek2019}, under the assumption that galaxies linearly map the over-density, denoted as '$\delta$'.
In essence, this approach modifies the NLA model predictions by applying a $\delta$-weight at the locations of galaxies, thereby refining the model's accuracy in representing the physical reality.
Implementing this adjustment in numerical simulations could theoretically be straightforward by enhancing the calculated NLA ellipticities with the aforementioned over-density weight:
%The NLA model presented in the last section has been widely used in cosmic data analyses, but it has important known limitations and is therefore bound to fail at describing the IA signal with high precision.
%A perturbation theory extension to the NLA has been introduced in \citet{Blazek2015} and  \citet{Blazek2019}, where it is recognised that higher order couplings could be important and should be considered.
%The first additional term to be included is an over-density weighting term, which arises from the fact that  the intrinsic alignment of galaxies can only be observed at the galaxy positions, which are not distributed randomly on the sky but instead trace the underlying matter density. 
%Accounting for this extra term in theoretical predictions is done with one-loop perturbation theory \citep{Blazek2019} by assuming that the over-density `$\delta$' is linearly traced by the galaxies. 
%Physically, it corresponds to adding a $\delta$-weight to the NLA predictions at the local galaxy positions. 
%At the level of numerical simulations, this could be done in principle simply by augmenting the NLA ellipticities with this weight, namely:
\begin{eqnarray}
\epsilon_{1/2}^{\delta-\rm NLA} = \epsilon_{1/2}^{\rm NLA}\times(1 + \delta \: b_{\rm TA}) \, .
\label{eq:tidal_th_deltaNLA}
\end{eqnarray}
%The $b_{\rm TA}$ term corresponds to the (largely unconstrained) biasing relation between the galaxies and the underlying matter field.
%In practice however, we find this method to be noisy, as many galaxies placed at random actually reside in regions of negative or small $\delta$.
%It is instead preferable to generate mock catalogues with the linear biasing directly applied when assigning galaxy positions, after which no weighting is necessary.
%Subsequently, Eq. (\ref{eq:tidal_th_deltaNLA}) can be used to modify the value of the effective $b_{\rm TA}$ if not wanting to re-populate the light-cone. 
%Indeed, from a mock with a given bias $b_{\rm TA, orig}$, we can rescale the IA contribution to a different $b_{\rm TA, new}$ as:
The term $b_{\rm TA}$ represents the bias relationship between galaxies and the matter field beneath them, a relationship that remains largely undetermined.
In practical applications, this method tends to produce unreliable results due to the tendency of galaxies to be located in areas with negative or minimal $\delta$ values when placed randomly.
A more effective approach is to create mock catalogs by directly applying linear biasing to determine galaxy positions, which eliminates the need for subsequent weighting.

For adjustments without the necessity to repopulate the entire light-cone distribution, Equation (\ref{eq:tidal_th_deltaNLA}) can be applied to alter the effective value of $b_{\rm TA}$. This allows for the recalibration of the intrinsic alignment contribution from an original bias value, $b_{\rm TA}^{\rm orig}$, to a new desired bias, $b_{\rm TA}^{\rm new}$, as:
%\begin{eqnarray}
%{\boldsymbol \epsilon}^{\rm int}_{b_{\rm TA}^{\rm new}}  = \frac{(1 + b_{\rm TA}^{\rm new} \delta)}{(1 + b_{\rm TA}^{\rm orig}\delta)}{\boldsymbol \epsilon}^{\rm int}_{b_{\rm TA}^{\rm orig}} \, .
%\label{eq:bta_rescale}
%\end{eqnarray}
\begin{eqnarray}
{\boldsymbol \epsilon}^{\rm new} = \frac{1 + \delta \: b_{\rm TA}^{\rm new}}{1 + \delta \: b_{\rm TA}^{\rm orig}}{\boldsymbol \epsilon}^{\rm orig} \, .
\label{eq:bta_rescale}
\end{eqnarray}

The extended-NLA model represents an enhanced approach to intrinsic alignment modeling, particularly effective at small scales, as noted by \citealt{Blazek2019}. 
It appears to align more closely with the outcomes of certain hydro-dynamical simulations, as indicated by \citealt{Hilbert_IA2017}.
From a theoretical standpoint, this model is more physically grounded because it accounts for the fact that galaxies in the universe are not dispersed randomly, an assumption the traditional NLA model makes.

Finally, we note that fully modelling our infusion method includes contributions beyond one-loop calculations in the $II$ term. Indeed, the two-point function correlating ellipticities (Eq. \ref{eq:tidal_th_deltaNLA}) between redshift bins $i,j$ is given by:
 \begin{eqnarray}
\langle \epsilon_{i}^{\delta-\rm NLA} \epsilon_{j}^{\delta-\rm NLA}\rangle &=& \langle \epsilon_{i}^{\rm NLA}\times(1 + b_{\rm TA}\delta_i) \epsilon_{j}^{\rm NLA}\times(1 + b_{\rm TA}\delta_j)\rangle\\
&=& \langle \epsilon_{i}^{\rm NLA}  \epsilon_{j}^{\rm NLA}\rangle \nonumber \\
&+& b_{\rm TA} \times \left(\langle \epsilon_{i}^{\rm NLA}  \epsilon_{j}^{\rm NLA}\delta_j  \rangle + \langle \epsilon_{i}^{\rm NLA}  \epsilon_{j}^{\rm NLA}\delta_i  \rangle \right)\nonumber\\
&+& b_{\rm TA}^2 \langle \epsilon_{i}^{\rm NLA}  \epsilon_{j}^{\rm NLA}\delta_i  \delta_j \rangle \, ,
\label{eq:2pcf_deltaNLA}
\end{eqnarray}
where the last term is fourth order and involves two-loop calculations. For this reason, our $\delta$-NLA model is not expected to be well described by the one-loop calculations. Note that replacing one of the ellipticity terms by the cosmic term includes only terms up to third order in the field (e.g $\langle \epsilon_{i}^{NLA}\delta_i \gamma_j \rangle$, ...), hence  we expect the GI term to be well described. The above equation also predict that the deviations from one-loop theory scales as $b_{\rm TA}^2$, hence should be larger for population that are more biased.
%Compared to the NLA, the \dNLA is a stronger IA model, especially on small scales \citep{Blazek2019}, and seems to be preferred by some hydro-dynamical simulations \citep{Hilbert_IA2017}.
%It is also better motivated from a physical point of view, since galaxies are not randomly distributed in our Universe as the NLA assumes.

%-----------------------------------
\subsection{Tidal Torque (TT) Model}
\label{subsec:IA_th_TT}

%As shown in \citet{Blazek2019}, one-loop perturbative calculations include another term, by which galaxies acquire an intrinsic alignment via a coupling between their angular momentum and the tidal field, which can be re-expressed as a quadratic coupling between the tidal field and their shape.
%In this tidal torque model (TT), intrinsic ellipticities are given by:
\citet{Blazek2019} demonstrates that one-loop perturbative calculations introduce an additional term, accounting for how galaxies develop intrinsic alignments through the interaction between their angular momentum and the tidal field.
This interaction can alternatively be described as a quadratic coupling between the tidal field and the shapes of the galaxies. 
Within this tidal torquing theory (TT), the intrinsic ellipticities of galaxies are determined as follows:

\begin{eqnarray}
\gamma_{ij}^{\rm IA, TT} = C_2 \left[ \sum_{k=x,y,z} s_{ik} s_{kj} -\frac{1}{3} \delta_{ij} s^2 \right] \, ,
\label{eq:tidal_th_TT}
\end{eqnarray}
where 
\begin{eqnarray}
C_2 = \frac{5 A_2 \bar{C_1} \Omega_{\rm m} \rho_{\rm crit}}{D^2(z)} \,  = \left[ \frac{-5 A_2}{A_1 D(z)} \right] C_1.
\end{eqnarray}
%Under the approximation that line-of-sight alignments are mostly suppressed from cosmic shear measurement due to the broad lensing kernels, we show in  Appendix \ref{app:2d_TT} that the terms inside the square bracket in Eq. (\ref{eq:tidal_th_TT}) lead to both quadratic in the tidal field components:
Assuming that alignments along the line of sight are largely suppressed in cosmic shear measurements due to the broadlensing kernels, we demonstrate in Appendix \ref{app:2d_TT} that the terms within the square brackets of Eq. (\ref{eq:tidal_th_TT}) result in quadratic terms of the tidal field components:

\begin{equation}
\begin{split}
\epsilon_1^{\rm TT} &= C_2  \left[ s_{xx}^2 - s_{yy}^2\right] \\
 \epsilon_2^{\rm TT} &= 2 C_2 s_{xy}\left[s_{xx}+s_{yy}  \right]\, .
\end{split}
\end{equation}
In this model, galaxies are also assumed to be randomly distributed on the sky. 
Incorporating the $\delta$-weighting necessitates third-order perturbation theory.

%In this model, galaxies are also assumed to be randomly distributed on the sky; the $\delta$-weighted term requires third order perturbations.

%-----------------------------------
\subsection{Extended-TT Model}
\label{subsec:IA_th_extTT}

%Following the relation between the NLA and the $\delta$-NLA model, galaxies in the TT model are also assume to be randomly scattered on the sky, which we know to be a bad approximation.

%Computing the next-order contribution to the TT model involves two-loop perturbation theory calculations that have not been carried out yet due to the significantly complexity of such task. 
%In simulations however, the $\delta$-weighting term is straight-forward to implement, as it involves to simply infuse the TT model onto galaxies that trace the matter field with a non-zero biasing factor.
%As for the \dNLA model, the \dTT ellipticities can  be related to the TT model as:
Calculating the next level of contribution to the TT model requires engaging in two-loop perturbation theory, a process that remains undone due to its considerable complexity.
However, in simulations, applying the $\delta$-weighting term to the TT model is relatively straightforward.
This step merely requires integrating the TT framework onto galaxies that map the matter field with a non-zero bias factor. 
Similar to the \dNLA model, the ellipticities within the \dTT framework can be connected back to the original TT model as follows:
\begin{eqnarray}
\epsilon_{1/2}^{\delta-\rm TT} = \epsilon_{1/2}^{\rm TT}\times(1 + \delta \: b_{\rm TA}) \, .
\label{eq:tidal_th_deltaTT}
\end{eqnarray}
%We choose instead here again to use galaxy positions that themselves are linearly biased.
%As there are currently no theoretical models for \dTT, predictions from this model are, at the moment, completely simulation-based. 
In this study, we opt to utilize galaxy positions that are subject to linear biasing, mirroring our earlier approach.
Given the lack of established theoretical frameworks for the \dTT model, any predictions derived from it are currently reliant solely on simulations.
 This approach underscores our reliance on empirical data to guide our understanding of the implications for \dTT, pending the development of a comprehensive theoretical model.

 %-----------------------------------
\subsection{$b_{\rm nl}$-TATT}
\label{subsec:HOD-TATT}
\niko{there is a compiling error here (due to the subscript) in the title, maybe we can consider renaming this?}

The previous four models combine the linear and quadratic couplings to the cosmic tidal forces  (Eqs. \ref{eq:tidal_th} and \ref{eq:tidal_th_TT}, respectively) with galaxies positioned  either at random or linearly tracing the total matter distribution.
While these are interesting and useful approximations, the connection between galaxies and dark matter is far more complex, and a more accurate picture consists of galaxies populating dark matter haloes, typically with a relaxed, older galaxy close to the centre, and a number of other satellite galaxies orbiting the former.
This halo occupation distribution (HOD) formalism has been used to describe many galaxy samples \citep[\eg][]{SDSS-HOD, BOSS-HOD, GAMA-HOD, DESI-HOD} and is therefore routinely used to in-paint galaxies in dark matter-only simulations.
The last two models from this paper exploit such HOD galaxy samples, extracted from the same underlying distributions, but in this case the galaxy bias is non-linear (labelled $b_{\rm nl}$), with levels on non-linearity that vary with HOD parameters (see Sec. \ref{subsec:HOD}).
We couple these galaxies with both Eqs. \ref{eq:tidal_th} and \ref{eq:tidal_th_TT}, resulting in two final models which we name  $b_{\rm nl}$-NLA and  $b_{\rm nl}$-TT, both being combined into the more general  $b_{\rm nl}$-TATT model.

%Finally, it is worth recalling here that other IA models exist in the literature, and that at this point observations are not precise enough to set strong constraints on them, further motivating our flexible multi-model approach.

%\subsection{Likelihood}
%\label{subsec:likelihood}

%Multi-Gaussian likelihood, analytical Covariance matrix (Gauss + non-Gauss + SSC) from {\sc TJPCov}, Firecrown, sampler, priors.

### 2024-03-27 figures/shear_corr_funcs/xi_delta_nla_rescaled.tex

--- 2024-02-19 paper_IA.tex
@@
-% mnras_template.tex 
-%
-% LaTeX template for creating an MNRAS paper
-%
-% v3.0 released 14 May 2015
-% (version numbers match those of mnras.cls)
-%
-% Copyright (C) Royal Astronomical Society 2015
-% Authors:
-% Keith T. Smith (Royal Astronomical Society)
-
-% Change log
-%
-% v3.0 May 2015
-%    Renamed to match the new package name
-%    Version number matches mnras.cls
-%    A few minor tweaks to wording
-% v1.0 September 2013
-%    Beta testing only - never publicly released
-%    First version: a simple (ish) template for creating an MNRAS paper
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Basic setup. Most papers should leave these options alone.
-%\documentclass[fleqn,usenatbib]{mnras}
-\documentclass[useAMS,usenatbib]{mn2e}
-
-% MNRAS is set in Times font. If you don't have this installed (most LaTeX
-% installations will be fine) or prefer the old Computer Modern fonts, comment
-% out the following line
-%\usepackage{newtxtext,newtxmath}
-% Depending on your LaTeX fonts installation, you might get better results with one of these:
-%\usepackage{mathptmx}
-%\usepackage{txfonts}
-
-% Use vector fonts, so it zooms properly in on-screen viewing software
-% Don't change these lines unless you know what you are doing
-%\usepackage[T1]{fontenc}
-
-% Allow "Thomas van Noord" and "Simon de Laguarde" and alike to be sorted by "N" and "L" etc. in the bibliography.
-% Write the name in the bibliography as "\VAN{Noord}{Van}{van} Noord, Thomas"
-%\DeclareRobustCommand{\VAN}[3]{#2}
-%\let\VANthebibliography\thebibliography
-%\def\thebibliography{\DeclareRobustCommand{\VAN}[3]{##3}\VANthebibliography}
-
-%%%%% AUTHORS - PLACE YOUR OWN PACKAGES HERE %%%%%
-\input{abbrev}
-\input{psfig.sty}
-
-\usepackage{graphicx}
-\usepackage{epsfig}
-\usepackage{amssymb}
-\usepackage{amsmath}
-\usepackage{amsfonts}
-\usepackage{txfonts}
-\usepackage{multirow}
-\usepackage{afterpage}
-\usepackage{xcolor}
-%\usepackage[draft]{hyperref}
-%\usepackage{ulem} % allows for strikethrough with \sout{}
-
-%\usepackage[paperheight=10in,paperwidth=8.5in]{geometry}
-
-\setlength{\topmargin}{-0.8in}
-\paperheight 11in
-\paperwidth 8.5in
-%\setlength{\textheight}{9.8in}
-%\setlength{\textwidth}{7.3in}
-\setlength{\textheight}{9.5in}
-\setlength{\textwidth}{7.1in}
-
-\definecolor{mypink1}{rgb}{0.858, 0.188, 0.478}
-\definecolor{mygreen1}{rgb}{0.258, 0.788, 0.878}
-\definecolor{myorange1}{rgb}{0.5, 0.2, 0.2}
-\newcommand{\NM}[1]{\textcolor[RGB]{0,150,0}{#1}}
-\newcommand{\RR}[1]{\textcolor{blue}{#1}}
-\newcommand{\JHD}[1]{\textcolor{mypink1}{#1}}
-\newcommand{\snr}{$\mathcal{S}/\mathcal{N}$ }
-\newcommand{\mycomment}[1]{}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%% AUTHORS - PLACE YOUR OWN COMMANDS HERE %%%%%
-
-% Please keep new commands to a minimum, and use \newcommand not \def to avoid
-% overwriting existing commands. Example:
-%\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%
-
-% Title of the paper, and the short title which is used in the headers.
-% Keep the title short and informative.
-\title[Lensing beyond 2pt: accounting for IA]{Intrinsic alignments from projected tidal fields: non-linear  impact on cosmic shear probes}
-
-% The list of authors, and the short list which is used in the headers.
-% If you need two or more lines of authors, add an extra line using \newauthor
-\author[J. Harnois-D\'{e}raps et al.]{Joachim Harnois-D\'{e}raps$^{1}$\thanks{E-mail: joachim.harnois-deraps@ncl.ac.uk} and others
-\\
-% List of institutions
-$^{1}$School of Mathematics, Statistics and Physics, Newcastle University, Herschel Building, NE1 7RU, Newcastle-upon-Tyne, UK\\
-}
-
-% These dates will be filled out by the publisher
-\date{Accepted XXX. Received YYY; in original form ZZZ}
-
-% Enter the current year, for the copyright statements etc.
-\pubyear{2021}
-
-% Don't change these lines
-\begin{document}
-\label{firstpage}
-\pagerange{\pageref{firstpage}--21}
-%\pagerange{\pageref{firstpage}--\pageref{lastpage}}
-\maketitle
-
-% Abstract of the paper
-\begin{abstract}
-TBD
-\end{abstract}
-
-% Select between one and six entries from the list of approved keywords.
-% Don't make up new ones.
-\begin{keywords}
-Gravitational lensing: weak -- Methods: numerical -- Cosmology: dark matter, dark energy \& large-scale structure of Universe 
-\end{keywords}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%% BODY OF PAPER %%%%%%%%%%%%%%%%%%
-
-%----------
-\section{Introduction}
-\label{sec:intro}
-%----------
-
-Cosmology, gravitational lensing, cosmic shear, 2pt, beyond-2pt, simulations for signal and for secondary signal/systematics, IA-infusion, this paper...
-
- %----------
-\section{Cosmic shear}
-\label{sec:theory}
-%----------
-
-As mentioned in the introduction, cosmic shear can be measured and modelled from a variety of methods, many of which are used in this paper and presented in this section.  
-%-------------------------
-\subsection{$\gamma$-2PCF}
-\label{subsec:wl-th}
-
-%---------------
-\begin{figure}
-\includegraphics[width=\columnwidth]{graphs/Nz}
-\caption{Redshift distribution in our simulations, taken from the Year-1 specifications of the LSST Science Requirement Document \citep{LSST-SRD} {[\it check Y1 vs Y10}].}
-\label{fig:Nz}
-\end{figure}
-%--------------
-
- Shear two-point correlation functions ($\gamma$-2PCFs hereafter) can be predicted with percent-level precision and are therefore an ideal quantity to validate weak lensing simulations.
-In the Limber approximation\footnote{See \citet{Kilbinger17} for a comparison between the Limber approximation and the exact calculations.}, the lensing power spectrum $C^{ij}_{\ell}$ is obtained from an integral over the three-dimensional matter power spectrum $P_{\delta}(k,z)$:
-  \begin{eqnarray}
-C_{\ell}^{ij} = \int_0^{\chi_{\rm H}}  \frac{q^i(\chi) \,q^j(\chi)}{\chi^2} \, P_{\delta}\, \bigg(\frac{\ell+1/2}{\chi},z(\chi)\bigg) \ {\rm d}\chi,
-\label{eq:C_ell}
-\end{eqnarray}
-where $\chi_{\rm H}$ is the co-moving distance to the horizon, $c$ is the speed of light, $H_0$ the Hubble parameter,  and the  lensing kernels $q^{i}$ are given by:
-\begin{eqnarray}
-q^i(\chi) = \frac{3}{2}\Omega_{\rm m} \, \bigg(\frac{H_0}{c} \bigg)^2 \frac{\chi}{a(\chi)} \int_{\chi}^{\chi_{\rm H}} n^i(\chi')\frac{{\rm d}z}{{\rm d} \chi'}\frac{\chi' - \chi}{\chi'}{\rm d}\chi' \, .
-\label{eq:q_lensing}
-\end{eqnarray}
-In the previous expression, $n^i(z)$ refers to the redshift distribution  in tomographic bin `$i$', while $a(\chi)$ is the scale factor at comoving distance $\chi$ from the observer {[\it might need to define $\Omega_m$ here]}.
- The matter power spectrum is computed from  {\sc Halofit} \citep{Takahashi2012}, however  other public tools provide $P_{\delta}(k,z)$ predictions, including e.g.
-{\sc HMcode} \citep{HMCode2020}, the {\sc EuclidEmulator} \citep{EuclidEmulator}, the {\sc BACCO} emulator \citep{BACCOEmulator} or the Mira Titan emulator \citep{miraTitan}.
- Predictions for the $\gamma$-2PCFs are finally computed from Eq. (\ref{eq:C_ell}) as:
- \begin{eqnarray}
-\xi_{\pm}^{ij}(\vartheta) = \frac{1}{2\pi}\int_0^{\infty} C_{\ell}^{ij} \, J_{0/4}(\ell \vartheta) \, \ell \, {\rm d}\ell,
-\label{eq:xipm_th}
-\end{eqnarray}
-where $J_{0/4}(x)$ are Bessel functions of the first kind.
-In this paper, these calculations are carried out by {\sc pyccl}\footnote{{\sc pyccl}:pypi.org/project/pyccl}  \citep{CCL} {\it or do we use cosmosis in the end?]}.
-The $n^i(z)$ are taken from the LSST Science Requirement Document \citep{LSST-SRD} and given by
- \begin{eqnarray}
-n(z) = N_0 z^2 {\rm exp} \left[-\left(\frac{z}{z_0}\right)^\alpha \right]\, ,
-\label{eq:nz}
-\end{eqnarray}
-with $(z_0, \alpha) = (0.13, 0.78)$ and $N_0$ normalised to provide a number density of $n_{\rm eff}$ = 3.0 gal arcmin$^{-2}$.
-This lower than the expected number density for the first data release ($n_{\rm eff}\sim10$ gal arcmin$^{-2}$), but is large enough to validate our methods, and makes the calculation more tractable.
-The $n(z)$ is further split into five equi-populated tomographic bins, and smoothed with a Gaussian filter of width $\sigma = 0.05(1+z)$ in order to mimic the photometric selection process [{\it confirm with Niko}].
-The resulting distributions\footnote{The construction of these tomographic $n(z)$ can be reproduced in {github...CCL\_SRD\_Niko}.} are shown in Figure \ref{fig:Nz}.
-
-The cosmic shear signal can be measured from the ellipticities $\epsilon_{1/2}$ of simulated or observed galaxies, which, in absence of systematics and secondary signals, are unbiased estimators  of the cosmic shear components $\gamma_{1/2}$.
-The $\gamma$-2PCF are then estimated as:
- \begin{eqnarray}
- \widehat{\xi_{\pm}^{ij}}(\vartheta) = \frac{\sum_{a,b} w_a w_b \left[\epsilon_{a, \rm t}^i\epsilon_{b, \rm t}^j     \pm \epsilon_{a, \times}^i\epsilon_{b, \times}^j    \right]\Delta_{ab}(\vartheta)}{\sum_{a,b} w_a w_b} \, ,
- \label{eq:2PCF_estimator}
-  \end{eqnarray}
-where the sum is over all pairs of galaxies $a,b$ separated by an angular separation $\vartheta$, taken from tomographic bins $i,j$.
-The tangential/cross components of their ellipticities are denoted as $\epsilon_{\rm t/\times}$, respectively.
-$\Delta_{ab}(\vartheta)$ is the binning operator, equal to unity if the angular separation between the two galaxies falls within the $\vartheta$-bin, and zero otherwise, and the shape weights $w_{a,b}$ are set to unity.
-In this paper, we construct lensing catalogues from numerical simulations (described in Sec.
-\ref{sec:sims}), from which we measure $ \widehat{\xi_{\pm}^{ij}}(\vartheta)$ with {\sc Treecorr} \citep{TreeCorr}.
-We set therein the {\sc bin\_slop} parameter to 0.05, then compute the correlations in nine logarithmically-spaced angular bins ranging from 0.5 to 475.5 arcmin.
-
- %-------------------------
-\subsection{Beyond-2pt}
-\label{subsec:beyond-2pt}
-
-Non-Gaussian statistics, often referred to `beyond-2pt' statistics, have the potential to extract cosmological information stored in the complex phases of the density field, whereas two-point functions such as the $\gamma$-2PCF can only access that encoded in the complex amplitudes.
-No optimal estimator has been identified to-date as being able to capture `all' information, but the numerous studies presented in the introduction all show a clear gain in constraining power, especially when used in combination with 2pt functions.
-Some of these take as input the galaxy catalogues directly, while others require instead convergence maps.
-Therefore, we produce convergence maps from the catalogues by assigning the shear signal onto spherical {\sc Healpix}\footnote{{\sc Healpix}: http://healpix.sf.net}  maps \citep{healpix} with $N_{\rm side}=4096$, then using the standard Kaiser \& Squires inversion technique \citep{KaiserSquires} implemented in {\sc healpy} to reconstruct a convergence maps with the same angular resolution, including a baseline 2.0 arcmin smoothing beam in the inverse transform.
-Note that this smoothing scales is quite small; some probes are difficult to model in that case, and would instead prefer larger smoothing scales.
-We take this into account on a case-by-case basis, as described below.
-
-  {\it [Discuss tomography...]}
-
-\subsubsection{Catalogue-based estimators}
-
-We consider the following shear-based estimators:
-\begin{enumerate}
-\item The squeezed bispectrum, has theoretical model (Anik, can you summarise the measurements and modelling, and provide references?)
-\end{enumerate}
-
-\subsubsection{Convergence-based estimators}
-
-\begin{enumerate}
-\item Convergence three-point correlation function: (Alejandro, can you summarise the measurements and modelling, and provide references?)
-\item Peaks and Minima: local maxima and minima in the {\sc Healpix} convergence maps are counted in bins of signal-to-noise ratios, $\nu$.
-This is one of the most widely used non-Gaussian lensing statistics as it is simple to measure.
-Theoretical models have been developed to describe the largest peaks \citep[see][]{Shan18, HSCY1_Peaks_th}, however we report here the results on a much wider range of statistics, which can only be accurately modelled from numerical simulations, as in \citet{HD21, DESY3_Zuercher, HSCY1_Peaks_Sims, HD23}.
-\item Lensing PDF, has theoretical model (Cora/Lina, can you summarise the measurements and modelling, and provide references?)
-\item Map2 and Map3, has theoretical model  (Laila, can you summarise the measurements and modelling, and provide references?)
-\item Minkowski functionals (Nisha, can you summarise the measurements and modelling, and provide references?)
-\end{enumerate}
-
- %-------------------
- \section{Intrinsic alignment models}
- \label{sec:IA_th}
- %-------------------
-
-Galaxies interact with the tidal forces caused by the large-scale structure  they live in, causing their intrinsic shapes to acquire correlated alignments that has nothing to do with the correlations caused by weak lensing.
-This therefore acts as a secondary signal that contaminates the shape correlation measurements carried out in a cosmic shear analysis.
-There is no consensus on the actual physical model that describes the IA signal, and even when adopting these, the free parameters they contain are only weakly constrained from the data \citep[see][for reviews]{IA_review1, IA_review2}.
-%The most widely used model in the literature is the non-linear alignment model of \citet{NLA}, however it is now recognised that this is an effective model with limited precision, and the community is now progressively shifting towards more complex models.
-In this paper we consider four such IA models that we describe in the following sub-sections.
-In all cases, our models couple the galaxy intrinsic shapes with the local over-density and projected tidal field , then prescribe an intrinsic ellipticity tensor $\gamma_{ij}^{\rm IA}$, from which observed ellipticities are extracted as:
- \begin{eqnarray}
-\epsilon_{1}^{\rm IA} = \gamma_{xx}^{\rm IA} - \gamma_{yy}^{\rm IA} \, , \hspace{1.5cm}\epsilon_{2}^{\rm IA} = 2 \gamma_{xy}^{\rm IA}\, .
-\label{eq:tidal_th_deltaNLA}
-\end{eqnarray}
-
-\subsection{Non-linear alignment (NLA)}
-
-%The observed ellipticity of a galaxy ${\boldsymbol \epsilon}_{\rm obs} $ is a combination of its intrinsic shape ${\boldsymbol \epsilon}_{\rm int}$ and a cosmic shear signal ${\boldsymbol \gamma}$, the former of which can be further divided in a random component ${\boldsymbol \epsilon}^{\rm ran}$ and an alignment term ${\boldsymbol \epsilon}^{\rm IA}$.
-The NLA model of \citet{NLA} is the most widely used IA model in the cosmic shear literature thus far.
-According to the NLA, IA are caused by a linear coupling between galaxy shapes and the non-linear large-scale tidal field at the galaxy position.
-In the context of  two-point functions, these intrinsic shapes contribute to an intrinsic-intrinsic ($II$) term and an intrinsic-shear coupling ($GI$) term \citep{Hirata2004}, both secondary signals to the true cosmic shear ($GG$) term, with the latter typically dominating the IA sector in cross-tomographic measurements.
-The $II$ and $GI$ terms  can be both computed from the matter power spectrum as:
- \begin{eqnarray}
-P_{II}(k,z) =  \left(\frac{A_{\rm IA}\bar{C_1}\bar{\rho}(z)}{D(z)}\right)^2a^4(z) P_{\delta}(k,z)
-\label{eq:Pk_II_th}
-\end{eqnarray}
-and
- \begin{eqnarray}
-P_{GI}(k,z) = - \frac{A_{\rm IA}\bar{C_1}\bar{\rho}(z)}{D(z)}a^2(z) P_{\delta}(k,z) \, ,
-\label{eq:Pk_GI_th}
-\end{eqnarray}
-which can then be past to the Limber integration (Eqs. \ref{eq:C_ell} and \ref{eq:xipm_th}) to compute  the secondary signals $\xi_{\pm}^{II}(\vartheta)$ and $\xi_{\pm}^{GI}(\vartheta)$. 
-In the above expression,  $D(z)$ is the linear growth factor, $\bar{\rho}(z)$ is the mean matter density at redshift $z$ and $\bar{C_1}=5\times 10^{-14} M_{\odot}^{-1} h^{-2} {\rm Mpc}^3$ is a constant calibrated in \citet{Brown2002}.
-The strength of the tidal coupling is modulated by the amplitude parameter $A_{\rm IA}$, which is the main NLA parameter constrained by current cosmic shear surveys.
-Note that this model can be augmented by redshift and luminosity dependences, however we do not use these here.
-
-The NLA intrinsic ellipticities $\epsilon_{1,2}^{\rm NLA}$ are related to tidal field $s_{ij}$ by:
- \begin{eqnarray}
-\epsilon_1^{\rm NLA} = - \frac{A_{\rm IA}\bar{C_1}\bar{\rho}(z)}{D(z)} (s_{xx} - s_{yy}) \,\,\,\,,   \epsilon_2^{\rm NLA} = - \frac{2 A_{\rm IA}\bar{C_1}\bar{\rho}(z)}{D(z)} s_{xy}\;,
-\label{eq:tidal_th}
-\end{eqnarray}
-where $s_{ij} = \partial_{ij}\phi$ are the Cartesian components of the tidal tensor of the gravitational potential.
-Note that the term `non-linear' in the model name can be  misleading, as it refers to the non-linear matter power spectrum $P(k)$ that is used in its calculations; the coupling between the intrinsic galaxy shapes and the tidal field is still linear.
-Eq.( \ref{eq:tidal_th}) is used to assign intrinsic ellipticities to galaxies, given maps of the tidal field components $s_{xx}$, $s_{yy}$ and $s_{xy}$ (see Sec.
-\ref {subsec:IA_infusion}).
-
-\subsection{$\delta$-NLA}
-\label{subsec:IA_th_ext}
-
-%[{\it here}]
-
-%As discussed later, the key quantity of interest to cosmic shear analysis is not the tidal tensor itself but its trace-free version, since shape correlations with the density field are subdominant, even though peaks in high density environments are less elliptical on average.
-Consequently, the model itself has a restricted range of validity: on small scales, higher order couplings to the ellipticity field ${\boldsymbol \epsilon}^{\rm IA}$  become important, however these are neglected in the NLA model.
-Only the non-linear evolution of the tidal tensor itself is taken into account, since it does fit observations quite well.
-
-%We note that the NLA predicts additional higher-order terms and non-zero $B$-modes \citep{Hirata2004} that we neglect  in this analysis.
-Also, as shown in \citet{IA_EFT}, the NLA model can be interpreted as the lowest order description of the alignment process of galaxies in the light of an effective field theory description.
-
-The NLA model presented in the last section has been widely used in cosmic data analyses, but it has important known limitations and is therefore bound to fail at describing the IA signal with high precision.
-A perturbation theory extension to the NLA has been introduced in \citet{Blazek2015} and  \citet{Blazek2019},  where it is recognised that higher order couplings could be important and should be considered.
-The first additional term to be included is the over-density weighting term, which is caused by the fact that the intrinsic alignment of galaxies can only be observed at the galaxy positions, which are not distributed randomly on the sky but instead trace the underlying matter density,  `$\delta$', although the exact biasing scheme is not currently know.
-Accounting for this extra term in theoretical predictions is done with one-loop perturbation theory  \citep{Blazek2019}, and is implemented in {\sc pyccl}.
-Physically, it corresponds to adding a $\delta$-weight to the NLA predictions at the local galaxy positions, effectively representing the different tracer properties.
-At the level of numerical simulations, this could be done in principle simply by augmenting the NLA ellipticities with this weight, namely:
- \begin{eqnarray}
-\epsilon_{1/2}^{\delta-\rm NLA} = \epsilon_{1/2}^{\rm NLA}\times(1 + b_{\rm TA}\delta) \, ,
-\label{eq:tidal_th_deltaNLA}
-\end{eqnarray}
-where the term $b_{\rm TA}$ corresponds to the (largely unconstrained) biasing relation between these source galaxies and the underlying matter field.
-In practice, however, we find that this is noisy, and that it is instead preferable to generate mocks catalogues with the biasing scheme directly applied when assigning galaxy positions, after which no weighting is necessary.
-Nevertheless, Eq.
-(\ref{eq:tidal_th_deltaNLA}) can be used to modify the value of $b_{\rm TA}$.
-Indeed, from a mock with a given bias $b_{\rm TA, orig}$, we can rescale the IA contribution to a different $b_{\rm TA, new}$  as:
-\begin{eqnarray}
-{\boldsymbol \epsilon}^{\rm int}_{b_{\rm TA, new}}  = \frac{(1 + b_{\rm TA, new}\delta)}{(1 + b_{\rm TA, orig}\delta)}{\boldsymbol \epsilon}^{\rm int}_{b_{\rm TA, orig}} \, .
-\label{eq:bta_rescale}
-\end{eqnarray}
-
-Compared to the NLA, the $\delta$-NLA is a stronger IA model, especially on small scales \citep{Blazek2019}, and seems to be preferred by some hydrodynamical simulations \citep{Hilbert_IA2017}.
-It is also better motivated from a physical point of view, since we know that the galaxies trace dark matter  and are not randomly distributed in our Universe as the NLA assumes.
-
-%-----------------------------------
-\subsection{Tidal Torque (TT)}
-\label{subsec:IA_th_TT}
-
-As shown in \citet{Blazek2019}, one-loop perturbative calculations include another term, by which galaxies acquire an intrinsic alignment via a coupling between their angular momentum and the tidal field, which can be re-expressed as a quadratic coupling between the tidal field and the shape.
-In this tidal torque model (TT), intrinsic ellipticities are given by:
-\begin{eqnarray}
-\gamma_{ij}^{\rm IA, TT} = C_2 \left[ \sum_{k=x,y,z} s_{ik} s_{kj} -\frac{1}{3} \delta_{ij} s^2 \right] \, ,
-\label{eq:tidal_th_TT}
-\end{eqnarray}
-where 
-\begin{eqnarray}
-C_2 = \frac{5 A_2 \bar{C_1} \Omega_{\rm m} \rho_{\rm crit}}{D^2(z)} \,  = \left[ \frac{-5 A_2}{A_1 D(z)} \right] C_1.
-\end{eqnarray}
-Under the approximation that line-of-sight alignments are mostly suppressed from cosmic shear measurement due to the broad lensing kernels, 
-we show in  Appendix \ref{app:2d_TT} that the terms inside the square bracket in Eq. (\ref{eq:tidal_th_TT}) leads to:
-\begin{eqnarray}
-\epsilon_1^{\rm TT} = C_2  \left[ s_{xx}^2 - s_{yy}^2\right] \, , \epsilon_2^{\rm TT} = 2 C_2 s_{xy}\left[s_{xx}+s_{yy}  \right]\, ,
-\end{eqnarray}
-both quadratic in the tidal field components.
-
-%-----------------------------------
-\subsection{$\delta$-TT}
-\label{subsec:IA_th_TT}
-
-Following the relation between the NLA and the $\delta$-NLA model, galaxies in the TT model are also assume to be randomly scattered on the sky, which we know to be a bad approximation.
-Computing the next-order contribution to the TT model involves two-loop perturbation theory calculations that have not been done yet due to the significantly higher complexity of such task.
-in simulations however, the $\delta$-weighting term is straight-forward to implement, as it involves to simply infuse the TT model onto galaxies that trace the matter field with a non-zero biasing factor.
-As for the $\delta$-NLA model, the $\delta$-TT ellipticities can  be related to the TT model as:
-\begin{eqnarray}
-\epsilon_{1/2}^{\delta-\rm TT} = \epsilon_{1/2}^{\rm TT}\times(1 + b_{\rm TA}\delta) \, .
-\label{eq:tidal_th_deltaTT}
-\end{eqnarray}
- There are currently no theoretical models for $\delta$-TT, which means that predictions from this model are, at the moment, completely simulation-based.
-
-It is worth recalling here that other IA models exist in the literature, and that at this point observations are not precise enough to set strong constraints on them, further motivating our flexible multi-model approach.
-
-%\subsection{Likelihood}
-%\label{subsec:likelihood}
-
-%Multi-Gaussian likelihood, analytical Covariance matrix (Gauss + non-Gauss + SSC) from {\sc TJPCov}, Firecrown, sampler, priors.
-
-%---------------------
-\section{Simulations}
-\label{sec:sims}
-
-%-------------
-\subsection{Cosmic shear galaxy catalogues} 
-\label{subsec:WL_cats}
-
-The weak lensing simulations developed for this work are based on ray-tracing mass sheets produced from the Outer Rim $N$-body simulation \citep{OuterRim}, which evolved 10,240$^3$ particles in a (5.225 Gpc)$^3$ cosmological volume, assuming a flat $\Lambda$CDM cosmology with $\Omega_{\rm m}$=0.2648, $\Omega_{\rm b}$=0.0448, $h$=0.71, $\sigma_8$ = 0.801, $n_{\rm s}$= 0.963, $w_0$=-1.00.
-A total of 101 particle snapshots were originally saved, of which we use only those with $z<4.0$.
-Particles from each dump are assigned to curved mass shells approximately 114 Mpc thick, producing a sequence of 57 {\sc Healpix} maps $\delta(\theta,\phi,\chi_i)$ with {\sc nside} = 8192 and $i=1..57$, filling up a light-cone over an octant up to $z=3$.
-%More details on this procedure can be found  in \citet{cosmoDC}, where lensing quantities are computed specifically for the generation of the {\sc cosmoDC2}  synthetic sky catalogue.
-
-Ray-tracing is performed in the Born approximation, summing over the mass shells using the $\chi$-integral of Eq.
-(\ref{eq:C_ell}).
-A source plane is placed at the high-redshift edge of every mass planes, resulting in a series of convergence  maps  $\kappa(\theta,\phi,\chi_i)$ that are subsequently transformed into shear maps $\gamma_{1/2}(\theta,\phi,\chi_i)$ using the Kaiser-Squires methods \citep{KaiserSquires}, which is implemented via efficient {\sc HealPy alm2map} routines.
-
-We position galaxies in the light cone following exactly our chosen $N(z)$, and interpolate the shear quantities at their location. We follow two distinct algorithm to achieve this:
-\begin{enumerate}
-\item {\it Random:} galaxies RA and Dec are distributed randomly on the octant, thereby matching this fundamental assumptions in the NLA and TT models. 
-\item {\it Linear bias:} galaxies RA and Dec are sampled from the mass sheets smoothed\footnote{We also tried sampling the field with 0.1 and 0.5 $h^{-1}$Mpc but this resulted in noisier results.} over 1.0 $h^{-1}$Mpc (comoving), assuming a linear bias of $b_{\rm TA}$, now matching instead the assumptions of the $\delta$-NLA and $\delta$-TT models.
-With this method we produce galaxy positions assuming first $b_{\rm TA}=1.0$ (our fiducial case) and also $b_{\rm TA}=2.0$, enhancing the  model flexibility.
-\end{enumerate}
-
-Since source clustering is a higher order effect in cosmic shear, the measured $\xi_{\pm}$ from these three mocks (random, $b_{\rm TA}=1.0$ and $b_{\rm TA}=2.0$) show negligible differences ({\it to quantify and cite}).
-In contrast, the impact on the IA contamination is significant and can double the secondary signal in certain circumstances.
-The main explanation for this is that while clustered sources are uncorrelated with the foreground matter responsible for the lensing signal, the high-density regions they live are also subject to the largest tidal fields.
-
-%----------
-\subsection{Projected tidal fields}
-\label{subsec:IA_sims}
-
-\begin{figure*}
-\caption{Density field and the associated projected tidal field tensors.}
-\label{fig:maps}
-\end{figure*}
-
-Our infusion method completely relies on couplings between intrinsic galaxy shapes and the local tidal field, hence the first step in our method consist in extracting the tidal field maps $s_{ij}(\theta,\phi,\chi_i)$ from the mass maps $\delta(\theta,\phi,\chi_i)$ that source them.
-In three dimensions, trace-free tidal tensor $s_{ij}(\boldsymbol x)$ can be obtained from the matter over-density field $\delta(\boldsymbol x)$ as   \citep{Catelan_IA_Tidal}:
-\begin{eqnarray}
- \widetilde{s}_{ij} (\boldsymbol k)  = \left[\frac{k_i k_j}{k^2} - \frac{\delta_{ij}}{3}\right]  \widetilde {\delta}(\boldsymbol k) \mathcal{G}(\sigma_{\rm G}) \, ,
- \label{eq:sij}
-\end{eqnarray}
-where $\mathcal{G}(\sigma_{\rm G})$ is a three-dimensional Gaussian function described by a single (free) parameter $\sigma_{\rm G}$ that  controls the physical scales which are allowed to affect the IA term in our model.
-Tilde symbols  denote Fourier transformed quantities,  the indices $(i,j)$ label the components of the Cartesian wave-vector $\boldsymbol{k}^T = (k_x,k_y,k_z)$, and $k^2 = k_x^2 + k_y^2 + k_z^2$. 
-As shown in \citet{Tidalator} for Cartesian coordinates, projected tidal fields  computed from projected mass sheets provide and excellent agreement with the NLA model, which in contrast computes the full tidal fields from the three-dimensional matter density and project along the radial dimension at the end.
-We promote this transformation to curved-sky in this work, exploiting the  polarisation {\sc alm2map} operations built in {\sc Healpy}.
-In particular, noting that $Q=s_{xx}-s_{yy}$, $U=s_{xy}$ and $\delta=s_{xx}+s_{yy}$, we compute the curved-sky tidal field tensors ${s}_{ij}({\boldsymbol \theta})$ as:
- \begin{eqnarray}
-s_{xx}({\boldsymbol \theta})  =  \left[\frac{ \delta + Q}{2}  - \frac{\delta}{3}\right] \, ,s_{yy}({\boldsymbol \theta})  =  \left[\frac{\delta - Q}{2}  - \frac{\delta}{3}\right] \, , s_{xy}({\boldsymbol \theta}) = U
- \label{eq:sij_2D_sph}
- \end{eqnarray}
-where the $U({\boldsymbol \theta})$ and $Q({\boldsymbol \theta})$ maps are smoothed by the Gaussian beam with width $\sigma_{\rm G}$.
-We suppress large artificial tidal fields at the maps boundary by replicating 8$\times$ the density maps defined on the octant and working on a full sky density $\delta$; we re-apply the octant mask on the tidal field maps after the operation.
-Note that the value of $\sigma_{\rm G}$ is a free parameter both in the infusion technique described in this paper and in the NLA and TATT models.
-We therefore explore two cases, $\sigma_{\rm G}=0.1$Mpc and 0.5Mpc, however this may be further optimised in the future.
-Finally, the full-sky density field is downgraded from $N_{\rm side}=8192$ to $N_{\rm side}=4096$ since the smoothing washed the smallest angular scales.
-
-%are specified within the NLA model.
-Smoothing amounts to selecting physical scales that do not contribute to the alignment of galaxies, which is still a debatable quantity, but is also introduced for numerical stability.
-\citet{Blazek2015} argues that 1.0 $h^{-1}$Mpc could be a reasonable fiducial value, being larger then the typical halo size, but recognizes that one-halo terms are also required to better match the observations.
-In their later work, \citet{Blazek2019} do not include smoothing at all, and neither do the KiDS-1000 nor DES-Y1 analyses based on the NLA model \citep{KiDS1000_Asgari,DESY1_Troxel}.
-In this work we used a two-dimensional Gaussian filter and calibrated $\sigma_{\rm G}$ empirically to $\sigma_{\rm G}=0.1h^{-1}$Mpc (see Sec.
-\ref{subsubsec:sigma_G}), however these two choices are arbitrary and could possibly be better optimised in the future; we also explore $\sigma_{\rm G}=0.5h^{-1}$Mpc later on.
-We note that the smoothing scale is degenerate with the resolution of the simulation itself, and that one should use caution when smoothing on scales that approach the resolution limits.
-
-%We employ a numerical technique worth mentioning here: the Fourier transforms involved in computing Eq.
-(\ref{eq:sij_2D}) are computed from the full (projected) periodic boxes of the simulations, then interpolated on the light-cones.
-We find that tidal field computed directly from the $10\times10$ deg$^2$ light-cones introduces significant large scales features in the tidal field maps, largely caused by  the non-periodic boundary conditions, which our method avoids.
-Projected tidal field maps $s_{11}$, $s_{22}$ and $s_{12}$ are constructed that way for each mass sheets; Fig.
-\ref{fig:maps} shows the  three tidal fields and the mass maps for one of them.
-We can clearly see the connection between all maps around over-dense regions.
-{\it (Include a figure of $s_ij$ and $\delta$)}.
-
-{\it [Mention normalisation of the tidal fields by $0.6252 = H_0/114$ = 1/shell-thickness}
-
-%of every light-cones and interpolated at the position of every galaxy.
-Fig.
-\ref{fig:tidalator} illustrates this process for a small zoomed-in patch at $z\sim0$, starting from a $\delta_{2D}(\boldsymbol \theta)$ map (upper large panel), computing the tidal field components (middle four panels) and comparing the results with the cosmic shear signal generated by the same mass distribution (bottom two panels).
-The tidal field maps clearly reproduce the cosmic shear maps, and the minus sign in front of both terms in Eq.
-(\ref{eq:tidal_th}) causes the IA to undo some of the lensing signal.
-
-\subsection{Infusion of intrinsic alignments}
-\label{subsec:IA_infusion}
-
-Having now produced shear catalogues and tidal field maps, we can now use Eq.
-\ref{eq:tidal_th} to couple linearly the alignment of galaxies with the local tidal field, or Eq.
-\ref{eq:tidal_th_TT} to use instead a quadratic coupling.
-These allow us to compute the intrinsic ellipticities ${\boldsymbol \epsilon}^{\rm int}$ for the four IA models described in Sec.
-\ref{sec:IA_th}, which we combine with the cosmic shear signal ${\boldsymbol g}$ to compute observed ellipticities:
-\begin{eqnarray}
-{\boldsymbol \epsilon}^{\rm obs} = \frac{{\boldsymbol \epsilon}^{\rm int} + {\boldsymbol g}}{1 + {\boldsymbol \epsilon}^{\rm int}{\boldsymbol g^*}} \,, {\rm with \, \, } 
-{\boldsymbol \epsilon}^{\rm int}  = \frac{{\boldsymbol \epsilon}^{\rm IA} + {\boldsymbol \epsilon}^{\rm ran}}{1 + {\boldsymbol \epsilon}^{\rm IA}{\boldsymbol \epsilon^{\rm ran, *}}}.
-\label{eq:eps_obs}
-\end{eqnarray}
-In the above expressions, the denominators ensures that the combined  ellipticities never exceed unity.
-The complex spin-2 reduced shear ${\boldsymbol g} \equiv (\gamma_1 + {\rm i} \gamma_2)/(1+\kappa)$ is computed from the shear  $(\gamma_{1/2}$) and convergence ($\kappa$) maps, interpolated at the galaxy positions and redshifts.
-The  random orientation term ${\boldsymbol \epsilon}^{\rm ran}$ is drawn from two Gaussians (one per component) with their standard deviations matching the LSST-Y1 forecast, $\sigma_{\epsilon} = 027$.
-We further constraint  the random ellipticity to satisfy $|{\boldsymbol \epsilon}^{\rm ran}| \le 1.0$.
-%We recall that since our simulated galaxy catalogues trace the dark matter density, our default IA-infusion method  is consistent with the $\delta$-NLA model (see Sec.
-\ref{subsec:IA_th_ext}).
-Analytical predictions for the two-point functions are more involved in this case \citep[see][]{Blazek2019} and not yet available on the public {\sc cosmoSIS} release.
-We therefore validate our methods with the standard NLA first, which we infuse by `correcting' the $\delta$-NLA measurement with Eq.
-(\ref{eq:tidal_th_deltaNLA}), i.e.
-by replacing ${\boldsymbol \epsilon}^{\rm IA}$ by ${\boldsymbol \epsilon}^{\rm IA}/(1 + b_{\rm TA} \delta)$ in our simulations.
-Once again, these are less realistic but better suited for validation of the measured $\gamma$-2PCFs against a theoretical model; after this is established, we use the $\delta-$NLA catalogues as our fiducial infusion model.
-We re-iterate here that the same tidal fields, shear maps and IA coupling equations are used for the NLA and $\delta$-NLA models, and separately for the TT and $\delta$-TT models; these  only differ by the fact that in one case the galaxies are placed at random on the octant, while in the other case they are linearly tracing the dark matter.
-
-Also note that our current IA models make no differentiation between galaxy colours or type, and instead treats the full sample as a single population that has a single, effective, alignment signall \citep[see][for an example with a red/blue split]{DESY1_IA_Samuroff}.
-
-%---------------------
-\section{Validation with $\xi_{\pm}$}
-\label{sec:validation}
-
-% Requires the booktabs if the memoir class is not being used
-\begin{table}
-   \centering
-   %\topcaption{Table captions are better up top} % requires the topcapt package
-   \begin{tabular}{@{} lcr @{}} % Column formatting, @{} suppresses leading/trailing space
-      \hline
-      \hline
-       %\multicolumn{2}{c}{Item} \\
-      model   		& ($A_{\rm IA}, b_{\rm TA}, A_2)$ \\
-      \hline
-      NLA     		& {($\pm$1,0,0) }&  \\
-      \multirow{2}{*}{$\delta-$NLA }  	&   {($\pm$1,1,0)}   \\
-      							&  {(1,2,0)}   \\
-      TT 			&  {(0,0,$\pm$1)} &  \\
-      \multirow{2}{*}{$\delta$-TT} 	&  {(0,1,$\pm$1)}   \\
-      				&  {(0,2,1)}   \\
-      TATT- fiducial	&  { (1,1,1)}  \\
-      %TATT-DESY3	&   (-0.7,1,1.9) & \\
-      \hline
-      \hline
-
-   \end{tabular}
-   \caption{IA models infused in this work.}
-   \label{table:IAmodels}
-\end{table}
-
-%------------------------------
-\subsection{NLA model}
-\label{subsubsec:sigma_G}
-
-See Fig. \ref{fig:xi_NLA}
-%---------------
-\begin{figure*}
-%\includegraphics[width=\columnwidth]{graphs/frac_xip_IA1_skysim}
-\includegraphics[width=\columnwidth]{graphs/frac_xip_IA1_skysim_NLA_srd.jpg}
-\includegraphics[width=\columnwidth]{graphs/frac_xim_IA1_skysim_NLA_srd.jpg}
-\caption{Ratio between the shear correlation functions with and without IA, assuming the NLA model with $A_{\rm IA}=1.0$ both in the simulations and theory.
-Measurements shown in green and brown correspond to smoothing scales of 0.1 and 0.5 $h^{-1}$Mpc in the tidal field.
-There is no shape noise in the simulations, but it is included in the error bars.}
-\label{fig:xi_NLA}
-\end{figure*}
-%---------------
-
-%------------------------------
-\subsection{$\delta$-NLA model}
-\label{subsec:deltaNLA}
-
-See Fig. \ref{fig:xi_deltaNLA}.
-
-\begin{figure*}
-\includegraphics[width=\columnwidth]{graphs/frac_xip_IA1_skysim_deltaNLA_srd}
-\includegraphics[width=\columnwidth]{graphs/frac_xim_IA1_skysim_deltaNLA_srd}
-\caption{Same as Fig.
-\ref{fig:xi_NLA}, but for the $\delta$-NLA model with $A_{\rm IA}=1.0$ and $b_{\rm TA}=1.0$, and only for smoothing of 0.5$h^{-1}$Mpc.
-The dashed black lines show the NLA predictions to better highlight the differences.
-}
-\label{fig:xi_deltaNLA}
-\end{figure*}
-
 \begin{figure}
@@
 \end{figure}
-
-We verified that it works equally well for $b_{\rm TA}$ = 1.0 and 2.0.
-
-%------------------------------
-
-Using this, we $b_{\rm TA}$-rescale our $b_{\rm TA}=1.0$ mock to $b_{\rm TA}=2.0$ and to $0.0$ mocks.
-Results are shown in Fig.
-\ref{fig:xi_deltaNLA_rescaled} for one of the tomographic bin.
-It works reasonably well, but lower redshift are less accurate due to the increased  shot noise (not shown), hence we do not recommend using this.
-
-%------------------------------
-\subsection{TT model}
-\label{subsec:TT}
-
-See Fig. \ref{fig:xi_TT}
-
-\begin{figure*}
-\includegraphics[width=\columnwidth]{graphs/frac_xip_IA1_skysim_TT_srd.jpg}
-\includegraphics[width=\columnwidth]{graphs/frac_xim_IA1_skysim_TT_srd.jpg}
-\caption{Same as Fig. \ref{fig:xi_NLA}, but for the TT model with $A_2=1.0$. Here, the dashed black lines show the NLA predictions to better highlight the differences. }
-\label{fig:xi_TT}
-\end{figure*}
-
-\begin{figure*}
-%\includegraphics[width=\columnwidth]{graphs/frac_xip_C2_m1_skysim_deltaTT}
-\includegraphics[width=\columnwidth]{graphs/frac_xip_IA1_skysim_deltaTT_srd.jpg}
-\includegraphics[width=\columnwidth]{graphs/frac_xim_IA1_skysim_deltaTT_srd.jpg}
-\caption{Same as Fig. \ref{fig:xi_deltaNLA}, but comparing the TT and the $\delta$-TT models, with $A_2=1.0$, $b_{\rm TA}$ = 1.0, and only for smoothing of 0.5$h^{-1}$Mpc. }
-\label{fig:xi_deltaTT}
-\end{figure*}
-
-To match the theory, we need to apply the following calibration: $\epsilon^{\rm IA, TT}(z<0.5) \rightarrow \epsilon^{\rm IA, TT} /2.5$.
-
-%------------------------------
-\subsection{$\delta$-TT model}
-\label{subsec:TT}
-
-See Fig. \ref{fig:xi_deltaTT}
-
-To match the TT theory, we need to apply the following calibration: $\epsilon^{\rm IA, TT}(z<0.5) \rightarrow \epsilon^{\rm IA, TT} /5.0$, followed by $\epsilon^{\rm IA, TT} \rightarrow \epsilon^{\rm IA, TT}/7.0$.
-
-\subsection{Validation with full inference}
- \label{sec:inference}
-\begin{figure}
-%\includegraphics[width=\columnwidth]{graphs/triangle_nla_5D.pdf}
-\includegraphics[width=\columnwidth]{graphs/triangle_bta_sweep.pdf}
-\caption{Cosmological inference from the NLA-infused simulations, analysed the extended-NLA model. The cross-hairs represent the truth as fixed in the OuterRim $N$-body simulations \citep{OuterRim}.}
-\label{fig:triangle_nla}
-\end{figure}
-priors, {\sc CosmoSIS}, Takahashi $P(k)$, etc.
-
-\section{Higher-order weak lensing statistics}
-\label{sec:HOWLS}
-
-... use the mocks from Table \ref{table:IAmodels} to compute derivatives. Show.
-
-%----------
-\section{Conclusions}
-\label{sec:conclusion}
-%----------
-
-\section*{Acknowledgements}
-
-JHD acknowledges support from an STFC Ernest Rutherford Fellowship (project reference ST/S004858/1).
-Ray-tracing computations were carried on the NERSC [acknowledgments] ...
-HACC [acknowledgements] ...
-OuterRim [Acknowledgments]
-\\
-
-Some of the results in this paper have been derived using the {\sc healpy} and {\sc HEALPix} packages.
-\\
-\\
-\\
-{\footnotesize All authors contributed to the development and writing of this paper. JHD led the analysis.... }
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Data Availability}
-
-%The SLICS numerical simulations can be found at http://slics.roe.ac.uk/, while the cosmo-SLICS can be made available upon request.
-
-%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%
-
-% The best way to enter references is to use BibTeX:
-
-\bibliographystyle{hapj}
-\bibliography{IA} % if your bibtex file is called example.bib
-
-% Alternatively you could enter them by hand, like this:
-% This method is tedious and prone to error if you have lots of references
-%\begin{thebibliography}{99}
-%\bibitem[\protect\citeauthoryear{Author}{2012}]{Author2012}
-%Author A.~N., 2013, Journal of Improbable Astronomy, 1, 1
-%\bibitem[\protect\citeauthoryear{Others}{2013}]{Others2013}
-%Others S., 2012, Journal of Interesting Stuff, 17, 198
-%\end{thebibliography}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%% APPENDICES %%%%%%%%%%%%%%%%%%%%%
-
-\appendix
-
-\begin{figure*}
-\includegraphics[width=\columnwidth]{graphs/xip_sims_vs_th.eps}
-\includegraphics[width=\columnwidth]{graphs/xim_sims_vs_th.eps}
-\caption{Fractional difference on $\xi_\pm$ between the measurements from SkySim5000 and the model predictions.  }
-\label{fig:frac_err_sims_th}
-\end{figure*}
-
-\section{Projected Tidal Field}
-\label{app:2d_TT}
-
-\JHD{[To reword]} We derive in this Appendix...  
-The prescription to assign an intrinsic alignment based on the projected tidal field, described in Eq.
-(\ref{eq:tidal_th}), involves the combinations $(s_{xx} - s_{yy})$ and $s_{xy}$, which therefore correspond to:
-\begin{eqnarray}
- \widetilde{\epsilon}_1^{\rm IA} (\boldsymbol k_{\perp})  &\propto& \left(\frac{k_x^2 - k_y^2}{k^2} \right) \widetilde{\delta}_{\rm 2D}(\boldsymbol k_{\perp})\mathcal{G_{\rm 2D}}(\sigma_{\rm G})  \, ,\nonumber \\
- \widetilde{\epsilon}_2^{\rm IA} (\boldsymbol k_\perp)  &\propto& \left(\frac{k_x k_y}{k^2} \right) \widetilde {\delta}_{\rm 2D}(\boldsymbol k_\perp)\mathcal{G_{\rm 2D}}(\sigma_{\rm G}) 
- %\label{eq:sij}
-\end{eqnarray}
-
-Aside from the smoothing kernel, these are the same filters that are used for converting convergence maps to shear maps under the \citet[][KS hereafter]{KaiserSquires} inversion:
- \begin{eqnarray}
- \widetilde{\gamma_1} (\boldsymbol \ell)  = \left(\frac{k_x^2 - k_y^2}{k^2} \right) \widetilde {\kappa}(\boldsymbol \ell) \, , \hspace{1cm} \widetilde{\gamma_2} (\boldsymbol \ell)  = \left(\frac{k_x k_y}{k^2} \right) \widetilde {\kappa}(\boldsymbol \ell)
- %\label{eq:sij}
-\end{eqnarray}
-meaning that on can linearly combine the mass sheets with the correct coefficients and obtain intrinsic ellipticities from a normal KS inversion.
-
-Projecting out the $z$ components (e.i. $s_{0i}$=$s_{i0}$=0 for all $i$),  the tidal torque terms from Eq. (\ref{eq:tidal_th_TT}) can be expanded as:
- \begin{eqnarray}
-\gamma^{\rm TT}_{ij}&=& C_2 \left[\sum_{k=x,y} s_{ik} s_{kj} -\frac{1}{3} \delta_{ij} s^2\right] \\
-                                  &=&C_2 \left[ s_{ix}s_{xj}  + s_{iy}s_{yj}  -  \frac{1}{3} \delta_{ij} \left( s_{xx}^2 + s_{yy}^2 +2s_{xy}^2 \right)  \right] \, .
-\end{eqnarray}
-Specifically, this yields:
- \begin{eqnarray}
-\gamma^{\rm TT}_{xx}&=& C_2 \left[\frac{2}{3}s_{xx}^2  -  \frac{1}{3}s_{yy}^2 + \frac{1}{3}s_{xy}^2 \right]\, ,  \nonumber \\
-\gamma^{\rm TT}_{yy}&=& C_2 \left[-\frac{1}{3}s_{xx}^2  +  \frac{2}{3}s_{yy}^2 + \frac{1}{3}s_{xy}^2  \right]\, , \\
-\gamma^{\rm TT}_{xy}&=& C_2 s_{xy}\left[s_{xx}+s_{yy}  \right]\, . \nonumber                                  
-\end{eqnarray}
-With the standard ellipticity definitions $\epsilon_1^{\rm TT}\equiv \gamma_{xx}^{\rm TT} - \gamma_{yy}^{\rm TT}$ and $\epsilon_2^{\rm TT}\equiv -2 \gamma_{xy}$, we obtain:
-\begin{eqnarray}
-\epsilon_1^{\rm TT} = C_2  \left[ s_{xx}^2 - s_{yy}^2\right] \, , \epsilon_2^{\rm TT} = -2 C_2 s_{xy}\left[s_{xx}+s_{yy}  \right]\, .
-\end{eqnarray}
-In the TATT model, the total intrinsic ellipticity component is therefore given by $\epsilon_{1/2}^{\rm IA} = \epsilon_{1/2}^{\rm TATT} = \epsilon_{1/2}^{\delta{\rm-NLA}} + \epsilon_{1/2}^{\rm TT}$.
-
-% Don't change these lines
-\bsp	% typesetting comment
-\label{lastpage}
-\end{document}
-
-% End of mnras_template.tex

### 2024-03-27 paper_IA.tex

--- 2024-02-19 paper_IA.tex
@@
 \usepackage{xcolor}
+\usepackage{orcidlink}
+\usepackage{xspace}
 %\usepackage[draft]{hyperref}
@@
 \newcommand{\JHD}[1]{\textcolor{mypink1}{#1}}
+\newcommand{\niko}[1]{\textcolor{orange}{niko: #1}}
 \newcommand{\snr}{$\mathcal{S}/\mathcal{N}$ }
 \newcommand{\mycomment}[1]{}
+\newcommand{\dNLA}{extended\text{-NLA}\xspace}
+\newcommand{\dTT}{extended\text{-TT}\xspace}
+\newcommand{\gtwopcf}{$\gamma$\text{-2PCF}\xspace}
+\newcommand{\eg}{\textit{e.g.}\xspace}
+\newcommand{\ie}{\textit{i.e.}\xspace}
+\newcommand{\lcdm}{$\Lambda$CDM\xspace}
 
@@
 % If you need two or more lines of authors, add an extra line using \newauthor
-\author[J. Harnois-D\'{e}raps et al.]{Joachim Harnois-D\'{e}raps$^{1}$\thanks{E-mail: joachim.harnois-deraps@ncl.ac.uk} and others
+\author[J. Harnois-D\'{e}raps et al.]{Joachim Harnois-D\'{e}raps$^{1}$
+\orcidlink{0000-0002-4864-1240}
+\thanks{E-mail: joachim.harnois-deraps@ncl.ac.uk},
+Nikolina \v{S}ar\v{c}evi\'c,$^{1}$
+\orcidlink{0000-0001-7301-6415},
+and others
+\newauthor
+and the LSST Dark Energy Science Collaboration
 \\
@@
 % Enter the current year, for the copyright statements etc.
-\pubyear{2021}
+\pubyear{2024}
 
@@
 % Abstract of the paper
-\begin{abstract}
-TBD
-\end{abstract}
-
-% Select between one and six entries from the list of approved keywords.
-% Don't make up new ones.
-\begin{keywords}
-Gravitational lensing: weak -- Methods: numerical -- Cosmology: dark matter, dark energy \& large-scale structure of Universe 
-\end{keywords}
+\input{sections/0_abstract_keywords}
 
@@
 
-%----------
-\section{Introduction}
-\label{sec:intro}
-%----------
+\input{sections/1_introduction} 
+\input{sections/2_cosmic_shear_stats}
+\input{sections/3_ia_models}
+\input{sections/4_simulations}
+\input{sections/5_validation}
+\input{sections/6_higher_order_wl_stats}
+\input{sections/7_conclusion}
+\input{sections/8_acknowledgements}
+\input{sections/9_data_availability}
 
-Cosmology, gravitational lensing, cosmic shear, 2pt, beyond-2pt, simulations for signal and for secondary signal/systematics, IA-infusion, this paper...
-
- %----------
-\section{Cosmic shear}
-\label{sec:theory}
-%----------
-
-As mentioned in the introduction, cosmic shear can be measured and modelled from a variety of methods, many of which are used in this paper and presented in this section.  
-%-------------------------
-\subsection{$\gamma$-2PCF}
-\label{subsec:wl-th}
-
-%---------------
-\begin{figure}
-\includegraphics[width=\columnwidth]{graphs/Nz}
-\caption{Redshift distribution in our simulations, taken from the Year-1 specifications of the LSST Science Requirement Document \citep{LSST-SRD} {[\it check Y1 vs Y10}].}
-\label{fig:Nz}
-\end{figure}
-%--------------
-
- Shear two-point correlation functions ($\gamma$-2PCFs hereafter) can be predicted with percent-level precision and are therefore an ideal quantity to validate weak lensing simulations.
-In the Limber approximation\footnote{See \citet{Kilbinger17} for a comparison between the Limber approximation and the exact calculations.}, the lensing power spectrum $C^{ij}_{\ell}$ is obtained from an integral over the three-dimensional matter power spectrum $P_{\delta}(k,z)$:
-  \begin{eqnarray}
-C_{\ell}^{ij} = \int_0^{\chi_{\rm H}}  \frac{q^i(\chi) \,q^j(\chi)}{\chi^2} \, P_{\delta}\, \bigg(\frac{\ell+1/2}{\chi},z(\chi)\bigg) \ {\rm d}\chi,
-\label{eq:C_ell}
-\end{eqnarray}
-where $\chi_{\rm H}$ is the co-moving distance to the horizon, $c$ is the speed of light, $H_0$ the Hubble parameter,  and the  lensing kernels $q^{i}$ are given by:
-\begin{eqnarray}
-q^i(\chi) = \frac{3}{2}\Omega_{\rm m} \, \bigg(\frac{H_0}{c} \bigg)^2 \frac{\chi}{a(\chi)} \int_{\chi}^{\chi_{\rm H}} n^i(\chi')\frac{{\rm d}z}{{\rm d} \chi'}\frac{\chi' - \chi}{\chi'}{\rm d}\chi' \, .
-\label{eq:q_lensing}
-\end{eqnarray}
-In the previous expression, $n^i(z)$ refers to the redshift distribution  in tomographic bin `$i$', while $a(\chi)$ is the scale factor at comoving distance $\chi$ from the observer {[\it might need to define $\Omega_m$ here]}.
- The matter power spectrum is computed from  {\sc Halofit} \citep{Takahashi2012}, however  other public tools provide $P_{\delta}(k,z)$ predictions, including e.g.
-{\sc HMcode} \citep{HMCode2020}, the {\sc EuclidEmulator} \citep{EuclidEmulator}, the {\sc BACCO} emulator \citep{BACCOEmulator} or the Mira Titan emulator \citep{miraTitan}.
- Predictions for the $\gamma$-2PCFs are finally computed from Eq. (\ref{eq:C_ell}) as:
- \begin{eqnarray}
-\xi_{\pm}^{ij}(\vartheta) = \frac{1}{2\pi}\int_0^{\infty} C_{\ell}^{ij} \, J_{0/4}(\ell \vartheta) \, \ell \, {\rm d}\ell,
-\label{eq:xipm_th}
-\end{eqnarray}
-where $J_{0/4}(x)$ are Bessel functions of the first kind.
-In this paper, these calculations are carried out by {\sc pyccl}\footnote{{\sc pyccl}:pypi.org/project/pyccl}  \citep{CCL} {\it or do we use cosmosis in the end?]}.
-The $n^i(z)$ are taken from the LSST Science Requirement Document \citep{LSST-SRD} and given by
- \begin{eqnarray}
-n(z) = N_0 z^2 {\rm exp} \left[-\left(\frac{z}{z_0}\right)^\alpha \right]\, ,
-\label{eq:nz}
-\end{eqnarray}
-with $(z_0, \alpha) = (0.13, 0.78)$ and $N_0$ normalised to provide a number density of $n_{\rm eff}$ = 3.0 gal arcmin$^{-2}$.
-This lower than the expected number density for the first data release ($n_{\rm eff}\sim10$ gal arcmin$^{-2}$), but is large enough to validate our methods, and makes the calculation more tractable.
-The $n(z)$ is further split into five equi-populated tomographic bins, and smoothed with a Gaussian filter of width $\sigma = 0.05(1+z)$ in order to mimic the photometric selection process [{\it confirm with Niko}].
-The resulting distributions\footnote{The construction of these tomographic $n(z)$ can be reproduced in {github...CCL\_SRD\_Niko}.} are shown in Figure \ref{fig:Nz}.
-
-The cosmic shear signal can be measured from the ellipticities $\epsilon_{1/2}$ of simulated or observed galaxies, which, in absence of systematics and secondary signals, are unbiased estimators  of the cosmic shear components $\gamma_{1/2}$.
-The $\gamma$-2PCF are then estimated as:
- \begin{eqnarray}
- \widehat{\xi_{\pm}^{ij}}(\vartheta) = \frac{\sum_{a,b} w_a w_b \left[\epsilon_{a, \rm t}^i\epsilon_{b, \rm t}^j     \pm \epsilon_{a, \times}^i\epsilon_{b, \times}^j    \right]\Delta_{ab}(\vartheta)}{\sum_{a,b} w_a w_b} \, ,
- \label{eq:2PCF_estimator}
-  \end{eqnarray}
-where the sum is over all pairs of galaxies $a,b$ separated by an angular separation $\vartheta$, taken from tomographic bins $i,j$.
-The tangential/cross components of their ellipticities are denoted as $\epsilon_{\rm t/\times}$, respectively.
-$\Delta_{ab}(\vartheta)$ is the binning operator, equal to unity if the angular separation between the two galaxies falls within the $\vartheta$-bin, and zero otherwise, and the shape weights $w_{a,b}$ are set to unity.
-In this paper, we construct lensing catalogues from numerical simulations (described in Sec.
-\ref{sec:sims}), from which we measure $ \widehat{\xi_{\pm}^{ij}}(\vartheta)$ with {\sc Treecorr} \citep{TreeCorr}.
-We set therein the {\sc bin\_slop} parameter to 0.05, then compute the correlations in nine logarithmically-spaced angular bins ranging from 0.5 to 475.5 arcmin.
-
- %-------------------------
-\subsection{Beyond-2pt}
-\label{subsec:beyond-2pt}
-
-Non-Gaussian statistics, often referred to `beyond-2pt' statistics, have the potential to extract cosmological information stored in the complex phases of the density field, whereas two-point functions such as the $\gamma$-2PCF can only access that encoded in the complex amplitudes.
-No optimal estimator has been identified to-date as being able to capture `all' information, but the numerous studies presented in the introduction all show a clear gain in constraining power, especially when used in combination with 2pt functions.
-Some of these take as input the galaxy catalogues directly, while others require instead convergence maps.
-Therefore, we produce convergence maps from the catalogues by assigning the shear signal onto spherical {\sc Healpix}\footnote{{\sc Healpix}: http://healpix.sf.net}  maps \citep{healpix} with $N_{\rm side}=4096$, then using the standard Kaiser \& Squires inversion technique \citep{KaiserSquires} implemented in {\sc healpy} to reconstruct a convergence maps with the same angular resolution, including a baseline 2.0 arcmin smoothing beam in the inverse transform.
-Note that this smoothing scales is quite small; some probes are difficult to model in that case, and would instead prefer larger smoothing scales.
-We take this into account on a case-by-case basis, as described below.
-
-  {\it [Discuss tomography...]}
-
-\subsubsection{Catalogue-based estimators}
-
-We consider the following shear-based estimators:
-\begin{enumerate}
-\item The squeezed bispectrum, has theoretical model (Anik, can you summarise the measurements and modelling, and provide references?)
-\end{enumerate}
-
-\subsubsection{Convergence-based estimators}
-
-\begin{enumerate}
-\item Convergence three-point correlation function: (Alejandro, can you summarise the measurements and modelling, and provide references?)
-\item Peaks and Minima: local maxima and minima in the {\sc Healpix} convergence maps are counted in bins of signal-to-noise ratios, $\nu$.
-This is one of the most widely used non-Gaussian lensing statistics as it is simple to measure.
-Theoretical models have been developed to describe the largest peaks \citep[see][]{Shan18, HSCY1_Peaks_th}, however we report here the results on a much wider range of statistics, which can only be accurately modelled from numerical simulations, as in \citet{HD21, DESY3_Zuercher, HSCY1_Peaks_Sims, HD23}.
-\item Lensing PDF, has theoretical model (Cora/Lina, can you summarise the measurements and modelling, and provide references?)
-\item Map2 and Map3, has theoretical model  (Laila, can you summarise the measurements and modelling, and provide references?)
-\item Minkowski functionals (Nisha, can you summarise the measurements and modelling, and provide references?)
-\end{enumerate}
-
- %-------------------
- \section{Intrinsic alignment models}
- \label{sec:IA_th}
- %-------------------
-
-Galaxies interact with the tidal forces caused by the large-scale structure  they live in, causing their intrinsic shapes to acquire correlated alignments that has nothing to do with the correlations caused by weak lensing.
-This therefore acts as a secondary signal that contaminates the shape correlation measurements carried out in a cosmic shear analysis.
-There is no consensus on the actual physical model that describes the IA signal, and even when adopting these, the free parameters they contain are only weakly constrained from the data \citep[see][for reviews]{IA_review1, IA_review2}.
-%The most widely used model in the literature is the non-linear alignment model of \citet{NLA}, however it is now recognised that this is an effective model with limited precision, and the community is now progressively shifting towards more complex models.
-In this paper we consider four such IA models that we describe in the following sub-sections.
-In all cases, our models couple the galaxy intrinsic shapes with the local over-density and projected tidal field , then prescribe an intrinsic ellipticity tensor $\gamma_{ij}^{\rm IA}$, from which observed ellipticities are extracted as:
- \begin{eqnarray}
-\epsilon_{1}^{\rm IA} = \gamma_{xx}^{\rm IA} - \gamma_{yy}^{\rm IA} \, , \hspace{1.5cm}\epsilon_{2}^{\rm IA} = 2 \gamma_{xy}^{\rm IA}\, .
-\label{eq:tidal_th_deltaNLA}
-\end{eqnarray}
-
-\subsection{Non-linear alignment (NLA)}
-
-%The observed ellipticity of a galaxy ${\boldsymbol \epsilon}_{\rm obs} $ is a combination of its intrinsic shape ${\boldsymbol \epsilon}_{\rm int}$ and a cosmic shear signal ${\boldsymbol \gamma}$, the former of which can be further divided in a random component ${\boldsymbol \epsilon}^{\rm ran}$ and an alignment term ${\boldsymbol \epsilon}^{\rm IA}$.
-The NLA model of \citet{NLA} is the most widely used IA model in the cosmic shear literature thus far.
-According to the NLA, IA are caused by a linear coupling between galaxy shapes and the non-linear large-scale tidal field at the galaxy position.
-In the context of  two-point functions, these intrinsic shapes contribute to an intrinsic-intrinsic ($II$) term and an intrinsic-shear coupling ($GI$) term \citep{Hirata2004}, both secondary signals to the true cosmic shear ($GG$) term, with the latter typically dominating the IA sector in cross-tomographic measurements.
-The $II$ and $GI$ terms  can be both computed from the matter power spectrum as:
- \begin{eqnarray}
-P_{II}(k,z) =  \left(\frac{A_{\rm IA}\bar{C_1}\bar{\rho}(z)}{D(z)}\right)^2a^4(z) P_{\delta}(k,z)
-\label{eq:Pk_II_th}
-\end{eqnarray}
-and
- \begin{eqnarray}
-P_{GI}(k,z) = - \frac{A_{\rm IA}\bar{C_1}\bar{\rho}(z)}{D(z)}a^2(z) P_{\delta}(k,z) \, ,
-\label{eq:Pk_GI_th}
-\end{eqnarray}
-which can then be past to the Limber integration (Eqs. \ref{eq:C_ell} and \ref{eq:xipm_th}) to compute  the secondary signals $\xi_{\pm}^{II}(\vartheta)$ and $\xi_{\pm}^{GI}(\vartheta)$. 
-In the above expression,  $D(z)$ is the linear growth factor, $\bar{\rho}(z)$ is the mean matter density at redshift $z$ and $\bar{C_1}=5\times 10^{-14} M_{\odot}^{-1} h^{-2} {\rm Mpc}^3$ is a constant calibrated in \citet{Brown2002}.
-The strength of the tidal coupling is modulated by the amplitude parameter $A_{\rm IA}$, which is the main NLA parameter constrained by current cosmic shear surveys.
-Note that this model can be augmented by redshift and luminosity dependences, however we do not use these here.
-
-The NLA intrinsic ellipticities $\epsilon_{1,2}^{\rm NLA}$ are related to tidal field $s_{ij}$ by:
- \begin{eqnarray}
-\epsilon_1^{\rm NLA} = - \frac{A_{\rm IA}\bar{C_1}\bar{\rho}(z)}{D(z)} (s_{xx} - s_{yy}) \,\,\,\,,   \epsilon_2^{\rm NLA} = - \frac{2 A_{\rm IA}\bar{C_1}\bar{\rho}(z)}{D(z)} s_{xy}\;,
-\label{eq:tidal_th}
-\end{eqnarray}
-where $s_{ij} = \partial_{ij}\phi$ are the Cartesian components of the tidal tensor of the gravitational potential.
-Note that the term `non-linear' in the model name can be  misleading, as it refers to the non-linear matter power spectrum $P(k)$ that is used in its calculations; the coupling between the intrinsic galaxy shapes and the tidal field is still linear.
-Eq.( \ref{eq:tidal_th}) is used to assign intrinsic ellipticities to galaxies, given maps of the tidal field components $s_{xx}$, $s_{yy}$ and $s_{xy}$ (see Sec.
-\ref {subsec:IA_infusion}).
-
-\subsection{$\delta$-NLA}
-\label{subsec:IA_th_ext}
-
-%[{\it here}]
-
-%As discussed later, the key quantity of interest to cosmic shear analysis is not the tidal tensor itself but its trace-free version, since shape correlations with the density field are subdominant, even though peaks in high density environments are less elliptical on average.
-Consequently, the model itself has a restricted range of validity: on small scales, higher order couplings to the ellipticity field ${\boldsymbol \epsilon}^{\rm IA}$  become important, however these are neglected in the NLA model.
-Only the non-linear evolution of the tidal tensor itself is taken into account, since it does fit observations quite well.
-
-%We note that the NLA predicts additional higher-order terms and non-zero $B$-modes \citep{Hirata2004} that we neglect  in this analysis.
-Also, as shown in \citet{IA_EFT}, the NLA model can be interpreted as the lowest order description of the alignment process of galaxies in the light of an effective field theory description.
-
-The NLA model presented in the last section has been widely used in cosmic data analyses, but it has important known limitations and is therefore bound to fail at describing the IA signal with high precision.
-A perturbation theory extension to the NLA has been introduced in \citet{Blazek2015} and  \citet{Blazek2019},  where it is recognised that higher order couplings could be important and should be considered.
-The first additional term to be included is the over-density weighting term, which is caused by the fact that the intrinsic alignment of galaxies can only be observed at the galaxy positions, which are not distributed randomly on the sky but instead trace the underlying matter density,  `$\delta$', although the exact biasing scheme is not currently know.
-Accounting for this extra term in theoretical predictions is done with one-loop perturbation theory  \citep{Blazek2019}, and is implemented in {\sc pyccl}.
-Physically, it corresponds to adding a $\delta$-weight to the NLA predictions at the local galaxy positions, effectively representing the different tracer properties.
-At the level of numerical simulations, this could be done in principle simply by augmenting the NLA ellipticities with this weight, namely:
- \begin{eqnarray}
-\epsilon_{1/2}^{\delta-\rm NLA} = \epsilon_{1/2}^{\rm NLA}\times(1 + b_{\rm TA}\delta) \, ,
-\label{eq:tidal_th_deltaNLA}
-\end{eqnarray}
-where the term $b_{\rm TA}$ corresponds to the (largely unconstrained) biasing relation between these source galaxies and the underlying matter field.
-In practice, however, we find that this is noisy, and that it is instead preferable to generate mocks catalogues with the biasing scheme directly applied when assigning galaxy positions, after which no weighting is necessary.
-Nevertheless, Eq.
-(\ref{eq:tidal_th_deltaNLA}) can be used to modify the value of $b_{\rm TA}$.
-Indeed, from a mock with a given bias $b_{\rm TA, orig}$, we can rescale the IA contribution to a different $b_{\rm TA, new}$  as:
-\begin{eqnarray}
-{\boldsymbol \epsilon}^{\rm int}_{b_{\rm TA, new}}  = \frac{(1 + b_{\rm TA, new}\delta)}{(1 + b_{\rm TA, orig}\delta)}{\boldsymbol \epsilon}^{\rm int}_{b_{\rm TA, orig}} \, .
-\label{eq:bta_rescale}
-\end{eqnarray}
-
-Compared to the NLA, the $\delta$-NLA is a stronger IA model, especially on small scales \citep{Blazek2019}, and seems to be preferred by some hydrodynamical simulations \citep{Hilbert_IA2017}.
-It is also better motivated from a physical point of view, since we know that the galaxies trace dark matter  and are not randomly distributed in our Universe as the NLA assumes.
-
-%-----------------------------------
-\subsection{Tidal Torque (TT)}
-\label{subsec:IA_th_TT}
-
-As shown in \citet{Blazek2019}, one-loop perturbative calculations include another term, by which galaxies acquire an intrinsic alignment via a coupling between their angular momentum and the tidal field, which can be re-expressed as a quadratic coupling between the tidal field and the shape.
-In this tidal torque model (TT), intrinsic ellipticities are given by:
-\begin{eqnarray}
-\gamma_{ij}^{\rm IA, TT} = C_2 \left[ \sum_{k=x,y,z} s_{ik} s_{kj} -\frac{1}{3} \delta_{ij} s^2 \right] \, ,
-\label{eq:tidal_th_TT}
-\end{eqnarray}
-where 
-\begin{eqnarray}
-C_2 = \frac{5 A_2 \bar{C_1} \Omega_{\rm m} \rho_{\rm crit}}{D^2(z)} \,  = \left[ \frac{-5 A_2}{A_1 D(z)} \right] C_1.
-\end{eqnarray}
-Under the approximation that line-of-sight alignments are mostly suppressed from cosmic shear measurement due to the broad lensing kernels, 
-we show in  Appendix \ref{app:2d_TT} that the terms inside the square bracket in Eq. (\ref{eq:tidal_th_TT}) leads to:
-\begin{eqnarray}
-\epsilon_1^{\rm TT} = C_2  \left[ s_{xx}^2 - s_{yy}^2\right] \, , \epsilon_2^{\rm TT} = 2 C_2 s_{xy}\left[s_{xx}+s_{yy}  \right]\, ,
-\end{eqnarray}
-both quadratic in the tidal field components.
-
-%-----------------------------------
-\subsection{$\delta$-TT}
-\label{subsec:IA_th_TT}
-
-Following the relation between the NLA and the $\delta$-NLA model, galaxies in the TT model are also assume to be randomly scattered on the sky, which we know to be a bad approximation.
-Computing the next-order contribution to the TT model involves two-loop perturbation theory calculations that have not been done yet due to the significantly higher complexity of such task.
-in simulations however, the $\delta$-weighting term is straight-forward to implement, as it involves to simply infuse the TT model onto galaxies that trace the matter field with a non-zero biasing factor.
-As for the $\delta$-NLA model, the $\delta$-TT ellipticities can  be related to the TT model as:
-\begin{eqnarray}
-\epsilon_{1/2}^{\delta-\rm TT} = \epsilon_{1/2}^{\rm TT}\times(1 + b_{\rm TA}\delta) \, .
-\label{eq:tidal_th_deltaTT}
-\end{eqnarray}
- There are currently no theoretical models for $\delta$-TT, which means that predictions from this model are, at the moment, completely simulation-based.
-
-It is worth recalling here that other IA models exist in the literature, and that at this point observations are not precise enough to set strong constraints on them, further motivating our flexible multi-model approach.
-
-%\subsection{Likelihood}
-%\label{subsec:likelihood}
-
-%Multi-Gaussian likelihood, analytical Covariance matrix (Gauss + non-Gauss + SSC) from {\sc TJPCov}, Firecrown, sampler, priors.
-
-%---------------------
-\section{Simulations}
-\label{sec:sims}
-
-%-------------
-\subsection{Cosmic shear galaxy catalogues} 
-\label{subsec:WL_cats}
-
-The weak lensing simulations developed for this work are based on ray-tracing mass sheets produced from the Outer Rim $N$-body simulation \citep{OuterRim}, which evolved 10,240$^3$ particles in a (5.225 Gpc)$^3$ cosmological volume, assuming a flat $\Lambda$CDM cosmology with $\Omega_{\rm m}$=0.2648, $\Omega_{\rm b}$=0.0448, $h$=0.71, $\sigma_8$ = 0.801, $n_{\rm s}$= 0.963, $w_0$=-1.00.
-A total of 101 particle snapshots were originally saved, of which we use only those with $z<4.0$.
-Particles from each dump are assigned to curved mass shells approximately 114 Mpc thick, producing a sequence of 57 {\sc Healpix} maps $\delta(\theta,\phi,\chi_i)$ with {\sc nside} = 8192 and $i=1..57$, filling up a light-cone over an octant up to $z=3$.
-%More details on this procedure can be found  in \citet{cosmoDC}, where lensing quantities are computed specifically for the generation of the {\sc cosmoDC2}  synthetic sky catalogue.
-
-Ray-tracing is performed in the Born approximation, summing over the mass shells using the $\chi$-integral of Eq.
-(\ref{eq:C_ell}).
-A source plane is placed at the high-redshift edge of every mass planes, resulting in a series of convergence  maps  $\kappa(\theta,\phi,\chi_i)$ that are subsequently transformed into shear maps $\gamma_{1/2}(\theta,\phi,\chi_i)$ using the Kaiser-Squires methods \citep{KaiserSquires}, which is implemented via efficient {\sc HealPy alm2map} routines.
-
-We position galaxies in the light cone following exactly our chosen $N(z)$, and interpolate the shear quantities at their location. We follow two distinct algorithm to achieve this:
-\begin{enumerate}
-\item {\it Random:} galaxies RA and Dec are distributed randomly on the octant, thereby matching this fundamental assumptions in the NLA and TT models. 
-\item {\it Linear bias:} galaxies RA and Dec are sampled from the mass sheets smoothed\footnote{We also tried sampling the field with 0.1 and 0.5 $h^{-1}$Mpc but this resulted in noisier results.} over 1.0 $h^{-1}$Mpc (comoving), assuming a linear bias of $b_{\rm TA}$, now matching instead the assumptions of the $\delta$-NLA and $\delta$-TT models.
-With this method we produce galaxy positions assuming first $b_{\rm TA}=1.0$ (our fiducial case) and also $b_{\rm TA}=2.0$, enhancing the  model flexibility.
-\end{enumerate}
-
-Since source clustering is a higher order effect in cosmic shear, the measured $\xi_{\pm}$ from these three mocks (random, $b_{\rm TA}=1.0$ and $b_{\rm TA}=2.0$) show negligible differences ({\it to quantify and cite}).
-In contrast, the impact on the IA contamination is significant and can double the secondary signal in certain circumstances.
-The main explanation for this is that while clustered sources are uncorrelated with the foreground matter responsible for the lensing signal, the high-density regions they live are also subject to the largest tidal fields.
-
-%----------
-\subsection{Projected tidal fields}
-\label{subsec:IA_sims}
-
-\begin{figure*}
-\caption{Density field and the associated projected tidal field tensors.}
-\label{fig:maps}
-\end{figure*}
-
-Our infusion method completely relies on couplings between intrinsic galaxy shapes and the local tidal field, hence the first step in our method consist in extracting the tidal field maps $s_{ij}(\theta,\phi,\chi_i)$ from the mass maps $\delta(\theta,\phi,\chi_i)$ that source them.
-In three dimensions, trace-free tidal tensor $s_{ij}(\boldsymbol x)$ can be obtained from the matter over-density field $\delta(\boldsymbol x)$ as   \citep{Catelan_IA_Tidal}:
-\begin{eqnarray}
- \widetilde{s}_{ij} (\boldsymbol k)  = \left[\frac{k_i k_j}{k^2} - \frac{\delta_{ij}}{3}\right]  \widetilde {\delta}(\boldsymbol k) \mathcal{G}(\sigma_{\rm G}) \, ,
- \label{eq:sij}
-\end{eqnarray}
-where $\mathcal{G}(\sigma_{\rm G})$ is a three-dimensional Gaussian function described by a single (free) parameter $\sigma_{\rm G}$ that  controls the physical scales which are allowed to affect the IA term in our model.
-Tilde symbols  denote Fourier transformed quantities,  the indices $(i,j)$ label the components of the Cartesian wave-vector $\boldsymbol{k}^T = (k_x,k_y,k_z)$, and $k^2 = k_x^2 + k_y^2 + k_z^2$. 
-As shown in \citet{Tidalator} for Cartesian coordinates, projected tidal fields  computed from projected mass sheets provide and excellent agreement with the NLA model, which in contrast computes the full tidal fields from the three-dimensional matter density and project along the radial dimension at the end.
-We promote this transformation to curved-sky in this work, exploiting the  polarisation {\sc alm2map} operations built in {\sc Healpy}.
-In particular, noting that $Q=s_{xx}-s_{yy}$, $U=s_{xy}$ and $\delta=s_{xx}+s_{yy}$, we compute the curved-sky tidal field tensors ${s}_{ij}({\boldsymbol \theta})$ as:
- \begin{eqnarray}
-s_{xx}({\boldsymbol \theta})  =  \left[\frac{ \delta + Q}{2}  - \frac{\delta}{3}\right] \, ,s_{yy}({\boldsymbol \theta})  =  \left[\frac{\delta - Q}{2}  - \frac{\delta}{3}\right] \, , s_{xy}({\boldsymbol \theta}) = U
- \label{eq:sij_2D_sph}
- \end{eqnarray}
-where the $U({\boldsymbol \theta})$ and $Q({\boldsymbol \theta})$ maps are smoothed by the Gaussian beam with width $\sigma_{\rm G}$.
-We suppress large artificial tidal fields at the maps boundary by replicating 8$\times$ the density maps defined on the octant and working on a full sky density $\delta$; we re-apply the octant mask on the tidal field maps after the operation.
-Note that the value of $\sigma_{\rm G}$ is a free parameter both in the infusion technique described in this paper and in the NLA and TATT models.
-We therefore explore two cases, $\sigma_{\rm G}=0.1$Mpc and 0.5Mpc, however this may be further optimised in the future.
-Finally, the full-sky density field is downgraded from $N_{\rm side}=8192$ to $N_{\rm side}=4096$ since the smoothing washed the smallest angular scales.
-
-%are specified within the NLA model.
-Smoothing amounts to selecting physical scales that do not contribute to the alignment of galaxies, which is still a debatable quantity, but is also introduced for numerical stability.
-\citet{Blazek2015} argues that 1.0 $h^{-1}$Mpc could be a reasonable fiducial value, being larger then the typical halo size, but recognizes that one-halo terms are also required to better match the observations.
-In their later work, \citet{Blazek2019} do not include smoothing at all, and neither do the KiDS-1000 nor DES-Y1 analyses based on the NLA model \citep{KiDS1000_Asgari,DESY1_Troxel}.
-In this work we used a two-dimensional Gaussian filter and calibrated $\sigma_{\rm G}$ empirically to $\sigma_{\rm G}=0.1h^{-1}$Mpc (see Sec.
-\ref{subsubsec:sigma_G}), however these two choices are arbitrary and could possibly be better optimised in the future; we also explore $\sigma_{\rm G}=0.5h^{-1}$Mpc later on.
-We note that the smoothing scale is degenerate with the resolution of the simulation itself, and that one should use caution when smoothing on scales that approach the resolution limits.
-
-%We employ a numerical technique worth mentioning here: the Fourier transforms involved in computing Eq.
-(\ref{eq:sij_2D}) are computed from the full (projected) periodic boxes of the simulations, then interpolated on the light-cones.
-We find that tidal field computed directly from the $10\times10$ deg$^2$ light-cones introduces significant large scales features in the tidal field maps, largely caused by  the non-periodic boundary conditions, which our method avoids.
-Projected tidal field maps $s_{11}$, $s_{22}$ and $s_{12}$ are constructed that way for each mass sheets; Fig.
-\ref{fig:maps} shows the  three tidal fields and the mass maps for one of them.
-We can clearly see the connection between all maps around over-dense regions.
-{\it (Include a figure of $s_ij$ and $\delta$)}.
-
-{\it [Mention normalisation of the tidal fields by $0.6252 = H_0/114$ = 1/shell-thickness}
-
-%of every light-cones and interpolated at the position of every galaxy.
-Fig.
-\ref{fig:tidalator} illustrates this process for a small zoomed-in patch at $z\sim0$, starting from a $\delta_{2D}(\boldsymbol \theta)$ map (upper large panel), computing the tidal field components (middle four panels) and comparing the results with the cosmic shear signal generated by the same mass distribution (bottom two panels).
-The tidal field maps clearly reproduce the cosmic shear maps, and the minus sign in front of both terms in Eq.
-(\ref{eq:tidal_th}) causes the IA to undo some of the lensing signal.
-
-\subsection{Infusion of intrinsic alignments}
-\label{subsec:IA_infusion}
-
-Having now produced shear catalogues and tidal field maps, we can now use Eq.
-\ref{eq:tidal_th} to couple linearly the alignment of galaxies with the local tidal field, or Eq.
-\ref{eq:tidal_th_TT} to use instead a quadratic coupling.
-These allow us to compute the intrinsic ellipticities ${\boldsymbol \epsilon}^{\rm int}$ for the four IA models described in Sec.
-\ref{sec:IA_th}, which we combine with the cosmic shear signal ${\boldsymbol g}$ to compute observed ellipticities:
-\begin{eqnarray}
-{\boldsymbol \epsilon}^{\rm obs} = \frac{{\boldsymbol \epsilon}^{\rm int} + {\boldsymbol g}}{1 + {\boldsymbol \epsilon}^{\rm int}{\boldsymbol g^*}} \,, {\rm with \, \, } 
-{\boldsymbol \epsilon}^{\rm int}  = \frac{{\boldsymbol \epsilon}^{\rm IA} + {\boldsymbol \epsilon}^{\rm ran}}{1 + {\boldsymbol \epsilon}^{\rm IA}{\boldsymbol \epsilon^{\rm ran, *}}}.
-\label{eq:eps_obs}
-\end{eqnarray}
-In the above expressions, the denominators ensures that the combined  ellipticities never exceed unity.
-The complex spin-2 reduced shear ${\boldsymbol g} \equiv (\gamma_1 + {\rm i} \gamma_2)/(1+\kappa)$ is computed from the shear  $(\gamma_{1/2}$) and convergence ($\kappa$) maps, interpolated at the galaxy positions and redshifts.
-The  random orientation term ${\boldsymbol \epsilon}^{\rm ran}$ is drawn from two Gaussians (one per component) with their standard deviations matching the LSST-Y1 forecast, $\sigma_{\epsilon} = 027$.
-We further constraint  the random ellipticity to satisfy $|{\boldsymbol \epsilon}^{\rm ran}| \le 1.0$.
-%We recall that since our simulated galaxy catalogues trace the dark matter density, our default IA-infusion method  is consistent with the $\delta$-NLA model (see Sec.
-\ref{subsec:IA_th_ext}).
-Analytical predictions for the two-point functions are more involved in this case \citep[see][]{Blazek2019} and not yet available on the public {\sc cosmoSIS} release.
-We therefore validate our methods with the standard NLA first, which we infuse by `correcting' the $\delta$-NLA measurement with Eq.
-(\ref{eq:tidal_th_deltaNLA}), i.e.
-by replacing ${\boldsymbol \epsilon}^{\rm IA}$ by ${\boldsymbol \epsilon}^{\rm IA}/(1 + b_{\rm TA} \delta)$ in our simulations.
-Once again, these are less realistic but better suited for validation of the measured $\gamma$-2PCFs against a theoretical model; after this is established, we use the $\delta-$NLA catalogues as our fiducial infusion model.
-We re-iterate here that the same tidal fields, shear maps and IA coupling equations are used for the NLA and $\delta$-NLA models, and separately for the TT and $\delta$-TT models; these  only differ by the fact that in one case the galaxies are placed at random on the octant, while in the other case they are linearly tracing the dark matter.
-
-Also note that our current IA models make no differentiation between galaxy colours or type, and instead treats the full sample as a single population that has a single, effective, alignment signall \citep[see][for an example with a red/blue split]{DESY1_IA_Samuroff}.
-
-%---------------------
-\section{Validation with $\xi_{\pm}$}
-\label{sec:validation}
-
-% Requires the booktabs if the memoir class is not being used
-\begin{table}
-   \centering
-   %\topcaption{Table captions are better up top} % requires the topcapt package
-   \begin{tabular}{@{} lcr @{}} % Column formatting, @{} suppresses leading/trailing space
-      \hline
-      \hline
-       %\multicolumn{2}{c}{Item} \\
-      model   		& ($A_{\rm IA}, b_{\rm TA}, A_2)$ \\
-      \hline
-      NLA     		& {($\pm$1,0,0) }&  \\
-      \multirow{2}{*}{$\delta-$NLA }  	&   {($\pm$1,1,0)}   \\
-      							&  {(1,2,0)}   \\
-      TT 			&  {(0,0,$\pm$1)} &  \\
-      \multirow{2}{*}{$\delta$-TT} 	&  {(0,1,$\pm$1)}   \\
-      				&  {(0,2,1)}   \\
-      TATT- fiducial	&  { (1,1,1)}  \\
-      %TATT-DESY3	&   (-0.7,1,1.9) & \\
-      \hline
-      \hline
-
-   \end{tabular}
-   \caption{IA models infused in this work.}
-   \label{table:IAmodels}
-\end{table}
-
-%------------------------------
-\subsection{NLA model}
-\label{subsubsec:sigma_G}
-
-See Fig. \ref{fig:xi_NLA}
-%---------------
-\begin{figure*}
-%\includegraphics[width=\columnwidth]{graphs/frac_xip_IA1_skysim}
-\includegraphics[width=\columnwidth]{graphs/frac_xip_IA1_skysim_NLA_srd.jpg}
-\includegraphics[width=\columnwidth]{graphs/frac_xim_IA1_skysim_NLA_srd.jpg}
-\caption{Ratio between the shear correlation functions with and without IA, assuming the NLA model with $A_{\rm IA}=1.0$ both in the simulations and theory.
-Measurements shown in green and brown correspond to smoothing scales of 0.1 and 0.5 $h^{-1}$Mpc in the tidal field.
-There is no shape noise in the simulations, but it is included in the error bars.}
-\label{fig:xi_NLA}
-\end{figure*}
-%---------------
-
-%------------------------------
-\subsection{$\delta$-NLA model}
-\label{subsec:deltaNLA}
-
-See Fig. \ref{fig:xi_deltaNLA}.
-
-\begin{figure*}
-\includegraphics[width=\columnwidth]{graphs/frac_xip_IA1_skysim_deltaNLA_srd}
-\includegraphics[width=\columnwidth]{graphs/frac_xim_IA1_skysim_deltaNLA_srd}
-\caption{Same as Fig.
-\ref{fig:xi_NLA}, but for the $\delta$-NLA model with $A_{\rm IA}=1.0$ and $b_{\rm TA}=1.0$, and only for smoothing of 0.5$h^{-1}$Mpc.
-The dashed black lines show the NLA predictions to better highlight the differences.
-}
-\label{fig:xi_deltaNLA}
-\end{figure*}
-
-\begin{figure}
-\includegraphics[width=\columnwidth]{graphs/frac_xip_bta1_rescaled}
-\caption{Ratio between the shear correlation functions with and without IA in tomographic bin combination 2-5.
-The brown and green symbols show measurements from simulations constructed with $b_{\rm TA}$ = 0.0 and 2.0 respectively,  the black solid and dotted lines shown their predictions, while the blue symbols are obtained by rescaling $b_{\rm TA}$ = 1.0 simulations using Eq.
-\ref{eq:bta_rescale}.
-}
-\label{fig:xi_deltaNLA_rescaled}
-\end{figure}
-
-We verified that it works equally well for $b_{\rm TA}$ = 1.0 and 2.0.
-
-%------------------------------
-
-Using this, we $b_{\rm TA}$-rescale our $b_{\rm TA}=1.0$ mock to $b_{\rm TA}=2.0$ and to $0.0$ mocks.
-Results are shown in Fig.
-\ref{fig:xi_deltaNLA_rescaled} for one of the tomographic bin.
-It works reasonably well, but lower redshift are less accurate due to the increased  shot noise (not shown), hence we do not recommend using this.
-
-%------------------------------
-\subsection{TT model}
-\label{subsec:TT}
-
-See Fig. \ref{fig:xi_TT}
-
-\begin{figure*}
-\includegraphics[width=\columnwidth]{graphs/frac_xip_IA1_skysim_TT_srd.jpg}
-\includegraphics[width=\columnwidth]{graphs/frac_xim_IA1_skysim_TT_srd.jpg}
-\caption{Same as Fig. \ref{fig:xi_NLA}, but for the TT model with $A_2=1.0$. Here, the dashed black lines show the NLA predictions to better highlight the differences. }
-\label{fig:xi_TT}
-\end{figure*}
-
-\begin{figure*}
-%\includegraphics[width=\columnwidth]{graphs/frac_xip_C2_m1_skysim_deltaTT}
-\includegraphics[width=\columnwidth]{graphs/frac_xip_IA1_skysim_deltaTT_srd.jpg}
-\includegraphics[width=\columnwidth]{graphs/frac_xim_IA1_skysim_deltaTT_srd.jpg}
-\caption{Same as Fig. \ref{fig:xi_deltaNLA}, but comparing the TT and the $\delta$-TT models, with $A_2=1.0$, $b_{\rm TA}$ = 1.0, and only for smoothing of 0.5$h^{-1}$Mpc. }
-\label{fig:xi_deltaTT}
-\end{figure*}
-
-To match the theory, we need to apply the following calibration: $\epsilon^{\rm IA, TT}(z<0.5) \rightarrow \epsilon^{\rm IA, TT} /2.5$.
-
-%------------------------------
-\subsection{$\delta$-TT model}
-\label{subsec:TT}
-
-See Fig. \ref{fig:xi_deltaTT}
-
-To match the TT theory, we need to apply the following calibration: $\epsilon^{\rm IA, TT}(z<0.5) \rightarrow \epsilon^{\rm IA, TT} /5.0$, followed by $\epsilon^{\rm IA, TT} \rightarrow \epsilon^{\rm IA, TT}/7.0$.
-
-\subsection{Validation with full inference}
- \label{sec:inference}
-\begin{figure}
-%\includegraphics[width=\columnwidth]{graphs/triangle_nla_5D.pdf}
-\includegraphics[width=\columnwidth]{graphs/triangle_bta_sweep.pdf}
-\caption{Cosmological inference from the NLA-infused simulations, analysed the extended-NLA model. The cross-hairs represent the truth as fixed in the OuterRim $N$-body simulations \citep{OuterRim}.}
-\label{fig:triangle_nla}
-\end{figure}
-priors, {\sc CosmoSIS}, Takahashi $P(k)$, etc.
-
-\section{Higher-order weak lensing statistics}
-\label{sec:HOWLS}
-
-... use the mocks from Table \ref{table:IAmodels} to compute derivatives. Show.
-
-%----------
-\section{Conclusions}
-\label{sec:conclusion}
-%----------
-
-\section*{Acknowledgements}
-
-JHD acknowledges support from an STFC Ernest Rutherford Fellowship (project reference ST/S004858/1).
-Ray-tracing computations were carried on the NERSC [acknowledgments] ...
-HACC [acknowledgements] ...
-OuterRim [Acknowledgments]
-\\
-
-Some of the results in this paper have been derived using the {\sc healpy} and {\sc HEALPix} packages.
-\\
-\\
-\\
-{\footnotesize All authors contributed to the development and writing of this paper. JHD led the analysis.... }
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Data Availability}
-
-%The SLICS numerical simulations can be found at http://slics.roe.ac.uk/, while the cosmo-SLICS can be made available upon request.
-
-%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%
+%%%%% REFERENCES %%%%%
 
 % The best way to enter references is to use BibTeX:
+%\bibliographystyle{hapj}
+\bibliographystyle{mnras}
+\bibliography{references}
 
-\bibliographystyle{hapj}
-\bibliography{IA} % if your bibtex file is called example.bib
+%%%%% APPENDICES %%%%%
 
-% Alternatively you could enter them by hand, like this:
-% This method is tedious and prone to error if you have lots of references
-%\begin{thebibliography}{99}
-%\bibitem[\protect\citeauthoryear{Author}{2012}]{Author2012}
-%Author A.~N., 2013, Journal of Improbable Astronomy, 1, 1
-%\bibitem[\protect\citeauthoryear{Others}{2013}]{Others2013}
-%Others S., 2012, Journal of Interesting Stuff, 17, 198
-%\end{thebibliography}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%% APPENDICES %%%%%%%%%%%%%%%%%%%%%
-
-\appendix
-
-\begin{figure*}
-\includegraphics[width=\columnwidth]{graphs/xip_sims_vs_th.eps}
-\includegraphics[width=\columnwidth]{graphs/xim_sims_vs_th.eps}
-\caption{Fractional difference on $\xi_\pm$ between the measurements from SkySim5000 and the model predictions.  }
-\label{fig:frac_err_sims_th}
-\end{figure*}
-
-\section{Projected Tidal Field}
-\label{app:2d_TT}
-
-\JHD{[To reword]} We derive in this Appendix...  
-The prescription to assign an intrinsic alignment based on the projected tidal field, described in Eq.
-(\ref{eq:tidal_th}), involves the combinations $(s_{xx} - s_{yy})$ and $s_{xy}$, which therefore correspond to:
-\begin{eqnarray}
- \widetilde{\epsilon}_1^{\rm IA} (\boldsymbol k_{\perp})  &\propto& \left(\frac{k_x^2 - k_y^2}{k^2} \right) \widetilde{\delta}_{\rm 2D}(\boldsymbol k_{\perp})\mathcal{G_{\rm 2D}}(\sigma_{\rm G})  \, ,\nonumber \\
- \widetilde{\epsilon}_2^{\rm IA} (\boldsymbol k_\perp)  &\propto& \left(\frac{k_x k_y}{k^2} \right) \widetilde {\delta}_{\rm 2D}(\boldsymbol k_\perp)\mathcal{G_{\rm 2D}}(\sigma_{\rm G}) 
- %\label{eq:sij}
-\end{eqnarray}
-
-Aside from the smoothing kernel, these are the same filters that are used for converting convergence maps to shear maps under the \citet[][KS hereafter]{KaiserSquires} inversion:
- \begin{eqnarray}
- \widetilde{\gamma_1} (\boldsymbol \ell)  = \left(\frac{k_x^2 - k_y^2}{k^2} \right) \widetilde {\kappa}(\boldsymbol \ell) \, , \hspace{1cm} \widetilde{\gamma_2} (\boldsymbol \ell)  = \left(\frac{k_x k_y}{k^2} \right) \widetilde {\kappa}(\boldsymbol \ell)
- %\label{eq:sij}
-\end{eqnarray}
-meaning that on can linearly combine the mass sheets with the correct coefficients and obtain intrinsic ellipticities from a normal KS inversion.
-
-Projecting out the $z$ components (e.i. $s_{0i}$=$s_{i0}$=0 for all $i$),  the tidal torque terms from Eq. (\ref{eq:tidal_th_TT}) can be expanded as:
- \begin{eqnarray}
-\gamma^{\rm TT}_{ij}&=& C_2 \left[\sum_{k=x,y} s_{ik} s_{kj} -\frac{1}{3} \delta_{ij} s^2\right] \\
-                                  &=&C_2 \left[ s_{ix}s_{xj}  + s_{iy}s_{yj}  -  \frac{1}{3} \delta_{ij} \left( s_{xx}^2 + s_{yy}^2 +2s_{xy}^2 \right)  \right] \, .
-\end{eqnarray}
-Specifically, this yields:
- \begin{eqnarray}
-\gamma^{\rm TT}_{xx}&=& C_2 \left[\frac{2}{3}s_{xx}^2  -  \frac{1}{3}s_{yy}^2 + \frac{1}{3}s_{xy}^2 \right]\, ,  \nonumber \\
-\gamma^{\rm TT}_{yy}&=& C_2 \left[-\frac{1}{3}s_{xx}^2  +  \frac{2}{3}s_{yy}^2 + \frac{1}{3}s_{xy}^2  \right]\, , \\
-\gamma^{\rm TT}_{xy}&=& C_2 s_{xy}\left[s_{xx}+s_{yy}  \right]\, . \nonumber                                  
-\end{eqnarray}
-With the standard ellipticity definitions $\epsilon_1^{\rm TT}\equiv \gamma_{xx}^{\rm TT} - \gamma_{yy}^{\rm TT}$ and $\epsilon_2^{\rm TT}\equiv -2 \gamma_{xy}$, we obtain:
-\begin{eqnarray}
-\epsilon_1^{\rm TT} = C_2  \left[ s_{xx}^2 - s_{yy}^2\right] \, , \epsilon_2^{\rm TT} = -2 C_2 s_{xy}\left[s_{xx}+s_{yy}  \right]\, .
-\end{eqnarray}
-In the TATT model, the total intrinsic ellipticity component is therefore given by $\epsilon_{1/2}^{\rm IA} = \epsilon_{1/2}^{\rm TATT} = \epsilon_{1/2}^{\delta{\rm-NLA}} + \epsilon_{1/2}^{\rm TT}$.
+\input{sections/10_appendix}
 

### 2024-03-27 sections/1_introduction.tex

%----------
\section{Introduction}
\label{sec:intro}
%----------

Recent cosmic shear measurements from the Kilo Degree Survey\footnote{KiDS:kids.strw.leidenuniv.nl}, the Dark Energy Survey\footnote{DES:www.darkenergysurvey.org}, and the Hyper Suprime Camera Survey\footnote{HSC:www.naoj.org/Projects/HSC} have established weak gravitational lensing as a competitive probe of cosmology \citep[see. \eg][]{KiDS1000_Asgari, KiDS1000_vdB, KiDS1000_Li, DESY3_Secco, DESY3_Amon, HSCY3_Cl, HSCY3_2pcf}, achieving  percent-level measurements of the structure growth parameter $S_8\equiv\sigma_8\sqrt{\Omega_{\rm m}/0.3}$.
The parameters $\Omega_{\rm m}$ and $\sigma_8$, which respectively describe the abundance and the fluctuations of the matter density fluctuations on scales of $8h^{-1}$ Mpc, are highly degenerate in the lensing signal, and additional data (\eg galaxy clustering data) are required to measure the two individually \citep{Heymans, DES3x2pt, HSC3x2} \niko{fix the refs}.
Despite these highly successful achievements, the current precision of cosmic shear cosmology is mainly limited by the large uncertainty in the intrinsic alignment (IA) of galaxies, a secondary signal that tends to cancel some of the shape correlations produced by lensing \citep[see. \eg][for reviews on IA]{Troxel_IA_review_2015, Kirk_IA_review_2015, Joachimi_IA_review_2015, Kiessling_IA_review_2015}. 
If unaccounted for, the IA can bias by XYZ$\sigma$ the inferred cosmological parameters \citep{BlazekKrause}.
Additionally, using an inaccurate IA model can substantially impair the inference process, as demonstrated by \citet{DESY3_Secco} in their study on DES-Y3 analysis and by \citep{Paopiamsap2024} in the context of an LSST-like cosmic shear analysis.
%Furthermore, an incorrect IA model can also cause significant damage to the inference, as shown in \citet{DESY3_Secco} in the context of DES-Y3 analysis, or in \citep{Paopiamsap2024} in the context of an LSST-like cosmic shear analysis.

Different physical models have been developed to describe the origin and impact of the IA, including the linear non-linear alignment model \citep[NLA hereafter, ][]{BridleKing2007}, the density-weighted NLA (aka $\delta$-NLA or extended-NLA), and the tidal torque model \citep[][TT hereafter]{BlazekTATT2017}, which respectively assume a linear and quadratic coupling between galaxy ellipticities and the local tidal field. 
The halo model can also describe the IA signal as a function of halo properties such as their mass, concentration, and shapes \citep{FortunaIA}.
A number of observations have sought to place constraints on the parameters from these models \citep[\eg][]{Singh, Sammuroff, Christos, Fortuna, Johnston}.
These observations seem to converge towards a strong colour-dependence: red bright galaxies (elliptical) are generally strongly aligned, with hints of a radial dependence, while blue galaxies (spiral) are consistent with the no-alignment scenario.
%A number of observations have sought to place constraints on the parameters from these models \citep[\eg][]{Singh, Sammuroff, Sammuroff, Christos, Fortuna, Johnston}, which seem to converge towards a strong colour-dependence (red bright galaxies are generally strongly aligned, with hints of a radial dependence), while blue galaxies are consistent with the no-alignment scenario.
The selection effects play a crucial role, making it difficult to generalise these measurements to a different galaxy sample, therefore leaving behind a large uncertainty on the IA parameters.

While most of these methods have been developed to provide prescriptions for modelling IA in lensing  two-point statistics, some have been used to infuse galaxy alignments directly into cosmological simulations, as in \citet{Fluri2019, Tidalator2D, MICE_IA, Borg, Lanzieri}. 
Access to IA-infused numerical simulations is crucial for several applications:
\begin{itemize}
    \item \textit{Validating theoretical models deep in the non-linear regime or utilizing the non-linear galaxy bias model \citep{IA_gal_bias}}.
    \item \textit{Predicting the impact of IA on non-Gaussian lensing probes, for which no models exist \citep{ZuercherXYZ, Tidalator2D}}.
    \item \textit{Testing IA mitigation techniques \citep{IA_selfCalibration}}.
    \item \textit{Exploring the connection between large dark matter haloes and IA \citep{vanAlfen}}.
\end{itemize}
%Having access to such IA-infused numerical simulations is crucial for a number of applications, including the possibility to validate theoretical models deep in the non-linear regime (or using the non-linear galaxy bias model) \citep{IA_gal_bias}, to predict the impact of IA on non-Gaussian lensing probes for which no model exist \citep{ZuercherXYZ, Tidalator2D}, to test IA mitigation techniques \citep{IA_selfCalibration}, or to learn about  the connection between large dark matter haloes and IA \citep{vanAlfen}. 
{\JHD{ (Any other important references?)}}

This paper addresses several of the above-mentioned applications \niko{shall we mention which ones?}.
After reviewing the modelling and measurement of cosmic shear data in Sec. \ref{sec:theory}, we describe our new flexible method to infuse different IA models in cosmological simulations (Sec. \ref{sec:IA_th}). 
Specifically, we infuse the NLA model, the \dNLA, and the TT model on the same underlying lensing simulation. 
In addition, we introduce the \dTT model (which takes into account the fact that galaxies trace dark matter even in the TT model), then proceed to couple the cosmic tidal fields with galaxies taken from halo occupation distributions (HOD) to investigate the impact of realistic non-linear galaxy bias on the IA signal.
These new models are both physically motivated and challenging to describe theoretically as they require perturbation expansions beyond the second order.  
The full numerical implementation is described in Sec. \ref{sec:sims} and validated against theoretical predictions at the level of  two-point shear correlation functions in Sec. \ref{sec:validation}.
Since our infusion method acts on shear galaxy catalogues and on convergence maps, we are in an ideal position to quantify the impact of multiple IA models on different non-Gaussian statistics, which we report in Sec. \ref{sec:HOWLS}, before concluding in Sec. \ref{sec:conclusion}.

### 2024-03-27 sections/2_cosmic_shear_stats.tex

\section{Cosmic shear statistics}
\label{sec:theory}

Cosmic shear data can be analysed using various summary statistics, each with its own advantages and disadvantages.
%Cosmic shear data can be analysed by a number of summary statistics, which all have their pros and cons.
We first review the modelling and measurement methods of shear two-point functions, then present other complementary cosmic shear statistics in the second part of this section.

%-------------------------
\subsection{$\gamma$-2PCF}
\label{subsec:wl-th}

\input{figures/lsst_redshift_distribution}

Shear two-point correlation functions (\gtwopcf hereafter) can be predicted with percent-level precision and are therefore an ideal quantity to validate weak lensing simulations.
In the Limber approximation\footnote{See \citet{Kilbinger17} for a comparison between the Limber approximation and the exact calculations.}, the lensing angular power spectrum $C^{ij}_{\ell}$ (in spherical harmonics space) in tomographic bins $i$ and $j$ is obtained from an integral over the three-dimensional matter power spectrum $P_{\delta}(k, z)$ (in Fourier space, and redshift $z$ dependant):
  \begin{eqnarray}
C_{\ell}^{ij} = \int_0^{\chi_{\rm H}}  \frac{q^i(\chi) \,q^j(\chi)}{\chi^2} \, P_{\delta}\, \bigg(\frac{\ell+1/2}{\chi},z(\chi)\bigg) \ {\rm d}\chi,
\label{eq:C_ell}
\end{eqnarray}
where $\ell$ is a multipole, $\chi_{\rm H}$ is the co-moving distance to the horizon, $c$ is the speed of light, $H_0$ the Hubble parameter, and the lensing kernels $q^{i}$ and $q^j$ are given by:
\begin{eqnarray}
q^{i(j)}(\chi) = \frac{3}{2}\Omega_{\rm m} \, \bigg(\frac{H_0}{c} \bigg)^2 \frac{\chi}{a(\chi)} \int_{\chi}^{\chi_{\rm H}} n^i(\chi')\frac{{\rm d}z}{{\rm d} \chi'}\frac{\chi' - \chi}{\chi'}{\rm d}\chi' \, .
\label{eq:q_lensing}
\end{eqnarray}
In the previous expression, $n^i(z)$ refers to the redshift distribution  in tomographic bins `$i (j)$', while $a(\chi)$ is the scale factor at co-moving distance $\chi$ from the observer.
For more details, consult \citealt{Lamman_IA_guide}.
The matter power spectrum is computed from  {\sc Halofit} \citep{Takahashi2012} in this work, however other public tools provide accurate predictions, including \eg  {\sc HMcode} \citep{HMCode2020}, the {\sc EuclidEmulator} \citep{EuclidEmulator}, the {\sc Bacco} emulator \citep{BACCOEmulator}, or the {\sc MiraTitan} emulator \citep{miraTitan}. 
Predictions for the \gtwopcf are finally computed from Eq. (\ref{eq:C_ell}) as:
\begin{eqnarray}
\xi_{\pm}^{ij}(\theta) = \frac{1}{2\pi} \int_0^{\infty} C_{\ell}^{ij} \, J_{0/4}(\ell \theta) \, \ell \, {\rm d}\ell,
\label{eq:xipm_th}
\end{eqnarray}
where $J_{0/4}(x)$ are Bessel functions of the first kind. 
In this paper, these calculations are carried out by the {\sc CosmoSIS} cosmological inference package \citep{cosmoSIS}.
The redshift distribution $n (z)$ is the source galaxy sample redshift distribution of LSST Year1 \citep{LSST-SRD}:
\begin{eqnarray}
n (z) =  z^2 \: {\rm exp} \left[-\left(\frac{z}{z_0}\right)^\alpha \right]\, ,
\label{eq:nz}
\end{eqnarray}
with pivot redshift $z_0=0.13$ and a power-law index $\alpha = 0.78$.
The distribution is normalised to provide a number density of $n_{\rm eff} = 3.0 $  galaxies per arcmin$^{2}$.
This lower than the expected number density for the first data release ($n_{\rm eff}\sim10$ galaxies arcmin$^{-2}$), but is large enough to validate our methods, and makes the calculation more tractable.
This global $n(z)$ is further split into five equi-populated tomographic bins, and smoothed with a Gaussian filter of width $\sigma = 0.05 \: (1 + z)$ to mimic the photometric selection process, shown by the solid lines in Fig. \ref{fig:Nz}.

The weak lensing signal is measured from the ellipticities $\epsilon_{1/2}$ of simulated or observed galaxies, which, in absence of systematics and secondary signals, are unbiased estimators  of the cosmic shear components $\gamma_{1/2}$.
In particular, the \gtwopcf are estimated as:
\begin{eqnarray}
\widehat{\xi_{\pm}^{ij}}(\theta) = \frac{\sum_{a,b} w_a w_b \left[\epsilon_{a, \rm +}^i\epsilon_{b, \rm +}^j     \pm \epsilon_{a, \times}^i\epsilon_{b, \times}^j    \right]\Delta_{ab}(\theta)}{\sum_{a,b} w_a w_b} \, ,
\label{eq:2PCF_estimator}
\end{eqnarray}
where the sum is over all pairs of galaxies $a, b$ separated by an angular distance $\theta$ on the sky, respectively belonging to the tomographic bins $i$ and $j$.
$w_{a (b)}$ represent the projected correlation functions, while the tangential/cross components of ellipticities are denoted as $\epsilon_{+/\times}$, respectively. 
$\Delta_{ab}(\theta)$ is the binning operator, equal to unity if the angular separation between the two galaxies falls within the $\theta$-bin, and zero otherwise, while the shape weights $w_{a,b}$ are set to unity.
In this work, we construct lensing catalogues from numerical simulations (described in Sec. \ref{sec:sims}), from which we measure $ \widehat{\xi_{\pm}^{ij}}(\theta)$ with {\sc Treecorr} \citep{TreeCorr}.
We set therein the {\sc bin\_slop} parameter to 0.05, then compute the correlations in 20 logarithmically-spaced angular bins with outer edges ranging from $0.5$ to $475.5$ arcmin.

 %-------------------------
\subsection{Non-Gaussian lensing statistics}
\label{subsec:beyond-2pt}

Non-Gaussian statistics have the potential to extract cosmological information stored in the complex phases of the density field, outperforming in that sense the \gtwopcf that can only access information encoded in the complex amplitudes.
No optimal estimator has been identified to-date as being able to capture `all' information, but numerous studies all show a clear gain in constraining power, especially when used in combination with two-point functions \citep{HD21, DESY3_Zuercher, HSC_PeaksSims}.
While some of these act on galaxy catalogues directly, many non-Gaussian statistics are measured on convergence or aperture mass maps, requiring the post-process the galaxy catalogues with a mass-reconstruction algorithm.
To accommodate a variety of cases, we therefore provide both galaxy catalogues and convergence maps, the latter being  produced from the galaxies' observed ellipticities with the standard Kaiser \& Squires inversion technique \citep{KaiserSquires}.
These are spherical {\sc Healpix}\footnote{{\sc Healpix}: http://healpix.sf.net}  maps \citep{healpix} with $N_{\rm side}=4096$ generated over an octant, and includes a baseline $2.0$ arcmin smoothing beam to suppress numerical noise.

It's worth noting that this smoothing scale is relatively small, posing challenges for theoretical modeling of some probes within this regime.
Consequently, modeling often requires direct inference from simulations \citep[see][]{HD21, DESY3_Zuercher, HSCY1_Peaks_sims}.
%Note that this smoothing scale is quite small; some probes are difficult to model theoretically in that regime, in which case the modelling needs to be inferred from simulations directly \citep[as in][]{HD21, DESY3_Zuercher, HSCY1_Peaks_sims}.
In the interest of brevity, this paper does not cover statistics derived from aperture mass maps, though our methods are equally applicable to those estimators.
%We do not discuss statistics based on aperture mass maps in this paper for the sake of conciseness, but all our methods can be applied to those estimators as well.
While tomographic \gtwopcf data include auto-correlation and cross-redshift correlations, certain non-Gaussian statistics extract further information from analyzing triplets, quadruplets, or quintuplets of redshift bins \citep{Martinet21a}.
This work focuses only on auto-tomographic bins, yet our methods and results can be straightforwardly extended to accommodate such analyses.

%Whereas tomographic \gtwopcf data consists of auto-correlation and cross-redshift correlations, some non-Gaussian statistics can learn additional information from analysing catalogues or maps constructed from triplets, quadruplets or quintuplet of redshift bins \citep{Martinet21a}. 
%We do not fully exploit this possibility here and consider auto-tomographic bin only, nevertheless all of our methods and findings can be easily generalised to include this.

\subsection{Catalogue-based statistics}

A number of higher-order statistics work at the level of shear catalogue,  and here we consider the following:
\begin{enumerate}
\item {\it Three-point correlation functions (or $M_{\rm ap}^3(\theta)$)}:  \JHD{ Lucas/Laila, can you summarise the measurements and modelling, and provide references?}
\item {\it Squeezed bispectrum}: \JHD{ Anik, can you summarise the measurements and modelling, and provide references?}
\end{enumerate}

\subsection{Convergence-based statistics}

We further consider the following convergence map-based statistics:
\begin{enumerate}
    \item \textit{Convergence three-point correlation function}: \JHD{Alejandro, can you summarise the measurements and modelling, and provide references?}
    \item \textit{Peaks and Minima}: local maxima and minima in the {\sc Healpix} convergence maps are counted in bins of signal-to-noise ratios, $\nu$, computed from the global level of shape noise in the survey. 
    These are amongst the most widely used non-Gaussian lensing statistics, as it is simple to measure yet highly sensitive to non-Gaussian structures.
    Although some theoretical models have been developed to describe the largest peaks \citep[see][]{Shan18, HSCY1_Peaks_th}, we report here the results on a much wider range of statistics, which can only be accurately modelled from numerical simulations.
    \item \textit{Lensing PDF}:  \JHD{Cora/Lina, can you summarise the measurements and modelling, and provide references?}
    \item  \textit{Minkowski functionals}: \JHD{Nisha, can you summarise the measurements and modelling, and provide references?}
\end{enumerate}

These statistics explore various physical scales and nonlinear phenomena, leading to differences in their sensitivity to cosmology and systematic errors.
For instance, a statistical method effective in recovering cosmological information could be significantly influenced by secondary effects like intrinsic alignments (IA), casting doubts on its robustness.
Thus, incorporating IA simulations at the field level is essential for addressing these concerns.

 %Each of these statistics probe different physical scales and nonlinearities, causing their sensitivities to cosmological and systematics to vary. 
% For example, a probe that is performing well at recovering cosmological information might be heavily affected by secondary signals such as IA and therefore deemed not robust.
%Having infused IA mocks at the field-level is therefore critical to answer such questions.

### 2024-03-27 sections/3_ia_models.tex

@@
 
-Finally, we note that fully modelling our infusion method includes contributions beyond one-loop calculations in the $II$ term.
-Indeed, the two-point function correlating ellipticities (Eq.
-\ref{eq:tidal_th_deltaNLA}) between redshift bins $i,j$ is given by:
- \begin{eqnarray}
-\langle \epsilon_{i}^{\delta-\rm NLA} \epsilon_{j}^{\delta-\rm NLA}\rangle &=& \langle \epsilon_{i}^{\rm NLA}\times(1 + b_{\rm TA}\delta_i) \epsilon_{j}^{\rm NLA}\times(1 + b_{\rm TA}\delta_j)\rangle\\
-&=& \langle \epsilon_{i}^{\rm NLA}  \epsilon_{j}^{\rm NLA}\rangle \nonumber \\
-&+& b_{\rm TA} \times \left(\langle \epsilon_{i}^{\rm NLA}  \epsilon_{j}^{\rm NLA}\delta_j  \rangle + \langle \epsilon_{i}^{\rm NLA}  \epsilon_{j}^{\rm NLA}\delta_i  \rangle \right)\nonumber\\
-&+& b_{\rm TA}^2 \langle \epsilon_{i}^{\rm NLA}  \epsilon_{j}^{\rm NLA}\delta_i  \delta_j \rangle \, ,
-\label{eq:2pcf_deltaNLA}
-\end{eqnarray}
-where the last term is fourth order and involves two-loop calculations.
-For this reason, our $\delta$-NLA model is not expected to be well described by the one-loop calculations.
-Note that replacing one of the ellipticity terms by the cosmic term includes only terms up to third order in the field (e.g $\langle \epsilon_{i}^{NLA}\delta_i \gamma_j \rangle$, ...), hence  we expect the GI term to be well described.
-The above equation also predict that the deviations from one-loop theory scales as $b_{\rm TA}^2$, hence should be larger for population that are more biased.
 %Compared to the NLA, the \dNLA is a stronger IA model, especially on small scales \citep{Blazek2019}, and seems to be preferred by some hydro-dynamical simulations \citep{Hilbert_IA2017}.

### 2024-03-27 sections/4_simulations.tex

\section{Simulations}
\label{sec:sims}

%-------------
\subsection{Cosmic shear galaxy catalogues} 
\label{subsec:WL_cats}

The weak lensing simulations developed for this work are based on ray-tracing mass sheets produced from the {\it Outer Rim} $N$-body simulation \citep{OuterRim}, which evolved 10,240$^3$ particles in a $(5.225 \mathrm{Gpc})^3$ cosmological volume, assuming a flat \lcdm cosmology with $\Omega_{\rm m}=0.2648$, $\Omega_{\rm b}=0.0448$, $h=0.71$, $\sigma_8 = 0.801$, $n_{\rm s}= 0.963$, $w_0=-1.00$.
A total of $101$ particle snapshots were originally saved, of which we use only those with $z<4.0$. Particles from each dump are assigned to curved mass shells approximately 114 Mpc thick, producing a sequence of 57 {\sc Healpix} maps $\delta(\theta, \phi, \chi_i)$ with {\sc nside} = 8192 and $i=1.57$, filling up a light-cone over an octant up to $z = 3$.
%More details on this procedure can be found  in \citet{cosmoDC}, where lensing quantities are computed specifically for the generation of the {\sc cosmoDC2}  synthetic sky catalogue.

Ray-tracing is performed in the Born approximation, summing over the mass shells using the $\chi$-integral of Eq. (\ref{eq:C_ell}).
A source plane is placed at the high-redshift edge of every mass planes, resulting in a series of convergence  maps $\kappa(\theta,\phi,\chi_i)$ that are subsequently transformed into shear maps $\gamma_{1/2}(\theta,\phi,\chi_i)$ using the Kaiser-Squires methods \citep{KaiserSquires}, which is implemented via efficient {\sc HealPy alm2map} routines.
We finally position galaxies in the light cone following three distinct algorithm, each impacting the strength of the IA signal:
\begin{enumerate}
\item {\it Random:} galaxies are distributed randomly on the octant, thereby reproducing one of the  fundamental assumptions in the NLA and TT models. 
\item {\it Linear bias:} galaxy positions are sampled from the mass sheets smoothed\footnote{We also tried sampling the field with $0.1$ and $0.5$ $h^{-1}\mathrm{Mpc}$ but this resulted in noisier results.} with a 1.0 $h^{-1}\mathrm{Mpc}$ (comoving) beam, assuming a linear bias of $b_{\rm TA}$, thereby building the one of the key assumptions of the \dNLA and \dTT models. 
We assume $b_{\rm TA}=1.0$ as our fiducial case but also consider $b_{\rm TA}=2.0$ to test  the  model flexibility. 
\item{\it Non-linear bias:} galaxy positions are obtained by populating dark matter haloes with the Halo Occupation Distribution prescription described in \citet{cosmoDC2}. 
\end{enumerate}
Note that while cases (i) and (ii) exactly the SRD-Y1 $N(z)$ presented in Fig. \ref{fig:Nz} (solid lines), the $N(z)$ in the latter case is not a perfect match (dashed lines); we return to this in Sec. \ref{subsec:HOD}, where we describe the HOD model and related quantities.

%----------
\subsection{Projected tidal fields}
\label{subsec:IA_sims}

\begin{figure*}
\caption{Density field and the associated projected tidal field tensors.}
\label{fig:maps}
\end{figure*}

Our infusion method completely relies on couplings between intrinsic galaxy shapes and the local tidal field, hence the first step in our method consist in extracting the tidal field maps $s_{ij}(\theta,\phi,\chi_i)$ from the mass maps $\delta(\theta,\phi,\chi_i)$ that source them.
In three dimensions, trace-free tidal tensor $s_{ij}(\boldsymbol x)$ can be obtained from the matter over-density field $\delta(\boldsymbol x)$ as   \citep{Catelan_IA_Tidal}:
\begin{eqnarray}
 \widetilde{s}_{ij} (\boldsymbol k)  = \left[\frac{k_i k_j}{k^2} - \frac{\delta_{ij}}{3}\right]  \widetilde {\delta}(\boldsymbol k) \mathcal{G}(\sigma_{\rm G}) \, ,
 \label{eq:sij}
\end{eqnarray}
where $\mathcal{G}(\sigma_{\rm G})$ is a three-dimensional Gaussian function described by a single (free) parameter $\sigma_{\rm G}$ that  controls the physical scales which are allowed to affect the IA term in our model. 
Tilde symbols denote Fourier transformed quantities, the indices $(i,j)$ label the components of the Cartesian wave-vector $\boldsymbol{k}^T = (k_x,k_y,k_z)$, and $k^2 = k_x^2 + k_y^2 + k_z^2$. 
As shown in \citet{Tidalator} for Cartesian coordinates, projected tidal fields  computed from projected mass sheets provide and excellent agreement with the NLA model, which in contrast computes the full tidal fields from the three-dimensional matter density and project along the radial dimension at the end.
We promote this transformation to curved-sky in this work, exploiting the  polarisation {\sc alm2map} operations built in {\sc Healpy}. 
In particular, noting that $Q=s_{xx}-s_{yy}$, $U=s_{xy}$, and $\delta=s_{xx}+s_{yy}$, we compute the curved-sky tidal field tensors ${s}_{ij}({\boldsymbol \theta})$ as:
\begin{equation}\label{eq:sij_2D_sph}
\begin{split}
    s_{xx}({\boldsymbol \theta})  &=  \left[\frac{ \delta + Q}{2}  - \frac{\delta}{3}\right] \\ s_{yy}({\boldsymbol \theta})  &=  \left[\frac{\delta - Q}{2}  - \frac{\delta}{3}\right] \\ s_{xy}({\boldsymbol \theta}) &= U
\end{split}
\end{equation}
where the $U({\boldsymbol \theta})$ and $Q({\boldsymbol \theta})$ maps are smoothed by the Gaussian beam with width $\sigma_{\rm G}$.
We suppress large artificial tidal fields at the maps boundary by replicating 8$\times$ the density maps defined on the octant and working on a full sky density $\delta$; we re-apply the octant mask on the tidal field maps after the operation.
Note that the value of $\sigma_{\rm G}$ is a free parameter both in the infusion technique described in this paper and in the NLA and TATT models.
We therefore explore two cases, $\sigma_{\rm G}=0.1\mathrm{Mpc}$ and $0.5\mathrm{Mpc}$, however this may be further optimised in the future.
Finally, the full-sky density field is downgraded from $N_{\rm side}=8192$ to $N_{\rm side}=4096$ since the smoothing washed the smallest angular scales.

%are specified within the NLA model. Smoothing amounts to selecting physical scales that do not contribute to the alignment of galaxies, which is still a debatable quantity, but is also introduced for numerical stability. \citet{Blazek2015} argues that 1.0 $h^{-1}$Mpc could be a reasonable fiducial value, being larger then the typical halo size, but recognizes that one-halo terms are also required to better match the observations. In their later work, \citet{Blazek2019} do not include smoothing at all, and neither do the KiDS-1000 nor DES-Y1 analyses based on the NLA model \citep{KiDS1000_Asgari,DESY1_Troxel}. In this work we used a two-dimensional Gaussian filter and calibrated $\sigma_{\rm G}$ empirically to $\sigma_{\rm G}=0.1h^{-1}$Mpc (see Sec. \ref{subsubsec:sigma_G}), however these two choices are arbitrary and could possibly be better optimised in the future; we also explore $\sigma_{\rm G}=0.5h^{-1}$Mpc later on.  We note that the smoothing scale is degenerate with the resolution of the simulation itself, and that one should use caution when smoothing on scales that approach the resolution limits.

%We employ a numerical technique worth mentioning here: the Fourier transforms involved in computing Eq. (\ref{eq:sij_2D}) are computed from the full (projected) periodic boxes of the simulations, then interpolated on the light-cones. We find that tidal field computed directly from the $10\times10$ deg$^2$ light-cones introduces significant large scales features in the tidal field maps, largely caused by  the non-periodic boundary conditions, which our method avoids.
Projected tidal field maps $s_{11}$, $s_{22}$, and $s_{12}$ are constructed that way for each mass sheets; Fig. \ref{fig:maps} shows the  three tidal fields and the mass maps for one of them.
We can clearly see the connection between all maps around over-dense regions. {\it (Include a figure of $s_ij$ and $\delta$)}.

{\it [Mention normalisation of the tidal fields by $0.6252 = H_0/114$ = 1/shell-thickness}

%of every light-cones and interpolated at the position of every galaxy. Fig. \ref{fig:tidalator} illustrates this process for a small zoomed-in patch at $z\sim0$, starting from a $\delta_{2D}(\boldsymbol \theta)$ map (upper large panel), computing the tidal field components (middle four panels) and comparing the results with the cosmic shear signal generated by the same mass distribution (bottom two panels). The tidal field maps clearly reproduce the cosmic shear maps, and the minus sign in front of both terms in Eq. (\ref{eq:tidal_th}) causes the IA to undo some of the lensing signal.

\subsection{Infusion of intrinsic alignments}
\label{subsec:IA_infusion}

Having now produced shear catalogues and tidal field maps, we can now use Eq. \ref{eq:tidal_th} to couple linearly the alignment of galaxies with the local tidal field, or Eq. \ref{eq:tidal_th_TT} to use instead a quadratic coupling. These allow us to compute the intrinsic ellipticities ${\boldsymbol \epsilon}^{\rm int}$ for the four IA models described in Sec. \ref{sec:IA_th}, which we combine with the cosmic shear signal ${\boldsymbol g}$ to compute observed ellipticities: 
\begin{equation}
{\boldsymbol \epsilon}^{\rm obs} = \frac{{\boldsymbol \epsilon}^{\rm int} + {\boldsymbol g}}{1 + {\boldsymbol \epsilon}^{\rm int}{\boldsymbol g^*}} 
\label{eq:eps_obs}
\end{equation}
with
\begin{equation}
{\boldsymbol \epsilon}^{\rm int}  = \frac{{\boldsymbol \epsilon}^{\rm IA} + {\boldsymbol \epsilon}^{\rm ran}}{1 + {\boldsymbol \epsilon}^{\rm IA}{\boldsymbol \epsilon^{\rm ran, *}}}.
\label{eq:eps_int}
\end{equation}
In the above expressions, the denominators ensure that the combined  ellipticities never exceed unity.
The complex spin-2 reduced shear
\begin{equation}
{\boldsymbol g} \equiv \frac{\gamma_1 + {\rm i} \gamma_2}{1 + \kappa}
\end{equation}
is computed from the shear  $(\gamma_{1/2}$) and convergence ($\kappa$) maps, interpolated at the galaxy positions and redshifts. 
The random orientation term ${\boldsymbol \epsilon}^{\rm ran}$ is drawn from two Gaussians (one per component) with their standard deviations matching the LSST-Y1 forecast, $\sigma_{\epsilon} = 027$. We further constraint  the random ellipticity to satisfy $|{\boldsymbol \epsilon}^{\rm ran}| \le 1.0$. 
%We recall that since our simulated galaxy catalogues trace the dark matter density, our default IA-infusion method  is consistent with the $\delta$-NLA model (see Sec. \ref{subsec:IA_th_ext}). Analytical predictions for the two-point functions are more involved in this case \citep[see][]{Blazek2019} and not yet available on the public {\sc cosmoSIS} release. We therefore validate our methods with the standard NLA first, which we infuse by `correcting' the $\delta$-NLA measurement with Eq. (\ref{eq:tidal_th_deltaNLA}), i.e. by replacing ${\boldsymbol \epsilon}^{\rm IA}$ by ${\boldsymbol \epsilon}^{\rm IA}/(1 + b_{\rm TA} \delta)$ in our simulations. Once again, these are less realistic but better suited for validation of the measured $\gamma$-2PCFs against a theoretical model; after this is established, we use the $\delta-$NLA catalogues as our fiducial infusion model. 
We re-iterate here that the same tidal fields, shear maps, and IA coupling equations are used for the NLA and \dNLA models, and separately for the TT and \dTT models; these only differ by the fact that in one case the galaxies are placed at random on the octant, while in the other case they are linearly tracing the dark matter.
Also note that our current IA models make no differentiation between galaxy colours or type, and instead treats the full sample as a single population that has a single, effective, alignment signal \citep[see][for an example with a red/blue split]{DESY1_IA_Samuroff}.

Finally, once all galaxies have been placed in the light-cone, we interpolate the shear and IA quantities at their exact location.

### 2024-03-27 tables/ia_models.tex

% Requires the booktabs if the memoir class is not being used
\begin{table}
   \centering
   %\topcaption{Table captions are better up top} % requires the topcapt package
    \caption{IA models infused in this work and the respective fiducial values of the model parameters.}
   \begin{tabular}{@{} lcr @{}} % Column formatting, @{} suppresses leading/trailing space
      \hline
      \hline
       %\multicolumn{2}{c}{Item} \\
      model   		& ($A_{\rm IA}, \: b_{\rm TA}, \: A_2)$ \\
      \hline
      NLA     		& {($\pm$1, 0, 0) }&  \\
      \multirow{2}{*}{extended-NLA }  	&   {($\pm$1, 1, 0)}   \\
      							&  {(1, 2, 0)}   \\
      TT 			&  {(0, 0, $\pm$1)} &  \\
      \multirow{2}{*}{extended-TT} 	&  {(0, 1 ,$\pm$1)}   \\
      				&  {(0, 2, 1)}   \\
      TATT- fiducial	&  { (1, 1, 1)}  \\
      %TATT-DESY3	&   (-0.7,1,1.9) & \\
      \hline
      \hline

   \end{tabular}
   \label{table:IAmodels}
\end{table}

### 2024-04-30 sections/1_introduction.tex
Modifications up to end of Sec. 4

@@
 \eg][]{KiDS1000_Asgari, KiDS1000_vdB, KiDS1000_Li, DESY3_Secco, DESY3_Amon, HSCY3_Cl, HSCY3_2pcf}, achieving  percent-level measurements of the structure growth parameter $S_8\equiv\sigma_8\sqrt{\Omega_{\rm m}/0.3}$.
-The parameters $\Omega_{\rm m}$ and $\sigma_8$, which respectively describe the abundance and the fluctuations of the matter density fluctuations on scales of $8h^{-1}$ Mpc, are highly degenerate in the lensing signal, and additional data (\eg galaxy clustering data) are required to measure the two individually \citep{Heymans, DES3x2pt, HSC3x2} \niko{fix the refs}.
-Despite these highly successful achievements, the current precision of cosmic shear cosmology is mainly limited by the large uncertainty in the intrinsic alignment (IA) of galaxies, a secondary signal that tends to cancel some of the shape correlations produced by lensing \citep[see.
-\eg][for reviews on IA]{Troxel_IA_review_2015, Kirk_IA_review_2015, Joachimi_IA_review_2015, Kiessling_IA_review_2015}.
-If unaccounted for, the IA can bias by XYZ$\sigma$ the inferred cosmological parameters \citep{BlazekKrause}.
-Additionally, using an inaccurate IA model can substantially impair the inference process, as demonstrated by \citet{DESY3_Secco} in their study on DES-Y3 analysis and by \citep{Paopiamsap2024} in the context of an LSST-like cosmic shear analysis.
+The parameters $\Omega_{\rm m}$ and $\sigma_8$, which respectively describe the abundance and the amplitude of the fluctuations in the matter density fluctuations on scales of $8h^{-1}$ Mpc, are highly degenerate in the lensing signal, and additional data (\eg galaxy clustering data) are required to measure the two individually from photometric galaxy surveys \citep{KiDS1000_Heymans, DESY3_3x2, HSCY3_3x2}.
+Despite these successful achievements, the current precision of cosmic shear cosmology is mainly limited by the large uncertainty in the intrinsic alignment (IA) of galaxies, a secondary signal that tends to cancel some of the shape correlations produced by lensing \citep[see.
+\eg][for reviews on IA]{Troxel_IA_review_2015, Kirk_IA_review_2015, Joachimi_IA_review_2015, Kiessling_IA_review_2015,Lamman_IA_guide}.
+If unaccounted for, the IA can bias by 4-5$\sigma$ the inferred cosmological parameters \citep{Kirk2012, Krause2016}.
+Additionally, using an inaccurate IA model can substantially impair the inference process, as demonstrated by \citet{DESY3_Secco} in their study on DES-Y3 analysis and by \citet{Paopiamsap2024} in the context of an LSST-like cosmic shear analysis.
 %Furthermore, an incorrect IA model can also cause significant damage to the inference, as shown in \citet{DESY3_Secco} in the context of DES-Y3 analysis, or in \citep{Paopiamsap2024} in the context of an LSST-like cosmic shear analysis.
 
-Different physical models have been developed to describe the origin and impact of the IA, including the linear non-linear alignment model \citep[NLA hereafter, ][]{BridleKing2007}, the density-weighted NLA (aka $\delta$-NLA or extended-NLA), and the tidal torque model \citep[][TT hereafter]{BlazekTATT2017}, which respectively assume a linear and quadratic coupling between galaxy ellipticities and the local tidal field.
-The halo model can also describe the IA signal as a function of halo properties such as their mass, concentration, and shapes \citep{FortunaIA}.
-A number of observations have sought to place constraints on the parameters from these models \citep[\eg][]{Singh, Sammuroff, Christos, Fortuna, Johnston}.
-These observations seem to converge towards a strong colour-dependence: red bright galaxies (elliptical) are generally strongly aligned, with hints of a radial dependence, while blue galaxies (spiral) are consistent with the no-alignment scenario.
+Different physical models have been developed to describe the origin and impact of the IA, including the linear non-linear alignment model \citep[NLA hereafter, ][]{NLA}, the density-weighted NLA (aka $\delta$-NLA or extended-NLA), and the tidal torque model \citep[][TT hereafter]{TATT}, which respectively assume a linear and quadratic coupling between galaxy ellipticities and the local tidal field.
+Alternatively, the halo model can also describe the IA signal as a function of halo properties such as their mass, concentration, and shapes \citep{Fortuna2020}.
+A number of observations have sought to place constraints on the parameters from these models \citep[\eg][]{BlueIA, Singh_IA_LOWZ, DESY1_IA_Samuroff, Johnston_IA} {(\it any more recent?)}.
+These observations seem to converge towards a strong colour-dependence: red bright galaxies (often elliptical) are generally strongly aligned, with hints of a radial dependence, while blue galaxies (typically spiral) are consistent with the no-alignment scenario.
 %A number of observations have sought to place constraints on the parameters from these models \citep[\eg][]{Singh, Sammuroff, Sammuroff, Christos, Fortuna, Johnston}, which seem to converge towards a strong colour-dependence (red bright galaxies are generally strongly aligned, with hints of a radial dependence), while blue galaxies are consistent with the no-alignment scenario.
@@
 
-While most of these methods have been developed to provide prescriptions for modelling IA in lensing  two-point statistics, some have been used to infuse galaxy alignments directly into cosmological simulations, as in \citet{Fluri2019, Tidalator2D, MICE_IA, Borg, Lanzieri}.
-Access to IA-infused numerical simulations is crucial for several applications:
-\begin{itemize}
-    \item \textit{Validating theoretical models deep in the non-linear regime or utilizing the non-linear galaxy bias model \citep{IA_gal_bias}}.
-    \item \textit{Predicting the impact of IA on non-Gaussian lensing probes, for which no models exist \citep{ZuercherXYZ, Tidalator2D}}.
-    \item \textit{Testing IA mitigation techniques \citep{IA_selfCalibration}}.
-    \item \textit{Exploring the connection between large dark matter haloes and IA \citep{vanAlfen}}.
-\end{itemize}
-%Having access to such IA-infused numerical simulations is crucial for a number of applications, including the possibility to validate theoretical models deep in the non-linear regime (or using the non-linear galaxy bias model) \citep{IA_gal_bias}, to predict the impact of IA on non-Gaussian lensing probes for which no model exist \citep{ZuercherXYZ, Tidalator2D}, to test IA mitigation techniques \citep{IA_selfCalibration}, or to learn about  the connection between large dark matter haloes and IA \citep{vanAlfen}.
-{\JHD{ (Any other important references?)}}
+While most theoretical methods have been developed to provide prescriptions for modelling IA in two-point statistics, some have been applied to infuse galaxy alignments directly into cosmological simulations, as in \citet{Fluri2019, Tidalator2D, MICE_IA, Lanzieri2023, vanAlfen2023}.
+Access to such IA-infused numerical simulations is crucial for several applications, including 
+validating theoretical models deep in the non-linear regime or utilising non-linear galaxy bias model \citep{IA_gal_bias}, 
+ predicting the impact of IA on non-Gaussian lensing probes ({\it i.e.} beyond-2pt statistics), for which no models exist \citep{Zuercher2020a, Tidalator2D},
+testing IA mitigation techniques such as self-calibration \citep[][Bera et al in prep.]{SelfCalibrationYao1, SelfCalibrationYao2, SelCalibrationPedersen} or exploring the connection between large dark matter haloes and IA \citep{vanAlfen2023}.
+{\JHD{ (Any other important references?)}} These are all important if we are to correctly interpret the cosmological data from photometric redshift surveys.
 
-This paper addresses several of the above-mentioned applications \niko{shall we mention which ones?}.
-After reviewing the modelling and measurement of cosmic shear data in Sec.
-\ref{sec:theory}, we describe our new flexible method to infuse different IA models in cosmological simulations (Sec.
-\ref{sec:IA_th}).
-Specifically, we infuse the NLA model, the \dNLA, and the TT model on the same underlying lensing simulation. 
-In addition, we introduce the \dTT model (which takes into account the fact that galaxies trace dark matter even in the TT model), then proceed to couple the cosmic tidal fields with galaxies taken from halo occupation distributions (HOD) to investigate the impact of realistic non-linear galaxy bias on the IA signal.
+This paper addresses several of the above-mentioned applications, as we present a novel  pipeline with which we infuse the NLAl, the \dNLA, and the TT model on the same underlying large lensing simulation.
+In addition, we introduce the \dTT model (which takes into account the fact that galaxies trace dark matter even in the TT model), then proceed to couple the cosmic tidal fields with galaxies taken from halo occupation distributions (HOD), thereby probing the impact of realistic non-linear galaxy bias on the IA signal.
 These new models are both physically motivated and challenging to describe theoretically as they require perturbation expansions beyond the second order.
-The full numerical implementation is described in Sec. \ref{sec:sims} and validated against theoretical predictions at the level of  two-point shear correlation functions in Sec. \ref{sec:validation}.
+Existing  beyond-2pt analyses of weak lensing data only model the NLA model \citep{DESY3_Zuercher, HD21}, which is bound to be insufficient with the precision increase provided with the new generation of cosmic shear surveys such as those from the Vera Rubin Observatory \citep{LSST-Design} or {\it Euclid} \citep{RedBook}.
+
+After reviewing the theory and measurement of cosmic shear data in Sec. \ref{sec:theory}, we describe our IA models in Sec. \ref{sec:IA_th}.  
+Their full numerical implementation is described in Sec.
+\ref{sec:sims} and validated against theoretical predictions at the level of  two-point shear correlation functions in Sec.
+\ref{sec:validation}.
 Since our infusion method acts on shear galaxy catalogues and on convergence maps, we are in an ideal position to quantify the impact of multiple IA models on different non-Gaussian statistics, which we report in Sec.

### 2024-04-30 sections/2_cosmic_shear_stats.tex
Modifications up to end of Sec. 4

@@
 %Cosmic shear data can be analysed by a number of summary statistics, which all have their pros and cons.
-We first review the modelling and measurement methods of shear two-point functions, then present other complementary cosmic shear statistics in the second part of this section.
+We start with shear two-point functions, then present other complementary cosmic shear statistics in the second part of this section.
 
@@
 Shear two-point correlation functions (\gtwopcf hereafter) can be predicted with percent-level precision and are therefore an ideal quantity to validate weak lensing simulations.
-In the Limber approximation\footnote{See \citet{Kilbinger17} for a comparison between the Limber approximation and the exact calculations.}, the lensing angular power spectrum $C^{ij}_{\ell}$ (in spherical harmonics space) in tomographic bins $i$ and $j$ is obtained from an integral over the three-dimensional matter power spectrum $P_{\delta}(k, z)$ (in Fourier space, and redshift $z$ dependant):
+In the Limber approximation\footnote{See \citet{Kilbinger17} for a comparison between the Limber approximation and the exact calculations.}, the tomographic lensing power spectrum $C^{ij}_{\ell}$, obtained for combinations of redshift bins $i$ and $j$, is calculated from an integral over the three-dimensional matter power spectrum $P_{\delta}(k, z)$ as:
   \begin{eqnarray}
@@
 \end{eqnarray}
-where $\ell$ is a multipole, $\chi_{\rm H}$ is the co-moving distance to the horizon, $c$ is the speed of light, $H_0$ the Hubble parameter, and the lensing kernels $q^{i}$ and $q^j$ are given by:
+where $\ell$ are angular multipoles, $k$ are amplitudes of Fourier modes, $\chi_{\rm H}$ is the comoving distance to the horizon, $c$ is the speed of light, $H_0$ the Hubble parameter, and the lensing kernels $q^{i}$ and $q^j$ are given by:
 \begin{eqnarray}
-q^{i(j)}(\chi) = \frac{3}{2}\Omega_{\rm m} \, \bigg(\frac{H_0}{c} \bigg)^2 \frac{\chi}{a(\chi)} \int_{\chi}^{\chi_{\rm H}} n^i(\chi')\frac{{\rm d}z}{{\rm d} \chi'}\frac{\chi' - \chi}{\chi'}{\rm d}\chi' \, .
+q^{i}(\chi) = \frac{3}{2}\Omega_{\rm m} \, \bigg(\frac{H_0}{c} \bigg)^2 \frac{\chi}{a(\chi)} \int_{\chi}^{\chi_{\rm H}} n^i(\chi')\frac{{\rm d}z}{{\rm d} \chi'}\frac{\chi' - \chi}{\chi'}{\rm d}\chi' \, .
 \label{eq:q_lensing}
 \end{eqnarray}
-In the previous expression, $n^i(z)$ refers to the redshift distribution  in tomographic bins `$i (j)$', while $a(\chi)$ is the scale factor at co-moving distance $\chi$ from the observer.
-For more details, consult \citealt{Lamman_IA_guide}.
+In the previous expression, $n^i(z)$ refers to the redshift distribution  in tomographic bins `$i$', while $a(\chi)$ is the scale factor at comoving distance $\chi$ from the observer.
 The matter power spectrum is computed from  {\sc Halofit} \citep{Takahashi2012} in this work, however other public tools provide accurate predictions, including \eg  {\sc HMcode} \citep{HMCode2020}, the {\sc EuclidEmulator} \citep{EuclidEmulator}, the {\sc Bacco} emulator \citep{BACCOEmulator}, or the {\sc MiraTitan} emulator \citep{miraTitan}.
@@
 \begin{eqnarray}
-\xi_{\pm}^{ij}(\theta) = \frac{1}{2\pi} \int_0^{\infty} C_{\ell}^{ij} \, J_{0/4}(\ell \theta) \, \ell \, {\rm d}\ell,
+\xi_{\pm}^{ij}(\vartheta) = \frac{1}{2\pi} \int_0^{\infty} C_{\ell}^{ij} \, J_{0/4}(\ell \vartheta) \, \ell \, {\rm d}\ell,
 \label{eq:xipm_th}
@@
 where $J_{0/4}(x)$ are Bessel functions of the first kind. 
-In this paper, these calculations are carried out by the {\sc CosmoSIS} cosmological inference package \citep{cosmoSIS}.
-The redshift distribution $n (z)$ is the source galaxy sample redshift distribution of LSST Year1 \citep{LSST-SRD}:
+In this paper, these calculations are carried out by the public\footnote{{\sc CosmoSIS}:https://cosmosis.readthedocs.io/en/latest/ } {\sc CosmoSIS} cosmological inference package \citep{cosmoSIS}.
+The redshift distribution $n (z)$ is taken from the LSST Year-1 forecast \citep{LSST-SRD}:
 \begin{eqnarray}
@@
 \begin{eqnarray}
-\widehat{\xi_{\pm}^{ij}}(\theta) = \frac{\sum_{a,b} w_a w_b \left[\epsilon_{a, \rm +}^i\epsilon_{b, \rm +}^j     \pm \epsilon_{a, \times}^i\epsilon_{b, \times}^j    \right]\Delta_{ab}(\theta)}{\sum_{a,b} w_a w_b} \, ,
+\widehat{\xi_{\pm}^{ij}}(\vartheta) = \frac{\sum_{a,b} w_a w_b \left[\epsilon_{a, \rm +}^i\epsilon_{b, \rm +}^j     \pm \epsilon_{a, \times}^i\epsilon_{b, \times}^j    \right]\Delta_{ab}(\vartheta)}{\sum_{a,b} w_a w_b} \, ,
 \label{eq:2PCF_estimator}
 \end{eqnarray}
-where the sum is over all pairs of galaxies $a, b$ separated by an angular distance $\theta$ on the sky, respectively belonging to the tomographic bins $i$ and $j$.
-$w_{a (b)}$ represent the projected correlation functions, while the tangential/cross components of ellipticities are denoted as $\epsilon_{+/\times}$, respectively. 
-$\Delta_{ab}(\theta)$ is the binning operator, equal to unity if the angular separation between the two galaxies falls within the $\theta$-bin, and zero otherwise, while the shape weights $w_{a,b}$ are set to unity.
+where the sum is over all pairs of galaxies $a, b$ separated by an angular distance $\vartheta$ on the sky, respectively belonging to the tomographic bins $i$ and $j$.
+$w_{a (b)}$ represent the weights, describing the precision of the shape measurement, which we ignore in this work, while the tangential/cross components of ellipticities are denoted as $\epsilon_{+/\times}$, respectively.
+$\Delta_{ab}(\vartheta)$ is the binning operator, equal to unity if the angular separation between the two galaxies falls within the $\vartheta$-bin, and zero otherwise.
 In this work, we construct lensing catalogues from numerical simulations (described in Sec.
-\ref{sec:sims}), from which we measure $ \widehat{\xi_{\pm}^{ij}}(\theta)$ with {\sc Treecorr} \citep{TreeCorr}.
+\ref{sec:sims}), from which we measure $ \widehat{\xi_{\pm}^{ij}}(\vartheta)$ with {\sc Treecorr} \citep{TreeCorr}.
 We set therein the {\sc bin\_slop} parameter to 0.05, then compute the correlations in 20 logarithmically-spaced angular bins with outer edges ranging from $0.5$ to $475.5$ arcmin.
@@
 
-Non-Gaussian statistics have the potential to extract cosmological information stored in the complex phases of the density field, outperforming in that sense the \gtwopcf that can only access information encoded in the complex amplitudes.
-No optimal estimator has been identified to-date as being able to capture `all' information, but numerous studies all show a clear gain in constraining power, especially when used in combination with two-point functions \citep{HD21, DESY3_Zuercher, HSC_PeaksSims}.
-While some of these act on galaxy catalogues directly, many non-Gaussian statistics are measured on convergence or aperture mass maps, requiring the post-process the galaxy catalogues with a mass-reconstruction algorithm.
-To accommodate a variety of cases, we therefore provide both galaxy catalogues and convergence maps, the latter being  produced from the galaxies' observed ellipticities with the standard Kaiser \& Squires inversion technique \citep{KaiserSquires}.
-These are spherical {\sc Healpix}\footnote{{\sc Healpix}: http://healpix.sf.net}  maps \citep{healpix} with $N_{\rm side}=4096$ generated over an octant, and includes a baseline $2.0$ arcmin smoothing beam to suppress numerical noise.
+Non-Gaussian statistics have the potential to extract cosmological information stored in the complex phases of the density field, outperforming in that sense the \gtwopcf that can only access information encoded in the complex amplitudes \citep{2002MNRAS.337..488C}.
+No optimal estimator has been identified to-date as being able to capture `all' information, but numerous studies all show a clear gain in constraining power, especially when used in combination with two-point functions \citep{Fu2014, Gruen2017, HD21, DESY3_Zuercher, HSCY1_peaks_sims, KiDS1000_Burger, KiDS1000_Map3}.
+While some of these act on galaxy catalogues directly, many non-Gaussian statistics are measured on convergence or aperture mass maps, requiring to post-process the galaxy catalogues with a mass-reconstruction algorithm.
+To accommodate a variety of cases, we therefore provide both galaxy catalogues and convergence maps, the latter being  produced from the galaxies' observed ellipticities with the standard Kaiser \& Squires (KS)  inversion technique \citep{KaiserSquires}, which relates the shear and convergence to the Newtonian potential.
+This is achieved by assigning the two ellipticity components of every galaxies on spherical {\sc Healpix}\footnote{{\sc Healpix}: http://healpix.sf.net}  maps \citep{healpix} with $N_{\rm side}=4096$, then converting the shear maps to convergence maps by solving  the KS inversion in spherical harmonic space \citep[][see their equation 10]{Gatti20}:
+\begin{eqnarray}
+\gamma_{\ell m} = - \sqrt{\frac{(\ell+2)(\ell - 1)}{\ell(\ell+1)}}\left( \kappa_{E,\ell m} + {\rm i} \kappa_{B,\ell m} \right)
+\label{eq:KS}
+\end{eqnarray}
+In the above, $\kappa_{E}$ and $\kappa_{B}$ are the $E/B$ decomposition of the convergence maps, the latter being generally only second order and hence set to zero in this work. 
+The inversion process is carried out with the polarised  {\sc map2alm} functions  in-built in {\sc Healpy}, and we further includes smoothing to suppress numerical noise, accomplished by convolving the $\kappa_E$ map with  a Gaussian beam with width $\sigma$=2.0 arcmin.
 
-It's worth noting that this smoothing scale is relatively small, posing challenges for theoretical modeling of some probes within this regime.
-Consequently, modeling often requires direct inference from simulations \citep[see][]{HD21, DESY3_Zuercher, HSCY1_Peaks_sims}.
+It is worth noting that this smoothing scale is relatively small, posing challenges for  the theoretical modelling of some probes within this regime.
+For this reason, many analyses opt for modelling directly from simulations \citep[see][]{HD21, DESY3_Zuercher, HSCY1_peaks_sims}, bypassing some of the theoretical challenges.
 %Note that this smoothing scale is quite small; some probes are difficult to model theoretically in that regime, in which case the modelling needs to be inferred from simulations directly \citep[as in][]{HD21, DESY3_Zuercher, HSCY1_Peaks_sims}.
@@
 %We do not discuss statistics based on aperture mass maps in this paper for the sake of conciseness, but all our methods can be applied to those estimators as well.
-While tomographic \gtwopcf data include auto-correlation and cross-redshift correlations, certain non-Gaussian statistics extract further information from analyzing triplets, quadruplets, or quintuplets of redshift bins \citep{Martinet21a}.
-This work focuses only on auto-tomographic bins, yet our methods and results can be straightforwardly extended to accommodate such analyses.
+Finally, while tomographic \gtwopcf data include auto-correlation and cross-redshift correlations, certain non-Gaussian statistics extract further information from analysing triplets, quadruplets, or quintuplets of redshift bins \citep{Martinet20}.
+This work focuses only on auto-tomographic bins, yet our methods and results can be straightforwardly extended to include these higher-order redshift combinations.
 
@@
 \begin{enumerate}
-\item {\it Three-point correlation functions (or $M_{\rm ap}^3(\theta)$)}:  \JHD{ Lucas/Laila, can you summarise the measurements and modelling, and provide references?}
+\item {\it Three-point correlation functions (or $M_{\rm ap}^3(\vartheta)$)}:  \JHD{Lucas/Laila, can you summarise the measurements and modelling, and provide references?}
 \item {\it Squeezed bispectrum}: \JHD{ Anik, can you summarise the measurements and modelling, and provide references?}
@@
 
-We further consider the following convergence map-based statistics:
+In addition to the probes mentioned above, we further consider the following convergence map-based statistics:
 \begin{enumerate}
     \item \textit{Convergence three-point correlation function}: \JHD{Alejandro, can you summarise the measurements and modelling, and provide references?}
-    \item \textit{Peaks and Minima}: local maxima and minima in the {\sc Healpix} convergence maps are counted in bins of signal-to-noise ratios, $\nu$, computed from the global level of shape noise in the survey.
-    These are amongst the most widely used non-Gaussian lensing statistics, as it is simple to measure yet highly sensitive to non-Gaussian structures.
-    Although some theoretical models have been developed to describe the largest peaks \citep[see][]{Shan18, HSCY1_Peaks_th}, we report here the results on a much wider range of statistics, which can only be accurately modelled from numerical simulations.
+    \item \textit{Peaks and Minima}: Local maxima and minima in the {\sc Healpix} convergence maps are counted in bins of signal-to-noise ratios, $\nu$, computed from the global  noise levels in the survey.
+Specifically, pure noise maps $\mathcal{N}$ are constructed from generating pure Gaussian maps with mean set to zero and variance set to $\sigma^2 =  \sigma_\epsilon^2 / (2 \Delta \Omega_{\rm pix} n_{\rm gal})$.
+Here, $\Delta \Omega_{\rm pix}$ is the average pixel area, $n_{\rm gal}$ is the mean galaxy density in our survey (0.6 gal / arcmin$^2$ per tomographic bin)  and $\sigma_\epsilon$ is the intrinsic dispersion in galaxy shapes, per component, which we set to 0.27.
+   Peak count statistics are amongst the most widely used non-Gaussian lensing statistics, as it is simple to measure yet highly sensitive to non-Gaussian structures.
+    Although some theoretical models have been developed to describe the largest peaks \citep[see][]{Shan18, HSCY1_Peaks_th}, we report here the results on a much wider range of statistics, which can only be accurately modelled from numerical simulations themselves.
     \item \textit{Lensing PDF}:  \JHD{Cora/Lina, can you summarise the measurements and modelling, and provide references?}
-    \item  \textit{Minkowski functionals}: \JHD{Nisha, can you summarise the measurements and modelling, and provide references?}
+   % \item  \textit{Minkowski functionals}: \JHD{Nisha, can you summarise the measurements and modelling, and provide references?}
 \end{enumerate}
 
-These statistics explore various physical scales and nonlinear phenomena, leading to differences in their sensitivity to cosmology and systematic errors.
+These non-Gaussian statistics explore various physical scales and non-linear phenomena, leading to differences in their sensitivity to cosmology and systematic errors.
 For instance, a statistical method effective in recovering cosmological information could be significantly influenced by secondary effects like intrinsic alignments (IA), casting doubts on its robustness.
-Thus, incorporating IA simulations at the field level is essential for addressing these concerns.
+Thus, incorporating IA  at the field level, with enough flexibility to account for the current uncertainty in our knowledge of the IA physics,  is essential for addressing these concerns (see Sec.
+\ref{sec:HOWLS}).
 

### 2024-04-30 sections/3_ia_models.tex
Modifications up to end of Sec. 4

--- 2024-03-27 sections/3_ia_models.tex
@@
 
-Galaxies are influenced by the gravitational tidal forces from the vast structures in which they reside, leading to their intrinsic shapes being aligned in a way unrelated to the effects observed through weak lensing.
-This alignment serves as an additional factor (a contamination) that skews the accuracy of shape correlation measurements carried in cosmic shear analyses.
-The underlying physical principles that govern intrinsic alignments (IA) remain unclear, and even the models that attempt to describe these alignments have parameters that are not definitively determined by existing data, as discussed in various review articles \citep[see][for reviews]{Joachimi_IA_review_2015, Kirk_IA_review_2015, Troxel_IA_review_2015, Kiessling_IA_review_2015}.
+Galaxy shapes are influenced by the gravitational forces produced from the vast structures in which they reside, leading to their intrinsic orientations being coupled with the local cosmic tidal field.
+This  intrinsic alignment is distinct from the weak lensing signal and introduces a secondary correlation that contaminates the cosmic shear measurements.
+The underlying physical principles that govern the IA remain unclear, and the current models that attempt to describe these alignments have parameters that are not definitively determined by existing data, as discussed in various review articles \citep[see][]{Joachimi_IA_review_2015, Kirk_IA_review_2015, Troxel_IA_review_2015, Kiessling_IA_review_2015}.
 
@@
 \begin{split}
-\epsilon_{1}^{\rm IA} &= \gamma_{xx}^{\rm IA} - \gamma_{yy}^{\rm IA} \, , 
+\epsilon_{1}^{\rm IA} &= \gamma_{11}^{\rm IA} - \gamma_{22}^{\rm IA} \, , 
 \\
-\epsilon_{2}^{\rm IA} &= 2 \gamma_{xy}^{\rm IA} \, .
+\epsilon_{2}^{\rm IA} &= 2 \gamma_{12}^{\rm IA} \, .
 \label{eq:tidal_th_deltaNLA}
@@
 \end{equation}
-\niko{shouldn't the indices be $i$ and $j$ here in the equation?}
+%\niko{shouldn't the indices be $i$ and $j$ here in the equation?}
 
-\subsection{Nonlinear alignment (NLA) Model}
+\subsection{Non-linear alignment (NLA) Model}
 
@@
 The NLA model of \citet{NLA} is the most widely used intrinsic alignment model in the cosmic shear literature thus far.
-According to the NLA, IA are caused by a linear coupling between galaxy shapes and the nonlinear large-scale tidal field at the galaxy position.
+According to the NLA, IA are caused by a linear coupling between galaxy shapes and the non-linear large-scale tidal field at the galaxy positions, which are assumed to be uncorrelated with the underlying matter field.
 The intrinsic ellipticities $\epsilon_{1,2}^{\rm NLA}$ are related to tidal field $s_{ij}$ by:
@@
 \begin{split}
-\epsilon_1^{\rm NLA} &= - \frac{A_{\rm IA}\bar{C_1}\bar{\rho}(z)}{D(z)} (s_{xx} - s_{yy}) , \\    \epsilon_2^{\rm NLA} &= - \frac{2 A_{\rm IA}\bar{C_1}\bar{\rho}(z)}{D(z)} s_{xy}\;,
+\epsilon_1^{\rm NLA} &= - \frac{A_{\rm IA}\bar{C_1}\bar{\rho}(z)}{D(z)} (s_{11} - s_{22}) , \\    \epsilon_2^{\rm NLA} &= - \frac{2 A_{\rm IA}\bar{C_1}\bar{\rho}(z)}{D(z)} s_{12}\;,
 \label{eq:tidal_th}
@@
 where $s_{ij} = \partial_{ij}\phi$ are the Cartesian components of the tidal tensor of the gravitational potential,  $D(z)$ is the linear growth factor, $\bar{\rho}(z)$ is the mean matter density at redshift $z$, and $\bar{C_1}=5\times 10^{-14} M_{\odot}^{-1} h^{-2} {\rm Mpc}^3$ is a constant calibrated in \citet{Brown2002}.
-The strength of tidal coupling is controlled by the parameter $A_{\rm IA}$, a key variable in the NLA model primarily constrained by current cosmic shear studies.
+The strength of tidal coupling is controlled by $A_{\rm IA}$, an effective parameter at the heart of the NLA model that is well constrained by current cosmic shear studies, although the reported values vary widely \citep{KiDS1000_Asgari, DESY3_Amon}.
+
 While this model can incorporate the dependency  on redshift and luminosity, such adjustments are not applied in our analysis.
-It's important to clarify that the "nonlinear" aspect of the model's name might be somewhat misleading; it actually pertains to the use of the nonlinear matter power spectrum $P(k)$ in its computations.
+It is important to clarify that the ``non-linear" aspect of the model's name can be misleading; it actually pertains to the use of the non-linear matter power spectrum $P(k)$ in its computations. 
 The relationship between the intrinsic shapes of galaxies and the tidal field remains linear.
-Equation (\ref{eq:tidal_th}) is employed to determine the intrinsic ellipticities of galaxies using the tidal field components $s_{xx}$, $s_{yy}$, and $s_{xy}$, which are detailed in Section \ref{subsec:IA_infusion}.
+Equation (\ref{eq:tidal_th}) is employed to determine the intrinsic ellipticities of galaxies using the three tidal field components $s_{ij}$, which computations are detailed in Section \ref{subsec:IA_infusion}.
 %The strength of the tidal coupling is modulated by the amplitude parameter $A_{\rm IA}$, which is the main NLA parameter constrained by current cosmic shear surveys.
 %Note that this model can be augmented by redshift and luminosity dependencies, however we do not use these here. 
-%Also note that the term `nonlinear' in the model name can be  misleading, as it refers to the nonlinear matter power spectrum $P(k)$ that is used in its calculations; the coupling between the intrinsic galaxy shapes and the tidal field is still linear and Eq.( \ref{eq:tidal_th}) is used to assign intrinsic ellipticities to galaxies, given maps of the tidal field components $s_{xx}$, $s_{yy}$ and $s_{xy}$ (presented in  Sec.
+%Also note that the term `non-linear' in the model name can be  misleading, as it refers to the non-linear matter power spectrum $P(k)$ that is used in its calculations; the coupling between the intrinsic galaxy shapes and the tidal field is still linear and Eq.( \ref{eq:tidal_th}) is used to assign intrinsic ellipticities to galaxies, given maps of the tidal field components $s_{xx}$, $s_{yy}$ and $s_{xy}$ (presented in  Sec.
 \ref {subsec:IA_infusion}).
 
-\niko{I think we should introduce II, GG, GI, and IG terms in the cosmic shear stats at the beginning when we define C ells. That way we do not mention them out of the blue here}
-In the context of two-point functions, these intrinsic shapes contribute to an intrinsic-intrinsic ($II$) term and an intrinsic-shear coupling ($GI$) term \citep{Hirata2004}, both secondary signals to the true cosmic shear ($GG$) term, with the $GI$ typically dominating the IA sector in cross-tomographic measurements.
+%\niko{I think we should introduce II, GG, GI, and IG terms in the cosmic shear stats at the beginning when we define C ells. That way we do not mention them out of the blue here}
+
+The observed ellipticities are, to linear order, the sum of the intrinsic shape ($I$) and the cosmic shear $G$.
+Then, in the context of two-point functions, these intrinsic shapes contribute to an intrinsic-intrinsic ($II$) term and an intrinsic-shear coupling ($GI$) term \citep{Hirata2004}, both secondary signals to the true cosmic shear ($GG$) term, with the $GI$ typically dominating the IA sector in cross-tomographic measurements.
 The $II$ and $GI$ terms  can be both computed from the matter power spectrum as: 
@@
 \end{eqnarray}
-which can then be past to the Limber integration (Eqs. \ref{eq:C_ell} and \ref{eq:xipm_th}) to compute  the secondary signals $\xi_{\pm}^{II}(\theta)$ and $\xi_{\pm}^{GI}(\theta)$.
+which can then be passed to the Limber and Bessel integration (Eqs. \ref{eq:C_ell} and \ref{eq:xipm_th}) to compute  the secondary signals $\xi_{\pm}^{II}(\theta)$ and $\xi_{\pm}^{GI}(\theta)$.
 
@@
 
-The NLA model, as discussed in the previous section, is a common tool for analyzing cosmic data but has significant limitations, indicating it might not accurately capture the intricacies of the intrinsic alignment signal.
-Recognizing the potential importance of more complex interactions, extensions to the NLA model that incorporate perturbation theory have been proposed by \citet{Blazek2015} and  \citet{Blazek2019}. 
-These extensions highlight the necessity of considering higher-order couplings.
-A key enhancement involves incorporating a term that accounts for over-density weighting.
-This adjustment stems from the observation that galaxies, which serve as the observational basis for IA, are not randomly distributed but rather follow the underlying matter density distribution. 
-The theoretical framework for including this term employs one-loop perturbation theory, as outlined by \citep{Blazek2019}, under the assumption that galaxies linearly map the over-density, denoted as '$\delta$'.
+The NLA model, as discussed in the previous section, is a common tool for analysing cosmic data but is an effective model with significant limitations, and hence might not accurately capture the intricacies of the physical intrinsic alignment signal.
+Recognising the potential importance of more complex interactions, extensions to the NLA model that incorporate higher-order perturbation theory have been proposed by \citet{Blazek2015} and  \citet{TATT}.
+%These extensions highlight the necessity of considering higher-order couplings.
+A key enhancement is the addition of an  over-density weighting term that accounts for the fact that galaxies, from which we sample the tidal interactions, are not randomly distributed on the sky but rather follow the underlying matter density distribution.
+The theoretical framework for including this term employs one-loop perturbation theory, as outlined by \citep{TATT}, under the assumption that galaxies linearly trace the over-density field `$\delta$'.
 In essence, this approach modifies the NLA model predictions by applying a $\delta$-weight at the locations of galaxies, thereby refining the model's accuracy in representing the physical reality.
-Implementing this adjustment in numerical simulations could theoretically be straightforward by enhancing the calculated NLA ellipticities with the aforementioned over-density weight:
+The extended-NLA model departs from the NLA model at small scales, as noted by \citet{TATT}, where the stronger alignments are more efficient at contaminating the cosmic shear signal. 
+It also appears to align more closely with the outcomes of certain hydro-dynamical simulations, as indicated by \citet{Hilbert_IA2017}.
+
+Implementing this model  in numerical simulations could theoretically be straightforwardly achieved  by enhancing the calculated NLA ellipticities with the aforementioned over-density weight:
 %The NLA model presented in the last section has been widely used in cosmic data analyses, but it has important known limitations and is therefore bound to fail at describing the IA signal with high precision.
@@
 \begin{eqnarray}
-\epsilon_{1/2}^{\delta-\rm NLA} = \epsilon_{1/2}^{\rm NLA}\times(1 + \delta \: b_{\rm TA}) \, .
+\epsilon_{1/2}^{\delta-\rm NLA} = \epsilon_{1/2}^{\rm NLA}\times(1 + \delta \: b_{\rm TA}) \, ,
 \label{eq:tidal_th_deltaNLA}
@@
 %Indeed, from a mock with a given bias $b_{\rm TA, orig}$, we can rescale the IA contribution to a different $b_{\rm TA, new}$ as:
-The term $b_{\rm TA}$ represents the bias relationship between galaxies and the matter field beneath them, a relationship that remains largely undetermined.
-In practical applications, this method tends to produce unreliable results due to the tendency of galaxies to be located in areas with negative or minimal $\delta$ values when placed randomly.
+with the term $b_{\rm TA}$ representing the (largely undetermined) bias relationship between galaxies and the local matter field.
+In practical applications, this method tends to produce unreliable results due to the large number of galaxies located in areas with negative or low $\delta$ values when placed randomly.
 A more effective approach is to create mock catalogs by directly applying linear biasing to determine galaxy positions, which eliminates the need for subsequent weighting.
 
-For adjustments without the necessity to repopulate the entire light-cone distribution, Equation (\ref{eq:tidal_th_deltaNLA}) can be applied to alter the effective value of $b_{\rm TA}$.
+For minor adjustments, Eq.
+(\ref{eq:tidal_th_deltaNLA}) can be applied to alter the effective value of $b_{\rm TA}$.
 This allows for the recalibration of the intrinsic alignment contribution from an original bias value, $b_{\rm TA}^{\rm orig}$, to a new desired bias, $b_{\rm TA}^{\rm new}$, as:
@@
 \end{eqnarray}
+This has imitations in tits accuracy, but we will show later that it can nevertheless be applied to modify existing $\delta$-NLA mock data and yields good approximate solutions.
 
-The extended-NLA model represents an enhanced approach to intrinsic alignment modeling, particularly effective at small scales, as noted by \citealt{Blazek2019}. 
-It appears to align more closely with the outcomes of certain hydro-dynamical simulations, as indicated by \citealt{Hilbert_IA2017}.
-From a theoretical standpoint, this model is more physically grounded because it accounts for the fact that galaxies in the universe are not dispersed randomly, an assumption the traditional NLA model makes.
+%From a theoretical standpoint, this model is more physically grounded, for the reasons mentioned above.
+% because it accounts for the fact that galaxies in the universe are not dispersed randomly, an assumption the traditional NLA model makes.
 
 Finally, we note that fully modelling our infusion method includes contributions beyond one-loop calculations in the $II$ term.
-Indeed, the two-point function correlating ellipticities (Eq.
+Indeed, the two-point function correlating ellipticities (defined in Eq.
 \ref{eq:tidal_th_deltaNLA}) between redshift bins $i,j$ is given by:
@@
 \end{eqnarray}
-where the last term is fourth order and involves two-loop calculations.
+where the last term is fourth order in field powers and involves two-loop calculations {\it (To confirm with Blazek)}.
 For this reason, our $\delta$-NLA model is not expected to be well described by the one-loop calculations.
-Note that replacing one of the ellipticity terms by the cosmic term includes only terms up to third order in the field (e.g $\langle \epsilon_{i}^{NLA}\delta_i \gamma_j \rangle$, ...), hence  we expect the GI term to be well described.
+Note that replacing one of the ellipticity terms by the cosmic shear term includes only terms up to third order in the field (e.g $\langle \epsilon_{i}^{NLA}\delta_i \gamma_j \rangle$, ...), hence  we expect the $GI$ term to be well described.
 The above equation also predict that the deviations from one-loop theory scales as $b_{\rm TA}^2$, hence should be larger for population that are more biased.
@@
 %In this tidal torque model (TT), intrinsic ellipticities are given by:
-\citet{Blazek2019} demonstrates that one-loop perturbative calculations introduce an additional term, accounting for how galaxies develop intrinsic alignments through the interaction between their angular momentum and the tidal field.
+\citet{TATT} demonstrates that one-loop perturbative calculations introduce an additional term, accounting for how galaxies develop intrinsic alignments through the interaction between their angular momentum and the tidal field.
 This interaction can alternatively be described as a quadratic coupling between the tidal field and the shapes of the galaxies. 
@@
 \begin{eqnarray}
-\gamma_{ij}^{\rm IA, TT} = C_2 \left[ \sum_{k=x,y,z} s_{ik} s_{kj} -\frac{1}{3} \delta_{ij} s^2 \right] \, ,
+\gamma_{ij}^{\rm IA, TT} = C_2 \left[ \sum_{k=1,2,3} s_{ik} s_{kj} -\frac{1}{3} \delta_{ij} s^2 \right] \, ,
 \label{eq:tidal_th_TT}
@@
 (\ref{eq:tidal_th_TT}) lead to both quadratic in the tidal field components:
-Assuming that alignments along the line of sight are largely suppressed in cosmic shear measurements due to the broadlensing kernels, we demonstrate in Appendix \ref{app:2d_TT} that the terms within the square brackets of Eq.
-(\ref{eq:tidal_th_TT}) result in quadratic terms of the tidal field components:
+Assuming that alignments along the line of sight ({\it i.e.} components involving $k$=3) are largely suppressed in cosmic shear measurements due to the broad lensing kernels, we demonstrate in Appendix \ref{app:2d_TT} that the terms within the square brackets of Eq.
+(\ref{eq:tidal_th_TT}) reduce to :
 
@@
 \begin{split}
-\epsilon_1^{\rm TT} &= C_2  \left[ s_{xx}^2 - s_{yy}^2\right] \\
- \epsilon_2^{\rm TT} &= 2 C_2 s_{xy}\left[s_{xx}+s_{yy}  \right]\, .
+\epsilon_1^{\rm TT} &= C_2  \left[ s_{11}^2 - s_{22}^2\right] \\
+ \epsilon_2^{\rm TT} &= 2 C_2 s_{12}\left[s_{11}+s_{22}  \right]\, .
 \end{split}
@@
 %As for the \dNLA model, the \dTT ellipticities can  be related to the TT model as:
-Calculating the next level of contribution to the TT model requires engaging in two-loop perturbation theory, a process that remains undone due to its considerable complexity.
+Calculating the next level of contribution to the TT model requires engaging in three-loop perturbation theory, a process that remains undone due to its considerable complexity.
 However, in simulations, applying the $\delta$-weighting term to the TT model is relatively straightforward.
@@
 %As there are currently no theoretical models for \dTT, predictions from this model are, at the moment, completely simulation-based. 
-In this study, we opt to utilize galaxy positions that are subject to linear biasing, mirroring our earlier approach.
-Given the lack of established theoretical frameworks for the \dTT model, any predictions derived from it are currently reliant solely on simulations.
- This approach underscores our reliance on empirical data to guide our understanding of the implications for \dTT, pending the development of a comprehensive theoretical model.
+In this study, we opt to utilise galaxy positions that are subject to linear biasing, mirroring our earlier approach.
+Given the lack of established theoretical frameworks for the \dTT model, it currently exists solely in numerical simulations.
+ %This approach demonstrates  our reliance on empirical data to guide our understanding of the implications for \dTT, pending the development of a comprehensive theoretical model.
 
  %-----------------------------------
-\subsection{$b_{\rm nl}$-TATT}
+\subsection{TATT beyond linear bias}
 \label{subsec:HOD-TATT}
-\niko{there is a compiling error here (due to the subscript) in the title, maybe we can consider renaming this?}
+%\niko{there is a compiling error here (due to the subscript) in the title, maybe we can consider renaming this?}
 
@@
 While these are interesting and useful approximations, the connection between galaxies and dark matter is far more complex, and a more accurate picture consists of galaxies populating dark matter haloes, typically with a relaxed, older galaxy close to the centre, and a number of other satellite galaxies orbiting the former.
-This halo occupation distribution (HOD) formalism has been used to describe many galaxy samples \citep[\eg][]{SDSS-HOD, BOSS-HOD, GAMA-HOD, DESI-HOD} and is therefore routinely used to in-paint galaxies in dark matter-only simulations.
-The last two models from this paper exploit such HOD galaxy samples, extracted from the same underlying distributions, but in this case the galaxy bias is non-linear (labelled $b_{\rm nl}$), with levels on non-linearity that vary with HOD parameters (see Sec.
+This halo occupation distribution (HOD) formalism has been used to describe many galaxy samples \citep[\eg][]{SDSS-HOD, BOSS-HOD, GAMA-HOD, DESI-HOD} and is therefore routinely used to in-paint galaxies in dark matter-only simulations \citep{MICE-HOD, SLICS-HOD,  Abbacus-HOD, Balrog}.
+The remaining two models in this paper exploit such HOD galaxy samples, extracted from the same underlying $N$-body simulations.
+In this case the lensing signal is the same to first order, but the galaxy bias is non-linear (labelled $b_{\rm nl}$), with levels on non-linearity that vary with HOD parameters (see Sec.
 \ref{subsec:HOD}).
 We couple these galaxies with both Eqs.
-\ref{eq:tidal_th} and \ref{eq:tidal_th_TT}, resulting in two final models which we name  $b_{\rm nl}$-NLA and  $b_{\rm nl}$-TT, both being combined into the more general  $b_{\rm nl}$-TATT model.
+(\ref{eq:tidal_th}) and (\ref{eq:tidal_th_TT}), resulting in two final models which we name  $b_{\rm nl}$-NLA and  $b_{\rm nl}$-TT, both being combined into the more general  $b_{\rm nl}$-TATT model.
 

### 2024-04-30 sections/4_simulations.tex
Modifications up to end of Sec. 4

@@
 
-The weak lensing simulations developed for this work are based on ray-tracing mass sheets produced from the {\it Outer Rim} $N$-body simulation \citep{OuterRim}, which evolved 10,240$^3$ particles in a $(5.225 \mathrm{Gpc})^3$ cosmological volume, assuming a flat \lcdm cosmology with $\Omega_{\rm m}=0.2648$, $\Omega_{\rm b}=0.0448$, $h=0.71$, $\sigma_8 = 0.801$, $n_{\rm s}= 0.963$, $w_0=-1.00$.
-A total of $101$ particle snapshots were originally saved, of which we use only those with $z<4.0$.
-Particles from each dump are assigned to curved mass shells approximately 114 Mpc thick, producing a sequence of 57 {\sc Healpix} maps $\delta(\theta, \phi, \chi_i)$ with {\sc nside} = 8192 and $i=1.57$, filling up a light-cone over an octant up to $z = 3$.
+The weak lensing simulations developed for this work are based on  the {\it Outer Rim} $N$-body simulation \citep{OuterRim}, which evolved 10,240$^3$ particles in a $(5.225 \mathrm{Gpc})^3$ cosmological volume, assuming a flat \lcdm cosmology with $\Omega_{\rm m}=0.2648$, $\Omega_{\rm b}=0.0448$, $h=0.71$, $\sigma_8 = 0.801$, $n_{\rm s}= 0.963$, $w_0=-1.00$.
+A total of $101$ particle snapshots were originally saved, of which we use only those with $z<3.0$.
+Particles from each dump are assigned to curved mass shells approximately 114 Mpc thick, producing a sequence of 57 {\sc Healpix} maps $\delta_i(\theta, \phi)$ with {\sc nside} = 8192 and $i=1...57$, filling up a light-cone over an octant up to $z = 3$.
 %More details on this procedure can be found  in \citet{cosmoDC}, where lensing quantities are computed specifically for the generation of the {\sc cosmoDC2}  synthetic sky catalogue.
 
-Ray-tracing is performed in the Born approximation, summing over the mass shells using the $\chi$-integral of Eq. (\ref{eq:C_ell}).
-A source plane is placed at the high-redshift edge of every mass planes, resulting in a series of convergence  maps $\kappa(\theta,\phi,\chi_i)$ that are subsequently transformed into shear maps $\gamma_{1/2}(\theta,\phi,\chi_i)$ using the Kaiser-Squires methods \citep{KaiserSquires}, which is implemented via efficient {\sc HealPy alm2map} routines.
+Ray-tracing is performed in the Born approximation, summing over the mass shells using a $\chi$-integral similar to Eq.
+(\ref{eq:C_ell}), but with only one power of $(q^i/\chi)$ instead of two, and replacing $P_\delta$ with $\delta_i(\theta,\phi)$.
+A source plane is placed at the high-redshift edge of every mass planes, resulting in a series of convergence  maps $\kappa_i(\theta,\phi)$ that are subsequently transformed into shear maps $\gamma_{1/2, i}(\theta,\phi)$ using Eq.
+(\ref{eq:KS}).
 We finally position galaxies in the light cone following three distinct algorithm, each impacting the strength of the IA signal:
@@
 \end{enumerate}
-Note that while cases (i) and (ii) exactly the SRD-Y1 $N(z)$ presented in Fig.
-\ref{fig:Nz} (solid lines), the $N(z)$ in the latter case is not a perfect match (dashed lines); we return to this in Sec.
+Note that while cases (i) and (ii) exactly reproduce the SRD-Y1 $N(z)$ presented in Fig.
+\ref{fig:Nz} (solid lines), the $N(z)$ in the latter case is not a perfect match, as shown with the dashed lines, although the agreement is good enough for our goal; we return to this in Sec.
 \ref{subsec:HOD}, where we describe the HOD model and related quantities.
@@
 
-Our infusion method completely relies on couplings between intrinsic galaxy shapes and the local tidal field, hence the first step in our method consist in extracting the tidal field maps $s_{ij}(\theta,\phi,\chi_i)$ from the mass maps $\delta(\theta,\phi,\chi_i)$ that source them.
+Our infusion method relies on couplings between intrinsic galaxy shapes and the local tidal field, hence the first step in our method consist in extracting the tidal field maps $s_{ij}(\theta,\phi)$ from the mass maps $\delta(\theta,\phi)$ that source them\footnote{Note that we have removed the redshift indexing of the maps here to simplify notation, {\it i.e.} $\delta_i(\theta,\phi) \rightarrow \delta(\theta,\phi)$.}.
 In three dimensions, trace-free tidal tensor $s_{ij}(\boldsymbol x)$ can be obtained from the matter over-density field $\delta(\boldsymbol x)$ as   \citep{Catelan_IA_Tidal}:
@@
 where $\mathcal{G}(\sigma_{\rm G})$ is a three-dimensional Gaussian function described by a single (free) parameter $\sigma_{\rm G}$ that  controls the physical scales which are allowed to affect the IA term in our model.
-Tilde symbols denote Fourier transformed quantities, the indices $(i,j)$ label the components of the Cartesian wave-vector $\boldsymbol{k}^T = (k_x,k_y,k_z)$, and $k^2 = k_x^2 + k_y^2 + k_z^2$. 
-As shown in \citet{Tidalator} for Cartesian coordinates, projected tidal fields  computed from projected mass sheets provide and excellent agreement with the NLA model, which in contrast computes the full tidal fields from the three-dimensional matter density and project along the radial dimension at the end.
-We promote this transformation to curved-sky in this work, exploiting the  polarisation {\sc alm2map} operations built in {\sc Healpy}. 
-In particular, noting that $Q=s_{xx}-s_{yy}$, $U=s_{xy}$, and $\delta=s_{xx}+s_{yy}$, we compute the curved-sky tidal field tensors ${s}_{ij}({\boldsymbol \theta})$ as:
+Tilde symbols denote Fourier-transformed quantities, the indices $(i,j)$ label the components of the Cartesian wave-vector $\boldsymbol{k}^T = (k_1,k_2,k_3)$, and $k^2 = k_1^2 + k_2^2 + k_3^2$. 
+As shown in \citet{Tidalator} in the flat-sky approximation, projected tidal fields  computed from projected mass sheets provide and excellent agreement with the  theoretical NLA model, which in contrast computes the full tidal fields from the three-dimensional matter density and project along the radial dimension at the end.
+We promote here this transformation to curved-sky maps, exploiting the  polarisation {\sc alm2map} operations built in {\sc Healpy}. 
+In particular, noting that $Q=s_{11}-s_{22}$, $U=s_{12}$, and $\delta=s_{11}+s_{22}$, we compute the curved-sky projected  tidal field tensors ${s}_{ij}({\boldsymbol \theta})$ as:
 \begin{equation}\label{eq:sij_2D_sph}
 \begin{split}
-    s_{xx}({\boldsymbol \theta})  &=  \left[\frac{ \delta + Q}{2}  - \frac{\delta}{3}\right] \\ s_{yy}({\boldsymbol \theta})  &=  \left[\frac{\delta - Q}{2}  - \frac{\delta}{3}\right] \\ s_{xy}({\boldsymbol \theta}) &= U
+    s_{11}({\boldsymbol \theta})  &=  \frac{1}{\Delta \chi_{\rm shell}}\left[\frac{ \delta + Q}{2}  - \frac{\delta}{3}\right] \\ s_{22}({\boldsymbol \theta})  &=   \frac{1}{\Delta \chi_{\rm shell}}\left[\frac{\delta - Q}{2}  - \frac{\delta}{3}\right] \\ s_{12}({\boldsymbol \theta}) &=  \frac{U}{\Delta \chi_{\rm shell}}
 \end{split}
 \end{equation}
-where the $U({\boldsymbol \theta})$ and $Q({\boldsymbol \theta})$ maps are smoothed by the Gaussian beam with width $\sigma_{\rm G}$.
-We suppress large artificial tidal fields at the maps boundary by replicating 8$\times$ the density maps defined on the octant and working on a full sky density $\delta$; we re-apply the octant mask on the tidal field maps after the operation.
+where the $U({\boldsymbol \theta})$ and $Q({\boldsymbol \theta})$ maps are smoothed by the Gaussian beam with width $\sigma_{\rm G}$, and the normalisation by  $\Delta \chi_{\rm shell}$ is required to account for the comoving thickness of the shells.
+We suppress large artificial tidal fields at the boundary of our simulated octant by replicating 8$\times$ the  $\delta$ maps and carrying out these harmonic calculations  on full sky densities; we re-apply the octant mask on the tidal field maps after the last operation.
 Note that the value of $\sigma_{\rm G}$ is a free parameter both in the infusion technique described in this paper and in the NLA and TATT models.
 We therefore explore two cases, $\sigma_{\rm G}=0.1\mathrm{Mpc}$ and $0.5\mathrm{Mpc}$, however this may be further optimised in the future.
-Finally, the full-sky density field is downgraded from $N_{\rm side}=8192$ to $N_{\rm side}=4096$ since the smoothing washed the smallest angular scales.
+Finally, the full-sky density field is downgraded from $N_{\rm side}=8192$ to $N_{\rm side}=4096$ since the smoothing washes the smallest angular scales.
 
@@
 Projected tidal field maps $s_{11}$, $s_{22}$, and $s_{12}$ are constructed that way for each mass sheets; Fig. \ref{fig:maps} shows the  three tidal fields and the mass maps for one of them.
-We can clearly see the connection between all maps around over-dense regions. {\it (Include a figure of $s_ij$ and $\delta$)}.
-
-{\it [Mention normalisation of the tidal fields by $0.6252 = H_0/114$ = 1/shell-thickness}
+We can clearly see the connection between all maps around over-dense regions. {\it (Include a figure of $s_{ij}$ and $\delta$)}.
 
@@
 
-Having now produced shear catalogues and tidal field maps, we can now use Eq.
-\ref{eq:tidal_th} to couple linearly the alignment of galaxies with the local tidal field, or Eq.
-\ref{eq:tidal_th_TT} to use instead a quadratic coupling.
-These allow us to compute the intrinsic ellipticities ${\boldsymbol \epsilon}^{\rm int}$ for the four IA models described in Sec.
+Having now produced shear catalogues and tidal field maps, we can use Eq.
+(\ref{eq:tidal_th}) to couple linearly the alignment of galaxies with the local tidal field, or Eq.
+(\ref{eq:tidal_th_TT}) to use instead a quadratic coupling.
+These allow us to compute the intrinsic ellipticities ${\boldsymbol \epsilon}^{\rm int}$ for the six IA models described in Sec.
 \ref{sec:IA_th}, which we combine with the cosmic shear signal ${\boldsymbol g}$ to compute observed ellipticities:
@@
 is computed from the shear  $(\gamma_{1/2}$) and convergence ($\kappa$) maps, interpolated at the galaxy positions and redshifts. 
-The random orientation term ${\boldsymbol \epsilon}^{\rm ran}$ is drawn from two Gaussians (one per component) with their standard deviations matching the LSST-Y1 forecast, $\sigma_{\epsilon} = 027$.
-We further constraint  the random ellipticity to satisfy $|{\boldsymbol \epsilon}^{\rm ran}| \le 1.0$.
+The random orientation term ${\boldsymbol \epsilon}^{\rm ran}$ is drawn from two Gaussians (one per component\footnote{We further constraint  the random ellipticity to satisfy $|{\boldsymbol \epsilon}^{\rm ran}| \le 1.0$.}) with their standard deviations matching the LSST-Y1 forecast, $\sigma_{\epsilon} = 0.27$, although in most calculations we work with noise-free shapes to better resolve the IA signal.
 %We recall that since our simulated galaxy catalogues trace the dark matter density, our default IA-infusion method  is consistent with the $\delta$-NLA model (see Sec.
@@
 Once again, these are less realistic but better suited for validation of the measured $\gamma$-2PCFs against a theoretical model; after this is established, we use the $\delta-$NLA catalogues as our fiducial infusion model.
-We re-iterate here that the same tidal fields, shear maps, and IA coupling equations are used for the NLA and \dNLA models, and separately for the TT and \dTT models; these only differ by the fact that in one case the galaxies are placed at random on the octant, while in the other case they are linearly tracing the dark matter.
-Also note that our current IA models make no differentiation between galaxy colours or type, and instead treats the full sample as a single population that has a single, effective, alignment signal \citep[see][for an example with a red/blue split]{DESY1_IA_Samuroff}.
-
+%We re-iterate here that the same tidal fields, shear maps, and IA coupling equations are used for the NLA and \dNLA models, and separately for the TT and \dTT models; these only differ by the fact that in one case the galaxies are placed at random on the octant, while in the other case they are linearly tracing the dark matter.
 Finally, once all galaxies have been placed in the light-cone, we interpolate the shear and IA quantities at their exact location.
+Note that our current IA models make no differentiation between galaxy colours or type, and instead treats the full sample as a single population that has a single, effective, alignment signal \citep[see][for an example with a red/blue split]{DESY1_IA_Samuroff}.

### 2024-04-30 sections/2_cosmic_shear_stats.tex
Updates from Overleaf

--- 2024-03-27 sections/2_cosmic_shear_stats.tex
@@
 The distribution is normalised to provide a number density of $n_{\rm eff} = 3.0 $  galaxies per arcmin$^{2}$.
-This lower than the expected number density for the first data release ($n_{\rm eff}\sim10$ galaxies arcmin$^{-2}$), but is large enough to validate our methods, and makes the calculation more tractable.
+This is a bit lower than the expected number density for the first data release ($n_{\rm eff}\sim10$ galaxies arcmin$^{-2}$), but is large enough to validate our methods, and makes the calculation more tractable.
 This global $n(z)$ is further split into five equi-populated tomographic bins, and smoothed with a Gaussian filter of width $\sigma = 0.05 \: (1 + z)$ to mimic the photometric selection process, shown by the solid lines in Fig.

### 2024-06-21 sections/1_introduction.tex
Lots of changes

@@
 
-This paper addresses several of the above-mentioned applications, as we present a novel  pipeline with which we infuse the NLAl, the \dNLA, and the TT model on the same underlying large lensing simulation.
+This paper addresses several of the above-mentioned applications, as we present a novel  pipeline with which we infuse the NLA, the \dNLA, and the TT model on the same underlying large lensing simulation.
 In addition, we introduce the \dTT model (which takes into account the fact that galaxies trace dark matter even in the TT model), then proceed to couple the cosmic tidal fields with galaxies taken from halo occupation distributions (HOD), thereby probing the impact of realistic non-linear galaxy bias on the IA signal.

### 2024-06-21 sections/3_ia_models.tex
Lots of changes

@@
  %-----------------------------------
-\subsection{TATT beyond linear bias}
+\subsection{HOD-TATT}
 \label{subsec:HOD-TATT}
@@
 While these are interesting and useful approximations, the connection between galaxies and dark matter is far more complex, and a more accurate picture consists of galaxies populating dark matter haloes, typically with a relaxed, older galaxy close to the centre, and a number of other satellite galaxies orbiting the former.
-This halo occupation distribution (HOD) formalism has been used to describe many galaxy samples \citep[\eg][]{SDSS-HOD, BOSS-HOD, GAMA-HOD, DESI-HOD} and is therefore routinely used to in-paint galaxies in dark matter-only simulations \citep{MICE-HOD, SLICS-HOD,  Abbacus-HOD, Balrog}.
+This HOD formalism has been used to describe many galaxy samples \citep[\eg][]{SDSS-HOD, BOSS-HOD, GAMA-HOD, DESI-HOD} and is therefore routinely used to in-paint galaxies in dark matter-only simulations \citep{MICE-HOD, SLICS-HOD,  Abbacus-HOD, Balrog}.
 The remaining two models in this paper exploit such HOD galaxy samples, extracted from the same underlying $N$-body simulations.
@@
 We couple these galaxies with both Eqs.
-(\ref{eq:tidal_th}) and (\ref{eq:tidal_th_TT}), resulting in two final models which we name  $b_{\rm nl}$-NLA and  $b_{\rm nl}$-TT, both being combined into the more general  $b_{\rm nl}$-TATT model.
+(\ref{eq:tidal_th}) and (\ref{eq:tidal_th_TT}), resulting in two final models which we name  HOD-NLA and  HOD-TT, both being combined into the more general  HOD-TATT model.
 

### 2024-06-21 sections/5_validation.tex
Lots of changes

@@
 \label{sec:validation}
+
+This section presents a comparison between theoretical predictions and measurements in the simulations for all our 6 models.
+We include here the statistical error obtained from covariance matrix computed analytically as described in \citet{KiDS1000_Joachimi}, which includes contributions from the Gaussian, non-Gaussian and super-sample covariance terms, assuming survey properties that match our simulation in terms of area, shape noise, galaxy density, tomographic $n(z)$ and cosmology.
+The diagonal elements are used to assign the error bars in our figures, and the full matrix is used in the MCMC analyses presented in Sec.
+\ref{sec:inference}.
+
+\input{figures/shear_corr_funcs/xi_nla}
+
+\subsection{Data vector}
+%------------------------------
+\subsubsection*{NLA model}
+
+We start by presenting a comparison between the relative impact of IA in the NLA model as measured in the simulations and as modelled by {\sc cosmoSIS}.
+Specifically, we show in Fig.
+\ref{fig:xi_NLA} the ratio between the $\gamma$-2PCF with and without IA, for all combinations of tomographic bins as indicated in the panels, and for two smoothing scales.
+The agreement is remarkable over all scales except for the smallest angular separations in $\xi_-$, where deviations are weaker in the simulations due to limits in the resolution.
+The grey bands  indicates scales that are not well modelled and should be avoided, set to 5 arcmin.
+The smaller smoothing scales shows better agreement with the model at the smallest angular scales.
+
+%------------------------------
+\subsubsection*{Extended-NLA model}
+\input{figures/shear_corr_funcs/xi_delta_nla}
+
+\input{figures/shear_corr_funcs/xi_delta_nla_II.tex}
+
+\input{figures/shear_corr_funcs/xi_delta_nla_rescaled}
+
+The equivalent comparison for the extended-NLA model is presented in Fig.
+\ref{fig:xi_deltaNLA}, where we also find an excellent match with the theoretical predictions except for redshift bins 1-1 and 2-2, where the $II$ term is important and much larger in the simulations than in the theory.
+This is expected since the former includes additional terms that are up to second order in perturbation theory.
+This is shown in Fig.
+\ref{fig:xi_deltaNLA_II}, where the different contributions are separated, clearly showing the disagreement in  the $II$ term.
+
+The results are shown here for $b_{\rm TA}$ = 1.0  and we verified that it works equally well for $b_{\rm TA}$ =  2.0.
+Using the former, we test the $b_{\rm TA}$-rescaling method introduced in Eq.
+\ref{eq:bta_rescale} to generate $b_{\rm TA}=2.0$ and $b_{\rm TA}=0.0$ mocks, and compare the outcome with mocks constructed directly with these bias values.
+Results are shown in Fig.
+\ref{fig:xi_deltaNLA_rescaled} for one of the tomographic bins for which IA has the strongest effect.
+The match is excellent here, however lower redshift are less accurate due to the increased shot noise (not shown){\it (should I show an example?)}, hence we recommend producing new mocks over using this rescaling method whenever possible.
+
+Note that since source clustering is a higher order effect in cosmic shear, the measured $\xi_{\pm}$ from mocks with $b_{\rm TA}$=0.0, 1.0 and 2.0 show negligible differences in $\xi_+$, and becomes detectable only at the smallest scales  (i.e.
+$\vartheta<5$arcmin) in $\xi_-$, consistent with  \citet{source_lens_clustering} who find an effect of a few percent for $\ell>3000$, and with \citet{DESY3_Gatti_source_clust}, who find minor impact for second moments of aperture mass maps.
+However the impact on higher order lensing statistics and on the overall  IA contamination is significant and can double the secondary signal in certain circumstances, due to the up-sampling of regions with strong tidal forces.
 
@@
 %------------------------------
-\subsection{NLA model}
-\label{subsubsec:sigma_G}
-
-See Fig. \ref{fig:xi_NLA}
-
-\input{figures/shear_corr_funcs/xi_nla}
 
 %------------------------------
-\subsection{Extended-NLA model}
-\label{subsec:deltaNLA}
-
-See Fig. \ref{fig:xi_deltaNLA}.
-
-\input{figures/shear_corr_funcs/xi_delta_nla}
-
-\input{figures/shear_corr_funcs/xi_delta_nla_rescaled}
-
-We verified that it works equally well for $b_{\rm TA}$ = 1.0 and 2.0.
-
-%------------------------------
-
-Using this, we $b_{\rm TA}$-rescale our $b_{\rm TA}=1.0$ mock to $b_{\rm TA}=2.0$ and to $0.0$ mocks. Results are shown in Fig. \ref{fig:xi_deltaNLA_rescaled} for one of the tomographic bin. 
-It works reasonably well, but lower redshift are less accurate due to the increased  shot noise (not shown), hence we do not recommend using this.
-
-%------------------------------
-\subsection{TT model}
+\subsubsection*{TT model}
 \label{subsec:TT}
 
-See Fig. \ref{fig:xi_TT}
+Results for the tidal torque model are presented in Fig.
+\ref{fig:xi_TT}, again for two smoothing scales.
+In this case, we see that the larger smoothing scales agrees better with the theoretical predictions, likely due a mis-matched caused by projection effects.
+Indeed, the TT model, being quadratic in the tidal field, is more sensitive to smaller scales \citep{TATT}, and the missing third dimension inherent to our method is more prone to cause inaccuracies.
+We observe discrepancies in the small angular separations for  $\xi_-$ at low redshifts, but achieve better match for $\vartheta>$  40 arcmin.
+
+Importantly, we found that our implementation of the TT model yields alignments that are too strong at low redshifts, and hence requires an empirical redshift-dependent calibration to improve the match with theory.
+We achieve this by rescaling $\epsilon^{\rm IA, TT}(z<0.5) \rightarrow \epsilon^{\rm IA, TT} /2.5$, acknowledging that this exhibits limits in our capacity to model the tidal torquing without accessing the third dimensional of the tidal field.
 
@@
 
-To match the theory, we need to apply the following calibration: $\epsilon^{\rm IA, TT}(z<0.5) \rightarrow \epsilon^{\rm IA, TT} /2.5$.
+%------------------------------
+\subsubsection*{Extended-TT model}
+\label{subsec:TT}
+
+The extended-TT model, constructed by using the TT coupling on galaxies linearly tracing the underlying matter density, also needs to be calibrated.
+This has some degree of arbitrariness due to the absence of theoretical model to match it against.
+We choose to match the TT theory on large angular separation at all redshifts, physically motivated from the fact that this modified galaxy bias should not impact strongly scales that are much larger than galaxy clusters.
+This therefore required us to lower the original ellipticities, especially at low $z$: $\epsilon^{{\rm IA}, \delta{\rm TT}}(z<0.5) \rightarrow \epsilon^{{\rm IA}, \delta{\rm TT}} /2.5$ as for the normal TT model, further followed by a global $\epsilon^{{\rm IA}, \delta{\rm TT}} \rightarrow \epsilon^{{\rm IA}, \delta{\rm TT}}/20.0$ rescaling.
+This is a large calibration condition, which compensate for the overly strong coupling computed from our simulations.
+The results are shown in Fig.
+\ref{fig:xi_deltaTT}, where we observed that the deviations with respect to the TT model occur at small angular scales ($\vartheta < $ 20 arcmin) in $\xi_+$, and for the lowest redshifts.
+Although this model is harder to match with current theoretical IA model, it provides a good example with which we can study the impact of IA mis-modelling, e.g.
+analysing this model with the TATT predictions, similar to the investigations of \citet{Paopiamsap2024}.
 
 %------------------------------
-\subsection{Extended-TT model}
-\label{subsec:TT}
-
-See Fig. \ref{fig:xi_deltaTT}
-
-To match the TT theory, we need to apply the following calibration: $\epsilon^{\rm IA, TT}(z<0.5) \rightarrow \epsilon^{\rm IA, TT} /5.0$, followed by $\epsilon^{\rm IA, TT} \rightarrow \epsilon^{\rm IA, TT}/7.0$.
-
-%------------------------------
-\subsection{HOD-NLA model}
+\subsubsection*{HOD-TATT model}
 \label{subsec:HOD}
@@
 
-The NLA and extended-NLA models respectively assume a null and a linear bias between the source galaxies and the underlying matter field, both of which are approximations to the galaxy dark matter connection.
-In fact, galaxies populate dark matter over-densities in a more complex manner \citep{GalaxyPopulationPapers}, which is better described by the Halo Occupation Distribution approach (HOD hereafter).
-The largest difference here is that these HOD galaxies are non-linear biased tracers of the matter distribution, which means that a larger number can populate regions of large over-densities, where the tidal fields are generally stronger.
+%The NLA and extended-NLA models respectively assume a null and a linear bias between the source galaxies and the underlying matter field, both of which are approximations to the galaxy-dark matter connection.
+%In fact, galaxies populate dark matter over-densities in a more complex manner \citep{GalaxyPopulationPapers}, which is better described by the Halo Occupation Distribution approach (HOD hereafter).
+The largest difference between the previous models and those based on HOD galaxies is that the latter are non-linear biased tracers of the matter distribution, which means that a larger number can populate regions of large over-densities, where the tidal fields are generally stronger.
 We therefore expect the impact of IA to be stronger in this case.
-
-We investigate this effect with HOD galaxies extracted from the SkySim5000 simulation \citep{SkySim5000_HOD} \footnote{We used version: {\tt skysim5000\_v1.2}, as detailed in XYZ..}, which are obtained by [...] (mention the TXPipe paper).
-Specifically, we select objects over a patch of 732.20 deg$^2$ given by  0$<$RA$<$ 20 and -36.61$<$DEC$<$0, we apply a magnitude cut of mag$_r<$24.8, and further downsample randomly to retain 20\% of the galaxies,
-therefore matching the global galaxy redshift distribution and number density found in the rest of this paper (Eq. \ref{eq:nz}).
-The sample is further split into five tomographic bins by using Charlie's magical code (Charlie), resulting in the $n(z)$ presented in Fig. \ref{fig:NzHOD}. 
-Compared to the analytical SRD-Y1 presented in Fig. \ref{fig:Nz}, the mean redshifts of the five tomographic bins are shifted by [-0.027, -0.018,  0.003, -0.010,  0.038], respectively.
-
-[{\it To put somewhere?: Since source clustering is a higher order effect in cosmic shear, the measured $\xi_{\pm}$ from these three mocks (random, $b_{\rm TA}=1.0$ and $b_{\rm TA}=2.0$) show negligible differences ({\it to quantify and cite}).
-In contrast, the impact on the IA contamination is significant and can double the secondary signal in certain circumstances. 
-The main explanation for this is that while clustered sources are uncorrelated with the foreground matter responsible for the lensing signal, the high-density regions they live are also subject to the largest tidal fields.
-}]
+We show in Figs.
+\ref{fig:xi_hod_nla} and \ref{fig:xi_hod_tt} show the results from the HOD-NLA  and HOD-TT models, which together make up our HOD-TATT.
+One of the most interesting features is that the HOD-NLA closely follows the normal NLA predictions over a large range of scales, suggesting that the impact of the non-linear galaxy bias is sub-dominant down to a few acrmin.
+We also observe a small-angle up-turn in bins 1-1 and 2-2, which can be attributed to mismodelling the $II$ term (as it is the case for the extended-NLA, see the discussion above) {\it (Also what's goiing on with bin 5?
+There seems to be no IA signal there...)}.
 
@@
  \label{sec:inference}
-\begin{figure}
-%\includegraphics[width=\columnwidth]{graphs/triangle_nla_5D.pdf}
-\includegraphics[width=\columnwidth]{graphs/triangle_bta_sweep.pdf}
-\caption{Cosmological inference from the NLA-infused simulations, analysed the extended-NLA model. 
-The cross-hairs represent the truth as fixed in the {\it Outer Rim} $N$-body simulations \citep{OuterRim}.}
-\label{fig:triangle_nla}
-\end{figure}
-priors, {\sc CosmoSIS}, Takahashi $P(k)$, etc.
+
+ \input{tables/priors.tex}
 
 \input{figures/corner_plots/corner_NLA_all}
+\input{figures/corner_plots/corner_TT}
+\input{figures/corner_plots/corner_eNLA}
+\input{figures/corner_plots/corner_deltaTT}
+\input{figures/corner_plots/corner_HOD_NLA}
+ \input{figures/corner_plots/corner_NLA_w0}
 
-\begin{figure}
-%\includegraphics[width=\columnwidth]{graphs/triangle_nla_5D.pdf}
-\includegraphics[width=\columnwidth]{graphs/TT_allsweep.pdf}
-\caption{Cosmological inference from the TT-infused simulations, with all 3 IA params varied.
-The cross-hairs represent the truth as fixed in the {\it Outer Rim} $N$-body simulations \citep{OuterRim}.}
-\label{fig:triangle_tt_all_ia_params}
-\end{figure}
+ The last section presented comparisons between measured and modelled signal, reaching generally an excellent agreement but highlighting some small differences.
+In order to quantify the importance of such differences in a cosmic shear analysis, our evaluation metric must be measurements of biases between the true and the inferred cosmological parameter.
+We achieve this by running nested likelihood sampling chains with {\sc multinest} \citep{Multinest}, which returns the posterior distributions $\mathcal{P}$ on the cosmological parameters $\boldsymbol \pi$ given a data vector $\boldsymbol  d$, a model vector $\boldsymbol m$, a covariance matrix C, and likelihood function $\mathcal L$ and a set of priors on the inferred parameters.
+More precisely, we use a multivariate Gaussian likelihood, and ignore the standard cosmic shear systematic effects caused by photometric redshift errors, shape calibrations or baryon feedback \citep[see][for a recent example]{DESY3-KiDS1000}.
+We vary a subset of the vanilla $\Lambda$CDM cosmological parameters to establish the general accuracy; increasing the number of varied parameters can lead to a number of projection effects that complicate the interpretation.
+We therefore focus on varying the parameters best measured by lensing, namely $S_8$, $\Omega_{\rm m}$ and the IA parameters ($A_{\rm IA}, b_{\rm TA}, C_2$).
+We adopt wide flat priors for all of these, as detailed in Table \ref{table:priors}.
 
-\input{figures/corner_plots/corner_TT}
+With the precision of the Rubin data, small fluctuations in the data vectors can lead to significant shifts in the inferred cosmology, which is statistically  expected but makes the IA validation exercise more difficult to interpret.
+We therefore run our likelihood analyses on  the lowest three redshift bins, deliberately excluding the highest two as they contribute mostly to cosmological information, while we want here to learn more about the recovery of the IA sector.
+For the same reason we ignore shape noise here, which would only create additional scatter in the posteriors.
+We additionally exclude angular bins where the models probes highly non-linear scales, and select $\vartheta \in [2 ; 200]$ arcmin for $\xi_+$, and $\vartheta \in [20 ; 400]$ arcmin for $\xi_-$.
+These scales are highly affected by other systematic effects such as baryonic feedback \citep[see, e.g.][]{Semboloni11, HWVH15, 2020arXiv200715026H} and hence are often removed from the data vectors \citep[as in][]{DESY3_Amon}.
+
+ The projected posteriors  are presented in Figs.
+\ref{fig:corner_nla_combo}-\ref{fig:corner_deltatt}, analysing simulated data from the six models introduced in Sec.
+\ref{sec:IA_th} model.
+In absence of IA contamination the inference from the simulated data is expected to yield posteriors on the cosmological parameters that are consistent with the input truth but not necessarily centred on it due to sample variance.
+We further dissect the analyses by varying either  one or  all three TATT parameters, highlighting some of the interesting degeneracies.
+When analysing the NLA-infused data (Fig.
+\ref{fig:corner_nla_combo}), all cosmological and IA  parameters are accurately recovered, both for the NLA and TATT modelling.
+In the later case, the inferred values for $b_{\rm TA}$ and $C_2$ are consistent with zero, but we observe a strong degeneracy between  $A_{\rm IA}$ and  $C_2$ as also found in e.g.
+\citet[][\it  cite other papers?]{Paopiamsap2024}.
+The inferred  $\Omega_{\rm m}$ is slightly shifted to higher values, however this is not surprising given that cosmic shear alone is generally not able to constrain this parameter.
+$S_8$, however,  is well recovered, slightly on the high side.
+As expected, opening up the full TATT parameter space slightly degrades the constrains on cosmology, but no large shifts are observed.
+The $w$CDM chains also show an excellent convergence, as shown with the pink contours.
+{\it [update colour, merge figures 11 and 16]}.
+
+ We next analyse the TT data with the TATT model in Fig.
+\ref{fig:triangle_tt_combo}, and  observe an accurate recovery of  $\Omega_{\rm m}$ and $S_8$, however the IA sector is strongly affected by the [$A_{\rm IA}; C_2$] degeneracy, which  pulls the posterior towards the NLA model, with values of $C_2$ consistent with 0 and preferring $A_{\rm IA}\sim 0.5$.
+When fixing $A_{\rm IA}$ and $b_{\rm TA}$ to the input truth however, the inferred $C_2$ just undershoots the input, pointing to residual differences between our implementation of the TT model and that calculated by TATT.
+Nevertheless, the fact that the cosmology is well recovered is promising, since ommiting completely the IA modelling would yield to catastrophic biases in $\Omega_{\rm m}$ and $S_8$.
+
+ As explained above, the extended NLA model infused in our simulations is not entirely well captured by the {\sc CosmoSIS} implementation, especially the $II$ term for the lowest redshift bins.
+This causes problems when inferring parameters with  {\sc CosmoSIS}, since the predictions attempt to compensate the difference in the IA model, leading to biases in the other parameters.
+Fig.
+\ref{fig:triangle_deltaNLA_combo} shows exactly this, failing to infer correctly most parameters.
+In this particular case,  $\Omega_{\rm m}$ and $S_8$ are only off by $2\sigma$, $A_{\rm IA}$ and $C_2$ are biased by 4-5$\sigma$, however $b_{\rm TA}$ is within 1$\sigma$.
+The $\delta$-TT model is even more affected by mis-modelling, with a 3$\sigma$ shift in both $\Omega_{\rm m}$ and $S_8$, as seen in Fig.
+\ref{fig:corner_deltatt}.
+
+The infusion with the HOD-NLA model shows much larger deviations, largely driven by the sharp upward turn observed in auto-correlation at low redshifts, which also caused biases on the extended NLA.
+This causes biases of 2-3$\sigma$ in the cosmological parameters, notably lower $S_8$.
+In other works, if the  real world IA model was the extended-NLA or HOD-NLA and that we'd analyse it with the {\it cosmoSIS} implementation of  NLA or TATT, this would significantly contribute toward the existing $S_8$ tension \citep{S8tension}, in the same direction currently observed (i.e.
+late-time probes observe a lower $S_8$ value compared to CMB probes).
+We are careful here not to claim that this is the single cause of the current tension, but clear mis-model in the IA sector could contribute significantly.
+We do not include inference of the HOD-TT here since the level of mismatch is even worst.
+
+ To summarise this section, aside from the NLA and TT, the infused IA models include terms that are different from the theory and hence lead to significant biases both in the cosmology and IA parameters.
+% We also show in Fig.
+\ref{fig:corner_nla_w0} the impact of promoting our $\Lambda$CDM inference to a $w$CDM inference, varying the dark energy  equation-of-state parameter $w$ in the range $[-2; -0.3]$.
+ These tests complete our validation of the IA-infusion pipeline, and we now look in the next section at the impact of IA on the weak lensing higher-order statistics mentioned in Sec.
+\ref{subsec:beyond-2pt}.

### 2024-06-21 sections/6_higher_order_wl_stats.tex
Lots of changes

@@
 
-... use the mocks from Table \ref{table:IAmodels} to compute derivatives. Show.
+\begin{figure*}
+\includegraphics[width=2.7in]{graphs/Map3_IA}
+\includegraphics[width=2.7in]{graphs/PDF_IA}
+\caption{Impact of IA on the $M_{\rm ap}^3$ (left) and lensing PDF (right) statistics (see Sec.
+\ref{subsec:beyond-2pt}), for different combinations of smoothing scales $\vartheta$ and IA models.
+The three panels are, from top to bottom, showing the results from tomographic bins 1 to 3, respectively.
+({\it This is huge and wrong!
+Must redo with new maps.})}
+\label{fig:Map3_IA}
+\end{figure*}
+
+\begin{figure*}
+\includegraphics[width=1.65in]{graphs/Peaks_IA}
+\includegraphics[width=3.3in]{graphs/i3PCF}
+\caption{Impact of different IA models on the peak statistic (left) and on the integrated three-point shear statistics $\zeta_+$ (centre) and $\zeta_-$ (right).}
+\label{fig:I3PCF}
+\end{figure*}
+
+This Section presents the impact of different IA model presented in Table \ref{table:IAmodels} on the measurements from higher-order weak lensing statistics introduced in Sec.
+\ref{subsec:beyond-2pt}.
+We focus on the relative impact on the data vector, but this could easily be extended to compute the derivatives with respect to the different IA parameters $[A_{\rm IA}, b_{\rm TA}, C_2]$, which can then be used in Fisher forecasts or for forward-modelling the effect directly inside  a likelihood analysis  as in e.g.
+\citet{DESY1_Heydenreich, KiDS1000_Burger, KiDS1000_JHD}.
+This method assumes that the data vector can be Taylor expanded to first order about the systematic parameters
+\begin{eqnarray}
+f(A_{\rm IA},b_{\rm TA},C_2) = f({\rm no-IA}) +  \sum_p \frac{{\rm d}f}{{\rm d}p}\times p \, ,
+\end{eqnarray}
+with $ p=[A_{\rm IA}, b_{\rm TA}, C_2]$ and $f$ any weak lensing statistics.
+This is of course  neglecting higher-order correlations between parameters, or variations with cosmology, but that is often a good approximation.
+
+Fig.
+\ref{fig:Map3_IA} shows the results for the $M_{\rm ap}^3$  and lensing PDF  statistics, where we can see that the impact is the largest at low redshift.
+Specifically, the different models do not impact the probes at the same level.
+For instance, ...

### 2024-06-21 tables/ia_models.tex
Lots of changes

@@
    %\topcaption{Table captions are better up top} % requires the topcapt package
-    \caption{IA models infused in this work and the respective fiducial values of the model parameters.}
+    \caption{IA models infused in this work, along with the respective values of the model parameters.
+The two HOD models, at the bottom of the table, follow a non-linear galaxy biasing, which we label here as $b_{\rm nl}$ and is partly fitted by the $b_{\rm TA}$ parameter in the MCMC, see Sec.
+\ref{sec:inference} for details.
+}
    \begin{tabular}{@{} lcr @{}} % Column formatting, @{} suppresses leading/trailing space
@@
        %\multicolumn{2}{c}{Item} \\
-      model   		& ($A_{\rm IA}, \: b_{\rm TA}, \: A_2)$ \\
+      model   		& ($A_{\rm IA}, \: b_{\rm TA}, \: C_2)$ \\
       \hline
-      NLA     		& {($\pm$1, 0, 0) }&  \\
-      \multirow{2}{*}{extended-NLA }  	&   {($\pm$1, 1, 0)}   \\
+      NLA     		& {(1, 0, 0) }&  \\
+      \multirow{2}{*}{extended-NLA }  	&   {(1, 1, 0)}   \\
       							&  {(1, 2, 0)}   \\
-      TT 			&  {(0, 0, $\pm$1)} &  \\
-      \multirow{2}{*}{extended-TT} 	&  {(0, 1 ,$\pm$1)}   \\
+      TT 			&  {(0, 0, 1)} &  \\
+      \multirow{2}{*}{extended-TT} 	&  {(0, 1 ,1)}   \\
       				&  {(0, 2, 1)}   \\
-      TATT- fiducial	&  { (1, 1, 1)}  \\
+				HOD-NLA & {(1, $b_{\rm nl}$, 0)} \\
+				HOD-TT & {(0, $b_{\rm nl}$, 1)} \\
+      %TATT- fiducial	&  { (1, 1, 1)}  \\
       %TATT-DESY3	&   (-0.7,1,1.9) & \\

### 2024-06-21 sections/3_ia_models.tex
Updates from Overleaf

--- 2024-04-30 sections/3_ia_models.tex
@@
 \end{eqnarray}
-This has imitations in tits accuracy, but we will show later that it can nevertheless be applied to modify existing $\delta$-NLA mock data and yields good approximate solutions.
+This has limitations in its accuracy, but we will show later that it can nevertheless be applied to modify existing $\delta$-NLA mock data and yields good approximate solutions.
 

### 2024-06-21 sections/5_validation.tex
Updates from Overleaf

--- 2024-03-27 sections/5_validation.tex
@@
 \caption{Cosmological inference from the NLA-infused simulations, analysed the extended-NLA model. 
-The cross-hairs represent the truth as fixed in the {\it Outer Rim} $N$-body simulations \citep{OuterRim}.}
+The cross-hairs represent the truth as fixed in the {\it Outer Rim} $N$-body simulations \citep{OuterRim}.
+\niko{we should remove this fig, it is now irrelevant.
+or i can redo it with the new scale cuts}}
 \label{fig:triangle_nla}
@@
 \caption{Cosmological inference from the TT-infused simulations, with all 3 IA params varied.
-The cross-hairs represent the truth as fixed in the {\it Outer Rim} $N$-body simulations \citep{OuterRim}.}
+The cross-hairs represent the truth as fixed in the {\it Outer Rim} $N$-body simulations \citep{OuterRim}.\niko{we should remove this fig, it is now irrelevant.
+or i can redo it with the new scale cuts}}
 \label{fig:triangle_tt_all_ia_params}

### 2024-06-21 sections/2_cosmic_shear_stats.tex

--- 2024-04-30 sections/2_cosmic_shear_stats.tex
@@
 This global $n(z)$ is further split into five equi-populated tomographic bins, and smoothed with a Gaussian filter of width $\sigma = 0.05 \: (1 + z)$ to mimic the photometric selection process, shown by the solid lines in Fig.
-\ref{fig:Nz}.
+\ref{fig:Nz}\footnote{The LSST SRD-Y1 forecasted redshift distribution can be generated here: github.com/LSSTDESC/CCLX/blob/master/srd\_redshift\_distributions.py}.
 
@@
     Although some theoretical models have been developed to describe the largest peaks \citep[see][]{Shan18, HSCY1_Peaks_th}, we report here the results on a much wider range of statistics, which can only be accurately modelled from numerical simulations themselves.
-    \item \textit{Lensing PDF}:  \JHD{Cora/Lina, can you summarise the measurements and modelling, and provide references?}
+    \item \textit{Lensing PDF}:  \JHD{Cora/Lina, can you summarise the measurements and modelling, and provide references? Cite \citet{LensingPDF}}
    % \item  \textit{Minkowski functionals}: \JHD{Nisha, can you summarise the measurements and modelling, and provide references?}

### 2024-06-21 sections/4_simulations.tex

@@
 We assume $b_{\rm TA}=1.0$ as our fiducial case but also consider $b_{\rm TA}=2.0$ to test  the  model flexibility. 
-\item{\it Non-linear bias:} galaxy positions are obtained by populating dark matter haloes with the Halo Occupation Distribution prescription described in \citet{cosmoDC2}. 
+\item{\it Non-linear bias:} galaxy positions are obtained by populating dark matter haloes with the Halo Occupation Distribution prescription described in \citet{cosmoDC2} and used recently in \citet{TXPipe}\footnote{We used version: {\tt skysim5000\_v1.2}.}.
+Specifically, we select objects over a patch of 732.20 deg$^2$ given by  0$<$RA$<$ 20 and -36.61$<$DEC$<$0, we apply a magnitude cut of mag$_r<$24.8, and further downsample randomly to retain 20\% of the galaxies, approaching the global galaxy redshift distribution and number density used with the other simulation catalogues (Eq.
+\ref{eq:nz}).
+The sample is further split into 5 tomographic bins by calculating the probability a given galaxy in the HOD sample lies in each bin, based on its true redshift.
+This is simply done by interpolating each of the tomographic $N(z)$ shown in Fig.
+1 at the galaxy?s true redshift, then using these as weights to assign a tomographic bin in a random draw.
+After a galaxy is assigned, it is removed from the sample to avoid double counting.
+This method allows us to capture some of the effect of photo-z uncertainty, as it gives all galaxies a small but non-zero probability of being included in tomographic bins outside of their true redshifts.
+The resulting in the $n(z)$ presented in Fig.
+\ref{fig:Nz} with the dashed lines, closely matching the target $n(z)$.
+Compared to the analytical SRD-Y1, the mean redshifts of the five tomographic bins are shifted by [-0.027, -0.018,  0.003, -0.010,  0.038], respectively, which we take into account when making predictions for these HOD lensing mocks.
 \end{enumerate}
-Note that while cases (i) and (ii) exactly reproduce the SRD-Y1 $N(z)$ presented in Fig.
+%Note that while cases (i) and (ii) exactly reproduce the SRD-Y1 $N(z)$ presented in Fig.
 \ref{fig:Nz} (solid lines), the $N(z)$ in the latter case is not a perfect match, as shown with the dashed lines, although the agreement is good enough for our goal; we return to this in Sec.
@@
 
-\begin{figure*}
-\caption{Density field and the associated projected tidal field tensors.}
+\begin{figure}
+\includegraphics[width=\columnwidth]{graphs/TidalFieldOuterRim_V0}
+\caption{Density field (top)  and the associated projected tidal field tensors $s_{11}$, $s_{22}$ and $s_{12}$, from left to right ({\it Improve this figure...}).}
 \label{fig:maps}
-\end{figure*}
+\end{figure}
 
@@
 We find that tidal field computed directly from the $10\times10$ deg$^2$ light-cones introduces significant large scales features in the tidal field maps, largely caused by  the non-periodic boundary conditions, which our method avoids.
-Projected tidal field maps $s_{11}$, $s_{22}$, and $s_{12}$ are constructed that way for each mass sheets; Fig. \ref{fig:maps} shows the  three tidal fields and the mass maps for one of them.
-We can clearly see the connection between all maps around over-dense regions. {\it (Include a figure of $s_{ij}$ and $\delta$)}.
+Projected tidal field maps $s_{11}$, $s_{22}$, and $s_{12}$ are constructed that way for each mass sheets; Fig.
+\ref{fig:maps} shows the  three tidal fields and the underlying density maps for one of them.
+We can clearly see the connection between all maps around over-dense regions. .
 

### 2024-06-21 tables/priors.tex

\begin{table}
   \centering
   \caption{Priors used in the likelihood sampling. {\it (verify these numbers with Niko)}}
   \tabcolsep=0.11cm
      \begin{tabular}{@{} cccccccc @{}} % Column formatting, @{} suppresses leading/trailing space
      \hline
      \hline
       Parameter       &  range & prior \\
       \hline
       Cosmology\\ 
       $\Omega_{\rm m}$ &[0.1, 0.55] & Flat\\
       $S_8$ & [0.6, 0.9] & Flat\\
       \hline
       IA\\
       $A_{\rm IA}$ & [-5, 5]&  Flat\\                    
        $b_{\rm TA}$ & [0, 2] & Flat\\
        $C_2$ & [-5, 5] & Flat\\
     \hline
    \hline 
    \end{tabular}
    \label{table:priors}
\end{table}

### 2024-06-21 sections/1_introduction.tex

@@
 \eg][]{KiDS1000_Asgari, KiDS1000_vdB, KiDS1000_Li, DESY3_Secco, DESY3_Amon, HSCY3_Cl, HSCY3_2pcf}, achieving  percent-level measurements of the structure growth parameter $S_8\equiv\sigma_8\sqrt{\Omega_{\rm m}/0.3}$.
-The parameters $\Omega_{\rm m}$ and $\sigma_8$, which respectively describe the abundance and the amplitude of the fluctuations in the matter density fluctuations on scales of $8h^{-1}$ Mpc, are highly degenerate in the lensing signal, and additional data (\eg galaxy clustering data) are required to measure the two individually from photometric galaxy surveys \citep{KiDS1000_Heymans, DESY3_3x2, HSCY3_3x2}.
+The parameters $\Omega_{\rm m}$ and $\sigma_8$, which respectively describe the abundance and the amplitude of the fluctuations in the matter density fluctuations on scales of $8 \: h^{-1}$ Mpc, are highly degenerate in the lensing signal, and additional data (\eg galaxy clustering data) are required to measure the two individually from photometric galaxy surveys \citep{KiDS1000_Heymans, DESY3_3x2, HSCY3_3x2}.
 Despite these successful achievements, the current precision of cosmic shear cosmology is mainly limited by the large uncertainty in the intrinsic alignment (IA) of galaxies, a secondary signal that tends to cancel some of the shape correlations produced by lensing \citep[see.
